### 2021-10-08 mnras_template.tex
Initial Overleaf Import

% mnras_template.tex 
%
% LaTeX template for creating an MNRAS paper
%
% v3.0 released 14 May 2015
% (version numbers match those of mnras.cls)
%
% Copyright (C) Royal Astronomical Society 2015
% Authors:
% Keith T. Smith (Royal Astronomical Society)

% Change log
%
% v3.0 May 2015
%    Renamed to match the new package name
%    Version number matches mnras.cls
%    A few minor tweaks to wording
% v1.0 September 2013
%    Beta testing only - never publicly released
%    First version: a simple (ish) template for creating an MNRAS paper

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Basic setup. Most papers should leave these options alone.
\documentclass[fleqn,usenatbib]{mnras}

% MNRAS is set in Times font. If you don't have this installed (most LaTeX
% installations will be fine) or prefer the old Computer Modern fonts, comment
% out the following line
\usepackage{newtxtext,newtxmath}
% Depending on your LaTeX fonts installation, you might get better results with one of these:
%\usepackage{mathptmx}
%\usepackage{txfonts}

% Use vector fonts, so it zooms properly in on-screen viewing software
% Don't change these lines unless you know what you are doing
\usepackage[T1]{fontenc}

% Allow "Thomas van Noord" and "Simon de Laguarde" and alike to be sorted by "N" and "L" etc. in the bibliography.
% Write the name in the bibliography as "\VAN{Noord}{Van}{van} Noord, Thomas"
\DeclareRobustCommand{\VAN}[3]{#2}
\let\VANthebibliography\thebibliography
\def\thebibliography{\DeclareRobustCommand{\VAN}[3]{##3}\VANthebibliography}

%%%%% AUTHORS - PLACE YOUR OWN PACKAGES HERE %%%%%
\usepackage{indentfirst}
\usepackage{physics}
\usepackage{lineno}
\linenumbers
% Only include extra packages if you really need them. Common packages are:
\usepackage{graphicx}	% Including figure files
\usepackage{amsmath}	% Advanced maths commands
\usepackage{amssymb}	% Extra maths symbols
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%% AUTHORS - PLACE YOUR OWN COMMANDS HERE %%%%%

% Please keep new commands to a minimum, and use \newcommand not \def to avoid
% overwriting existing commands. Example:
%\newcommand{\pcm}{\,cm$^{-2}$}	% per cm-squared

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%% TITLE PAGE %%%%%%%%%%%%%%%%%%%

% Title of the paper, and the short title which is used in the headers.
% Keep the title short and informative.
\title[Metacalibration with Roman High-Latitude Imaging Survey]{Weak gravitational lensing shear estimates with \textsc{metacalibration} for the High-Latitude Imaging Survey Program of the \emph{Roman} Space Telescope}

% The list of authors, and the short list which is used in the headers.
% If you need two or more lines of authors, add an extra line using \newauthor
\author[M. Yamamoto et al.]{
Masaya Yamamoto,$^{1}$\thanks{E-mail: masaya.yamamoto@duke.edu}
Michael A. Troxel,$^{1}$
Mike Jarvis,$^{2}$
Rachel Mandelbaum,$^{3}$
Christopher Hirata$^{4,5,6}$
\\
% List of institutions
$^{1}$Department of Physics, Duke University, Durham, NC, 27710\\
$^{2}$Department of Physics and Astronomy, University of Pennsylvania, Philadelphia, PA 19104, USA\\
$^{3}$McWilliams Center for Cosmology, Department of Physics, Carnegie Mellon University, Pittsburgh, Pennsylvania 15213, USA\\
$^{4}$Center for Cosmology and Astro-Particle Physics, The Ohio State University, 191 West Woodruff Avenue, Columbus, OH 43210, USA\\
$^{5}$Department of Physics, The Ohio State University, 191 West Woodruff Avenue, Columbus, OH 43210, USA\\
$^{6}$Department of Astronomy, The Ohio State University, 140 West 18th Avenue, Columbus, OH 43210, USA\\
}

% These dates will be filled out by the publisher
\date{Accepted XXX. Received YYY; in original form ZZZ}

% Enter the current year, for the copyright statements etc.
\pubyear{2015}

% Don't change these lines
\begin{document}
\label{firstpage}
\pagerange{\pageref{firstpage}--\pageref{lastpage}}
\maketitle

% Abstract of the paper
\begin{abstract}
We investigate the performance of the \textsc{metacalibration} scheme in the framework of the \emph{Nancy Grace Roman} Space Telescope (\emph{Roman}) image simulations. By comparing non-calibrated results from the previous work, shear calibration bias can be reduced significantly with \textsc{metacalibration}. Exploring shear bias is a robust way to test the requirements of the instrument and the overall weak lensing survey strategy. The weak lensing program of \emph{Roman} mission requires the galaxy shapes to be calibrated within about 0.03\%. To reach this goal, we can test our calibration scheme with these simulations and can isolate the sources where these residual shear biases come from, (whether it is the algorithm or detector physics). We incorporate several new updates that are more realistic and necessary to calibrate shear with a better precision relative to the previous version of the simulations. Without the coadditions of the single epoch images, across all three filters we are able to achieve the multiplicative bias of 0.70 per cent within 1.8 $\sigma$ with the current simulation volume. Meanwhile, average additive bias is not consistent with zero due to the strong correlation with the input PSF for one of the spin-2 component directions but consistent with zero for the other direction. This is worse for coadded images. We find no evidence that shape calibration becomes worse with decreasing image sampling factor based on the Nyquist sampling theorem. Overall, within the current simulation volume, we find that \textsc{metacalibration} can calibrate shapes with zero systematics on relatively undersampled images that \emph{Roman} will produce. In the future, we will need to substantially increase the simulation volume by 8 to reach the accuracy necessary for the program. 
\end{abstract}

% Select between one and six entries from the list of approved keywords.
% Don't make up new ones.
\begin{keywords}
gravitational lensing: weak -- cosmology: observations -- techniques: image processing
\end{keywords}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%% BODY OF PAPER %%%%%%%%%%%%%%%%%%

\section{Introduction}

Since the formulation of the physical cosmological model, more observational evidence has shown that the contents of the universe are mostly in the dark sector (\citealt{2020A&A...633A..69H, 2018PhRvD..98d3528T, 2019PhRvL.122q1301A, 2019PASJ...71...43H, 2021A&A...645A.104A}). Within the dark sector, dark energy accounts for the accelerating expansion of the universe (e.g., \citealt{1998AJ....116.1009R, 1999AIPC..478..129P}) and the combination of dark energy and dark matter which only interacts with the same kind are responsible for the growth of the large-scale structure (\citealt{2015RPPh...78h6901K, 2017grle.book.....D}). The growth can be studied by carefully reconstructing the paths of the light leaving distant galaxies and going through the region where masses concentrate in the universe; this physical phenomenon is called gravitational lensing. “Weak” gravitational lensing causes a slight distortion to intrinsic galaxy shapes, and measuring the distorted shapes describes the gravitational shear field the light passes through. By using millions of these gravitationally lensed galaxies we can explore the matter density and the amplitude of matter fluctuation in the universe (e.g., \citealt{2001PhR...340..291B}). Measuring these quantities eventually help us learn the history of the development of the structure. For that reason, weak lensing is and will continue to be one of the key probes in the current and next-decade imaging surveys to constrain cosmological parameters with high precision. \par

Due to the subtlety in the lensing effect and its systematics dominant nature in the “weak” regime, observational efforts have been challenging. Over the past decade, large international collaborations such as the Dark Energy Survey\footnote{\url{http://www.darkenergysurvey.org/}} (DES: \citealt{2005astro.ph.10346T}), the Hyper Supreme-Cam\footnote{\url{http://hsc.mtk.nao.ac.jp/ssp/}} (HSC: \citealt{2018PASJ...70S...4A}), and the Kilo-Degree Survey\footnote{\url{http://kids.strw.leidenuniv.nl/}} (KiDS) have been successful at constraining the cosmological parameters, and the precision in calibrating the shapes of distant galaxies has reached a few percent (\citealt{2020arXiv201103408G, 2020arXiv201208567M, 2021A&A...645A.105G}) (include most recent HSC catalog). As we cover more areas in the sky and develop better tools (observatories and algorithms), we find more galaxies and we have already reached to the point where statistical and systematic uncertainties are comparable. Thus, the next-decade legacy surveys, the Stage IV surveys (\citealt{2006astro.ph..9591A}) such as Euclid\footnote{\url{ http://sci.esa.int/euclid}} (Euclid Study Scientist & the Science Advisory Team 2010), the Vera C. Rubin Observatory Legacy Survey of Space and Time\footnote{\url{ http://www.lsst.org}} (LSST: \citealt{2009arXiv0912.0201L, 2019ApJ...873..111I}), and \emph{Nancy Grace Roman} Space Telescope\footnote{\url{https://roman.gsfc.nasa.gov}} (\emph{Roman}: \citealt{2015arXiv150303757S}) require even better control of systematics. In order to manage the systematic uncertainties, we must develop realistic image simulations, apply the shape measurement on the simulated images, and determine any potential systematic effects and the strategy of mitigating them.

Based on our current knowledge, systematic biases for weak lensing science, both observational and astrophysical, could occur throughout imaging surveys (\citealt{2018ARA&A..56..393M}). Particularly, observational systematics can be found in, 
\begin{itemize}
    \item observing strategy
    \item instrumentation effects such as Brighter-Fatter Effect
    \item post-processing pipeline such as image coaddition and object detection
    \item cosmological inference 
\end{itemize}

In this study, we focus on shear calibration bias, which describes the relationship between gravitational lensing shear and measured galaxy shapes. In the limit of weak lensing ($\lvert\gamma\rvert\ll1$), the ensemble average of ellipticities $\langle e \rangle$ of galaxy shapes is directly related to the shear field $\gamma$, and the estimated shear can be written as a linear model with multiplicative ($m_{i}$) and additive bias ($c_{i}$) as described in the equation below. (\citealt{2006MNRAS.368.1323H, 2006MNRAS.366..101H, 2007MNRAS.376...13M}) 
\begin{equation}
    \gamma^{obs}_{i} = (1+m_{i})\gamma^{true}_{i} + c_{i}, 
    \label{eqn:linear}
\end{equation}
where i=(1,2) and $\gamma^{obs}_{i}$ is the two-component observed shear after calibrations and $\gamma^{true}_{i}$ is the true shear. This shear bias arises for various reasons. For space-based surveys, it can be mainly introduced in places such as PSF modelling, blending, and the undersampling of the image (e.g., \citealt{2018ARA&A..56..393M}). Additionally, complex detector effects such as brighter-fatter effect are the potential sources of bias (\citealt{2013MNRAS.429..661M}), where it is shown that for \emph{Roman} the effect of persistence will not be an issue (\citealt{2021arXiv210610273L}). Qualitatively, if the recovered shear is biased by 1$\%$ (m=1$\%$), $S_{8} = \sigma_{8} \sqrt{\Omega_{m}/0.3}$ would be biased about 1.5$\%$ in the final cosmology result. Thus, quantifying this shear bias before the survey is extremely important. \par

Several shear calibration and bias mitigation efforts have been proposed by STEP (\citealt{2006MNRAS.368.1323H, 2007MNRAS.376...13M}) and GREAT (\citealt{2010MNRAS.405.2044B, 2013ApJS..205...12K, 2015MNRAS.450.2963M}) challenges, to meet the requirements for the current imaging surveys. In particular, one of the state-of-the-art self-calibration methods, \textsc{metacalibration} (\citealt{2017arXiv170202600H, 2017ApJ...841...24S}) has been shown to be able to reduce the significant of shear bias. It has also confirmed that the shear can be calibrated with \textsc{metacalibration} at a-few-percent level in DES (\citealt{2018MNRAS.481.1149Z, 2020arXiv201103408G}), without accounting for galaxy blending. Tackling the issue of blending is on the way of Y6 DES analysis with the shear-dependent detection and calibration technique (\textsc{metadetect}; \citealt{2020ApJ...902..138S}). While the major advantage of \textsc{metacalibration} is that it can be directly applied upon real galaxy images, which does not depend on galaxy morphology in simulations, the limitations for future surveys are not well-known. One possible limitation might lie in the effect of the undersampled images, because future space-based surveys like \emph{Euclid} and \emph{Roman} have such a small pixel scale that galaxy images will not be Nyquist sampled at native resolution (\citealt{2013PASP..125.1496S}) based on the Nyquist-Shannon Sampling Theorem. We define the sampling factor of each filter in \emph{Roman} to be, 
\begin{equation}
    Q = \frac{\lambda_{min}N_{f}}{p}, 
    \label{eqn:sampling}
\end{equation}
where $\lambda_{min}$ is the shortest wavelength of the incident light of the filter, $N_{f}$ is the focal ratio of the telescope ($N_{f}=7.8$ for \emph{Roman}) and $p$ is the pixel spacing of the sensor ($p=10\mu m$ for \emph{Roman}). The image with the sampling factor, $Q < 2$, is not Nyquist sampled and reffered to as the undersampled image. It is problematic to measure galaxy shapes solely from the undersampled images, because the \emph{Roman} PSF that will be used to recover the shapes is also undersampled and has a complex structure, not simply Gaussian. It is, therefore, necessary to build a robust strategy that can reconstruct better sampled PSF to allow unbiased shape measurement.

Recently, Kannawadi et al. (2021) addressed this potential issue of the limitations of \textsc{metacalibration} on undersampled images on \emph{Euclid} image simulations and found that for \emph{Euclid} mission the shear estimate is biased about 1$\%$ (\citealt{2021MNRAS.502.4048K}). They mentioned that his result could be extended to the \emph{Roman} mission due to their similarities in the instruments and for \emph{Roman} they predicted the multiplicative bias was more than 1\% for H158 and F184 filters. Regardless of this extended result, we should validate if \textsc{metacalibration} is non-biased with the image simulations specifically made for the \emph{Roman} mission. Our work is based on the image simulation suite of the \emph{Roman} Space Telescope developed by \citet{2021MNRAS.501.2044T}, where we render star and galaxy images from \texttt{GalSim}\footnote{\url{ https://github.com/GalSim-developers/GalSim}} (\citealt{2015A&C....10..121R}). With a few simulation updates and an implementation of \textsc{metacalibration}, we can start to explore if the shear calibration goal of the High-Latitude Survey program for Roman ($m=~3.2\times10^{-4}$) (\citealt{2019BAAS...51c.341D}) can be achieved. \par

This paper is organized as follows. We briefly discuss the simulation suite details we used and the updates we implemented for this project in Sec.~\ref{sec:sims}. Then, in Sec.~\ref{sec:methods}, we show how coadditions of single exposure postage stamps are produced and how shape measurements are completed using \textsc{metacalibration}. We present the galaxy catalog properties and calibration results for single-band and multiband measurements in Sec.~\ref{sec:results}. Finally, in Sec.~\ref{sec:discussion}, we discuss how we will be able to constrain the shear bias better in terms of further updates in the image simulations and what we can conclude from this study.

\section{Simulations}
\label{sec:sims}
In this section, we briefly summarize the full simulation details from building a truth catalog to measuring galaxy shapes. Then we describe the simulation updates that are implemented particularly for this work.
\subsection{Simulation Summary}
\label{subsec:imsim}
The base of our image simulations of the \emph{Roman} Space Telescope is the \emph{Roman} simulation suite\footnote{\url{ https://github.com/matroxel/roman_imsim}} developed by \citet{2021MNRAS.501.2044T}, which renders realistic galaxy and star images on 18 Sensor-Chip Assemblies (SCAs) of a 2.5$\times$2.5 deg$^{2}$ patch of the sky provided the observing strategy for the 5-year reference mission and Cycle7 specifications\footnote{\url{https://roman.gsfc.nasa.gov/science/Roman_Reference_Information.html}}. We begin by creating a truth catalog using the simulated galaxy distribution from the Buzzard simulation (\citealt{2019arXiv190102401D}), photometric galaxy catalog sampled from the CANDELS survey (e.g., \citealt{2019ApJ...877..117H}), and Milky Way simulation (Galaxia; \citealt{2011ApJ...730....3S}) for star positions and magnitudes. Then, the following properties are applied to each galaxy.
\begin{itemize}
    \item positions (RA, Dec)
    \item photometries for each \emph{Roman} filter (F184/H158/J129/Y106)
    \item intrinsic galaxy shapes and random orientations
    \item flux ratios of de Vaucouleurs bulge, exponential disk, and star-forming knots
    \item artificial gravitational lensing shears
\end{itemize} 
Within the identical realizations of the simulation, we produce four truth catalogs using four sets of gravitational shears ($e_{1}$, $e_{2}$)=\{(+0.02, 0.00), (-0.02, 0.00), (0.00, +0.02), (0.00, -0.02)\}. This approach helps us to reduce shape and measurement noise when taking the difference in recovered shapes to compute multiplicative bias (\citealt{2019A&A...621A...2P}).

The next step of the process is to create postage stamps and SCA images using \texttt{GalSim}. In this stage, Point-Spread Function (PSF) is convolved with the stamps. Here, the \emph{Roman} PSF is rendered using the \texttt{galsim.roman} module under \texttt{GalSim}, which has implemented \emph{Roman}-specific instrument properties such as the PSF and World Coordinate System (WCS). The module is able to estimate an object position on the sky in RA, Dec using the \emph{Roman} WCS and produce the \emph{Roman} PSF which, for example, correctly describes the diffraction spikes pattern made by the struts and camera in the pupil plane.

After we generate the object stamps across all the SCAs and pointings, we create Multi-Epoch Data Structure (MEDS) files in which each unique object dictionary contains information of all the exposures. These MEDS files are generated according to the Hierarchical Equal Area isoLatitude Pixelisation (HEALPix) of $n_{side}=512$. These MEDS files contain all objects that are located in the area of the sky partitioned according to a HEALPix of $n_{side}$=512. Once the objects are sorted in MEDS files, we pass them and the corresponding PSF for the SCA to a shape measurement. We pass these multiple exposures with corresponding PSFs to \textsc{ngmix}\footnote{\url{ https://github.com/esheldon/ngmix}} to fit the galaxy shapes with the Gaussian mixture fitting method (\citealt{2014MNRAS.444L..25S}). This shape measurement process produces shape catalogs from which the shear calibration bias can be calculated with \textsc{metacalibration}.

\begin{figure}
	\includegraphics[width=\columnwidth]{figure1.pdf}
	\vspace*{-3mm}
    \caption{The rotation of the Roman PSF produced from the \texttt{galsim.roman} module. Position angle (PA) which determines the rotation of the telescope is $0^{\circ}$ and $30^{\circ}$. The rotation of the PSF is particularly important when an object has multiple exposures and needs to be coadded. If each galaxy image is rotated but each PSF is not, the coadded PSF would have a particular pattern and its shape would not be averaged down. By correctly rotating the PSF that is convolved with galaxy images, the effect of the PSF on the recoverd galaxy shape will be less.}
    \label{fig:psfrot}
\end{figure}

\begin{figure*}
	\includegraphics[width=\textwidth]{figure2.pdf}
	\vspace*{-10mm}
    \caption{The top row shows the first entry of the single epoch images and its coadded image, single and coadded oversampled PSF for an object with low signal-to-noise ratio (S/N=9.69). The bottom row shows the same for an object with high signal-to-noise ratio (S/N=1552.97).}
    \label{fig:singlecoadd}
\end{figure*}

\subsection{Simulation Updates}
In order to accomplish science goals, and build and test the pipelines of weak lensing program in \emph{Roman}, we must keep updating the simulations to be more realistic. Along the way to test calibrating shears using \textsc{metacalibration}, we have implemented and made updates to the following parts of the simulation framework. 
\begin{itemize}
    \setlength\itemsep{1em}
    \item \textbf{Saturation Cuts}:
    We have implemented the pixel saturation of 100,000 electrons. This value is an approximate pixel saturation but in the next generation of the simulations we will use the true saturation from the flight candidate detectors. 
    \item \textbf{Rotation of the \emph{Roman} PSF on the sky}:
    In the study by Troxel et al. (2021), the rotations of the \emph{Roman} PSF with respect to the telescope rotation were not engaged properly by \texttt{galsim.roman} module. Since a non-rotating PSF could trigger a preferred direction in the shapes when being deconvolved, we believe that this contributed to the non-zero multiplicative bias. There has been an update in \texttt{galsim.roman} module to correctly rotate the PSF given the WCS on the SCA. Figure \ref{fig:psfrot} shows a toy PSF of the same pointing but with a different rotation angle of the telescope. 
    \item \textbf{Single-band and multiband Coadds}: 
    We have added and modified the postage stamp coadds (\texttt{psc}) algorithm\footnote{\url{https://github.com/esheldon/psc}} to create coadditions of single-epoch postage stamps. Coadds are usually performed to enhance the signal-to-noise ratio (S/N) of an object and mitigate the potential systematics for an accurate shape measurement. If we take advantage of fitting an object in the coadd instead of fitting multiple images of each object in each filter, we can save a factor of 6 in computing time, which is the average number of exposures from the reference survey. Additionally, coadding is one way to reduce the effect of the undersampling of the images since by coadding multiple exposures the product is naturally better sampled. Thus, for these reasons, we must utilize a coadding scheme for the \emph{Roman} galaxies. We can turn this on and off so that the effect of undersampling is clear. The detailed overview of the coadd process in \texttt{psc} is in Sec. \ref{subsec:psc}. 
    \item \textbf{\textsc{metacalibration} implementation}: We used \textsc{metacalibration}\footnote{\url{https://github.com/esheldon/ngmix/wiki/Metacalibration}} bootstrapper method, which is a wrapper class to run measurements in the \textsc{ngmix} package and is used extensively to produce weak lensing shape catalog in DES Y3 analysis. \textsc{metacalibration} process takes place after making coadded images, if applicable for the coadd measurements. With this calibration method, we hope to significantly reduce some of the shear calibration bias Troxel et al. (2021) measured. The detailed overview of \textsc{metacalibration} can be found in Sec.\ref{subsec:mcal}. 
    %\item (Any other changes?)
\end{itemize}

%\subsection{Simple Simulations}
%\label{subsec:simplesim}
%The purpose of the simple simulations is to verify that there are no systematic biases at the basic levels of the simulation (e.g., no complex detector effects). The simple simulation is based on the real observational pointing strategy, and we use the real Sensor-Array Chips (SCAs) scheme, the band filters and the pixel scale as basic Roman specifications.

\section{Post-catalog Processes}
\label{sec:methods}
Our goal is to show that the recovered shapes with \textsc{metacalibration} are non-biased. In order to do so, we need to build a measurement pipeline within the simulation framework that contributes to the final measurement. In this section, we present in detail how coadds are produced with \texttt{psc} from the undersampled single-epoch images, how \textsc{metacalibration} calibrates shapes, and how we measure the shear calibration bias from the \textsc{metacalibration} catalog.

\subsection{Postage Stamp Coadds}
\label{subsec:psc}
Coaddition is the process that reconstructs a Nyquist-sampled image out of multiple exposures of an object. While this process can benefit in increasing the S/N value of an object and reducing the impact of pixel noise, several challenges need to be addressed for images that are taken with equatorial mount telescopes, which can only move vertically and horizontally, and for images with telescopes that can rotate. When the rotation is introduced, this coadding process becomes more complex to interpolate the image to stack pixel grid. While coaddition could introduce systematic bias due to the complexity of the original PSF and its interpolation scheme, the undersampling of the images can be overcome. We describe our coaddition pipeline that is based on \texttt{psc}.

We reconstruct the Nyquist-sampled image from multiple exposures in MEDS files. For the coaddition of the PSF, we choose to coadd the image with the oversampled PSF over the undersampled original PSF. We oversample the original PSF by a factor of 4 to simulate the better sampled PSF that \emph{Roman} will eventually produce when it constructs the PSF from the full focal plane. It will be highly resolved than native pixel scale. For each exposure of the object we render the \emph{Roman} PSF with a stamp size of 32 pixels at the galaxy centroid. We modified the original code to improve performance of our algorithm, and these modifications are listed below with the general coadding process in \texttt{psc}.

The algorithm: 
\begin{enumerate}
    \setlength\itemsep{1em}
    \item Finds the wcs of the first exposure of the object.
    \item Translates the original wcs to a flat wcs, because it produces stable results with \textsc{ngmix}.
    \item Creates the coadd stamp with 0.8 $\times$ original pixel scale. We scale the original pixel scale of the final coadd stamp to minimize the effect of undersampling. We noticed that too much oversampling can introduce the artifacts into the structure of the PSF. 
    \item Creates the interpolated image with \texttt{GalSim} with the center offset for each image with \texttt{lanczos3} resampling method. Out of several interpolation methods we tried, \texttt{lanczos3} produced the best coadd of the PSF.
    \item Recreates the coadded noise image from the weight of the original weight map.
\end{enumerate}

Figure \ref{fig:singlecoadd} shows an example of the simulated single-epoch and coadded images and PSFs for objects with low and high S/N. Note that the shape and struts pattern in the original PSF can be washed out by coadding the rotationally dithered PSFs.

Before we calibrate and measure shapes with \textsc{ngmix}, we downsample the high-resolution PSF to the original pixel size. Figure \ref{fig:coadd_oversample_res} shows the coadded oversampled PSF and the then-downsampled PSF, and their differences. We downsampled the oversampled PSF (128 x 128 pixels) by summing 4 square-pixels and creating the original size PSF (32 x 32 pixels), in order to ensure that the shape fit with \textsc{ngmix} can be processed. Since a better sampled PSF generally enables the shape of the PSF to be more isotropic, from the difference image in Figure \ref{fig:coadd_oversample_res}, we can state that the original PSF has an anisotropic shape, which can lead to biased shape measurement.

\begin{figure}
	\includegraphics[width=\columnwidth]{figure3.pdf}
    \vspace*{-5mm}
    \caption{The left and middle panel of the figure illustrates the coadded \emph{Roman} PSF at its native pixel scale and the coadded PSF with a pixel scale that is smaller by a factor of 4. These are visualized in a log scale. The right panel shows the difference image between the two PSFs. }
    \label{fig:coadd_oversample_res}
\end{figure}

Finally, Figure \ref{fig:single_to_coadd_rgb} shows the coadd products in different bandpasses for a relatively high S/N object. It is worth noting that the multiband PSF is the oversampled version for a visualization purpose.

\begin{figure*}
	\includegraphics[width=\textwidth]{figure4_og.pdf}
    \vspace*{-20mm}
    \caption{The left 3 panels show an example of the coadded galaxy images for each filter. The S/N for each filter is S/N=2292, 1558, 1336. The 4th and 5th panels show the multiband coadd images of the same object; each with xxx scale and RGB scale. The S/N of the image is S/N=1755. Finally, the right-most panel shows the coadded oversampled PSF with the original scale.}
    \label{fig:single_to_coadd_rgb}
\end{figure*}

\par

\subsection{Shape measurement with \textsc{metacalibration}}
\label{subsec:mcal}
Once we construct the coadds from the galaxy catalogs to recover the shear signal, we feed them into the \textsc{metacalibration} process. The bootstrapper method in \textsc{ngmix} wraps the \textsc{metacalibration} and the shape fit steps. The priors passed to the fit are listed below.

\begin{table}
    \centering
    \begin{tabular}{|p{3cm}||p{3cm}|p{3cm}|p{3cm}|}
    \hline
    Prior & Value \\
    \hline
    Pixel centroid offset & 0 < $p_{x,y}$ < 0.11\\
    Shear & $|g|=1.0$, $\sigma_{|g|} = 0.3$\\
    Half-light radius & $10^{-5}$ < T < $10^{4}$\\
    Flux fraction of the bulge component & $\langle f\rangle = 0.5$, $\sigma_{f} = 0.1$\\
    Total flux & $0$ < F < $10^{6}$\\
    \hline
    \end{tabular}
    \caption{List of prior values used for the Gaussian mixture fit.}
    \label{tab:priors}
\end{table}

Once we have the \textsc{metacalibration} catalog, we can calculate shear calibration bias from the measured object ellipticities, \vb*{e} = ($e_{1}$, $e_{2}$). The observed ellipticities can be approximated using a Taylor expansion around the two-component shear, $\vb*{\gamma}=0$. Higher terms here can be dropped assuming the gravitational shear is small. It is also known that \textsc{metacalibration} works under the same assumption, otherwise the recovered shear would be biased. It is challenging to find a good input shear that results in higher S/N of an object and unbiased shape measurement. We verify that our input gravitational shear is unbiased in \textsc{metacalibration} framework and the uncertainty in the recovered shape is small enough by constructing the same but simpler framework of the fiducial image simulations which renders Gaussian profile galaxy and PSF on the \emph{Roman} pixel scale cutout image without any detector effects. Figure \ref{fig:metacal_shear_linear} demonstrates that even with the simple enough simulations \textsc{metacalibration} becomes biased after $g=0.05$ since the assumption is starting to break down. 
\begin{equation}
    \vb*{e} = \vb*{e}\rvert_{\vb*{\gamma}=0} + \frac{\partial \vb*{e}}{\partial \vb*{\gamma}}\bigg\rvert_{\vb*{\gamma}=0}\vb*{\gamma} + \ldots
\end{equation}
From this expression, the shear response matrix can be defined as, 
\begin{equation}
    \vb*{R} \equiv \frac{\partial \vb*{e}}{\partial \vb*{\gamma}}\bigg\rvert_{\vb*{\gamma}=0} = 
    \begin{pmatrix}
        \partial e_{1}/\partial \gamma_{1} & \partial e_{2}/\partial \gamma_{1} \\ 
        \partial e_{1}/\partial \gamma_{2} & \partial e_{2}/\partial \gamma_{2}
    \end{pmatrix}. 
\end{equation}
For each redshift bin, the ensemble mean of measured ellipticities $\langle\vb*{e}\rangle$ is computed. Since we expect galaxies in the redshift bin to be randomly oriented such that $\langle\vb*{e}\rangle\rvert_{\vb*{\gamma}=0}=0$, we have a relationship between the measured ellipticities and the input shear in the simulations, 
\begin{equation}
    \langle\vb*{e}\rangle \approx \langle \vb*{R}\vb*{\gamma} \rangle. 
\end{equation} 
In actual observations, the observable is the galaxy shapes $\langle\vb*{e}\rangle$ and we can take advantage of image simulations and calculate the shear response of the particular calibration technique we employ, and finally compute the gravitational lensing shear signal $\langle\vb*{\gamma}\rangle$.

\textsc{metacalibration} creates one unsheared and four artificially-sheared images of each galaxy stamp. Each is deconvolved with the original PSF, unsheard or sheared with the gravitational shear of $\gamma=0.01$ in four directions ($+g1$, $-g1$, $+g2$, $-g2$) and re-convolved with a new slightly larger isotropic, Gaussian PSF. In our simulation framework, we know the exact input shear and five measured galaxy shapes for each galaxy produced by \textsc{metacalibration} and fitted with the Gaussian mixture method in \textsc{ngmix}. We can calculate the ensemble mean of the shear response from the five versions of \textsc{metacalibration} catalog with the equation below.

\begin{equation}
    \langle\vb*{R_{ij}}\rangle = 
    \frac{\langle e^{+}_{i} - e^{-}_{i} \rangle}{\Delta\gamma_{j}}, 
\end{equation}
where $e^{+}_{i}$ and $e^{-}_{i}$ is the $i$-th component of the galaxy ellipticity where positive ($+$) or negative ($-$) shear is applied in $i$-th direction.

Then, this shear response is used to compute the multiplicative ($\vb*{M}$) and additive ($\vb*{C}$) bias using the linear shear bias model (\ref{eqn:linear}).

\begin{equation}
    \small
    \vb*{M_{ij}} = 
    \frac{\langle e^{+}_{i}/R_{ii} \rangle - \langle e^{-}_{i}/R_{ii} \rangle}{\abs{\Delta g_{j}}} - \delta_{ij} 
    = \frac{\langle e^{obs,+}_{i}\rangle - \langle e^{obs,-}_{i}\rangle}{\abs{\Delta g_{j}}} - \delta_{ij}, 
\end{equation}

where the numerator calculates the \textsc{metacalibration} calibrated observed shear by dividing $i$-th component of the ellipticity of the unsheared \textsc{metacalibration} catalog by shear response.

\begin{equation}
    \small
    \vb*{C_{ij}} = \frac{\langle e^{obs,+}_{i} - (\delta_{ij}+M_{ij})e^{true,+}_{i})\rangle + \langle e^{obs,-}_{i} - (\delta_{ij}+M_{ij})e^{true,-}_{i}) \rangle}{2}
\end{equation}

The covariances are computed using the bootstrap estimate of standard error. From the observed ellipticity catalogs, we randomly choose $n$ samples with replacement which is the length of the data set, and compute the distributions of multiplicative ($f^{M}_{i}$) and additive ($f^{C}_{i}$) bias for $i=1,2,3,...,N$ in the same way as above. The distributions are then used to compute the error estimate,

\begin{equation}
    \sigma_{N,f} = \sqrt{\frac{1}{N-1} \sum_{i=1}^{N}(f_{i}-\bar{f_{i}})^{2}}, 
\end{equation}
where we use sample $N$=200.

\begin{figure}
	\includegraphics[width=\columnwidth]{metacal_bias_shear.png}
    \vspace*{-5mm}
    \caption{It shows the quadratic relationship between the input gravitational shear for the simple simulations and the multiplicative bias estimated from the recovered shape in the \textsc{metacalibration} catalogs. }
    \label{fig:metacal_shear_linear}
\end{figure}

\section{Results}
\label{sec:results}
In this section, we present the characteristics of the simulated data products. We divide our shape measurements into two categories; single-band and multiband. For single-band measurements, in each filter, we measure the shapes from the original single exposures by joint-fitting them. We set our base case to be this single-band joint-fit measurement. As the more developed case, we measure shapes with the single-band coadd in each filter by single-fitting it. For one multiband measurement, we match the objects, accumulate the single exposures from each filter catalog and measure the shapes with the joint-fit. The other multiband measurement joint-fit the three coadds from each filter together to recover the shape.

From the COSMOS catalog, based on the \emph{Roman} Weak Lensing mission requirements, objects are pre-selected and simulated. In total, we simulate 907,170 galaxies on 18 SCAs across 198 pointings for F184, 227 pointings for H158, and 238 pointings for J129 bandpass. We do not make any selection cuts on the simulated catalogs based on measured properties. Even so, due to the misestimation of the PSF or low S/N, the Gaussian mixture fit with \textsc{ngmix} fails about 5\% of all simulated objects, and so the total number of the recovered objects for single-band measurements is, 861,960 for F184, 863,358 for H158, and 859,645 for J129. For the multiband (H158+J129+F184) coadd measurements, we measure objects that are covered by all of the filters and the total number of the recovered objects is 851,821.
Here are the measured properties of the objects in the \textsc{metacalibration} shape catalogs.

% (galaxy and PSF properties; SNR, $e_{1,psf}$, $e_{2,psf}$, PSF FWHM) 
% havent decided on which plot to use. 
% \begin{figure}
% 	\includegraphics[width=\columnwidth]{figure5.pdf}
%     \caption{}
%     \label{fig:psf_properties}
% \end{figure}
% \begin{figure}
% 	\includegraphics[width=\columnwidth]{figure6.pdf}
%     \caption{}
%     \label{fig:other_properties}
% \end{figure}

\subsection{Shape Calibration Bias}
\label{subsec:shapes}
We compute the estimated values of multiplicative and additive bias from the recovered shear with \textsc{metacalibration}. The results from the complete set of different runs are in Table \ref{tab:bias_summary} and the summary plot can be found in Figure \ref{fig:final_result}.

For the single-band measurements, we can use the sampling factor defined in Equation \ref{eqn:sampling} to visualize the relationship between the sampling factor and the shear bias. The sampling factor is an indication of how undersampled the image in the filter is and it is respectively $Q_{J129}=1.01, Q_{H158}=1.23, Q_{F184}=1.44$. This was previously explored in \citealt{2021MNRAS.502.4048K}, where they found that the estimates shear bias has a large dependence on the sampling factor. We note that we have run \textsc{metacalibration} with \texttt{fitgauss} and \texttt{gauss} parameters for the new PSF model, and we found that it is preferrable to use \texttt{gauss} for our case. Hence, from here we present the result that is calibrated with \texttt{gauss} PSF model for \textsc{metacalibration}. The multiplicative bias of single-band single-epochs measurements for each filter is, 1.04$\pm$0.47 per cent for J129, -1.30$\pm$0.46 per cent for H158 and -0.40$\pm$0.53 per cent for F184. When the coadds of each filter are used, the bias becomes, -0.47$\pm$0.49 per cent for J129, -0.07$\pm$0.45 per cent for H158 and -0.06$\pm$0.61 per cent for F184. Coadd results are consistent with zero multiplicative bias within 1 sigma and the signals increase by xx per cent. Generally, coadding produces better sampled images as in Figure\ref{fig:single_to_coadd_rgb} and less multiplicative bias than single epochs measurements. We can conclude that in the \emph{Roman} simulation we have seen that the multiplicative bias has no strong dependence on the sampling factor.

Meanwhile the measured additive bias is the same level as the Y3 analysis in DES. The additive bias of the single-band single-epochs measurements for each filter is, (3.22$\pm$0.92)$10^{-4}$ for J129, (2.63$\pm$0.88)$10^{-4}$ for H158 and (3.25$\pm$1.11)$10^{-4}$ for F184. When the coadds of each filter are used, the bias becomes, (3.39$\pm$0.90)$10^{-4}$ for J129, (8.08$\pm$0.87)$10^{-4}$ for H158 and (9.36$\pm$1.10)$10^{-4}$ for F184. From the Table \ref{tab:bias_table}, it is worth noting that the coadd process clearly introduces non-trivial additive biases in one direction, but not the other. We believe this is due to the effect of an imperfect PSF model. We see this in the Figure xx where the recovered shear has a strong linear dependence on the PSF ellipticity measured by an adaptive moments method. The impact of the PSF leakage can be estimated by computing $\rho$-statistics (\citealt{2008A&A...484...67P, 2010MNRAS.404..350R, 2016MNRAS.460.2245J}). However, we do not explore the $\rho$-statistics for our PSF model since it is an approximation to accurately represent the features of the instrument, not computed from the real pupil plane images, and the coadding scheme for the 5-year mission has not been finalized yet.

Next, we pressent the results with multiband measurements. We performed multiband measurements with 3 filters used in the previous measurements. One multiband measurement used all of the single epoch images from all the filters and joint-fit the shape of the galaxy. The multiplicative and additive bias is, respectively, $m=(-0.70\pm0.39)$ per cent and $c=(2.96\pm0.85)10^{-4}$. The other measurement performed the joint-fit on the three coadded image for each filter. The multiplicative and additive bias is, respectively, $m=(-0.59\pm0.46)$ per cent and $c=(7.78\pm0.94)10^{-4}$. The multiplicative bias is reduced but the additive bias increased due to the imperfect PSF modeling in one of the spin-2 axes.

\begin{figure*}
	\includegraphics[width=\textwidth]{final_result.pdf}
    \caption{The multiplicative ($m$) and additive ($c$) bias of several simulation runs. The left panel shows $m$ and $c$ against the sampling factor for each filter. The right panel shows the same for multiband fit result. The number in the parenthesis gives how many filters are used. (3) means J129, H158 and F184 are used, whereas (2) means only J129 and H158 are used. Include the definition of sampling factor. }
    \label{fig:final_result}
\end{figure*}

\begin{table*}
	\centering
	\label{tab:bias_summary}
	\begin{tabular}[width=0.9*\textwidth]{ c|c|c|c|c|c } 
		\hline
		Bands & simulation variants & $m_{1}\times10^{-2}$ & $m_{2}\times10^{-2}$ & $c_{1}\times10^{-4}$ & $c_{2}\times10^{-4}$\\
		\hline
		\multirow{single-band} & single-epochs (J129) & 1.80$\pm$0.67 & 0.28$\pm$0.69 & 6.48$\pm$1.31 & -0.04$\pm$1.51\\
		& single-epochs (F184) & -0.62$\pm$0.81 & -0.17$\pm$0.79 & 3.92$\pm$1.52 & 2.58$\pm$1.57\\
		& single-epochs (H158; w/o noise fix) & -1.09$\pm$0.63 & -1.50$\pm$0.68 & 3.90$\pm$1.21 & 1.37$\pm$1.28\\
		& single-epochs (H158; w/ noise fix) & -1.18$\pm$0.63 & -1.43$\pm$0.67 & 2.14$\pm$1.35 & 1.83$\pm$1.19\\
		& single-band coadd with oversampling (H158; w/o noise fix) & -0.03$\pm$0.59 & -0.11$\pm$0.67 & 14.10$\pm$1.24 & 2.05$\pm$1.42\\
		& single-band coadd with oversampling (H158; w/ noise fix) & -1.51$\pm$0.68 & -1.41$\pm$0.66 & 14.79$\pm$1.32 & 4.45$\pm$1.42\\
		& single-band coadd with oversampling (H158; w/ noise fix, original pixel scale) & -5.89$\pm$0.72 & -5.53$\pm$0.64 & 2.54$\pm$1.25 & 3.09$\pm$1.21\\
		& single-band coadd with oversampling (H158; w/ noise fix, original pixel scale, diff draw) & -5.49$\pm$0.70 & -5.99$\pm$0.62 & 3.19$\pm$1.20 & 411$\pm$1.33\\
		& single-band coadd with oversampling (J129) & -0.49$\pm$0.65 & -0.45$\pm$0.62 & 10.50$\pm$1.33 & -3.72$\pm$1.42\\
		& single-band coadd with oversampling (F184) & 0.47$\pm$0.80 & -0.59$\pm$0.81 & 12.40$\pm$1.67 & 6.32$\pm$1.82\\

		\multirow{multiband} & multiband single-epochs (gauss) (H158+J129+F184) & -0.66$\pm$0.58 & -0.74$\pm$0.59 & 4.32$\pm$1.17 & 1.60$\pm$1.16 \\
		& multiband coadd (gauss; H158+J129+F184; all noise fixed; use noise flag turned off) & -2.14$\pm$0.58 & -2.51$\pm$0.58 & 14.17$\pm$1.21 & 4.55$\pm$1.21\\
		& multiband coadd (gauss; H158+J129+F184; only F184 noise fixed; use noise flag turned off) & -0.61$\pm$0.66 & -0.57$\pm$0.69 & 14.03$\pm$1.25 & 1.54$\pm$1.22\\
		& multiband coadd (gauss; H158+J129; no noise fix) & -0.39$\pm$0.59 & -0.32$\pm$0.68 & 13.72$\pm$1.24 & 1.85$\pm$1.29\\
% 		& (v2) multiband coadd (gauss; H158+J129) & -0.36$\pm$0.45 & -0.35$\pm$0.43 & 11.45$\pm$0.93 & 1.83$\pm$0.98\\

		\hline
	\end{tabular}
	\caption{Shear calibration bias for different simulation runs.}
	\label{tab:result}
\end{table*}

\section{Discussion}
\label{sec:discussion}

So far we have seen how \textsc{metacalibration} handles the relatively undersampled \emph{Roman} images without the effect of blending. The proportion of blended galaxies in the COSMOS catalog is xx per cent and it has been found that the galaxy blending at different redshifts could introduce a significant shear-dependent detection bias when calibrated with \textsc{metacalibration} (\citealt{2020ApJ...902..138S}). In the future study, we should investigate the impact of blending in the image simulations to verify if \textsc{metacalibration} is practical in the real survey.

In the next generation of the simulations, we would like to add the following updates or upgrade these parts of the simulation. 
\begin{itemize}
    \item Expand the simulated area by at least 8 times.
    \item Incorporate the detector effects observed in the real flight candidate detectors.
    \item Enable the detector effects to be on and off to measure their effects on the final cosmology result.
    \item Implement the object detection scheme.
    \item Implement a new coadding methodology which coadds the whole scene instead of individual stamp cutouts (e.g., \texttt{pizza-cutter}\footnote{\url{https://github.com/beckermr/pizza-cutter}})
    \item Implement selection cuts (e.g., S/N) in the shape catalog.
\end{itemize}
With these potential changes, we would like to produce a reference image and shape catalog that can be widely used by other communities.

\section{Conclusions}
\label{sec:conclusion}
We explored the performance of \textsc{metacalibration} methodology with \textsc{psc} coadding scheme to reduce the shear calibration bias in the image simulation framework of the \emph{Roman} Space Telescope. Accurately characterizing how much shear bias exists in this framework is required to successfully complete the weak lensing program of the High-Latitude Survey of the \emph{Roman}. \par

By coadding the single-epoch images and oversampling the PSF for a better shape fit, we find that shear estimates with \textsc{metacalibration} are slightly biased within 1 sigma but within the mission requirement. We conclude that to further constrain the shear calibration bias in the simulation and determine if the \emph{Roman} mission will be able to use the current Stage-III imaging survey schemes, we need more simulation volume well beyond the 2.5 deg$^{2}$ area of the simulated sky.

\section*{Acknowledgements}

We thank Matthew Becker, Erin Sheldon, and Arun Kannawadi for many useful discussions. This work was supported by xx funding agencies.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \section*{Data Availability}

% The inclusion of a Data Availability Statement is a requirement for articles published in MNRAS. Data Availability Statements provide a standardised format for readers to understand the availability of data underlying the research results described in the article. The statement may refer to original data generated in the course of the study or to third-party data analysed in the article. The statement should describe and provide means of access, where possible, by linking to the data or providing the required accession numbers for the relevant databases or DOIs.

%%%%%%%%%%%%%%%%%%%% REFERENCES %%%%%%%%%%%%%%%%%%

% The best way to enter references is to use BibTeX:

\bibliographystyle{mnras}
\bibliography{example} % if your bibtex file is called example.bib

% Alternatively you could enter them by hand, like this:
% This method is tedious and prone to error if you have lots of references
%\begin{thebibliography}{99}
%\bibitem[\protect\citeauthoryear{Author}{2012}]{Author2012}
%Author A.~N., 2013, Journal of Improbable Astronomy, 1, 1
%\bibitem[\protect\citeauthoryear{Others}{2013}]{Others2013}
%Others S., 2012, Journal of Interesting Stuff, 17, 198
%\end{thebibliography}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%% APPENDICES %%%%%%%%%%%%%%%%%%%%%

\appendix

% \section{Coadding of F184 single epochs}
% \label{app:coadd_F}
% If you want to present additional material which would interrupt the flow of the main paper,
% it can be placed in an Appendix which appears after the list of references.

% \begin{table*}
% 	\centering
% 	\label{tab:bias_F}
% 	\begin{tabular}[width=0.9*\textwidth]{ c|c|c|c|c } 
% 		\hline
% 		simulation variants & $m_{1}\times10^{-2}$ & $m_{2}\times10^{-2}$ & $c_{1}\times10^{-4}$ & $c_{2}\times10^{-4}$\\
% 		\hline
% 		single-epochs (F184) & -0.62+-0.81 & -0.17+-0.79 & 3.92+-1.52 & 2.58+-1.57\\
% 		single-band coadd (F184) & 4.62$\pm$0.80 & 5.09$\pm$0.88 & -2.16$\pm$1.61 & -4.19$\pm$1.69\\
% 		single-band coadd with oversampling (F184) & 0.47$\pm$0.80 & -0.59$\pm$0.81 & 12.40$\pm$1.67 & 6.32$\pm$1.82\\
% 		multiband coadd with oversampling (F184+H158+J129) & 2.29$\pm$0.73 & 2.74$\pm$0.73 & 18.24$\pm$1.52 & 0.72$\pm$1.52\\
% 		\hline
% 	\end{tabular}
% 	\caption{Shear calibration bias for different simulation runs.}
% \end{table*}

% fitgauss or gauss appendix
% \begin{table*}
% 	\centering
% 	\label{tab:bias_table}
% 	\begin{tabular}[width=0.9*\textwidth]{ c|c|c|c|c|c } 
% 		\hline
% 		Bands & simulation variants & $m_{1}\times10^{-2}$ & $m_{2}\times10^{-2}$ & $c_{1}\times10^{-4}$ & $c_{2}\times10^{-4}$\\
% 		\hline
% 		\multirow{single-band} & single-epochs (J129) & 1.80$\pm$0.67 & 0.28$\pm$0.69 & 6.48$\pm$1.31 & -0.04$\pm$1.51\\
% 		& single-epochs (H158) & -1.09$\pm$0.63 & -1.50$\pm$0.68 & 3.90$\pm$1.21 & 1.37$\pm$1.28\\
% 		& single-epochs (F184) & -0.62$\pm$0.81 & -0.17$\pm$0.79 & 3.92$\pm$1.52 & 2.58$\pm$1.57\\
% 		& single-band coadd with oversampling (J129) & -0.49$\pm$0.65 & -0.45$\pm$0.62 & 10.50$\pm$1.33 & -3.72$\pm$1.42\\
% 		& single-band coadd with oversampling (H158) & -0.03$\pm$0.59 & -0.11$\pm$0.67 & 14.10$\pm$1.24 & 2.05$\pm$1.42\\
% 		& single-band coadd with oversampling (F184) & 0.47$\pm$0.80 & -0.59$\pm$0.81 & 12.40$\pm$1.67 & 6.32$\pm$1.82\\

% 		\multirow{multiband} & multiband single-epochs (fitgauss) (H158+J129+F184) & 1.78$\pm$0.62 & 0.07$\pm$0.63 & 8.80$\pm$1.22 & 1.57$\pm$1.27 \\
% 		& multiband single-epochs (gauss) (H158+J129+F184) & -0.66$\pm$0.58 & -0.74$\pm$0.59 & 4.32$\pm$1.17 & 1.60$\pm$1.16 \\
% 		& multiband coadd with oversampling (fitgauss; H158+J129) & -1.02$\pm$0.63 & 0.02$\pm$0.70 & 18.51$\pm$1.36 & 0.70$\pm$1.33\\
% 		& multiband coadd with oversampling (gauss; H158+J129) & -0.39$\pm$0.59 & -0.32$\pm$0.68 & 13.72$\pm$1.24 & 1.85$\pm$1.29\\
% 		& (v2) multiband coadd with oversampling (fitgauss; H158+J129) & -0.73$\pm$0.45 & -0.08$\pm$0.48 & 15.80$\pm$0.88 & 0.53$\pm$0.96\\
% 		& (v2) multiband coadd with oversampling (gauss; H158+J129) & -0.36$\pm$0.45 & -0.35$\pm$0.43 & 11.45$\pm$0.93 & 1.83$\pm$0.98\\

% 		\hline
% 	\end{tabular}
% 	\caption{Shear calibration bias for different simulation runs.}
% 	\label{tab:result}
% \end{table*}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% Don't change these lines
\bsp	% typesetting comment
\label{lastpage}
\end{document}

% End of mnras_template.tex

### 2021-10-28 mnras_template.tex
updates

@@
 \linenumbers
+\usepackage{ulem}
 % Only include extra packages if you really need them. Common packages are:
@@
 \usepackage{amssymb}	% Extra maths symbols
+\usepackage{xcolor}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 % Keep the title short and informative.
+\normalem
 \title[Metacalibration with Roman High-Latitude Imaging Survey]{Weak gravitational lensing shear estimates with \textsc{metacalibration} for the High-Latitude Imaging Survey Program of the \emph{Roman} Space Telescope}
@@
 \begin{abstract}
-We investigate the performance of the \textsc{metacalibration} scheme in the framework of the \emph{Nancy Grace Roman} Space Telescope (\emph{Roman}) image simulations.
-By comparing non-calibrated results from the previous work, shear calibration bias can be reduced significantly with \textsc{metacalibration}.
+We investigate the performance of the \textsc{metacalibration} in the framework of the \emph{Nancy Grace Roman} Space Telescope (\emph{Roman}) image simulations.
+Compared with the non-calibrated results from the previous work, \textsc{metacalibration} can significantly reduce the shear calibration bias.
 Exploring shear bias is a robust way to test the requirements of the instrument and the overall weak lensing survey strategy.
 The weak lensing program of \emph{Roman} mission requires the galaxy shapes to be calibrated within about 0.03\%.
-To reach this goal, we can test our calibration scheme with these simulations and can isolate the sources where these residual shear biases come from, (whether it is the algorithm or detector physics).
-We incorporate several new updates that are more realistic and necessary to calibrate shear with a better precision relative to the previous version of the simulations.
-Without the coadditions of the single epoch images, across all three filters we are able to achieve the multiplicative bias of 0.70 per cent within 1.8 $\sigma$ with the current simulation volume.
-Meanwhile, average additive bias is not consistent with zero due to the strong correlation with the input PSF for one of the spin-2 component directions but consistent with zero for the other direction.
-This is worse for coadded images.
+To reach this goal, we can test our calibration scheme with these simulations and can isolate the sources where these residual shear biases arise.
+We incorporate \textcolor{red}{several new updates that are more realistic} and necessary to calibrate shear with a better precision relative to the previous version of the simulations.
+Without the coadditions of the single epoch images, across all three filters we are able to achieve the multiplicative bias of 0.70 per cent within 1.8 $\sigma$.
+Meanwhile, average additive bias is not consistent with zero due to the strong correlation with the input PSF for one of the spin-2 component directions.
+This additive bias is worse for the coadded images, while \textcolor{red}{the average multiplicative bias for multiband coadds was xxx}.
 We find no evidence that shape calibration becomes worse with decreasing image sampling factor based on the Nyquist sampling theorem.
-Overall, within the current simulation volume, we find that \textsc{metacalibration} can calibrate shapes with zero systematics on relatively undersampled images that \emph{Roman} will produce.
+Overall, within the current simulation volume, we find that \textsc{metacalibration} can calibrate shapes with zero shear bias on relatively undersampled images that \emph{Roman} will produce.
 In the future, we will need to substantially increase the simulation volume by 8 to reach the accuracy necessary for the program.
@@
 Since the formulation of the physical cosmological model, more observational evidence has shown that the contents of the universe are mostly in the dark sector (\citealt{2020A&A...633A..69H, 2018PhRvD..98d3528T, 2019PhRvL.122q1301A, 2019PASJ...71...43H, 2021A&A...645A.104A}).
-Within the dark sector, dark energy accounts for the accelerating expansion of the universe (e.g., \citealt{1998AJ....116.1009R, 1999AIPC..478..129P}) and the combination of dark energy and dark matter which only interacts with the same kind are responsible for the growth of the large-scale structure (\citealt{2015RPPh...78h6901K, 2017grle.book.....D}).
+Within the sector, dark energy accounts for the accelerating expansion of the universe (e.g., \citealt{1998AJ....116.1009R, 1999AIPC..478..129P}) and the combination of dark energy and dark matter which only interacts with non-relativistic matter are responsible for the growth of the large-scale structure (\citealt{2015RPPh...78h6901K, 2017grle.book.....D}).
 The growth can be studied by carefully reconstructing the paths of the light leaving distant galaxies and going through the region where masses concentrate in the universe; this physical phenomenon is called gravitational lensing.
-“Weak” gravitational lensing causes a slight distortion to intrinsic galaxy shapes, and measuring the distorted shapes describes the gravitational shear field the light passes through.
-By using millions of these gravitationally lensed galaxies we can explore the matter density and the amplitude of matter fluctuation in the universe (e.g., \citealt{2001PhR...340..291B}).
-Measuring these quantities eventually help us learn the history of the development of the structure.
-For that reason, weak lensing is and will continue to be one of the key probes in the current and next-decade imaging surveys to constrain cosmological parameters with high precision.
+“Weak” gravitational lensing causes a slight distortion to intrinsic galaxy shapes when observed from the Earth.
+By detecting millions of these gravitationally lensed galaxies and computing their distortion levels, we can explore the matter density and the amplitude of matter fluctuation in the universe (e.g., \citealt{2001PhR...340..291B}).
+Measuring these quantities eventually help us learn the history of the development of the large-scale structure in the universe.
+For that reason, weak lensing is and will continue to be one of the powerful probes in the current and next-decade imaging surveys to constrain cosmological parameters with high precision.
 \par
@@
 Due to the subtlety in the lensing effect and its systematics dominant nature in the “weak” regime, observational efforts have been challenging.
-Over the past decade, large international collaborations such as the Dark Energy Survey\footnote{\url{http://www.darkenergysurvey.org/}} (DES: \citealt{2005astro.ph.10346T}), the Hyper Supreme-Cam\footnote{\url{http://hsc.mtk.nao.ac.jp/ssp/}} (HSC: \citealt{2018PASJ...70S...4A}), and the Kilo-Degree Survey\footnote{\url{http://kids.strw.leidenuniv.nl/}} (KiDS) have been successful at constraining the cosmological parameters, and the precision in calibrating the shapes of distant galaxies has reached a few percent (\citealt{2020arXiv201103408G, 2020arXiv201208567M, 2021A&A...645A.105G}) (include most recent HSC catalog).
+Over the past decade, large international collaborations such as the Dark Energy Survey\footnote{\url{http://www.darkenergysurvey.org/}} (DES: \citealt{2005astro.ph.10346T}), the Hyper Supreme-Cam\footnote{\url{http://hsc.mtk.nao.ac.jp/ssp/}} (HSC: \citealt{2018PASJ...70S...4A}), and the Kilo-Degree Survey\footnote{\url{http://kids.strw.leidenuniv.nl/}} (KiDS) have been successful at constraining the cosmological parameters, and the precision in calibrating the shapes of distant galaxies has reached a few percent (\citealt{2020arXiv201103408G, 2020arXiv201208567M, 2021A&A...645A.105G}).
 As we cover more areas in the sky and develop better tools (observatories and algorithms), we find more galaxies and we have already reached to the point where statistical and systematic uncertainties are comparable.
-Thus, the next-decade legacy surveys, the Stage IV surveys (\citealt{2006astro.ph..9591A}) such as Euclid\footnote{\url{ http://sci.esa.int/euclid}} (Euclid Study Scientist & the Science Advisory Team 2010), the Vera C.
+Thus, the next-decade legacy surveys, the Stage IV surveys (\citealt{2006astro.ph..9591A}) such as Euclid\footnote{\url{ http://sci.esa.int/euclid}} (Euclid Study Scientist \& the Science Advisory Team 2010), the Vera C.
 Rubin Observatory Legacy Survey of Space and Time\footnote{\url{ http://www.lsst.org}} (LSST: \citealt{2009arXiv0912.0201L, 2019ApJ...873..111I}), and \emph{Nancy Grace Roman} Space Telescope\footnote{\url{https://roman.gsfc.nasa.gov}} (\emph{Roman}: \citealt{2015arXiv150303757S}) require even better control of systematics.
-In order to manage the systematic uncertainties, we must develop realistic image simulations, apply the shape measurement on the simulated images, and determine any potential systematic effects and the strategy of mitigating them.
+In order to manage the systematic uncertainties, we must develop realistic image simulations, apply the pre-existing shape measurement on the simulated images, and determine any potential systematic effects and build the strategy of mitigating them.
 
-Based on our current knowledge, systematic biases for weak lensing science, both observational and astrophysical, could occur throughout imaging surveys (\citealt{2018ARA&A..56..393M}).
+Based on our current knowledge, systematic biases for weak lensing science, both observational and astrophysical, could occur throughout imaging surveys (e.g., \citealt{2018ARA&A..56..393M}).
 Particularly, observational systematics can be found in,
@@
     \item post-processing pipeline such as image coaddition and object detection
-    \item cosmological inference 
 \end{itemize}
@@
 where i=(1,2) and $\gamma^{obs}_{i}$ is the two-component observed shear after calibrations and $\gamma^{true}_{i}$ is the true shear.
-This shear bias arises for various reasons.
+These shear biases arise for various reasons.
 For space-based surveys, it can be mainly introduced in places such as PSF modelling, blending, and the undersampling of the image (e.g., \citealt{2018ARA&A..56..393M}).
 Additionally, complex detector effects such as brighter-fatter effect are the potential sources of bias (\citealt{2013MNRAS.429..661M}), where it is shown that for \emph{Roman} the effect of persistence will not be an issue (\citealt{2021arXiv210610273L}).
-Qualitatively, if the recovered shear is biased by 1$\%$ (m=1$\%$), $S_{8} = \sigma_{8} \sqrt{\Omega_{m}/0.3}$ would be biased about 1.5$\%$ in the final cosmology result.
-Thus, quantifying this shear bias before the survey is extremely important.
+Qualitatively, if the recovered shear is biased by 1$\%$ (m=0.01), $S_{8} = \sigma_{8} \sqrt{\Omega_{m}/0.3}$ would be biased about 1.5$\%$ in the final cosmology result.
+Thus, quantifying these biases before the real survey is extremely important.
 \par
@@
 It has also confirmed that the shear can be calibrated with \textsc{metacalibration} at a-few-percent level in DES (\citealt{2018MNRAS.481.1149Z, 2020arXiv201103408G}), without accounting for galaxy blending.
-Tackling the issue of blending is on the way of Y6 DES analysis with the shear-dependent detection and calibration technique (\textsc{metadetect}; \citealt{2020ApJ...902..138S}).
+Tackling the issue of blending is on the way of DES Y6 analysis with the shear-dependent detection and calibration technique (\textsc{metadetect}; \citealt{2020ApJ...902..138S}).
 While the major advantage of \textsc{metacalibration} is that it can be directly applied upon real galaxy images, which does not depend on galaxy morphology in simulations, the limitations for future surveys are not well-known.
-One possible limitation might lie in the effect of the undersampled images, because future space-based surveys like \emph{Euclid} and \emph{Roman} have such a small pixel scale that galaxy images will not be Nyquist sampled at native resolution (\citealt{2013PASP..125.1496S}) based on the Nyquist-Shannon Sampling Theorem.
+One possible limitation might lie in the effect of the undersampled images, because future space-based surveys like \emph{Euclid} and \emph{Roman} have such a small pixel scale that galaxy images will not be Nyquist sampled at a native resolution (\citealt{2013PASP..125.1496S}) based on the Nyquist-Shannon Sampling Theorem.
 We define the sampling factor of each filter in \emph{Roman} to be,
@@
 \end{equation}
-where $\lambda_{min}$ is the shortest wavelength of the incident light of the filter, $N_{f}$ is the focal ratio of the telescope ($N_{f}=7.8$ for \emph{Roman}) and $p$ is the pixel spacing of the sensor ($p=10\mu m$ for \emph{Roman}).
+where $\lambda_{min}$ is the shortest wavelength of the incident light in the filter, $N_{f}$ is the focal ratio of the telescope ($N_{f}=7.8$ for \emph{Roman}) and $p$ is the pixel spacing of the sensor ($p=10\mu m$ for \emph{Roman}).
 The image with the sampling factor, $Q < 2$, is not Nyquist sampled and reffered to as the undersampled image.
 It is problematic to measure galaxy shapes solely from the undersampled images, because the \emph{Roman} PSF that will be used to recover the shapes is also undersampled and has a complex structure, not simply Gaussian.
-It is, therefore, necessary to build a robust strategy that can reconstruct better sampled PSF to allow unbiased shape measurement.
+\textcolor{red}{It is, therefore, necessary to build a robust strategy that can reconstruct better sampled PSF to allow unbiased shape measurement.
+}
 
 Recently, Kannawadi et al.
-(2021) addressed this potential issue of the limitations of \textsc{metacalibration} on undersampled images on \emph{Euclid} image simulations and found that for \emph{Euclid} mission the shear estimate is biased about 1$\%$ (\citealt{2021MNRAS.502.4048K}).
-They mentioned that his result could be extended to the \emph{Roman} mission due to their similarities in the instruments and for \emph{Roman} they predicted the multiplicative bias was more than 1\% for H158 and F184 filters.
-Regardless of this extended result, we should validate if \textsc{metacalibration} is non-biased with the image simulations specifically made for the \emph{Roman} mission.
+(2021) addressed this potential issue of the limitations of \textsc{metacalibration} on undersampled images on \emph{Euclid} image simulations.
+They found that for \emph{Euclid} mission the shear estimate is biased about 1$\%$ (\citealt{2021MNRAS.502.4048K}).
+It is mentioned that their result could be extended to the \emph{Roman} mission due to their similarities in the instruments and for \emph{Roman} they predicted the multiplicative bias was more than 1\% for H158 and F184 filters.
+Regardless of this extended result, we should validate if \textsc{metacalibration} is unbiased with the image simulations specifically made for the \emph{Roman} mission.
 Our work is based on the image simulation suite of the \emph{Roman} Space Telescope developed by \citet{2021MNRAS.501.2044T}, where we render star and galaxy images from \texttt{GalSim}\footnote{\url{ https://github.com/GalSim-developers/GalSim}} (\citealt{2015A&C....10..121R}).
-With a few simulation updates and an implementation of \textsc{metacalibration}, we can start to explore if the shear calibration goal of the High-Latitude Survey program for Roman ($m=~3.2\times10^{-4}$) (\citealt{2019BAAS...51c.341D}) can be achieved.
+With a few simulation updates and an implementation of \textsc{metacalibration}, we can start to explore if the shear calibration goal of the High-Latitude Survey program for \emph{Roman} ($m=~3.2\times10^{-4}$) (\citealt{2019BAAS...51c.341D}) can be achieved.
 \par
@@
 \label{sec:sims}
-In this section, we briefly summarize the full simulation details from building a truth catalog to measuring galaxy shapes.
-Then we describe the simulation updates that are implemented particularly for this work.
+In this section, we briefly summarize the full simulation details from building a truth catalog to measuring galaxy shapes. Then we describe the simulation updates that are implemented for this work.
 \subsection{Simulation Summary}
@@
 These MEDS files contain all objects that are located in the area of the sky partitioned according to a HEALPix of $n_{side}$=512.
-Once the objects are sorted in MEDS files, we pass them and the corresponding PSF for the SCA to a shape measurement.
-We pass these multiple exposures with corresponding PSFs to \textsc{ngmix}\footnote{\url{ https://github.com/esheldon/ngmix}} to fit the galaxy shapes with the Gaussian mixture fitting method (\citealt{2014MNRAS.444L..25S}).
+Once the objects are sorted in MEDS files, we pass these multiple exposures with the corresponding PSF to \textsc{ngmix}\footnote{\url{ https://github.com/esheldon/ngmix}} to fit the galaxy shapes with the Gaussian mixture fitting method (\citealt{2014MNRAS.444L..25S}).
 This shape measurement process produces shape catalogs from which the shear calibration bias can be calculated with \textsc{metacalibration}.
@@
 In order to accomplish science goals, and build and test the pipelines of weak lensing program in \emph{Roman}, we must keep updating the simulations to be more realistic.
-Along the way to test calibrating shears using \textsc{metacalibration}, we have implemented and made updates to the following parts of the simulation framework.
+We have implemented and made updates to the following parts of the simulation framework to be able to measure unbiased shapes with \textsc{metacalibration}.
 \begin{itemize}
@@
 This value is an approximate pixel saturation but in the next generation of the simulations we will use the true saturation from the flight candidate detectors.
+
     \item \textbf{Rotation of the \emph{Roman} PSF on the sky}:
@@
 (2021), the rotations of the \emph{Roman} PSF with respect to the telescope rotation were not engaged properly by \texttt{galsim.roman} module.
-Since a non-rotating PSF could trigger a preferred direction in the shapes when being deconvolved, we believe that this contributed to the non-zero multiplicative bias.
+Since a non-rotating PSF could trigger a preferred direction in the shapes when being deconvolved, we believe that this contributed to the non-zero multiplicative bias result.
 There has been an update in \texttt{galsim.roman} module to correctly rotate the PSF given the WCS on the SCA.
 Figure \ref{fig:psfrot} shows a toy PSF of the same pointing but with a different rotation angle of the telescope.
-    \item \textbf{Single-band and multiband Coadds}: 
+
+    \item \textbf{Single-band and Multiband Coadds}: 
     We have added and modified the postage stamp coadds (\texttt{psc}) algorithm\footnote{\url{https://github.com/esheldon/psc}} to create coadditions of single-epoch postage stamps.
-Coadds are usually performed to enhance the signal-to-noise ratio (S/N) of an object and mitigate the potential systematics for an accurate shape measurement.
+Coadds are usually performed to enhance the signal-to-noise ratio (S/N) of an object and mitigate the measurement noise.
 If we take advantage of fitting an object in the coadd instead of fitting multiple images of each object in each filter, we can save a factor of 6 in computing time, which is the average number of exposures from the reference survey.
-Additionally, coadding is one way to reduce the effect of the undersampling of the images since by coadding multiple exposures the product is naturally better sampled.
-Thus, for these reasons, we must utilize a coadding scheme for the \emph{Roman} galaxies.
-We can turn this on and off so that the effect of undersampling is clear.
+Additionally, coadding is one way to reduce the effect of the undersampling of the images since the coadd is naturally better sampled.
+For these reasons, we must utilize a coadding scheme for the \emph{Roman} galaxies.
 The detailed overview of the coadd process in \texttt{psc} is in Sec.
 \ref{subsec:psc}.
-    \item \textbf{\textsc{metacalibration} implementation}: We used \textsc{metacalibration}\footnote{\url{https://github.com/esheldon/ngmix/wiki/Metacalibration}} bootstrapper method, which is a wrapper class to run measurements in the \textsc{ngmix} package and is used extensively to produce weak lensing shape catalog in DES Y3 analysis.
-\textsc{metacalibration} process takes place after making coadded images, if applicable for the coadd measurements.
+
+    \item \textbf{\textsc{metacalibration} in \textsc{ngmix}}: We implemented \textsc{metacalibration}\footnote{\url{https://github.com/esheldon/ngmix/wiki/Metacalibration}} bootstrapper method, which is a wrapper class to run measurements in the \textsc{ngmix} package and is used extensively to produce weak lensing shape catalog in DES Y3 analysis.
+\textsc{metacalibration} process takes place after making coadded images.
+\textsc{ngmix} is able to fit multiple exposures in case for measuring shapes on single-epoch images.
 With this calibration method, we hope to significantly reduce some of the shear calibration bias Troxel et al.
@@
 Our goal is to show that the recovered shapes with \textsc{metacalibration} are non-biased.
-In order to do so, we need to build a measurement pipeline within the simulation framework that contributes to the final measurement.
+In order to do so, we need to build a measurement pipeline within the current simulation framework that contributes to the final measurement.
 In this section, we present in detail how coadds are produced with \texttt{psc} from the undersampled single-epoch images, how \textsc{metacalibration} calibrates shapes, and how we measure the shear calibration bias from the \textsc{metacalibration} catalog.
@@
 Coaddition is the process that reconstructs a Nyquist-sampled image out of multiple exposures of an object.
-While this process can benefit in increasing the S/N value of an object and reducing the impact of pixel noise, several challenges need to be addressed for images that are taken with equatorial mount telescopes, which can only move vertically and horizontally, and for images with telescopes that can rotate.
+While this process can benefit in increasing the S/N value of an object and reducing the impact of pixel noise, several challenges need to be addressed for images taken with telescopes that can rotate.
 When the rotation is introduced, this coadding process becomes more complex to interpolate the image to stack pixel grid.
-While coaddition could introduce systematic bias due to the complexity of the original PSF and its interpolation scheme, the undersampling of the images can be overcome.
+While coaddition could introduce systematic bias due to the complexity of the original PSF and its interpolation scheme, the bias with the undersampled images can be overcome \textcolor{red}{by the combinations of the effective coadding process and the careful treatment of the input PSF}.
 We describe our coaddition pipeline that is based on \texttt{psc}.
@@
 We reconstruct the Nyquist-sampled image from multiple exposures in MEDS files.
-For the coaddition of the PSF, we choose to coadd the image with the oversampled PSF over the undersampled original PSF.
+For the coaddition of the PSF, we choose to coadd the image with the oversampled PSF.
 We oversample the original PSF by a factor of 4 to simulate the better sampled PSF that \emph{Roman} will eventually produce when it constructs the PSF from the full focal plane.
 It will be highly resolved than native pixel scale.
-For each exposure of the object we render the \emph{Roman} PSF with a stamp size of 32 pixels at the galaxy centroid.
-We modified the original code to improve performance of our algorithm, and these modifications are listed below with the general coadding process in \texttt{psc}.
+For each exposure of the object we render the \emph{Roman} PSF with a stamp size of 32 pixels at the galaxy centroid, not the image centroid.
+We modified the original code to improve performance of the \textsc{metacalibration} process later, and these modifications are listed below with the general coadding process in \texttt{psc}.
 
@@
 We downsampled the oversampled PSF (128 x 128 pixels) by summing 4 square-pixels and creating the original size PSF (32 x 32 pixels), in order to ensure that the shape fit with \textsc{ngmix} can be processed.
-Since a better sampled PSF generally enables the shape of the PSF to be more isotropic, from the difference image in Figure \ref{fig:coadd_oversample_res}, we can state that the original PSF has an anisotropic shape, which can lead to biased shape measurement.
+Since a better sampled PSF generally enables the shape of the PSF to be more isotropic, we can state that the original PSF can lead to the biased shape measurement from Figure \ref{fig:coadd_oversample_res}.
 
@@
     \vspace*{-5mm}
-    \caption{The left and middle panel of the figure illustrates the coadded \emph{Roman} PSF at its native pixel scale and the coadded PSF with a pixel scale that is smaller by a factor of 4.
+    \caption{The left and middle panel of the figure illustrates the coadded \emph{Roman} PSF at its native pixel scale and the coadded PSF with a pixel scale that is oversampled by a factor of 4 and then down-sampled.
 These are visualized in a log scale.
-The right panel shows the difference image between the two PSFs.
+The right panel shows the difference image between the two linear-scaled PSFs.
 }
@@
 
-\subsection{Shape measurement with \textsc{metacalibration}}
+\subsection{Shape Measurement with \textsc{metacalibration}}
 \label{subsec:mcal}
@@
 
-Once we have the \textsc{metacalibration} catalog, we can calculate shear calibration bias from the measured object ellipticities, \vb*{e} = ($e_{1}$, $e_{2}$).
+Once we have the \textsc{metacalibration} catalog, we can calculate shear calibration bias from the measured object ellipticities, $\vb*{e}$ = ($e_{1}$, $e_{2}$).
 The observed ellipticities can be approximated using a Taylor expansion around the two-component shear, $\vb*{\gamma}=0$.
@@
 In actual observations, the observable is the galaxy shapes $\langle\vb*{e}\rangle$ and we can take advantage of image simulations and calculate the shear response of the particular calibration technique we employ, and finally compute the gravitational lensing shear signal $\langle\vb*{\gamma}\rangle$.
+
+\begin{figure}
+	\includegraphics[width=\columnwidth]{metacal_bias_shear.png}
+    \vspace*{-5mm}
+    \caption{It shows the quadratic relationship between the input gravitational shear for the simple simulations and the multiplicative bias estimated from the recovered shape in the \textsc{metacalibration} catalogs.
+}
+    \label{fig:metacal_shear_linear}
+\end{figure}
 
@@
 
-\begin{figure}
-	\includegraphics[width=\columnwidth]{metacal_bias_shear.png}
-    \vspace*{-5mm}
-    \caption{It shows the quadratic relationship between the input gravitational shear for the simple simulations and the multiplicative bias estimated from the recovered shape in the \textsc{metacalibration} catalogs.
-}
-    \label{fig:metacal_shear_linear}
-\end{figure}
+\textcolor{red}{\textsc{ngmix} utilizes xx method to compute the size of the galaxy, while we compute the adaptive moments of objects to measure the shape and size of the input PSF (\citealt{2003MNRAS.343..459H})}.
 
@@
 \label{sec:results}
-In this section, we present the characteristics of the simulated data products.
+In this section, we present the properties of the simulated data products and the shape measurement results from various simulation variants.
 We divide our shape measurements into two categories; single-band and multiband.
@@
 As the more developed case, we measure shapes with the single-band coadd in each filter by single-fitting it.
-For one multiband measurement, we match the objects, accumulate the single exposures from each filter catalog and measure the shapes with the joint-fit.
-The other multiband measurement joint-fit the three coadds from each filter together to recover the shape.
+For one multiband measurement, we match the objects between each filter and measure the shapes with the joint-fit of single exposures across all the filters.
+The other multiband measurement joint-fit the three coadds from each filter to recover the shapes.
 
+\subsection{Statistics of the Shape Catalog}
 From the COSMOS catalog, based on the \emph{Roman} Weak Lensing mission requirements, objects are pre-selected and simulated.
@@
 We do not make any selection cuts on the simulated catalogs based on measured properties.
-Even so, due to the misestimation of the PSF or low S/N, the Gaussian mixture fit with \textsc{ngmix} fails about 5\% of all simulated objects, and so the total number of the recovered objects for single-band measurements is, 861,960 for F184, 863,358 for H158, and 859,645 for J129.
-For the multiband (H158+J129+F184) coadd measurements, we measure objects that are covered by all of the filters and the total number of the recovered objects is 851,821.
-Here are the measured properties of the objects in the \textsc{metacalibration} shape catalogs.
+Even so, due to the misestimation of the PSF or low S/N, the Gaussian mixture in \textsc{ngmix} fails to fit about 5\% of all simulated objects, and so the total number of the recovered objects for single-band measurements is, 861,960 for F184, 863,358 for H158, and 859,645 for J129.
+For the multiband (H158+J129+F184) coadd measurements, we measure objects that are found by all of the filters and the total number of the recovered objects is 851,821.
+Figure \ref{fig:true_properties} and \ref{fig:measured_properties} show the true properties from the truth catalog and measured properties from the \textsc{metacalibration} shape catalogs.
 
-% (galaxy and PSF properties; SNR, $e_{1,psf}$, $e_{2,psf}$, PSF FWHM) 
-% havent decided on which plot to use. 
-% \begin{figure}
-% 	\includegraphics[width=\columnwidth]{figure5.pdf}
-%     \caption{}
-%     \label{fig:psf_properties}
-% \end{figure}
-% \begin{figure}
-% 	\includegraphics[width=\columnwidth]{figure6.pdf}
-%     \caption{}
-%     \label{fig:other_properties}
-% \end{figure}
+\begin{figure}
+    \hspace*{-1.5cm}
+	\includegraphics[scale=0.3]{true_properties.pdf}
+	\centering
+    \caption{The left panel shows input galaxies magnitudes for all the 3 filter we have used to measure shapes.
+The mean magnitude for H158, F184, J129 are respectively 23.098, 22.976, and 23.273.
+The right panel shows the half-light radius in units of arcsec for H158 for input and measured objects.
+The mean half-light radii for input and measured galaxies are 0.294 and 0.221 arcsec for H158.
+For these histograms, we are showing the objects with the successful fit in \textsc{ngmix}.}
+    \label{fig:true_properties}
+\end{figure}
+
+\begin{figure*}
+    \hspace*{-3.0cm}
+    \centering
+	\includegraphics[scale=0.34]{ngmix_snr_T.pdf}
+    \caption{add multiband to each window and F184 coadd for PSF properties.}
+    \label{fig:measured_properties}
+\end{figure*}
 
@@
 Coadd results are consistent with zero multiplicative bias within 1 sigma and the signals increase by xx per cent.
-Generally, coadding produces better sampled images as in Figure\ref{fig:single_to_coadd_rgb} and less multiplicative bias than single epochs measurements.
+Generally, coadding produces better sampled images as in Figure \ref{fig:single_to_coadd_rgb} and less multiplicative bias than single epochs measurements.
 We can conclude that in the \emph{Roman} simulation we have seen that the multiplicative bias has no strong dependence on the sampling factor.
@@
 When the coadds of each filter are used, the bias becomes, (3.39$\pm$0.90)$10^{-4}$ for J129, (8.08$\pm$0.87)$10^{-4}$ for H158 and (9.36$\pm$1.10)$10^{-4}$ for F184.
-From the Table \ref{tab:bias_table}, it is worth noting that the coadd process clearly introduces non-trivial additive biases in one direction, but not the other.
+From the Table \ref{tab:result}, it is worth noting that the coadd process clearly introduces non-trivial additive biases in one direction, but not the other.
 We believe this is due to the effect of an imperfect PSF model.
@@
 
+\begin{table*}
+	\centering
+	\label{tab:bias_summary}
+	\begin{tabular}[scale=1.4]{ c|c|c|c|c } 
+		\hline
+		simulation variants & $m_{1}\times10^{-2}$ & $m_{2}\times10^{-2}$ & $c_{1}\times10^{-4}$ & $c_{2}\times10^{-4}$\\
+		\hline
+		\textcolor{red}{single-epochs (J129; w/ noise fix)} & 1.30$\pm$0.70 & 0.30$\pm$0.63 & 4.65$\pm$1.45 & 1.33$\pm$1.40\\
+		\textcolor{red}{single-epochs (F184)} & -0.62$\pm$0.81 & -0.17$\pm$0.79 & 3.92$\pm$1.52 & 2.58$\pm$1.57\\
+		\textcolor{red}{single-epochs (H158; w/ noise fix)} & -1.18$\pm$0.63 & -1.43$\pm$0.67 & 2.14$\pm$1.35 & 1.83$\pm$1.19\\
+		\hline
+		\textcolor{red}{single-band coadd with oversampling (H158; w/ noise fix)} & -1.51$\pm$0.68 & -1.41$\pm$0.66 & 14.79$\pm$1.32 & 4.45$\pm$1.42\\
+		\textcolor{red}{single-band coadd with oversampling (J129 w/ noise fix)} & -1.59$\pm$0.64 & -2.31$\pm$0.70 & 11.61$\pm$1.20 & -0.09$\pm$1.34\\
+		\textcolor{red}{single-band coadd with oversampling (F184 w/ noise fix)} & 0.47$\pm$0.80 & -0.59$\pm$0.81 & 12.40$\pm$1.67 & 6.32$\pm$1.82\\
+		\hline
+		\textcolor{red}{multiband single-epochs (gauss) (H158+J129+F184)} & -0.66$\pm$0.58 & -0.74$\pm$0.59 & 4.32$\pm$1.17 & 1.60$\pm$1.16 \\
+		\textcolor{red}{multiband coadd (w/ noise fix)} & -2.16$\pm$0.60 & -2.16$\pm$0.60 & 14.03$\pm$1.13 & 4.44$\pm$1.31\\
+
+		\hline
+	\end{tabular}
+	\caption{Shear calibration bias for different simulation runs.}
+	\label{tab:result}
+\end{table*}
+
 \begin{figure*}
-	\includegraphics[width=\textwidth]{final_result.pdf}
+	\includegraphics[scale=0.5]{final_result.pdf}
     \caption{The multiplicative ($m$) and additive ($c$) bias of several simulation runs.
@@
 
-\begin{table*}
+\begin{figure*}
+    \hspace*{-3.5cm}
     \centering
-	\label{tab:bias_summary}
-	\begin{tabular}[width=0.9*\textwidth]{ c|c|c|c|c|c } 
-		\hline
-		Bands & simulation variants & $m_{1}\times10^{-2}$ & $m_{2}\times10^{-2}$ & $c_{1}\times10^{-4}$ & $c_{2}\times10^{-4}$\\
-		\hline
-		\multirow{single-band} & single-epochs (J129) & 1.80$\pm$0.67 & 0.28$\pm$0.69 & 6.48$\pm$1.31 & -0.04$\pm$1.51\\
-		& single-epochs (F184) & -0.62$\pm$0.81 & -0.17$\pm$0.79 & 3.92$\pm$1.52 & 2.58$\pm$1.57\\
-		& single-epochs (H158; w/o noise fix) & -1.09$\pm$0.63 & -1.50$\pm$0.68 & 3.90$\pm$1.21 & 1.37$\pm$1.28\\
-		& single-epochs (H158; w/ noise fix) & -1.18$\pm$0.63 & -1.43$\pm$0.67 & 2.14$\pm$1.35 & 1.83$\pm$1.19\\
-		& single-band coadd with oversampling (H158; w/o noise fix) & -0.03$\pm$0.59 & -0.11$\pm$0.67 & 14.10$\pm$1.24 & 2.05$\pm$1.42\\
-		& single-band coadd with oversampling (H158; w/ noise fix) & -1.51$\pm$0.68 & -1.41$\pm$0.66 & 14.79$\pm$1.32 & 4.45$\pm$1.42\\
-		& single-band coadd with oversampling (H158; w/ noise fix, original pixel scale) & -5.89$\pm$0.72 & -5.53$\pm$0.64 & 2.54$\pm$1.25 & 3.09$\pm$1.21\\
-		& single-band coadd with oversampling (H158; w/ noise fix, original pixel scale, diff draw) & -5.49$\pm$0.70 & -5.99$\pm$0.62 & 3.19$\pm$1.20 & 411$\pm$1.33\\
-		& single-band coadd with oversampling (J129) & -0.49$\pm$0.65 & -0.45$\pm$0.62 & 10.50$\pm$1.33 & -3.72$\pm$1.42\\
-		& single-band coadd with oversampling (F184) & 0.47$\pm$0.80 & -0.59$\pm$0.81 & 12.40$\pm$1.67 & 6.32$\pm$1.82\\
-
-		\multirow{multiband} & multiband single-epochs (gauss) (H158+J129+F184) & -0.66$\pm$0.58 & -0.74$\pm$0.59 & 4.32$\pm$1.17 & 1.60$\pm$1.16 \\
-		& multiband coadd (gauss; H158+J129+F184; all noise fixed; use noise flag turned off) & -2.14$\pm$0.58 & -2.51$\pm$0.58 & 14.17$\pm$1.21 & 4.55$\pm$1.21\\
-		& multiband coadd (gauss; H158+J129+F184; only F184 noise fixed; use noise flag turned off) & -0.61$\pm$0.66 & -0.57$\pm$0.69 & 14.03$\pm$1.25 & 1.54$\pm$1.22\\
-		& multiband coadd (gauss; H158+J129; no noise fix) & -0.39$\pm$0.59 & -0.32$\pm$0.68 & 13.72$\pm$1.24 & 1.85$\pm$1.29\\
-% 		& (v2) multiband coadd (gauss; H158+J129) & -0.36$\pm$0.45 & -0.35$\pm$0.43 & 11.45$\pm$0.93 & 1.83$\pm$0.98\\
-
-		\hline
-	\end{tabular}
-	\caption{Shear calibration bias for different simulation runs.}
-	\label{tab:result}
-\end{table*}
+	\includegraphics[scale=0.34]{H158_meanshear_measured_properties_perbin.pdf}
+    \caption{H158 coadd, add multiband, do delta e.}
+    \label{fig:meanshear}
+\end{figure*}
 
@@
 So far we have seen how \textsc{metacalibration} handles the relatively undersampled \emph{Roman} images without the effect of blending.
-The proportion of blended galaxies in the COSMOS catalog is xx per cent and it has been found that the galaxy blending at different redshifts could introduce a significant shear-dependent detection bias when calibrated with \textsc{metacalibration} (\citealt{2020ApJ...902..138S}).
-In the future study, we should investigate the impact of blending in the image simulations to verify if \textsc{metacalibration} is practical in the real survey.
+However, it has been found that the galaxy blending at different redshifts could introduce a significant shear-dependent detection bias when calibrated with \textsc{metacalibration} (\citealt{2020ApJ...902..138S}).
+In the future study, we should investigate the impact of blending in the image simulations to verify if \textsc{metacalibration} combined with the new version of \textsc{ngmix} can be the shear calibration algorithm in the real survey.
 
@@
 \begin{itemize}
-    \item Expand the simulated area by at least 8 times.
-    \item Incorporate the detector effects observed in the real flight candidate detectors.
-    \item Enable the detector effects to be on and off to measure their effects on the final cosmology result.
-    \item Implement the object detection scheme.
-    \item Implement a new coadding methodology which coadds the whole scene instead of individual stamp cutouts (e.g., \texttt{pizza-cutter}\footnote{\url{https://github.com/beckermr/pizza-cutter}})
-    \item Implement selection cuts (e.g., S/N) in the shape catalog.
+    \setlength\itemsep{1em}
+    \item \textbf{Simulation Volume}: Expand the simulated area by at least 8 times. (Troxel et al. in prep.)
+
+    \item \textbf{Near-Infrared Detectors}: Incorporate the detector effects measured in the real flight candidate detectors and produce two catalogs with and without them to determine the impact on the final cosmology result.
+
+    \item \textbf{Image Coadditions}: Implement a new coadding methodology which coadds the whole scene instead of individual stamp cutouts (e.g., \textsc{astrodrizzle}\footnote{\url{https://github.com/spacetelescope/drizzlepac}}).
+With \textsc{astrodrizzle} which employs the linear reconstruction of the individual images, we are able to further mitigate the effect of undersampled \emph{Roman} images.
+If we set the final coadd pixel scale with \textsc{astrodrizzle} to be 70\% smaller than the original \emph{Roman} pixel scale, F184 will be fully sampled (Q > 2) and J129 will be sampled at the similar level with F184 without coadding.
+
+    \item \textbf{Source Detection}: Implement a source detection methodology with \texttt{Photutils}\footnote{\url{https://photutils.readthedocs.io/en/stable/}} on the coadds.
+
+    \item \textbf{Selection Cuts}: Implement quality assurance cuts (e.g., S/N) on the shape catalog to avoid the noise on the shape fit and compute the measurement biases accounting for the selection effects (\citealt{2017ApJ...841...24S}).
 \end{itemize}
-With these potential changes, we would like to produce a reference image and shape catalog that can be widely used by other communities.
+\textcolor{red}{With these potential changes, we will produce a reference image and shape catalog that can be widely used by other communities.}
 
@@
 
-\section*{Acknowledgements}
+\section{Acknowledgements}
 
@@
 
-% Alternatively you could enter them by hand, like this:
-% This method is tedious and prone to error if you have lots of references
-%\begin{thebibliography}{99}
-%\bibitem[\protect\citeauthoryear{Author}{2012}]{Author2012}
-%Author A.~N., 2013, Journal of Improbable Astronomy, 1, 1
-%\bibitem[\protect\citeauthoryear{Others}{2013}]{Others2013}
-%Others S., 2012, Journal of Interesting Stuff, 17, 198
-%\end{thebibliography}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
 %%%%%%%%%%%%%%%%% APPENDICES %%%%%%%%%%%%%%%%%%%%%
@@
 
-% \section{Coadding of F184 single epochs}
-% \label{app:coadd_F}
+\section{Simple Simulations}
+\label{app:coadd_F}
 % If you want to present additional material which would interrupt the flow of the main paper,
 % it can be placed in an Appendix which appears after the list of references.
-
-% \begin{table*}
-% 	\centering
-% 	\label{tab:bias_F}
-% 	\begin{tabular}[width=0.9*\textwidth]{ c|c|c|c|c } 
-% 		\hline
-% 		simulation variants & $m_{1}\times10^{-2}$ & $m_{2}\times10^{-2}$ & $c_{1}\times10^{-4}$ & $c_{2}\times10^{-4}$\\
-% 		\hline
-% 		single-epochs (F184) & -0.62+-0.81 & -0.17+-0.79 & 3.92+-1.52 & 2.58+-1.57\\
-% 		single-band coadd (F184) & 4.62$\pm$0.80 & 5.09$\pm$0.88 & -2.16$\pm$1.61 & -4.19$\pm$1.69\\
-% 		single-band coadd with oversampling (F184) & 0.47$\pm$0.80 & -0.59$\pm$0.81 & 12.40$\pm$1.67 & 6.32$\pm$1.82\\
-% 		multiband coadd with oversampling (F184+H158+J129) & 2.29$\pm$0.73 & 2.74$\pm$0.73 & 18.24$\pm$1.52 & 0.72$\pm$1.52\\
-% 		\hline
-% 	\end{tabular}
-% 	\caption{Shear calibration bias for different simulation runs.}
-% \end{table*}
 

### 2021-11-03 roman_metacal.tex
updates

--- 2021-10-28 mnras_template.tex
@@
 where i=(1,2) and $\gamma^{obs}_{i}$ is the two-component observed shear after calibrations and $\gamma^{true}_{i}$ is the true shear.
-These shear biases arise for various reasons.
-For space-based surveys, it can be mainly introduced in places such as PSF modelling, blending, and the undersampling of the image (e.g., \citealt{2018ARA&A..56..393M}).
+The bias arises for various reasons.
+For space-based surveys, the bias can be mainly introduced in places such as PSF modelling, blending, and the undersampling of the image (e.g., \citealt{2018ARA&A..56..393M}).
 Additionally, complex detector effects such as brighter-fatter effect are the potential sources of bias (\citealt{2013MNRAS.429..661M}), where it is shown that for \emph{Roman} the effect of persistence will not be an issue (\citealt{2021arXiv210610273L}).
@@
 		\hline
-		\textcolor{red}{single-epochs (J129; w/ noise fix)} & 1.30$\pm$0.70 & 0.30$\pm$0.63 & 4.65$\pm$1.45 & 1.33$\pm$1.40\\
-		\textcolor{red}{single-epochs (F184)} & -0.62$\pm$0.81 & -0.17$\pm$0.79 & 3.92$\pm$1.52 & 2.58$\pm$1.57\\
-		\textcolor{red}{single-epochs (H158; w/ noise fix)} & -1.18$\pm$0.63 & -1.43$\pm$0.67 & 2.14$\pm$1.35 & 1.83$\pm$1.19\\
+		\textcolor{red}{single-epochs (J129)} & 1.30$\pm$0.70 & 0.30$\pm$0.63 & 4.65$\pm$1.45 & 1.33$\pm$1.40\\
+		single-epochs (F184) & -0.86$\pm$0.72 & -0.69$\pm$0.83 & 2.62$\pm$1.56 & 0.23$\pm$1.53\\
+		single-epochs (H158) & -1.07$\pm$0.62 & -1.61$\pm$0.66 & 2.83$\pm$1.35 & 2.33$\pm$1.22\\
 		\hline

### 2021-11-09 roman_metacal.tex
updates

@@
 We investigate the performance of the \textsc{metacalibration} in the framework of the \emph{Nancy Grace Roman} Space Telescope (\emph{Roman}) image simulations.
-Compared with the non-calibrated results from the previous work, \textsc{metacalibration} can significantly reduce the shear calibration bias.
-Exploring shear bias is a robust way to test the requirements of the instrument and the overall weak lensing survey strategy.
+Measuring shear bias is a conclusive way to confirm that the requirements of the instrument and the overall weak lensing survey strategy are met, and that none of the processes in image simulations biases the science with real data.
 The weak lensing program of \emph{Roman} mission requires the galaxy shapes to be calibrated within about 0.03\%.
-To reach this goal, we can test our calibration scheme with these simulations and can isolate the sources where these residual shear biases arise.
-We incorporate \textcolor{red}{several new updates that are more realistic} and necessary to calibrate shear with a better precision relative to the previous version of the simulations.
-Without the coadditions of the single epoch images, across all three filters we are able to achieve the multiplicative bias of 0.70 per cent within 1.8 $\sigma$.
-Meanwhile, average additive bias is not consistent with zero due to the strong correlation with the input PSF for one of the spin-2 component directions.
-This additive bias is worse for the coadded images, while \textcolor{red}{the average multiplicative bias for multiband coadds was xxx}.
-We find no evidence that shape calibration becomes worse with decreasing image sampling factor based on the Nyquist sampling theorem.
-Overall, within the current simulation volume, we find that \textsc{metacalibration} can calibrate shapes with zero shear bias on relatively undersampled images that \emph{Roman} will produce.
-In the future, we will need to substantially increase the simulation volume by 8 to reach the accuracy necessary for the program.
+To reach this goal, we can test our calibration process with these simulations and can isolate the sources where these residual shear biases arise.
+We incorporate several new realistic processing-pipeline updates necessary to calibrate shear with a better precision relative to the previous version of the simulations.
+We found that compared with the non-calibrated results from the previous work, \textsc{metacalibration} can significantly reduce the shear calibration bias.
+With the single-epoch images, across all three filters we are able to achieve the multiplicative bias, \textcolor{red}{$m=0.70\%$ within 1.8 $\sigma$ and additive bias, $c=3.37\times10^{-4}$ within xx $\sigma$}.
+$c$ is worse for the coadded images due to the strong correlation with the input PSF while \textcolor{red}{$m=-2.16\%$ for the multiband coadds}.
+In both single-epoch and coadd cases, we find that shape calibration becomes worse with decreasing image sampling factor.
+Overall, within the current simulation volume, \textsc{metacalibration} does not calibrate shapes with zero shear bias on relatively undersampled images that \emph{Roman} will produce.
+In the future, we will need to substantially increase the simulation volume to reach the accuracy necessary for the program.
 \end{abstract}
@@
 These MEDS files contain all objects that are located in the area of the sky partitioned according to a HEALPix of $n_{side}$=512.
-Once the objects are sorted in MEDS files, we pass these multiple exposures with the corresponding PSF to \textsc{ngmix}\footnote{\url{ https://github.com/esheldon/ngmix}} to fit the galaxy shapes with the Gaussian mixture fitting method (\citealt{2014MNRAS.444L..25S}).
+Once the objects are sorted in MEDS files, we pass these multiple exposures with the corresponding PSF to \texttt{ngmix}\footnote{\url{ https://github.com/esheldon/ngmix}} to fit the galaxy shapes with the Gaussian mixture fitting method (\citealt{2014MNRAS.444L..25S}).
 This shape measurement process produces shape catalogs from which the shear calibration bias can be calculated with \textsc{metacalibration}.
@@
 
-    \item \textbf{\textsc{metacalibration} in \textsc{ngmix}}: We implemented \textsc{metacalibration}\footnote{\url{https://github.com/esheldon/ngmix/wiki/Metacalibration}} bootstrapper method, which is a wrapper class to run measurements in the \textsc{ngmix} package and is used extensively to produce weak lensing shape catalog in DES Y3 analysis.
+    \item \textbf{\textsc{metacalibration} in \texttt{ngmix}}: We implemented \textsc{metacalibration}\footnote{\url{https://github.com/esheldon/ngmix/wiki/Metacalibration}} bootstrapper method, which is a wrapper class to run measurements in the \texttt{ngmix} package and is used extensively to produce weak lensing shape catalog in DES Y3 analysis.
 \textsc{metacalibration} process takes place after making coadded images.
-\textsc{ngmix} is able to fit multiple exposures in case for measuring shapes on single-epoch images.
+\texttt{ngmix} is able to fit multiple exposures in case for measuring shapes on single-epoch images.
 With this calibration method, we hope to significantly reduce some of the shear calibration bias Troxel et al.
@@
     \item Finds the wcs of the first exposure of the object.
-    \item Translates the original wcs to a flat wcs, because it produces stable results with \textsc{ngmix}.
+    \item Translates the original wcs to a flat wcs, because it produces stable results with \texttt{ngmix}.
     \item Creates the coadd stamp with 0.8 $\times$ original pixel scale.
@@
 
-Before we calibrate and measure shapes with \textsc{ngmix}, we downsample the high-resolution PSF to the original pixel size.
+Before we calibrate and measure shapes with \texttt{ngmix}, we downsample the high-resolution PSF to the original pixel size.
 Figure \ref{fig:coadd_oversample_res} shows the coadded oversampled PSF and the then-downsampled PSF, and their differences.
-We downsampled the oversampled PSF (128 x 128 pixels) by summing 4 square-pixels and creating the original size PSF (32 x 32 pixels), in order to ensure that the shape fit with \textsc{ngmix} can be processed.
+We downsampled the oversampled PSF (128 x 128 pixels) by summing 4 square-pixels and creating the original size PSF (32 x 32 pixels), in order to ensure that the shape fit with \texttt{ngmix} can be processed.
 Since a better sampled PSF generally enables the shape of the PSF to be more isotropic, we can state that the original PSF can lead to the biased shape measurement from Figure \ref{fig:coadd_oversample_res}.
@@
 
-\subsection{Shape Measurement with \textsc{metacalibration}}
+\subsection{Shape Calibration \& Measurement with \texttt{ngmix}}
 \label{subsec:mcal}
-Once we construct the coadds from the galaxy catalogs to recover the shear signal, we feed them into the \textsc{metacalibration} process.
-The bootstrapper method in \textsc{ngmix} wraps the \textsc{metacalibration} and the shape fit steps.
-The priors passed to the fit are listed below.
+Once we construct the individual galaxy stamp coadds from the MEDS files to recover the shear signal, we feed them into the \textsc{metacalibration} process.
+The bootstrapper method in \texttt{ngmix} wraps the \textsc{metacalibration} and the shape fit processes.
+The priors needed for the fit are listed in Table \ref{tab:priors}.
+We note that we have run \textsc{metacalibration} with \texttt{fitgauss} and \texttt{gauss} parameters for the new PSF model, and we found that it is preferrable to use \texttt{gauss} for our case.
 
@@
 
-Once we have the \textsc{metacalibration} catalog, we can calculate shear calibration bias from the measured object ellipticities, $\vb*{e}$ = ($e_{1}$, $e_{2}$).
-The observed ellipticities can be approximated using a Taylor expansion around the two-component shear, $\vb*{\gamma}=0$.
-Higher terms here can be dropped assuming the gravitational shear is small.
-It is also known that \textsc{metacalibration} works under the same assumption, otherwise the recovered shear would be biased.
+\textsc{metacalibration} creates one unsheared and four artificially-sheared galaxy stamps.
+Each is deconvolved with the input PSF, unsheard or sheared with the gravitational shear of $\gamma=0.01$ in four directions ($+g1$, $-g1$, $+g2$, $-g2$) and re-convolved with a new slightly larger isotropic, Gaussian PSF.
+It is known that \textsc{metacalibration} works under the assumption that the input shear needs to be small, otherwise the recovered shear would be biased.
 It is challenging to find a good input shear that results in higher S/N of an object and unbiased shape measurement.
@@
 Figure \ref{fig:metacal_shear_linear} demonstrates that even with the simple enough simulations \textsc{metacalibration} becomes biased after $g=0.05$ since the assumption is starting to break down.
+
+After processing the images in \textsc{metacalibration} and measuring the shapes in \texttt{ngmix}, we have 5 shape catalogs in each \textsc{metacalibration} shear direction.
+The caveat of calibrating with \textsc{metacalibration} is we can then compute the shear response from these catalogs and compute the calibrated galaxy ellipticities.
+Shear response can be understood as the change in object ellipticities with respect to the change in gravitational shear.
+Mathematically, the observed ellipticities, $\vb*{e}$ = ($e_{1}$, $e_{2}$), can be approximated using a Taylor expansion around the two-component shear, $\vb*{\gamma}=0$.
+Higher terms here can be dropped assuming the gravitational shear is small.
 \begin{equation}
@@
 \end{equation}
-For each redshift bin, the ensemble mean of measured ellipticities $\langle\vb*{e}\rangle$ is computed.
-Since we expect galaxies in the redshift bin to be randomly oriented such that $\langle\vb*{e}\rangle\rvert_{\vb*{\gamma}=0}=0$, we have a relationship between the measured ellipticities and the input shear in the simulations,
+The ensemble mean of measured ellipticities $\langle\vb*{e}\rangle$ can then computed.
+Since we expect galaxies to be randomly oriented such that $\langle\vb*{e}\rangle\rvert_{\vb*{\gamma}=0}=0$, we have a relationship between the measured ellipticities and the input shear in the simulations,
 \begin{equation}
@@
 \end{equation}
-In actual observations, the observable is the galaxy shapes $\langle\vb*{e}\rangle$ and we can take advantage of image simulations and calculate the shear response of the particular calibration technique we employ, and finally compute the gravitational lensing shear signal $\langle\vb*{\gamma}\rangle$.
 
@@
 
-\textsc{metacalibration} creates one unsheared and four artificially-sheared images of each galaxy stamp.
-Each is deconvolved with the original PSF, unsheard or sheared with the gravitational shear of $\gamma=0.01$ in four directions ($+g1$, $-g1$, $+g2$, $-g2$) and re-convolved with a new slightly larger isotropic, Gaussian PSF.
-In our simulation framework, we know the exact input shear and five measured galaxy shapes for each galaxy produced by \textsc{metacalibration} and fitted with the Gaussian mixture method in \textsc{ngmix}.
-We can calculate the ensemble mean of the shear response from the five versions of \textsc{metacalibration} catalog with the equation below.
+With \textsc{metacalibration}, we can compute the shear response from the five versions of \textsc{metacalibration} catalog using the finite difference method.
 
@@
 
-\textcolor{red}{\textsc{ngmix} utilizes xx method to compute the size of the galaxy, while we compute the adaptive moments of objects to measure the shape and size of the input PSF (\citealt{2003MNRAS.343..459H})}.
+\textcolor{red}{\texttt{ngmix} utilizes xx method to compute the size of the galaxy, while we compute the adaptive moments of objects to measure the shape and size of the input PSF (\citealt{2003MNRAS.343..459H})}.
+
+In the actual observations of cosmic shear, the observable is the galaxy shapes $\langle\vb*{e}\rangle$ and we can take advantage of image simulations and calculate the shear response with the calibration algorithms, and finally compute the gravitational lensing shear signal $\langle\vb*{\gamma}\rangle$.
+The shear response is used to compute the shear calibration bias and the bias is used as priors to the cosmological analysis.
 
@@
 In this section, we present the properties of the simulated data products and the shape measurement results from various simulation variants.
-We divide our shape measurements into two categories; single-band and multiband.
+We divide our shape measurement into two categories; single-band and multiband.
 For single-band measurements, in each filter, we measure the shapes from the original single exposures by joint-fitting them.
@@
 We do not make any selection cuts on the simulated catalogs based on measured properties.
-Even so, due to the misestimation of the PSF or low S/N, the Gaussian mixture in \textsc{ngmix} fails to fit about 5\% of all simulated objects, and so the total number of the recovered objects for single-band measurements is, 861,960 for F184, 863,358 for H158, and 859,645 for J129.
+Even so, due to the misestimation of the PSF or low S/N, the Gaussian mixture in \texttt{ngmix} fails to fit about 5\% of all simulated objects, and so the total number of the recovered objects for single-band measurements is, 861,960 for F184, 863,358 for H158, and 859,645 for J129.
 For the multiband (H158+J129+F184) coadd measurements, we measure objects that are found by all of the filters and the total number of the recovered objects is 851,821.
@@
 The mean half-light radii for input and measured galaxies are 0.294 and 0.221 arcsec for H158.
-For these histograms, we are showing the objects with the successful fit in \textsc{ngmix}.}
+For these histograms, we are showing the objects with the successful fit in \texttt{ngmix}.}
     \label{fig:true_properties}
@@
 	\includegraphics[scale=0.34]{ngmix_snr_T.pdf}
-    \caption{add multiband to each window and F184 coadd for PSF properties.}
+    \caption{This shows the distribution histograms of measured galaxy and PSF properties in \texttt{ngmix} for single-band coadd and multiband coadd measurement.
+It includes S/N, galaxy size $T{gal}$, and the shape and size of the PSF.}
     \label{fig:measured_properties}
@@
 
-\subsection{Shape Calibration Bias}
+\subsection{Shear Calibration Bias}
 \label{subsec:shapes}
-We compute the estimated values of multiplicative and additive bias from the recovered shear with \textsc{metacalibration}.
-The results from the complete set of different runs are in Table \ref{tab:bias_summary} and the summary plot can be found in Figure \ref{fig:final_result}.
+We estimate the levels of shear calibration bias associated with calibrating shapes with \textsc{metacalibration} in \emph{Roman} images as described in Sec.
+\ref{subsec:mcal}.
+The multiplicative and additive bias values in texts are the average of $m_{1}$ and $m_{2}$, and $c_{1} and c_{2}$.
+The comprehensive results can be found in Table \ref{tab:bias_summary}.
 
-For the single-band measurements, we can use the sampling factor defined in Equation \ref{eqn:sampling} to visualize the relationship between the sampling factor and the shear bias.
-The sampling factor is an indication of how undersampled the image in the filter is and it is respectively $Q_{J129}=1.01, Q_{H158}=1.23, Q_{F184}=1.44$.
-This was previously explored in \citealt{2021MNRAS.502.4048K}, where they found that the estimates shear bias has a large dependence on the sampling factor.
-We note that we have run \textsc{metacalibration} with \texttt{fitgauss} and \texttt{gauss} parameters for the new PSF model, and we found that it is preferrable to use \texttt{gauss} for our case.
-Hence, from here we present the result that is calibrated with \texttt{gauss} PSF model for \textsc{metacalibration}.
-The multiplicative bias of single-band single-epochs measurements for each filter is, 1.04$\pm$0.47 per cent for J129, -1.30$\pm$0.46 per cent for H158 and -0.40$\pm$0.53 per cent for F184.
-When the coadds of each filter are used, the bias becomes, -0.47$\pm$0.49 per cent for J129, -0.07$\pm$0.45 per cent for H158 and -0.06$\pm$0.61 per cent for F184.
-Coadd results are consistent with zero multiplicative bias within 1 sigma and the signals increase by xx per cent.
-Generally, coadding produces better sampled images as in Figure \ref{fig:single_to_coadd_rgb} and less multiplicative bias than single epochs measurements.
-We can conclude that in the \emph{Roman} simulation we have seen that the multiplicative bias has no strong dependence on the sampling factor.
+For the single-band measurements, we can use the sampling factor defined in Equation \ref{eqn:sampling} to \textcolor{red}{visualize} the relationship between the sampling factor and the shear bias.
+The sampling factor is an indication of how undersampled the image in the filter is and it is respectively $Q_{J129,single}=1.01, Q_{J129,coadd}=1.26, Q_{H158,single}=1.23, Q_{H158,coadd}=1.54, Q_{F184,single}=1.44, Q_{H158,coadd}=1.79$.
+This relationship between sampling factors and shear bias was previously explored in \citealt{2021MNRAS.502.4048K} using \emph{Euclid} simulation with different shape measurement algorithms, where they found that the estimated multiplicative bias has a relatively large dependence on the sampling factor.
+Their result can be extrapolated to our single-band coadd results in Figure \ref{fig:final_result}.
+The multiplicative bias of single-band single-epochs measurements for each filter is, \textcolor{red}{1.04$\pm$0.47 per cent for J129, -1.30$\pm$0.46 per cent for H158 and -0.40$\pm$0.53 per cent for F184}.
+When the coadds of each filter are used, the bias is \textcolor{red}{-0.47$\pm$0.49 per cent for J129, -0.07$\pm$0.45 per cent for H158 and -0.06$\pm$0.61 per cent for F184}.
+We do not see any improvements on the recovered shear when we coadd the single-epoch images.
+We can conclude that in the current \emph{Roman} simulation the multiplicative bias has a slight dependence on the sampling factor.
 
-Meanwhile the measured additive bias is the same level as the Y3 analysis in DES.
-The additive bias of the single-band single-epochs measurements for each filter is, (3.22$\pm$0.92)$10^{-4}$ for J129, (2.63$\pm$0.88)$10^{-4}$ for H158 and (3.25$\pm$1.11)$10^{-4}$ for F184.
-When the coadds of each filter are used, the bias becomes, (3.39$\pm$0.90)$10^{-4}$ for J129, (8.08$\pm$0.87)$10^{-4}$ for H158 and (9.36$\pm$1.10)$10^{-4}$ for F184.
-From the Table \ref{tab:result}, it is worth noting that the coadd process clearly introduces non-trivial additive biases in one direction, but not the other.
+Meanwhile the estimated additive bias is the same order as the Y3 analysis in DES.
+The additive bias of the single-band single-epochs measurements for each filter is, \textcolor{red}{(3.22$\pm$0.92)$10^{-4}$ for J129, (2.63$\pm$0.88)$10^{-4}$ for H158 and (3.25$\pm$1.11)$10^{-4}$ for F184}.
+When the measurements are based on coadds, the bias is, \textcolor{red}{(3.39$\pm$0.90)$10^{-4}$ for J129, (8.08$\pm$0.87)$10^{-4}$ for H158 and (9.36$\pm$1.10)$10^{-4}$ for F184}.
+In Table \ref{tab:result}, it is worth noting that the coadd process mentioned in \ref{subsec:psc} clearly introduces non-trivial additive biases in one direction of the shear, but not the other.
 We believe this is due to the effect of an imperfect PSF model.
-We see this in the Figure xx where the recovered shear has a strong linear dependence on the PSF ellipticity measured by an adaptive moments method.
-The impact of the PSF leakage can be estimated by computing $\rho$-statistics (\citealt{2008A&A...484...67P, 2010MNRAS.404..350R, 2016MNRAS.460.2245J}).
-However, we do not explore the $\rho$-statistics for our PSF model since it is an approximation to accurately represent the features of the instrument, not computed from the real pupil plane images, and the coadding scheme for the 5-year mission has not been finalized yet.
+We see this in the Figure \ref{fig:meanshear} where the recovered shear has a strong linear dependence on the PSF ellipticity measured by an adaptive moments method.
+The impact of the PSF shape and size leakage in the estimated galaxy shapes can be estimated by computing $\rho$-statistics (\citealt{2008A&A...484...67P, 2010MNRAS.404..350R, 2016MNRAS.460.2245J}).
+However, we do not explore the $\rho$-statistics for our PSF model since it is an approximation to accurately represent the features of the instrument, not computed from the real pupil plane images, and the coadding process for the 5-year mission is not yet finalized.
 
-Next, we pressent the results with multiband measurements.
+Finally, we discuss the results with multiband measurements.
 We performed multiband measurements with 3 filters used in the previous measurements.
 One multiband measurement used all of the single epoch images from all the filters and joint-fit the shape of the galaxy.
-The multiplicative and additive bias is, respectively, $m=(-0.70\pm0.39)$ per cent and $c=(2.96\pm0.85)10^{-4}$.
-The other measurement performed the joint-fit on the three coadded image for each filter.
-The multiplicative and additive bias is, respectively, $m=(-0.59\pm0.46)$ per cent and $c=(7.78\pm0.94)10^{-4}$.
-The multiplicative bias is reduced but the additive bias increased due to the imperfect PSF modeling in one of the spin-2 axes.
+The multiplicative and additive bias is, respectively, \textcolor{red}{$m=(-1.34\pm0.67)$ per cent and $c=(2.58\pm1.26)10^{-4}$}.
+This result generally agrees with the single-band single-epochs measurements.
+However, performing the joint-fit over different bandpasses for one galaxy does not necessarily constrain the shape of the object.
+The other measurement performed the joint-fit on the three coadded images for each filter.
+The multiplicative and additive bias is, respectively, \textcolor{red}{$m=(-2.16\pm0.60)$ per cent and $c=(9.24\pm1.22)10^{-4}$}.
+\textcolor{red}{Although coadding produces better sampled images as in Figure \ref{fig:single_to_coadd_rgb} and less multiplicative bias than single-epochs measurements, The multiplicative bias does not represent the average of 3 single-band coadd measurements and we think that...}.
+Overall, as in Figure \ref{fig:meanshear} we do not find any correlation of mean shear against the input and measured properties of the galaxies.
 
@@
 		\textcolor{red}{single-epochs (J129)} & 1.30$\pm$0.70 & 0.30$\pm$0.63 & 4.65$\pm$1.45 & 1.33$\pm$1.40\\
+		single-epochs (H158) & -1.07$\pm$0.62 & -1.61$\pm$0.66 & 2.83$\pm$1.35 & 2.33$\pm$1.22\\
 		single-epochs (F184) & -0.86$\pm$0.72 & -0.69$\pm$0.83 & 2.62$\pm$1.56 & 0.23$\pm$1.53\\
-		single-epochs (H158) & -1.07$\pm$0.62 & -1.61$\pm$0.66 & 2.83$\pm$1.35 & 2.33$\pm$1.22\\
 		\hline
-		\textcolor{red}{single-band coadd with oversampling (H158; w/ noise fix)} & -1.51$\pm$0.68 & -1.41$\pm$0.66 & 14.79$\pm$1.32 & 4.45$\pm$1.42\\
-		\textcolor{red}{single-band coadd with oversampling (J129 w/ noise fix)} & -1.59$\pm$0.64 & -2.31$\pm$0.70 & 11.61$\pm$1.20 & -0.09$\pm$1.34\\
-		\textcolor{red}{single-band coadd with oversampling (F184 w/ noise fix)} & 0.47$\pm$0.80 & -0.59$\pm$0.81 & 12.40$\pm$1.67 & 6.32$\pm$1.82\\
+		\textcolor{red}{single-band coadd (J129)} & -1.59$\pm$0.64 & -2.31$\pm$0.70 & 11.61$\pm$1.20 & -0.09$\pm$1.34\\
+		\textcolor{red}{single-band coadd (H158)} & -1.51$\pm$0.68 & -1.41$\pm$0.66 & 14.79$\pm$1.32 & 4.45$\pm$1.42\\
+		\textcolor{red}{single-band coadd (F184)} & 0.47$\pm$0.80 & -0.59$\pm$0.81 & 12.40$\pm$1.67 & 6.32$\pm$1.82\\
 		\hline
-		\textcolor{red}{multiband single-epochs (gauss) (H158+J129+F184)} & -0.66$\pm$0.58 & -0.74$\pm$0.59 & 4.32$\pm$1.17 & 1.60$\pm$1.16 \\
-		\textcolor{red}{multiband coadd (w/ noise fix)} & -2.16$\pm$0.60 & -2.16$\pm$0.60 & 14.03$\pm$1.13 & 4.44$\pm$1.31\\
+		multiband single-epochs & -1.07$\pm$0.66 & -1.61$\pm$0.67 & 2.83$\pm$1.30 & 2.33$\pm$1.22 \\
+		\textcolor{red}{multiband coadd} & -2.16$\pm$0.60 & -2.16$\pm$0.60 & 14.03$\pm$1.13 & 4.44$\pm$1.31\\
 
@@
 	\end{tabular}
-	\caption{Shear calibration bias for different simulation runs.}
+	\caption{This table compares the shear calibration bias, both multiplicative and additive bias for different simulation runs.}
 	\label{tab:result}
@@
 	\includegraphics[scale=0.5]{final_result.pdf}
-    \caption{The multiplicative ($m$) and additive ($c$) bias of several simulation runs.
-The left panel shows $m$ and $c$ against the sampling factor for each filter.
-The right panel shows the same for multiband fit result.
-The number in the parenthesis gives how many filters are used.
-(3) means J129, H158 and F184 are used, whereas (2) means only J129 and H158 are used.
-Include the definition of sampling factor.
-}
+    \caption{The multiplicative ($m$) and additive ($c$) bias of the single-band coadd measurements. From left data point to the right, they represent each data for J129, H158, F184 bandpasses. }
     \label{fig:final_result}
@@
     \centering
-	\includegraphics[scale=0.34]{H158_meanshear_measured_properties_perbin.pdf}
-    \caption{H158 coadd, add multiband, do delta e.}
+	\includegraphics[scale=0.34]{H158_meanshear_measured_properties_perbin_e1.pdf}
+    \caption{This shows the mean shear residual ($\Delta e_{1}$; $\langle e_{1,measured} \rangle - \langle e_{1,expected} \rangle$) as a function of various properties of galaxies for H158 single-band single-epochs, coadds, and multiband measurements.
+In this plot, the shear response is computed in each bin.
+The properties include the S/N, measured galaxy size $T_{gal,measured}$, input galaxy size $T_{gal,input}$, the shape and size of the input PSF.}
     \label{fig:meanshear}
@@
 
-So far we have seen how \textsc{metacalibration} handles the relatively undersampled \emph{Roman} images without the effect of blending.
-However, it has been found that the galaxy blending at different redshifts could introduce a significant shear-dependent detection bias when calibrated with \textsc{metacalibration} (\citealt{2020ApJ...902..138S}).
-In the future study, we should investigate the impact of blending in the image simulations to verify if \textsc{metacalibration} combined with the new version of \textsc{ngmix} can be the shear calibration algorithm in the real survey.
+We have so far found how \textsc{metacalibration} handles the relatively undersampled \emph{Roman} images without accounting for the effect of blending.
+However, it has been found that the galaxy blending at different redshifts could introduce a significant shear-dependent detection bias when calibrated with \textsc{metacalibration} (e.g., \citealt{2020ApJ...902..138S}).
+In the future study, we will investigate the impact of blending in the image simulations to verify if \textsc{metacalibration} combined with the new version of \texttt{ngmix} can be applied as the shear calibration algorithm in the real survey.
 
+Our team continues to increase the realism of the image simulations in the future.
 In the next generation of the simulations, we would like to add the following updates or upgrade these parts of the simulation.
@@
 
-    \item \textbf{Near-Infrared Detectors}: Incorporate the detector effects measured in the real flight candidate detectors and produce two catalogs with and without them to determine the impact on the final cosmology result.
+    \item \textbf{Near-Infrared Detector Effects}: Incorporate the detector effects measured in the real flight candidate detectors and produce two catalogs with and without them to determine the impact on the final cosmology result.
 
@@
 \end{itemize}
-\textcolor{red}{With these potential changes, we will produce a reference image and shape catalog that can be widely used by other communities.}
+\textcolor{red}{Ongoing work to make a reference survey. }
 
@@
 \label{sec:conclusion}
-We explored the performance of \textsc{metacalibration} methodology with \textsc{psc} coadding scheme to reduce the shear calibration bias in the image simulation framework of the \emph{Roman} Space Telescope.
+We explored the performance of \textsc{metacalibration} shape measurement calibration algorithm with \textsc{psc} coadding scheme to reduce the shear calibration bias in the image simulation framework of the \emph{Roman} Space Telescope.
 Accurately characterizing how much shear bias exists in this framework is required to successfully complete the weak lensing program of the High-Latitude Survey of the \emph{Roman}.
-\par
-
-By coadding the single-epoch images and oversampling the PSF for a better shape fit, we find that shear estimates with \textsc{metacalibration} are slightly biased within 1 sigma but within the mission requirement.
-We conclude that to further constrain the shear calibration bias in the simulation and determine if the \emph{Roman} mission will be able to use the current Stage-III imaging survey schemes, we need more simulation volume well beyond the 2.5 deg$^{2}$ area of the simulated sky.
+By coadding the single-epoch images and oversampling the PSF for a better shape fit, we find that shear estimates with \textsc{metacalibration} are slightly biased within 1 $\sigma$.
+We conclude that to further constrain the shear calibration bias in the simulation and determine if the \emph{Roman} mission will be able to achieve the bias required for the survey without further developing new techniques that the current Stage-III imaging surveys do not use, we need more simulation volume well beyond the 2.5 deg$^{2}$ area of the simulated sky.
 

### 2021-11-18 roman_metacal_v2.tex
v1 to v2

--- 2021-11-09 roman_metacal.tex
@@
 \normalem
-\title[Metacalibration with Roman High-Latitude Imaging Survey]{Weak gravitational lensing shear estimates with \textsc{metacalibration} for the High-Latitude Imaging Survey Program of the \emph{Roman} Space Telescope}
+\title[Metacalibration with The Roman High-Latitude Imaging Survey]{Weak gravitational lensing shear estimates with \textsc{metacalibration} for the \emph{Roman} High-Latitude Imaging Survey}
 
@@
 \begin{abstract}
-We investigate the performance of the \textsc{metacalibration} in the framework of the \emph{Nancy Grace Roman} Space Telescope (\emph{Roman}) image simulations.
-Measuring shear bias is a conclusive way to confirm that the requirements of the instrument and the overall weak lensing survey strategy are met, and that none of the processes in image simulations biases the science with real data.
-The weak lensing program of \emph{Roman} mission requires the galaxy shapes to be calibrated within about 0.03\%.
-To reach this goal, we can test our calibration process with these simulations and can isolate the sources where these residual shear biases arise.
-We incorporate several new realistic processing-pipeline updates necessary to calibrate shear with a better precision relative to the previous version of the simulations.
-We found that compared with the non-calibrated results from the previous work, \textsc{metacalibration} can significantly reduce the shear calibration bias.
-With the single-epoch images, across all three filters we are able to achieve the multiplicative bias, \textcolor{red}{$m=0.70\%$ within 1.8 $\sigma$ and additive bias, $c=3.37\times10^{-4}$ within xx $\sigma$}.
-$c$ is worse for the coadded images due to the strong correlation with the input PSF while \textcolor{red}{$m=-2.16\%$ for the multiband coadds}.
+We investigate the performance of the \textsc{metacalibration} shear calibration framework using image simulations for the \emph{Nancy Grace Roman} Space Telescope (\emph{Roman}) reference High-Latitude Imaging Survey (HLIS).
+These large-scale realistic image simulations are necessary to measure shear bias to confirm that the requirements of the instrument and the overall weak lensing survey strategy are met.
+The weak lensing program of the \emph{Roman} mission requires the galaxy shapes to be calibrated within about 0.03\%.
+To reach this goal, we can test our calibration process with these simulations and ultimately isolate the sources where these residual shear biases arise.
+In this work, we incorporate several new realistic processing-pipeline updates necessary to calibrate shear with a better precision relative to the previous version of the simulations and show first results for the reference HLIS using \textsc{metacalibration}.
+We find that compared with the non-calibrated results from previous work, \textsc{metacalibration} as used in current experiments can significantly reduce the shear calibration bias to the percent level.
+With the single-epoch images, across all three filters we are able to achieve a multiplicative bias \textcolor{red}{$m=0.70\%$ within 1.8 $\sigma$}, while for coadd cutouts, \textcolor{red}{$m=-2.16\%$}.
 In both single-epoch and coadd cases, we find that shape calibration becomes worse with decreasing image sampling factor.
-Overall, within the current simulation volume, \textsc{metacalibration} does not calibrate shapes with zero shear bias on relatively undersampled images that \emph{Roman} will produce.
-In the future, we will need to substantially increase the simulation volume to reach the accuracy necessary for the program.
+Overall, within the current simulation volume, there is evidence that \textsc{metacalibration} as currently implemented will not calibrate shapes with zero shear bias in the \emph{Roman} HLIS and further work on the shear calibration methodology is necessary.
+In the future, we will need to substantially increase the simulation volume to reach the precision necessary for the HLIS.
+\textcolor{red}{insert approx.
+factor of sim size needed}
 \end{abstract}
@@
 
-Since the formulation of the physical cosmological model, more observational evidence has shown that the contents of the universe are mostly in the dark sector (\citealt{2020A&A...633A..69H, 2018PhRvD..98d3528T, 2019PhRvL.122q1301A, 2019PASJ...71...43H, 2021A&A...645A.104A}).
-Within the sector, dark energy accounts for the accelerating expansion of the universe (e.g., \citealt{1998AJ....116.1009R, 1999AIPC..478..129P}) and the combination of dark energy and dark matter which only interacts with non-relativistic matter are responsible for the growth of the large-scale structure (\citealt{2015RPPh...78h6901K, 2017grle.book.....D}).
-The growth can be studied by carefully reconstructing the paths of the light leaving distant galaxies and going through the region where masses concentrate in the universe; this physical phenomenon is called gravitational lensing.
+Since the formulation of a physical cosmological model, more observational evidence has shown that the contents of the universe are mostly in the dark sector (\citealt{2020A&A...633A..69H, 2018PhRvD..98d3528T, 2019PhRvL.122q1301A, 2019PASJ...71...43H, 2021A&A...645A.104A}).
+Within this sector, dark energy accounts for the accelerating expansion of the universe (e.g., \citealt{1998AJ....116.1009R, 1999AIPC..478..129P}) and the combination of dark energy and dark matter are responsible for the observed growth of large-scale structure (\citealt{2015RPPh...78h6901K, 2017grle.book.....D}).
+The growth can be studied by carefully reconstructing the paths of the light leaving distant galaxies and going through the regions where mass concentrates in the universe; this physical phenomenon is called gravitational lensing.
 “Weak” gravitational lensing causes a slight distortion to intrinsic galaxy shapes when observed from the Earth.
-By detecting millions of these gravitationally lensed galaxies and computing their distortion levels, we can explore the matter density and the amplitude of matter fluctuation in the universe (e.g., \citealt{2001PhR...340..291B}).
-Measuring these quantities eventually help us learn the history of the development of the large-scale structure in the universe.
-For that reason, weak lensing is and will continue to be one of the powerful probes in the current and next-decade imaging surveys to constrain cosmological parameters with high precision.
+By detecting millions of these gravitationally lensed galaxies and computing their ensemble distortion levels, we can explore the dark matter density and the amplitude of matter fluctuation in the universe (e.g., \citealt{2001PhR...340..291B}).
+Measuring these quantities eventually helps us learn about the history of the development of the large-scale structure in the universe.
+For that reason, weak lensing is one of the most powerful probes in current and near-future imaging surveys to constrain cosmological parameters with high precision.
 \par
 
-Due to the subtlety in the lensing effect and its systematics dominant nature in the “weak” regime, observational efforts have been challenging.
-Over the past decade, large international collaborations such as the Dark Energy Survey\footnote{\url{http://www.darkenergysurvey.org/}} (DES: \citealt{2005astro.ph.10346T}), the Hyper Supreme-Cam\footnote{\url{http://hsc.mtk.nao.ac.jp/ssp/}} (HSC: \citealt{2018PASJ...70S...4A}), and the Kilo-Degree Survey\footnote{\url{http://kids.strw.leidenuniv.nl/}} (KiDS) have been successful at constraining the cosmological parameters, and the precision in calibrating the shapes of distant galaxies has reached a few percent (\citealt{2020arXiv201103408G, 2020arXiv201208567M, 2021A&A...645A.105G}).
-As we cover more areas in the sky and develop better tools (observatories and algorithms), we find more galaxies and we have already reached to the point where statistical and systematic uncertainties are comparable.
-Thus, the next-decade legacy surveys, the Stage IV surveys (\citealt{2006astro.ph..9591A}) such as Euclid\footnote{\url{ http://sci.esa.int/euclid}} (Euclid Study Scientist \& the Science Advisory Team 2010), the Vera C.
-Rubin Observatory Legacy Survey of Space and Time\footnote{\url{ http://www.lsst.org}} (LSST: \citealt{2009arXiv0912.0201L, 2019ApJ...873..111I}), and \emph{Nancy Grace Roman} Space Telescope\footnote{\url{https://roman.gsfc.nasa.gov}} (\emph{Roman}: \citealt{2015arXiv150303757S}) require even better control of systematics.
-In order to manage the systematic uncertainties, we must develop realistic image simulations, apply the pre-existing shape measurement on the simulated images, and determine any potential systematic effects and build the strategy of mitigating them.
+Due to the subtlety in the lensing effect and its systematics-dominant nature in the weak regime, observational efforts have been challenging.
+Over the past decade, large international collaborations such as the Dark Energy Survey\footnote{\url{http://www.darkenergysurvey.org/}} (DES: \citealt{2005astro.ph.10346T}), the Hyper Supreme-Cam\footnote{\url{http://hsc.mtk.nao.ac.jp/ssp/}} (HSC: \citealt{2018PASJ...70S...4A}), and the Kilo-Degree Survey\footnote{\url{http://kids.strw.leidenuniv.nl/}} (KiDS)\textcolor{red}{insert cite like others} have been successful at constraining the cosmological parameters, and the precision in calibrating the shapes of distant galaxies has reached a few percent (\citealt{2020arXiv201103408G, 2020arXiv201208567M, 2021A&A...645A.105G}).
+As we observe more area of the sky and develop better tools (observatories and algorithms), we detect more galaxies, and have already reached the point where statistical and systematic uncertainties are comparable.
+Thus, near-future Stage IV surveys (\citealt{2006astro.ph..9591A}) such as Euclid\footnote{\url{ http://sci.esa.int/euclid}} (Euclid Study Scientist \& the Science Advisory Team 2010), the Vera C.
+Rubin Observatory Legacy Survey of Space and Time\footnote{\url{ http://www.lsst.org}} (\emph{Rubin}: \citealt{2009arXiv0912.0201L, 2019ApJ...873..111I}), and \emph{Nancy Grace Roman} Space Telescope\footnote{\url{https://roman.gsfc.nasa.gov}} (\emph{Roman}: \citealt{2015arXiv150303757S}) require even better control of systematics.
+In order to understand the systematic uncertainties we face, we must develop realistic image simulations, apply pre-existing shape measurement to the simulated images, and determine any potential residual systematic effects and build a strategy for modifying the calibration methodology to mitigate them.
 
-Based on our current knowledge, systematic biases for weak lensing science, both observational and astrophysical, could occur throughout imaging surveys (e.g., \citealt{2018ARA&A..56..393M}).
-Particularly, observational systematics can be found in,
+Based on our current knowledge, systematic biases for weak lensing science, both observational and astrophysical, can occur at all stages of the imaging survey (e.g., \citealt{2018ARA&A..56..393M}).
+Particularly, observational systematics can be due to:
 \begin{itemize}
-    \item observing strategy
-    \item instrumentation effects such as Brighter-Fatter Effect
-    \item post-processing pipeline such as image coaddition and object detection
+    \item inhomogeneous observing strategy,
+    \item instrumentation effects,
+    \item post-processing pipelines such as image coaddition and object detection.
 \end{itemize}
 
-In this study, we focus on shear calibration bias, which describes the relationship between gravitational lensing shear and measured galaxy shapes.
-In the limit of weak lensing ($\lvert\gamma\rvert\ll1$), the ensemble average of ellipticities $\langle e \rangle$ of galaxy shapes is directly related to the shear field $\gamma$, and the estimated shear can be written as a linear model with multiplicative ($m_{i}$) and additive bias ($c_{i}$) as described in the equation below.
-(\citealt{2006MNRAS.368.1323H, 2006MNRAS.366..101H, 2007MNRAS.376...13M})
+In this study, we focus on the shear calibration bias, which describes the relationship between gravitational lensing shear $\gamma$ and measured galaxy shapes.
+In the limit of weak lensing ($\lvert\gamma\rvert\ll1$) and random intrinsic galaxy shapes, the ensemble average of ellipticities $\langle e \rangle$ of galaxy shapes is directly related to the shear field $\gamma$, and the estimated shear can be written as a linear model with multiplicative ($m_{i}$) and additive bias ($c_{i}$) as described in the equation below (\citealt{2006MNRAS.368.1323H, 2006MNRAS.366..101H, 2007MNRAS.376...13M})
 \begin{equation}
@@
 where i=(1,2) and $\gamma^{obs}_{i}$ is the two-component observed shear after calibrations and $\gamma^{true}_{i}$ is the true shear.
-The bias arises for various reasons.
-For space-based surveys, the bias can be mainly introduced in places such as PSF modelling, blending, and the undersampling of the image (e.g., \citealt{2018ARA&A..56..393M}).
-Additionally, complex detector effects such as brighter-fatter effect are the potential sources of bias (\citealt{2013MNRAS.429..661M}), where it is shown that for \emph{Roman} the effect of persistence will not be an issue (\citealt{2021arXiv210610273L}).
-Qualitatively, if the recovered shear is biased by 1$\%$ (m=0.01), $S_{8} = \sigma_{8} \sqrt{\Omega_{m}/0.3}$ would be biased about 1.5$\%$ in the final cosmology result.
-Thus, quantifying these biases before the real survey is extremely important.
+The bias can be introduced in places such as PSF modeling, blending, and the undersampling of the image (e.g., \citealt{2018ARA&A..56..393M}).
+Additionally, complex detector effects such as the brighter-fatter effect are potential sources of bias (\citealt{2013MNRAS.429..661M}), while it has been shown that for \emph{Roman} the effect of persistence will not be an issue (\citealt{2021arXiv210610273L}).
+Qualitatively, if the recovered shear is biased by 1$\%$ (m=0.01), $S_{8} = \sigma_{8} \sqrt{\Omega_{m}/0.3}$ could be biased about 1.5$\%$ in the final cosmology result.
+Thus, quantifying and correcting these biases before the real survey begins is extremely important.
 \par
@@
 Several shear calibration and bias mitigation efforts have been proposed by STEP (\citealt{2006MNRAS.368.1323H, 2007MNRAS.376...13M}) and GREAT (\citealt{2010MNRAS.405.2044B, 2013ApJS..205...12K, 2015MNRAS.450.2963M}) challenges, to meet the requirements for the current imaging surveys.
-In particular, one of the state-of-the-art self-calibration methods, \textsc{metacalibration} (\citealt{2017arXiv170202600H, 2017ApJ...841...24S}) has been shown to be able to reduce the significant of shear bias.
-It has also confirmed that the shear can be calibrated with \textsc{metacalibration} at a-few-percent level in DES (\citealt{2018MNRAS.481.1149Z, 2020arXiv201103408G}), without accounting for galaxy blending.
-Tackling the issue of blending is on the way of DES Y6 analysis with the shear-dependent detection and calibration technique (\textsc{metadetect}; \citealt{2020ApJ...902..138S}).
-While the major advantage of \textsc{metacalibration} is that it can be directly applied upon real galaxy images, which does not depend on galaxy morphology in simulations, the limitations for future surveys are not well-known.
-One possible limitation might lie in the effect of the undersampled images, because future space-based surveys like \emph{Euclid} and \emph{Roman} have such a small pixel scale that galaxy images will not be Nyquist sampled at a native resolution (\citealt{2013PASP..125.1496S}) based on the Nyquist-Shannon Sampling Theorem.
+In particular, one of the state-of-the-art self-calibration methods, \textsc{metacalibration} (\citealt{2017arXiv170202600H, 2017ApJ...841...24S}) has been shown to be able to substantially reduce the significance of shear bias.
+It has been confirmed that shear can be calibrated with \textsc{metacalibration} at the few-percent level in DES (\citealt{2018MNRAS.481.1149Z, 2020arXiv201103408G}), without accounting for galaxy blending and detection.
+Tackling the issue of blending/detection is one key step forward for the DES Y6 analysis and preparatory Rubin LSST work with the shear-dependent detection and calibration technique (\textsc{metadetect}; \citealt{2020ApJ...902..138S}).
+While the major advantage of \textsc{metacalibration} is that it can be directly applied to real galaxy images without needing to rely on an ensemble calibration from image simulations, limitations for future surveys are not well-known.
+
+One possible limitation might lie in the effect of undersampled images in space-based misssions like \emph{Euclid} and \emph{Roman}, which have such a small pixel scale that images will not be Nyquist sampled in the near-infrared at the detector pixel scale (\citealt{2013PASP..125.1496S}) based on the Nyquist-Shannon Sampling Theorem.
 We define the sampling factor of each filter in \emph{Roman} to be,
@@
 where $\lambda_{min}$ is the shortest wavelength of the incident light in the filter, $N_{f}$ is the focal ratio of the telescope ($N_{f}=7.8$ for \emph{Roman}) and $p$ is the pixel spacing of the sensor ($p=10\mu m$ for \emph{Roman}).
-The image with the sampling factor, $Q < 2$, is not Nyquist sampled and reffered to as the undersampled image.
-It is problematic to measure galaxy shapes solely from the undersampled images, because the \emph{Roman} PSF that will be used to recover the shapes is also undersampled and has a complex structure, not simply Gaussian.
-\textcolor{red}{It is, therefore, necessary to build a robust strategy that can reconstruct better sampled PSF to allow unbiased shape measurement.
-}
+An image with sampling factor $Q < 2$ is not Nyquist sampled (i.e., undersampled).
+The PSF needs to be interpolated and estimated from well-sampled images to deconvolve and measure shapes with, because the \emph{Roman} PSF has a complex structure that cannot be captured in the original undersampled images.
+It is, therefore, necessary to build a robust strategy to reconstruct well-sampled images to estimate the PSF to allow unbiased shape measurement.
+Recently, Kannawadi et al.
+(2021) addressed this potential issue of the limitations of \textsc{metacalibration} on undersampled images in \emph{Euclid} image simulations.
+They found that for the \emph{Euclid} mission the shear estimate is biased by about 1$\%$ (\citealt{2021MNRAS.502.4048K}).
+It is mentioned that their result could be extended to the \emph{Roman} mission due to similarities in the instruments and for \emph{Roman} they predicted the multiplicative bias was more than 1\%.
+They show that these effects can be mitigated using additional weighting kernels in the measurement.
 
-Recently, Kannawadi et al.
-(2021) addressed this potential issue of the limitations of \textsc{metacalibration} on undersampled images on \emph{Euclid} image simulations.
-They found that for \emph{Euclid} mission the shear estimate is biased about 1$\%$ (\citealt{2021MNRAS.502.4048K}).
-It is mentioned that their result could be extended to the \emph{Roman} mission due to their similarities in the instruments and for \emph{Roman} they predicted the multiplicative bias was more than 1\% for H158 and F184 filters.
-Regardless of this extended result, we should validate if \textsc{metacalibration} is unbiased with the image simulations specifically made for the \emph{Roman} mission.
-Our work is based on the image simulation suite of the \emph{Roman} Space Telescope developed by \citet{2021MNRAS.501.2044T}, where we render star and galaxy images from \texttt{GalSim}\footnote{\url{ https://github.com/GalSim-developers/GalSim}} (\citealt{2015A&C....10..121R}).
-With a few simulation updates and an implementation of \textsc{metacalibration}, we can start to explore if the shear calibration goal of the High-Latitude Survey program for \emph{Roman} ($m=~3.2\times10^{-4}$) (\citealt{2019BAAS...51c.341D}) can be achieved.
+In this work, we explore how \textsc{metacalibration} performs using coadd images at higher resolution, taking advantage of the dithering of images in the reference HLIS.
+We use an updated suite of image simulations specifically made for the \emph{Roman} reference HLIS mission.
+Our work is based on the image simulation suite for the \emph{Roman} Space Telescope developed by \citet{2021MNRAS.501.2044T}, where we render star and galaxy images using \texttt{GalSim}\footnote{\url{ https://github.com/GalSim-developers/GalSim}} (\citealt{2015A&C....10..121R}).
+We describe several important updates to the simulation capabilities and realism following \cite{2021MNRAS.501.2044T}.
+We also implement for the first time \textsc{metacalibration} using the simulated imaging, so that we can start to explore if the shear calibration goals of the HLIS for \emph{Roman} ($m=~3.2\times10^{-4}$) (\citealt{2018arXiv180403628D}) can be achieved with current \textsc{metacalibration} pipelines,\footnote{We limit the study to \textsc{metacalibration} for now, since we can extract unblended cutouts of objects in our simulations.} or will require substantial additional development.
 \par
@@
 \label{sec:sims}
-In this section, we briefly summarize the full simulation details from building a truth catalog to measuring galaxy shapes. Then we describe the simulation updates that are implemented for this work.
-\subsection{Simulation Summary}
-\label{subsec:imsim}
-The base of our image simulations of the \emph{Roman} Space Telescope is the \emph{Roman} simulation suite\footnote{\url{ https://github.com/matroxel/roman_imsim}} developed by \citet{2021MNRAS.501.2044T}, which renders realistic galaxy and star images on 18 Sensor-Chip Assemblies (SCAs) of a 2.5$\times$2.5 deg$^{2}$ patch of the sky provided the observing strategy for the 5-year reference mission and Cycle7 specifications\footnote{\url{https://roman.gsfc.nasa.gov/science/Roman_Reference_Information.html}}.
-We begin by creating a truth catalog using the simulated galaxy distribution from the Buzzard simulation (\citealt{2019arXiv190102401D}), photometric galaxy catalog sampled from the CANDELS survey (e.g., \citealt{2019ApJ...877..117H}), and Milky Way simulation (Galaxia; \citealt{2011ApJ...730....3S}) for star positions and magnitudes.
-Then, the following properties are applied to each galaxy.
+The base of our image simulations of the \emph{Roman} Space Telescope is the \emph{Roman} simulation suite\footnote{\url{ https://github.com/matroxel/roman_imsim}} developed by \citet{2021MNRAS.501.2044T}, which renders realistic galaxy and star images on 18 Sensor-Chip Assemblies (SCAs) of a 2.5$\times$2.5 deg$^{2}$ patch of the sky following the observing strategy for the 5-year reference mission and Cycle7 instrument specifications\footnote{\url{https://roman.gsfc.nasa.gov/science/Roman_Reference_Information.html}}.
+We begin by creating a truth catalog using the simulated galaxy distribution from the Buzzard simulation (\citealt{2019arXiv190102401D}), a photometric galaxy catalog sampled from the CANDELS survey (e.g., \citealt{2019ApJ...877..117H}), and a Milky Way simulation (Galaxia; \citealt{2011ApJ...730....3S}) for star positions and magnitudes.
+Then, the following properties are applied to each galaxy:
 \begin{itemize}
-    \item positions (RA, Dec)
-    \item photometries for each \emph{Roman} filter (F184/H158/J129/Y106)
-    \item intrinsic galaxy shapes and random orientations
-    \item flux ratios of de Vaucouleurs bulge, exponential disk, and star-forming knots
-    \item artificial gravitational lensing shears
+    \item positions (RA, Dec),
+    \item flux within each \emph{Roman} filter (F184/H158/J129/Y106),
+    \item intrinsic galaxy shapes and random orientations,
+    \item flux ratios of de Vaucouleurs bulge, exponential disk, and star-forming knots, and
+    \item artificial gravitational lensing shears.
 \end{itemize} 
-Within the identical realizations of the simulation, we produce four truth catalogs using four sets of gravitational shears ($e_{1}$, $e_{2}$)=\{(+0.02, 0.00), (-0.02, 0.00), (0.00, +0.02), (0.00, -0.02)\}.
-This approach helps us to reduce shape and measurement noise when taking the difference in recovered shapes to compute multiplicative bias (\citealt{2019A&A...621A...2P}).
+Within four identical realizations of the simulation, we use four sets of gravitational shears ($e_{1}$, $e_{2}$)=\{(+0.02, 0.00), (-0.02, 0.00), (0.00, +0.02), (0.00, -0.02)\}.
+This approach helps us to reduce shape and measurement noise when taking the difference in recovered shapes to compute the multiplicative bias (\citealt{2019A&A...621A...2P}).
 
 The next step of the process is to create postage stamps and SCA images using \texttt{GalSim}.
-In this stage, Point-Spread Function (PSF) is convolved with the stamps.
-Here, the \emph{Roman} PSF is rendered using the \texttt{galsim.roman} module under \texttt{GalSim}, which has implemented \emph{Roman}-specific instrument properties such as the PSF and World Coordinate System (WCS).
-The module is able to estimate an object position on the sky in RA, Dec using the \emph{Roman} WCS and produce the \emph{Roman} PSF which, for example, correctly describes the diffraction spikes pattern made by the struts and camera in the pupil plane.
+In this stage, the point-spread function (PSF) is convolved with the stamps.
+Here, the \emph{Roman} PSF is rendered using the \texttt{galsim.roman} module under \texttt{GalSim}, which has implemented \emph{Roman}-specific instrument properties such as the PSF and World Coordinate System (WCS) for a given telescope pointing, rotation angle, and SCA.
 
-After we generate the object stamps across all the SCAs and pointings, we create Multi-Epoch Data Structure (MEDS) files in which each unique object dictionary contains information of all the exposures.
+After we generate the object stamps across all the SCAs and pointings, we create Multi-Epoch Data Structure (MEDS) files in which each unique object dictionary contains information of all the exposures it appears in.
 These MEDS files are generated according to the Hierarchical Equal Area isoLatitude Pixelisation (HEALPix) of $n_{side}=512$.
-These MEDS files contain all objects that are located in the area of the sky partitioned according to a HEALPix of $n_{side}$=512.
-Once the objects are sorted in MEDS files, we pass these multiple exposures with the corresponding PSF to \texttt{ngmix}\footnote{\url{ https://github.com/esheldon/ngmix}} to fit the galaxy shapes with the Gaussian mixture fitting method (\citealt{2014MNRAS.444L..25S}).
+They contain all objects that are located in that region of the sky partitioned according HEALPixel.
+\textcolor{red}{add healpix reference} Once the objects are sorted in MEDS files, we pass these multiple exposures with the corresponding PSFs to \texttt{ngmix}\footnote{\url{ https://github.com/esheldon/ngmix}} to fit the galaxy shapes with the Gaussian mixture fitting method (\citealt{2014MNRAS.444L..25S}).
 This shape measurement process produces shape catalogs from which the shear calibration bias can be calculated with \textsc{metacalibration}.
@@
     \caption{The rotation of the Roman PSF produced from the \texttt{galsim.roman} module.
-Position angle (PA) which determines the rotation of the telescope is $0^{\circ}$ and $30^{\circ}$.
-The rotation of the PSF is particularly important when an object has multiple exposures and needs to be coadded.
-If each galaxy image is rotated but each PSF is not, the coadded PSF would have a particular pattern and its shape would not be averaged down.
-By correctly rotating the PSF that is convolved with galaxy images, the effect of the PSF on the recoverd galaxy shape will be less.}
+The position angle (PA) which determines the rotation of the focal plane is $0^{\circ}$ and $30^{\circ}$.
+The rotation of the PSF is particularly important when an object has multiple exposures.
+As more exposures are rotated relative to one another on the sky, the average impact of the PSF will be rounder.
+This will translate to a substantially less-elliptical coadd PSF.}
     \label{fig:psfrot}
@@
 	\vspace*{-10mm}
-    \caption{The top row shows the first entry of the single epoch images and its coadded image, single and coadded oversampled PSF for an object with low signal-to-noise ratio (S/N=9.69).
-The bottom row shows the same for an object with high signal-to-noise ratio (S/N=1552.97).}
+    \caption{The top row shows the first entry of the single epoch images and its coadded image, and the corresponding single-epoch and coadded oversampled PSF images for an object with low signal-to-noise ratio (S/N=9.69).
+The bottom row shows the same for an object with high signal-to-noise ratio (S/N=1552.97).
+\textcolor{red}{is snr in single-epoch or coadd?}}
     \label{fig:singlecoadd}
@@
 
-\subsection{Simulation Updates}
-In order to accomplish science goals, and build and test the pipelines of weak lensing program in \emph{Roman}, we must keep updating the simulations to be more realistic.
-We have implemented and made updates to the following parts of the simulation framework to be able to measure unbiased shapes with \textsc{metacalibration}.
+\subsection{Updates to Simulation Capabilities}
+In order to accomplish the science goals, and build and test weak lensing calibration pipelines for in \emph{Roman}, we have continued to update the realism of our image simulations.
+We have implemented and made updates to the following parts of the simulation framework to be able to better test shear calibration using \textsc{metacalibration}.
 \begin{itemize}
@@
     \item \textbf{Saturation Cuts}:
-    We have implemented the pixel saturation of 100,000 electrons.
-This value is an approximate pixel saturation but in the next generation of the simulations we will use the true saturation from the flight candidate detectors.
+    We have implemented a pixel saturation limit of 100,000 electrons.
+This value is an approximate pixel saturation level, but in the next generation of the simulations we will use a more accurate pixel saturation limit measured directly from the flight candidate detectors.
 
     \item \textbf{Rotation of the \emph{Roman} PSF on the sky}:
-    In the study by Troxel et al.
-(2021), the rotations of the \emph{Roman} PSF with respect to the telescope rotation were not engaged properly by \texttt{galsim.roman} module.
-Since a non-rotating PSF could trigger a preferred direction in the shapes when being deconvolved, we believe that this contributed to the non-zero multiplicative bias result.
-There has been an update in \texttt{galsim.roman} module to correctly rotate the PSF given the WCS on the SCA.
-Figure \ref{fig:psfrot} shows a toy PSF of the same pointing but with a different rotation angle of the telescope.
+    In the study by \textcolor{red}{Troxel et al.
+(2021)}, the rotations of the \emph{Roman} PSF with respect to the telescope rotation were not properly applied by the \texttt{galsim.roman} module.
+Since a non-rotating PSF produces an artificial preferred direction, which can translate to galaxy shapes through errors in the process of deconvolvution, properly accounting for the averaging of the PSF orientation across exposures due to the survey dithering strategy is essential for a realistic shear calibration estimate.
+There has been an update in the \texttt{galsim.roman} module to correctly rotate the PSF given the WCS of the SCA in a given telescope pointing.
+Figure \ref{fig:psfrot} shows an example of how the PSF for one SCA changes with the rotation angle of the telescope.
 
     \item \textbf{Single-band and Multiband Coadds}: 
-    We have added and modified the postage stamp coadds (\texttt{psc}) algorithm\footnote{\url{https://github.com/esheldon/psc}} to create coadditions of single-epoch postage stamps.
-Coadds are usually performed to enhance the signal-to-noise ratio (S/N) of an object and mitigate the measurement noise.
-If we take advantage of fitting an object in the coadd instead of fitting multiple images of each object in each filter, we can save a factor of 6 in computing time, which is the average number of exposures from the reference survey.
-Additionally, coadding is one way to reduce the effect of the undersampling of the images since the coadd is naturally better sampled.
-For these reasons, we must utilize a coadding scheme for the \emph{Roman} galaxies.
-The detailed overview of the coadd process in \texttt{psc} is in Sec.
+    We have used the postage stamp coadds (\texttt{psc}) algorithm\footnote{\url{https://github.com/esheldon/psc}} to create coadditions of single-epoch postage stamps of individual objects.
+Coadds are usually performed to enhance the signal-to-noise ratio (S/N) of an image and mitigate the impacts of measurement noise, while allowing for better sampling of the image if the overlapping images are dithered.
+However, it is challenging to create a robust, continuous coadd PSF model over an entire image.
+This is mitigated if we instead construct small, local coadds (at the size of an object postage stamp cutout in this work), which is a method also utilized in \textsc{metadetection}.
+If we take advantage of fitting an object in the coadd instead of fitting multiple images of each object in each filter, we can save a factor of approx.
+six in computing time, which is the average number of exposures from the reference survey.
+Additionally, coadding is one way to reduce the effect of the undersampling of the images since the coadd can be better sampled due to dithering.
+For these reasons, we explore utilizing a coadding scheme for the \emph{Roman} galaxies.
+The detailed overview of the coadd process in \texttt{psc} is described in in Sec.
 \ref{subsec:psc}.
 
-    \item \textbf{\textsc{metacalibration} in \texttt{ngmix}}: We implemented \textsc{metacalibration}\footnote{\url{https://github.com/esheldon/ngmix/wiki/Metacalibration}} bootstrapper method, which is a wrapper class to run measurements in the \texttt{ngmix} package and is used extensively to produce weak lensing shape catalog in DES Y3 analysis.
-\textsc{metacalibration} process takes place after making coadded images.
-\texttt{ngmix} is able to fit multiple exposures in case for measuring shapes on single-epoch images.
-With this calibration method, we hope to significantly reduce some of the shear calibration bias Troxel et al.
-(2021) measured.
+    \item \textbf{\textsc{metacalibration} in \texttt{ngmix}}: We implemented the \textsc{metacalibration}\footnote{\url{https://github.com/esheldon/ngmix/wiki/Metacalibration}} bootstrapper method, which is a wrapper class to run measurements in the \texttt{ngmix} package and was used to produce the weak lensing shape catalog in the DES Y3 analysis \textcolor{red}{citation}.
+The \textsc{metacalibration} process can be performed on single-epoch or coadd images in each bandpass.
+With this calibration method, we hope to significantly reduce some of the shear calibration bias \textcolor{red}{Troxel et al.
+(2021)} measured in order to make comparisons of effects contributing to the bias more realistic and meaingful as we explore future \emph{Roman} pipeline development.
 The detailed overview of \textsc{metacalibration} can be found in Sec.\ref{subsec:mcal}.
@@
 
-\section{Post-catalog Processes}
+\section{Coadd and shear calibration pipelines}
 \label{sec:methods}
-Our goal is to show that the recovered shapes with \textsc{metacalibration} are non-biased.
-In order to do so, we need to build a measurement pipeline within the current simulation framework that contributes to the final measurement.
-In this section, we present in detail how coadds are produced with \texttt{psc} from the undersampled single-epoch images, how \textsc{metacalibration} calibrates shapes, and how we measure the shear calibration bias from the \textsc{metacalibration} catalog.
+Our goal is to test whether the recovered shapes with \textsc{metacalibration} are non-biased for \emph{Roman}.
+In order to do so, we need to build measurement pipelines within the current simulation framework that produces a final calibrated shear measurement.
+In this section, we present in detail how coadd images are produced with \texttt{psc} from the undersampled single-epoch images and how \textsc{metacalibration} is implemented to calibrates the measured shear using the \textsc{metacalibration} catalog.
 
@@
 \label{subsec:psc}
-Coaddition is the process that reconstructs a Nyquist-sampled image out of multiple exposures of an object.
-While this process can benefit in increasing the S/N value of an object and reducing the impact of pixel noise, several challenges need to be addressed for images taken with telescopes that can rotate.
-When the rotation is introduced, this coadding process becomes more complex to interpolate the image to stack pixel grid.
-While coaddition could introduce systematic bias due to the complexity of the original PSF and its interpolation scheme, the bias with the undersampled images can be overcome \textcolor{red}{by the combinations of the effective coadding process and the careful treatment of the input PSF}.
-We describe our coaddition pipeline that is based on \texttt{psc}.
+Coaddition is the process of summing information from multiple overlapping images.
+If the single-epoch images are dithered, a Nyquist-sampled image can be constructed out of multiple exposures of an object.
+While this process can also be beneficial in increasing the S/N value of an object and reducing the impact of pixel noise, several challenges need to be addressed for images taken with telescopes that can rotate.
+When rotation is introduced, this coadding process becomes more complex to interpolate the image to stack a pixel grid.
+While coaddition can introduce new challenges and potential biases due to the complexity of coadding the original PSF and its interpolation scheme, the bias due to the undersampling of the original images can be mitigated by appropriately coadding dithered images.
 
-We reconstruct the Nyquist-sampled image from multiple exposures in MEDS files.
-For the coaddition of the PSF, we choose to coadd the image with the oversampled PSF.
-We oversample the original PSF by a factor of 4 to simulate the better sampled PSF that \emph{Roman} will eventually produce when it constructs the PSF from the full focal plane.
-It will be highly resolved than native pixel scale.
-For each exposure of the object we render the \emph{Roman} PSF with a stamp size of 32 pixels at the galaxy centroid, not the image centroid.
-We modified the original code to improve performance of the \textsc{metacalibration} process later, and these modifications are listed below with the general coadding process in \texttt{psc}.
+We reconstruct a better-sampled coadd image from multiple exposures in MEDS files.
+For the coaddition of the PSF, we choose to coadd the image with an oversampled PSF `model'.
+We oversample the original PSF by a factor of 4 to simulate the better sampled PSF model that will eventually be possible to construct during the \emph{Roman} mission.
+For each exposure of the object we render the \emph{Roman} PSF with a stamp size of 32 pixels at the galaxy centroid.
+We modified the original \texttt{psc} code to improve performance for this \emph{Roman} study, and these modifications are listed below with the general coadding process in \texttt{psc}.
 
@@
     \item Finds the wcs of the first exposure of the object.
-    \item Translates the original wcs to a flat wcs, because it produces stable results with \texttt{ngmix}.
+    \item Translates the original wcs to a flat wcs, because it produces more stable results with \texttt{ngmix}.
     \item Creates the coadd stamp with 0.8 $\times$ original pixel scale.
-We scale the original pixel scale of the final coadd stamp to minimize the effect of undersampling.
-We noticed that too much oversampling can introduce the artifacts into the structure of the PSF.
-    \item Creates the interpolated image with \texttt{GalSim} with the center offset for each image with \texttt{lanczos3} resampling method.
+We scale the original pixel scale of the final coadd stamp to mitigate the effect of undersampling.
+This final pixel scale was chosen to prevent the presence of visual artifacts in the structure of the coadd PSF image.
+    \item Creates an interpolated image with \texttt{GalSim} with the object centroid appropriately offset for each image using a \texttt{lanczos3} interpolantion method and sums them.
 Out of several interpolation methods we tried, \texttt{lanczos3} produced the best coadd of the PSF.
-    \item Recreates the coadded noise image from the weight of the original weight map.
+    \item Recreates a coadd noise image from the weight of the original weight map. \textcolor{red}{don't follow this}
 \end{enumerate}
-
 Figure \ref{fig:singlecoadd} shows an example of the simulated single-epoch and coadded images and PSFs for objects with low and high S/N.
@@
 
-Before we calibrate and measure shapes with \texttt{ngmix}, we downsample the high-resolution PSF to the original pixel size.
+Before we measure and calibrate shapes with \texttt{ngmix}, we downsample the high-resolution PSF to the original pixel size \textcolor{red}{you mean new coadd pixel size?}.
 Figure \ref{fig:coadd_oversample_res} shows the coadded oversampled PSF and the then-downsampled PSF, and their differences.
-We downsampled the oversampled PSF (128 x 128 pixels) by summing 4 square-pixels and creating the original size PSF (32 x 32 pixels), in order to ensure that the shape fit with \texttt{ngmix} can be processed.
-Since a better sampled PSF generally enables the shape of the PSF to be more isotropic, we can state that the original PSF can lead to the biased shape measurement from Figure \ref{fig:coadd_oversample_res}.
+Having a matching pixel scale in the galaxy and PSF image is a requirement for the current \texttt{ngmix} pipeline.
+Future versions of these measurements should include the ability to provide a better-sampled PSF image for deconvolution in the measurement.
+Figure \ref{fig:single_to_coadd_rgb} shows the coadd products in different bandpasses for a relatively high S/N object.
+The multiband PSF image is the oversampled version for better visualization.
 
@@
     \vspace*{-5mm}
-    \caption{The left and middle panel of the figure illustrates the coadded \emph{Roman} PSF at its native pixel scale and the coadded PSF with a pixel scale that is oversampled by a factor of 4 and then down-sampled.
+    \caption{The left and middle panels illustrate the coadded \emph{Roman} PSF at its original pixel scale and the coadded PSF with a pixel scale that is generated with a pixel scale that is smaller by a factor of 4 and then down-sampled to this original pixel scale.
 These are visualized in a log scale.
-The right panel shows the difference image between the two linear-scaled PSFs.
+The right panel shows the difference image between the two PSF images.
 }
@@
 \end{figure}
-
-Finally, Figure \ref{fig:single_to_coadd_rgb} shows the coadd products in different bandpasses for a relatively high S/N object.
-It is worth noting that the multiband PSF is the oversampled version for a visualization purpose.
 
@@
     \caption{The left 3 panels show an example of the coadded galaxy images for each filter.
-The S/N for each filter is S/N=2292, 1558, 1336.
-The 4th and 5th panels show the multiband coadd images of the same object; each with xxx scale and RGB scale.
-The S/N of the image is S/N=1755.
-Finally, the right-most panel shows the coadded oversampled PSF with the original scale.}
+The S/N for each filter is S/N=2292, 1558, 1336, respectively.
+The 4th and 5th panels show the multiband coadd images of the same object; each with \textcolor{red}{xxx} scale and RGB scale.
+The S/N of the coadd image is S/N=1755 (check?).
+Finally, the right-most panel shows the coadded \textcolor{red}{oversampled PSF with the original scale - what does this mean?}.}
     \label{fig:single_to_coadd_rgb}
@@
 \label{subsec:mcal}
-Once we construct the individual galaxy stamp coadds from the MEDS files to recover the shear signal, we feed them into the \textsc{metacalibration} process.
-The bootstrapper method in \texttt{ngmix} wraps the \textsc{metacalibration} and the shape fit processes.
+Once we construct the individual galaxy stamp coadds from the MEDS files, we recover the calibrated shear signal using the \textsc{metacalibration} process.
+The bootstrapper method used in \texttt{ngmix} wraps the \textsc{metacalibration} and the shape fit processes.
 The priors needed for the fit are listed in Table \ref{tab:priors}.
-We note that we have run \textsc{metacalibration} with \texttt{fitgauss} and \texttt{gauss} parameters for the new PSF model, and we found that it is preferrable to use \texttt{gauss} for our case.
+We note that we have run \textsc{metacalibration} with \texttt{fitgauss} and \texttt{gauss} parameters for the new PSF model, and we found that the \texttt{gauss} method performs better for our case.
 
@@
     Half-light radius & $10^{-5}$ < T < $10^{4}$\\
-    Flux fraction of the bulge component & $\langle f\rangle = 0.5$, $\sigma_{f} = 0.1$\\
+    Flux fraction of the bulge  & $\langle f\rangle = 0.5$, $\sigma_{f} = 0.1$\\
     Total flux & $0$ < F < $10^{6}$\\
@@
 \textsc{metacalibration} creates one unsheared and four artificially-sheared galaxy stamps.
-Each is deconvolved with the input PSF, unsheard or sheared with the gravitational shear of $\gamma=0.01$ in four directions ($+g1$, $-g1$, $+g2$, $-g2$) and re-convolved with a new slightly larger isotropic, Gaussian PSF.
-It is known that \textsc{metacalibration} works under the assumption that the input shear needs to be small, otherwise the recovered shear would be biased.
-It is challenging to find a good input shear that results in higher S/N of an object and unbiased shape measurement.
-We verify that our input gravitational shear is unbiased in \textsc{metacalibration} framework and the uncertainty in the recovered shape is small enough by constructing the same but simpler framework of the fiducial image simulations which renders Gaussian profile galaxy and PSF on the \emph{Roman} pixel scale cutout image without any detector effects.
-Figure \ref{fig:metacal_shear_linear} demonstrates that even with the simple enough simulations \textsc{metacalibration} becomes biased after $g=0.05$ since the assumption is starting to break down.
+Each is deconvolved with the input PSF, left unsheared or sheared with an additional gravitational shear of $\delta\gamma=\pm 0.01$ in the two basis directions ($+g1$, $-g1$, $+g2$, $-g2$) and re-convolved with a new slightly larger isotropic, Gaussian PSF.
+\textsc{metacalibration} works under the assumption that the input shear is small, otherwise the recovered shear would be biased without accounting for higher order terms.
+It is a balance to choose an input shear that results in higher S/N of an object and unbiased shape measurement.
+We verify that our input gravitational shear is unbiased in \textsc{metacalibration} framework and the uncertainty in the recovered shape is small enough by constructing a simpler framework of the fiducial image simulations which renders Gaussian profile galaxies and PSFs on the \emph{Roman} pixel scale cutout image without any detector effects or other complications in the fiducial simulations.
+Figure \ref{fig:metacal_shear_linear} shows the performance as a function of input shear leading to the choice of $\delta\gamma=\pm 0.01$.
 
 After processing the images in \textsc{metacalibration} and measuring the shapes in \texttt{ngmix}, we have 5 shape catalogs in each \textsc{metacalibration} shear direction.
-The caveat of calibrating with \textsc{metacalibration} is we can then compute the shear response from these catalogs and compute the calibrated galaxy ellipticities.
-Shear response can be understood as the change in object ellipticities with respect to the change in gravitational shear.
+We can then compute the shear response from these catalogs and calculate the calibrated ensemble galaxy ellipticities.
+The shear response can be understood as the change in objects' ellipticities with respect to the change in gravitational shear.
 Mathematically, the observed ellipticities, $\vb*{e}$ = ($e_{1}$, $e_{2}$), can be approximated using a Taylor expansion around the two-component shear, $\vb*{\gamma}=0$.
@@
     \vspace*{-5mm}
-    \caption{It shows the quadratic relationship between the input gravitational shear for the simple simulations and the multiplicative bias estimated from the recovered shape in the \textsc{metacalibration} catalogs.
-}
+    \caption{At first order, the \textsc{metacalibration} method only works for small shears.
+The next order effect is seen as a quadratic dependence of the multiplicative shear bias on on the applied shear.
+A larger input shear increases the signal-to-noise of bias estimates, but to keep this effect small compared to requirements, we limit input shears to $\pm 0.01$.}
     \label{fig:metacal_shear_linear}
@@
 
-With \textsc{metacalibration}, we can compute the shear response from the five versions of \textsc{metacalibration} catalog using the finite difference method.
+In practice, we compute the shear response from the five versions of \textsc{metacalibration} catalog using the finite difference method.
 
@@
 
+\textcolor{red}{
 \begin{equation}
@@
 \end{equation}
-
 where the numerator calculates the \textsc{metacalibration} calibrated observed shear by dividing $i$-th component of the ellipticity of the unsheared \textsc{metacalibration} catalog by shear response.
-
 \begin{equation}
@@
 \end{equation}
+ (could remove this)}
 
@@
 \end{equation}
-where we use sample $N$=200.
+where we use sample $N$=200.  \textcolor{red}{is it the same if you do jackknife?}
 
@@
 The shear response is used to compute the shear calibration bias and the bias is used as priors to the cosmological analysis.
+\textcolor{red}{not sure I follow this paragraph}
 
@@
 We divide our shape measurement into two categories; single-band and multiband.
-For single-band measurements, in each filter, we measure the shapes from the original single exposures by joint-fitting them.
+For single-band measurements, in each filter, we measure the shapes from the original single exposures by jointly fitting them.
 We set our base case to be this single-band joint-fit measurement.
-As the more developed case, we measure shapes with the single-band coadd in each filter by single-fitting it.
-For one multiband measurement, we match the objects between each filter and measure the shapes with the joint-fit of single exposures across all the filters.
-The other multiband measurement joint-fit the three coadds from each filter to recover the shapes.
+As the more developed case, we measure shapes with the single-band coadd in each filter.
+For the single-epoch multiband measurement, we match the objects between each filter and measure the shapes with the joint-fit of single exposures across all the filters.
+The coadd multiband measurement is jointly fit across the three coadds from each filter to recover the shapes.
 
@@
 In total, we simulate 907,170 galaxies on 18 SCAs across 198 pointings for F184, 227 pointings for H158, and 238 pointings for J129 bandpass.
-We do not make any selection cuts on the simulated catalogs based on measured properties.
+We do not make any selection cuts on the simulated catalogs based on measured properties, since all input objects should pass requirements for weak lensing selection (e.g., S/N>18).
 Even so, due to the misestimation of the PSF or low S/N, the Gaussian mixture in \texttt{ngmix} fails to fit about 5\% of all simulated objects, and so the total number of the recovered objects for single-band measurements is, 861,960 for F184, 863,358 for H158, and 859,645 for J129.
-For the multiband (H158+J129+F184) coadd measurements, we measure objects that are found by all of the filters and the total number of the recovered objects is 851,821.
-Figure \ref{fig:true_properties} and \ref{fig:measured_properties} show the true properties from the truth catalog and measured properties from the \textsc{metacalibration} shape catalogs.
+For the multiband (H158+J129+F184) coadd measurements, we use objects that are measured successfully in all of the filters and the total number of the recovered objects is 851,821.
+Figures \ref{fig:true_properties} and \ref{fig:measured_properties} show the true properties from the truth catalog and measured properties from the \textsc{metacalibration} shape catalogs.
 
@@
 	\centering
-    \caption{The left panel shows input galaxies magnitudes for all the 3 filter we have used to measure shapes.
-The mean magnitude for H158, F184, J129 are respectively 23.098, 22.976, and 23.273.
+    \caption{The left panel shows the simulated magnitudes of galaxies for all the 3 filter we have used to measure shapes.
+The mean magnitude for H158, F184, and J129 are respectively 23.098, 22.976, and 23.273.
 The right panel shows the half-light radius in units of arcsec for H158 for input and measured objects.
 The mean half-light radii for input and measured galaxies are 0.294 and 0.221 arcsec for H158.
-For these histograms, we are showing the objects with the successful fit in \texttt{ngmix}.}
+For these histograms, we are showing the objects with a successful fit in \texttt{ngmix}.}
     \label{fig:true_properties}
@@
 	\includegraphics[scale=0.34]{ngmix_snr_T.pdf}
-    \caption{This shows the distribution histograms of measured galaxy and PSF properties in \texttt{ngmix} for single-band coadd and multiband coadd measurement.
-It includes S/N, galaxy size $T{gal}$, and the shape and size of the PSF.}
+    \caption{The histograms of measured galaxy and PSF properties in \texttt{ngmix} for single-band coadd and multiband coadd measurements.
+It includes S/N, galaxy size $T{gal}$, and the shape and size of the PSF.
+The S/N is significantly improved in the multiband fit.}
     \label{fig:measured_properties}
@@
 \ref{subsec:mcal}.
-The multiplicative and additive bias values in texts are the average of $m_{1}$ and $m_{2}$, and $c_{1} and c_{2}$.
+The multiplicative and additive bias values listed in the text are the average of $m_{1}$ and $m_{2}$, and $c_{1} and c_{2}$.
+These are usually symmetric, except in the case of the coadd measurements, where $c_1>c_2$.
 The comprehensive results can be found in Table \ref{tab:bias_summary}.
 
-For the single-band measurements, we can use the sampling factor defined in Equation \ref{eqn:sampling} to \textcolor{red}{visualize} the relationship between the sampling factor and the shear bias.
-The sampling factor is an indication of how undersampled the image in the filter is and it is respectively $Q_{J129,single}=1.01, Q_{J129,coadd}=1.26, Q_{H158,single}=1.23, Q_{H158,coadd}=1.54, Q_{F184,single}=1.44, Q_{H158,coadd}=1.79$.
-This relationship between sampling factors and shear bias was previously explored in \citealt{2021MNRAS.502.4048K} using \emph{Euclid} simulation with different shape measurement algorithms, where they found that the estimated multiplicative bias has a relatively large dependence on the sampling factor.
+For the single-band measurements, we can use the sampling factor defined in Equation \ref{eqn:sampling} per bandpass to show the relationship between the shear bias and image sampling.
+The sampling factor is an indication of how undersampled the image in some bandpass is.
+\textcolor{red}{It is respectively $Q_{J129,single}=1.01, Q_{J129,coadd}=1.26, Q_{H158,single}=1.23, Q_{H158,coadd}=1.54, Q_{F184,single}=1.44, Q_{H158,coadd}=1.79$.
+(put in table and reference?)} This relationship between sampling factor and shear bias was previously explored in \citealt{2021MNRAS.502.4048K} using \emph{Euclid} simulation with different shape measurement algorithms, where they found that the estimated multiplicative bias has a relatively large dependence on the sampling factor.
 Their result can be extrapolated to our single-band coadd results in Figure \ref{fig:final_result}.
-The multiplicative bias of single-band single-epochs measurements for each filter is, \textcolor{red}{1.04$\pm$0.47 per cent for J129, -1.30$\pm$0.46 per cent for H158 and -0.40$\pm$0.53 per cent for F184}.
-When the coadds of each filter are used, the bias is \textcolor{red}{-0.47$\pm$0.49 per cent for J129, -0.07$\pm$0.45 per cent for H158 and -0.06$\pm$0.61 per cent for F184}.
-We do not see any improvements on the recovered shear when we coadd the single-epoch images.
-We can conclude that in the current \emph{Roman} simulation the multiplicative bias has a slight dependence on the sampling factor.
+The multiplicative bias of single-band single-epoch measurements for each filter is, \textcolor{red}{1.04$\pm$0.47 per cent for J129, -1.30$\pm$0.46 per cent for H158 and -0.40$\pm$0.53 per cent for F184}.
+When the coadd images for each filter are used, the bias is \textcolor{red}{-0.47$\pm$0.49 per cent for J129, -0.07$\pm$0.45 per cent for H158 and -0.06$\pm$0.61 per cent for F184}.
+We can conclude that in the current \emph{Roman} simulation the multiplicative bias has a similar dependence on the sampling factor as shown in \citealt{2021MNRAS.502.4048K}, but with a smaller amplitude.
+We do not see any clear improvements in the recovered shear when we coadd the single-epoch images, despite having a smaller pixel scale (better sampling) in the images.
+This is most likely due to an issue with how we're currently treating the PSF or correlated noise in the coadding process, given the large observed $c_1$ when coadding discussed below.
 
-Meanwhile the estimated additive bias is the same order as the Y3 analysis in DES.
 The additive bias of the single-band single-epochs measurements for each filter is, \textcolor{red}{(3.22$\pm$0.92)$10^{-4}$ for J129, (2.63$\pm$0.88)$10^{-4}$ for H158 and (3.25$\pm$1.11)$10^{-4}$ for F184}.
 When the measurements are based on coadds, the bias is, \textcolor{red}{(3.39$\pm$0.90)$10^{-4}$ for J129, (8.08$\pm$0.87)$10^{-4}$ for H158 and (9.36$\pm$1.10)$10^{-4}$ for F184}.
-In Table \ref{tab:result}, it is worth noting that the coadd process mentioned in \ref{subsec:psc} clearly introduces non-trivial additive biases in one direction of the shear, but not the other.
-We believe this is due to the effect of an imperfect PSF model.
-We see this in the Figure \ref{fig:meanshear} where the recovered shear has a strong linear dependence on the PSF ellipticity measured by an adaptive moments method.
-The impact of the PSF shape and size leakage in the estimated galaxy shapes can be estimated by computing $\rho$-statistics (\citealt{2008A&A...484...67P, 2010MNRAS.404..350R, 2016MNRAS.460.2245J}).
-However, we do not explore the $\rho$-statistics for our PSF model since it is an approximation to accurately represent the features of the instrument, not computed from the real pupil plane images, and the coadding process for the 5-year mission is not yet finalized.
+The estimated additive bias is the same order as that found in the Y3 analysis in DES, which uses a similar shear calibration pipeline.
+In Table \ref{tab:result}, it is worth noting that the coadd process clearly introduces non-trivial additive biases in one direction of the shear, but not the other.
+We believe this is due to the effect of an imperfect coadd PSF model.
+\textcolor{red}{We see this in the Figure \ref{fig:meanshear} where the recovered shear has a strong linear dependence on the PSF ellipticity measured by an adaptive moments method.} The impact of the PSF shape and size leakage in the estimated galaxy shapes at the correlation function level can be estimated by computing $\rho$-statistics (\citealt{2008A&A...484...67P, 2010MNRAS.404..350R, 2016MNRAS.460.2245J}).
+However, we do not explore the $\rho$-statistics for our PSF model since there is no realistic shear field in this version of the simulations.
+We can explore these effects further in the next generation of simulations that are being worked on in parallel, which are commented on in Sec.
+\ref{}.
+We are also developing a more sophisticated coadd treatment that will be applied to future simulation versions and may alleviate these issues.
+
+\textcolor{red}{You can reference the table of m,c values and just summarize in the text, instead of listing them for all cases again.}
 
 Finally, we discuss the results with multiband measurements.
-We performed multiband measurements with 3 filters used in the previous measurements.
-One multiband measurement used all of the single epoch images from all the filters and joint-fit the shape of the galaxy.
+We performed multiband measurements with the three filters used in the previous measurements.
+One multiband measurement used all of the single epoch images from all the filters and jointly fit the shape of the galaxy.
 The multiplicative and additive bias is, respectively, \textcolor{red}{$m=(-1.34\pm0.67)$ per cent and $c=(2.58\pm1.26)10^{-4}$}.
-This result generally agrees with the single-band single-epochs measurements.
-However, performing the joint-fit over different bandpasses for one galaxy does not necessarily constrain the shape of the object.
-The other measurement performed the joint-fit on the three coadded images for each filter.
+This result generally agrees with the single-band single-epochs measurements, and is consistent with zero bias at the approx.
+2$\sigma$ level.
+We can't conclude more than that this result may be acceptable without significantly larger simulation volume \texcolor{red}{how large?}.
+\textcolor{red}{However, performing the joint-fit over different bandpasses for one galaxy does not necessarily constrain the shape of the object.
+(what does this sentence mean?)} The other measurement is performed as a joint fit across the coadd images for each filter.
 The multiplicative and additive bias is, respectively, \textcolor{red}{$m=(-2.16\pm0.60)$ per cent and $c=(9.24\pm1.22)10^{-4}$}.

### 2021-11-18 roman_metacal_v2.tex
v2 edit

@@
 Due to the subtlety in the lensing effect and its systematics-dominant nature in the weak regime, observational efforts have been challenging.
-Over the past decade, large international collaborations such as the Dark Energy Survey\footnote{\url{http://www.darkenergysurvey.org/}} (DES: \citealt{2005astro.ph.10346T}), the Hyper Supreme-Cam\footnote{\url{http://hsc.mtk.nao.ac.jp/ssp/}} (HSC: \citealt{2018PASJ...70S...4A}), and the Kilo-Degree Survey\footnote{\url{http://kids.strw.leidenuniv.nl/}} (KiDS)\textcolor{red}{insert cite like others} have been successful at constraining the cosmological parameters, and the precision in calibrating the shapes of distant galaxies has reached a few percent (\citealt{2020arXiv201103408G, 2020arXiv201208567M, 2021A&A...645A.105G}).
+Over the past decade, large international collaborations such as the Dark Energy Survey\footnote{\url{http://www.darkenergysurvey.org/}} (DES: \citealt{2005astro.ph.10346T}), the Hyper Supreme-Cam\footnote{\url{http://hsc.mtk.nao.ac.jp/ssp/}} (HSC: \citealt{2018PASJ...70S...4A}), and the Kilo-Degree Survey\footnote{\url{http://kids.strw.leidenuniv.nl/}} (KiDS: \citealt{2013ExA....35...25D}) have been successful at constraining the cosmological parameters, and the precision in calibrating the shapes of distant galaxies has reached a few percent (\citealt{2020arXiv201103408G, 2020arXiv201208567M, 2021A&A...645A.105G}).
 As we observe more area of the sky and develop better tools (observatories and algorithms), we detect more galaxies, and have already reached the point where statistical and systematic uncertainties are comparable.
@@
 We use an updated suite of image simulations specifically made for the \emph{Roman} reference HLIS mission.
-Our work is based on the image simulation suite for the \emph{Roman} Space Telescope developed by \citet{2021MNRAS.501.2044T}, where we render star and galaxy images using \texttt{GalSim}\footnote{\url{ https://github.com/GalSim-developers/GalSim}} (\citealt{2015A&C....10..121R}).
-We describe several important updates to the simulation capabilities and realism following \cite{2021MNRAS.501.2044T}.
+Our work is based on the image simulation suite for the \emph{Roman} Space Telescope developed by \cite{2021MNRAS.501.2044T} (hereafter T21), where we render star and galaxy images using \texttt{GalSim}\footnote{\url{ https://github.com/GalSim-developers/GalSim}} (\citealt{2015A&C....10..121R}).
+We describe several important updates to the simulation capabilities and realism following T21.
 We also implement for the first time \textsc{metacalibration} using the simulated imaging, so that we can start to explore if the shear calibration goals of the HLIS for \emph{Roman} ($m=~3.2\times10^{-4}$) (\citealt{2018arXiv180403628D}) can be achieved with current \textsc{metacalibration} pipelines,\footnote{We limit the study to \textsc{metacalibration} for now, since we can extract unblended cutouts of objects in our simulations.} or will require substantial additional development.
@@
 \label{sec:sims}
-The base of our image simulations of the \emph{Roman} Space Telescope is the \emph{Roman} simulation suite\footnote{\url{ https://github.com/matroxel/roman_imsim}} developed by \citet{2021MNRAS.501.2044T}, which renders realistic galaxy and star images on 18 Sensor-Chip Assemblies (SCAs) of a 2.5$\times$2.5 deg$^{2}$ patch of the sky following the observing strategy for the 5-year reference mission and Cycle7 instrument specifications\footnote{\url{https://roman.gsfc.nasa.gov/science/Roman_Reference_Information.html}}.
+The base of our image simulations of the \emph{Roman} Space Telescope is the \emph{Roman} simulation suite\footnote{\url{ https://github.com/matroxel/roman_imsim}} developed by T21, which renders realistic galaxy and star images on 18 Sensor-Chip Assemblies (SCAs) of a 2.5$\times$2.5 deg$^{2}$ patch of the sky following the observing strategy for the 5-year reference mission and Cycle7 instrument specifications\footnote{\url{https://roman.gsfc.nasa.gov/science/Roman_Reference_Information.html}}.
 We begin by creating a truth catalog using the simulated galaxy distribution from the Buzzard simulation (\citealt{2019arXiv190102401D}), a photometric galaxy catalog sampled from the CANDELS survey (e.g., \citealt{2019ApJ...877..117H}), and a Milky Way simulation (Galaxia; \citealt{2011ApJ...730....3S}) for star positions and magnitudes.
@@
 These MEDS files are generated according to the Hierarchical Equal Area isoLatitude Pixelisation (HEALPix) of $n_{side}=512$.
-They contain all objects that are located in that region of the sky partitioned according HEALPixel.
-\textcolor{red}{add healpix reference} Once the objects are sorted in MEDS files, we pass these multiple exposures with the corresponding PSFs to \texttt{ngmix}\footnote{\url{ https://github.com/esheldon/ngmix}} to fit the galaxy shapes with the Gaussian mixture fitting method (\citealt{2014MNRAS.444L..25S}).
+They contain all objects that are located in that region of the sky partitioned according HEALPixel\footnote{\url{https://healpix.jpl.nasa.gov/}} (\citealt{2005ApJ...622..759G, Zonca2019}).
+Once the objects are sorted in MEDS files, we pass these multiple exposures with the corresponding PSFs to \texttt{ngmix}\footnote{\url{ https://github.com/esheldon/ngmix}} to fit the galaxy shapes with the Gaussian mixture fitting method (\citealt{2014MNRAS.444L..25S}).
 This shape measurement process produces shape catalogs from which the shear calibration bias can be calculated with \textsc{metacalibration}.
@@
 	\vspace*{-10mm}
-    \caption{The top row shows the first entry of the single epoch images and its coadded image, and the corresponding single-epoch and coadded oversampled PSF images for an object with low signal-to-noise ratio (S/N=9.69).
-The bottom row shows the same for an object with high signal-to-noise ratio (S/N=1552.97).
-\textcolor{red}{is snr in single-epoch or coadd?}}
+    \caption{The top row shows the first entry of the single epoch images and its coadded image, and the corresponding single-epoch and coadded oversampled PSF images for an object with low signal-to-noise ratio (S/N=9.69 in a single-epoch image).
+The bottom row shows the same for an object with high signal-to-noise ratio (S/N=1552.97 in a single-epoch image).
+The PSFs are shown in a log-scale.}
     \label{fig:singlecoadd}
@@
     \item \textbf{Rotation of the \emph{Roman} PSF on the sky}:
-    In the study by \textcolor{red}{Troxel et al.
-(2021)}, the rotations of the \emph{Roman} PSF with respect to the telescope rotation were not properly applied by the \texttt{galsim.roman} module.
+    In the study by T21, the rotations of the \emph{Roman} PSF with respect to the telescope rotation were not properly applied by the \texttt{galsim.roman} module.
 Since a non-rotating PSF produces an artificial preferred direction, which can translate to galaxy shapes through errors in the process of deconvolvution, properly accounting for the averaging of the PSF orientation across exposures due to the survey dithering strategy is essential for a realistic shear calibration estimate.
@@
 
-    \item \textbf{\textsc{metacalibration} in \texttt{ngmix}}: We implemented the \textsc{metacalibration}\footnote{\url{https://github.com/esheldon/ngmix/wiki/Metacalibration}} bootstrapper method, which is a wrapper class to run measurements in the \texttt{ngmix} package and was used to produce the weak lensing shape catalog in the DES Y3 analysis \textcolor{red}{citation}.
+    \item \textbf{\textsc{metacalibration} in \texttt{ngmix}}: We implemented the \textsc{metacalibration}\footnote{\url{https://github.com/esheldon/ngmix/wiki/Metacalibration}} bootstrapper method, which is a wrapper class to run measurements in the \texttt{ngmix} package and was used to produce the weak lensing shape catalog in the DES Y3 analysis (\citealt{2020arXiv201103408G}).
 The \textsc{metacalibration} process can be performed on single-epoch or coadd images in each bandpass.
-With this calibration method, we hope to significantly reduce some of the shear calibration bias \textcolor{red}{Troxel et al.
-(2021)} measured in order to make comparisons of effects contributing to the bias more realistic and meaingful as we explore future \emph{Roman} pipeline development.
+With this calibration method, we hope to significantly reduce some of the shear calibration bias T21 measured in order to make comparisons of effects contributing to the bias more realistic and meaningful as we explore future \emph{Roman} pipeline development.
 The detailed overview of \textsc{metacalibration} can be found in Sec.\ref{subsec:mcal}.
@@
 Out of several interpolation methods we tried, \texttt{lanczos3} produced the best coadd of the PSF.
-    \item Recreates a coadd noise image from the weight of the original weight map. \textcolor{red}{don't follow this}
+    \item Recreates a coadd noise image from the weight of the original weight map. \textcolor{red}{don't follow this -> line 76-78 in psc code.}
 \end{enumerate}
@@
 The S/N for each filter is S/N=2292, 1558, 1336, respectively.
-The 4th and 5th panels show the multiband coadd images of the same object; each with \textcolor{red}{xxx} scale and RGB scale.
-The S/N of the coadd image is S/N=1755 (check?).
-Finally, the right-most panel shows the coadded \textcolor{red}{oversampled PSF with the original scale - what does this mean?}.}
+The 4th and 5th panels show the multiband coadd images of the same object; each with linear scale and RGB scale.
+The S/N of the coadd image is S/N=1755 \textbf{red}{check?}.
+Finally, the right-most panel shows the coadded oversampled PSF in linear scale.}
     \label{fig:single_to_coadd_rgb}
@@
 
-\textcolor{red}{\texttt{ngmix} utilizes xx method to compute the size of the galaxy, while we compute the adaptive moments of objects to measure the shape and size of the input PSF (\citealt{2003MNRAS.343..459H})}.
-
-In the actual observations of cosmic shear, the observable is the galaxy shapes $\langle\vb*{e}\rangle$ and we can take advantage of image simulations and calculate the shear response with the calibration algorithms, and finally compute the gravitational lensing shear signal $\langle\vb*{\gamma}\rangle$.
-The shear response is used to compute the shear calibration bias and the bias is used as priors to the cosmological analysis.
-\textcolor{red}{not sure I follow this paragraph}
-
 \section{Results}
@@
 \ref{subsec:mcal}.
-The multiplicative and additive bias values listed in the text are the average of $m_{1}$ and $m_{2}$, and $c_{1} and c_{2}$.
+The multiplicative and additive bias values listed in the text are the average of $m_{1}$ and $m_{2}$, and $c_{1}$ and $c_{2}$.
 These are usually symmetric, except in the case of the coadd measurements, where $c_1>c_2$.
@@
 The sampling factor is an indication of how undersampled the image in some bandpass is.
-\textcolor{red}{It is respectively $Q_{J129,single}=1.01, Q_{J129,coadd}=1.26, Q_{H158,single}=1.23, Q_{H158,coadd}=1.54, Q_{F184,single}=1.44, Q_{H158,coadd}=1.79$.
-(put in table and reference?)} This relationship between sampling factor and shear bias was previously explored in \citealt{2021MNRAS.502.4048K} using \emph{Euclid} simulation with different shape measurement algorithms, where they found that the estimated multiplicative bias has a relatively large dependence on the sampling factor.
+The sampling factor for each single-band measurement can be found in Table \ref{tab:bias_summary}.
+This relationship between sampling factor and shear bias was previously explored in \citealt{2021MNRAS.502.4048K} using \emph{Euclid} simulation with different shape measurement algorithms, where they found that the estimated multiplicative bias has a relatively large dependence on the sampling factor.
 Their result can be extrapolated to our single-band coadd results in Figure \ref{fig:final_result}.
@@
 In Table \ref{tab:result}, it is worth noting that the coadd process clearly introduces non-trivial additive biases in one direction of the shear, but not the other.
-We believe this is due to the effect of an imperfect coadd PSF model.
-\textcolor{red}{We see this in the Figure \ref{fig:meanshear} where the recovered shear has a strong linear dependence on the PSF ellipticity measured by an adaptive moments method.} The impact of the PSF shape and size leakage in the estimated galaxy shapes at the correlation function level can be estimated by computing $\rho$-statistics (\citealt{2008A&A...484...67P, 2010MNRAS.404..350R, 2016MNRAS.460.2245J}).
+This is due to the effect of an imperfect coadd PSF model.
+We find this correlation in the Figure \ref{fig:meanshear} where the recovered shear on the coadd images has a strong linear dependence on the PSF ellipticity measured by an adaptive moments method (\citealt{2003MNRAS.343..459H}).
+The impact of the PSF shape and size leakage in the estimated galaxy shapes at the correlation function level can be estimated by computing $\rho$-statistics (\citealt{2008A&A...484...67P, 2010MNRAS.404..350R, 2016MNRAS.460.2245J}).
 However, we do not explore the $\rho$-statistics for our PSF model since there is no realistic shear field in this version of the simulations.
 We can explore these effects further in the next generation of simulations that are being worked on in parallel, which are commented on in Sec.
-\ref{}.
+\ref{sec:discussion}.
 We are also developing a more sophisticated coadd treatment that will be applied to future simulation versions and may alleviate these issues.
@@
 2$\sigma$ level.
-We can't conclude more than that this result may be acceptable without significantly larger simulation volume \texcolor{red}{how large?}.
-\textcolor{red}{However, performing the joint-fit over different bandpasses for one galaxy does not necessarily constrain the shape of the object.
-(what does this sentence mean?)} The other measurement is performed as a joint fit across the coadd images for each filter.
+We can't conclude more than that this result may be acceptable without significantly larger simulation volume \textcolor{red}{how large?}.
+The other measurement is performed as a joint-fit across the coadd images for each filter.
 The multiplicative and additive bias is, respectively, \textcolor{red}{$m=(-2.16\pm0.60)$ per cent and $c=(9.24\pm1.22)10^{-4}$}.
-\textcolor{red}{Although coadding produces better sampled images as in Figure \ref{fig:single_to_coadd_rgb} and less multiplicative bias than single-epochs measurements, The multiplicative bias does not represent the average of 3 single-band coadd measurements and we think that...}.
-Overall, as in Figure \ref{fig:meanshear} we do not find any correlation of mean shear against the input and measured properties of the galaxies.
+Figure \ref{fig:meanshear} shows the relationship between the mean shear and several input and measured properties of galaxies and PSF for all the measurement cases.
+We find that the mean shear has a linear trend as a function of input galaxy size.
+(\textcolor{red}{Any explanation?})
 
@@
 	\label{tab:bias_summary}
-	\begin{tabular}[scale=1.4]{ c|c|c|c|c } 
+	\begin{tabular}[scale=1.4]{ c|c|c|c|c|c } 
 		\hline
-		simulation variants & $m_{1}\times10^{-2}$ & $m_{2}\times10^{-2}$ & $c_{1}\times10^{-4}$ & $c_{2}\times10^{-4}$\\
+		simulation variants & sampling factor ($Q$) & $m_{1}\times10^{-2}$ & $m_{2}\times10^{-2}$ & $c_{1}\times10^{-4}$ & $c_{2}\times10^{-4}$\\
 		\hline
-		\textcolor{red}{single-epochs (J129)} & 1.30$\pm$0.70 & 0.30$\pm$0.63 & 4.65$\pm$1.45 & 1.33$\pm$1.40\\
-		single-epochs (H158) & -1.07$\pm$0.62 & -1.61$\pm$0.66 & 2.83$\pm$1.35 & 2.33$\pm$1.22\\
-		single-epochs (F184) & -0.86$\pm$0.72 & -0.69$\pm$0.83 & 2.62$\pm$1.56 & 0.23$\pm$1.53\\
+		\textcolor{red}{single-epochs (J129)} & 1.01 & 1.30$\pm$0.70 & 0.30$\pm$0.63 & 4.65$\pm$1.45 & 1.33$\pm$1.40\\
+		single-epochs (H158) & 1.23 & -1.07$\pm$0.62 & -1.61$\pm$0.66 & 2.83$\pm$1.35 & 2.33$\pm$1.22\\
+		single-epochs (F184) & 1.44 & -0.86$\pm$0.72 & -0.69$\pm$0.83 & 2.62$\pm$1.56 & 0.23$\pm$1.53\\
 		\hline
-		\textcolor{red}{single-band coadd (J129)} & -1.59$\pm$0.64 & -2.31$\pm$0.70 & 11.61$\pm$1.20 & -0.09$\pm$1.34\\
-		\textcolor{red}{single-band coadd (H158)} & -1.51$\pm$0.68 & -1.41$\pm$0.66 & 14.79$\pm$1.32 & 4.45$\pm$1.42\\
-		\textcolor{red}{single-band coadd (F184)} & 0.47$\pm$0.80 & -0.59$\pm$0.81 & 12.40$\pm$1.67 & 6.32$\pm$1.82\\
+		\textcolor{red}{single-band coadd (J129)} & 1.26 & -1.59$\pm$0.64 & -2.31$\pm$0.70 & 11.61$\pm$1.20 & -0.09$\pm$1.34\\
+		single-band coadd (H158) & 1.54 & -1.91$\pm$0.67 & -2.11$\pm$0.67 & 13.99$\pm$1.34 & 5.40$\pm$1.35\\
+		single-band coadd (F184) & 1.79 & -0.28$\pm$0.83 & -0.27$\pm$0.78 & 12.15$\pm$1.56 & 5.66$\pm$1.56\\
 		\hline
-		multiband single-epochs & -1.07$\pm$0.66 & -1.61$\pm$0.67 & 2.83$\pm$1.30 & 2.33$\pm$1.22 \\
-		\textcolor{red}{multiband coadd} & -2.16$\pm$0.60 & -2.16$\pm$0.60 & 14.03$\pm$1.13 & 4.44$\pm$1.31\\
+		multiband single-epochs & N/A & -1.07$\pm$0.66 & -1.61$\pm$0.67 & 2.83$\pm$1.30 & 2.33$\pm$1.22 \\
+		multiband coadd & N/A & -2.32$\pm$0.64 & -2.34$\pm$0.63 & 14.45$\pm$1.10 & 4.49$\pm$1.22\\
 
@@
     \centering
-	\includegraphics[scale=0.34]{H158_meanshear_measured_properties_perbin_e1.pdf}
+	\includegraphics[scale=0.34]{H158_meanshear_measured_properties_perbin_e1_v2.pdf}
     \caption{This shows the mean shear residual ($\Delta e_{1}$; $\langle e_{1,measured} \rangle - \langle e_{1,expected} \rangle$) as a function of various properties of galaxies for H158 single-band single-epochs, coadds, and multiband measurements.
@@
 
-    \item \textbf{Image Coadditions}: Implement a new coadding methodology which coadds the whole scene instead of individual stamp cutouts (e.g., \textsc{astrodrizzle}\footnote{\url{https://github.com/spacetelescope/drizzlepac}}).
-With \textsc{astrodrizzle} which employs the linear reconstruction of the individual images, we are able to further mitigate the effect of undersampled \emph{Roman} images.
-If we set the final coadd pixel scale with \textsc{astrodrizzle} to be 70\% smaller than the original \emph{Roman} pixel scale, F184 will be fully sampled (Q > 2) and J129 will be sampled at the similar level with F184 without coadding.
+    \item \textbf{Image Coadditions}: Implement a new coadding methodology which coadds the whole scene instead of individual stamp cutouts (e.g., \texttt{AstroDrizzle}\footnote{\url{https://github.com/spacetelescope/drizzlepac}}: A Python implementation of MultiDrizzle which was used for \emph{Hubble} Space Telescope (\citealt{2003hstc.conf..325B})).
+With \texttt{AstroDrizzle} which employs the linear reconstruction of the individual images, we are able to further mitigate the effect of undersampled \emph{Roman} images.
+If we set the final coadd pixel scale with \texttt{AstroDrizzle} to be 70\% smaller than the original \emph{Roman} pixel scale, F184 will be fully sampled (Q > 2) and J129 will be sampled at the similar level with F184 without coadding.
 
@@
 
-\appendix
+% \appendix
 
-\section{Simple Simulations}
-\label{app:coadd_F}
+% \section{Simple Simulations}
+% \label{app:coadd_F}
 % If you want to present additional material which would interrupt the flow of the main paper,

### 2021-11-22 roman_metacal_v2.tex
v2

@@
 \normalem
-\title[Metacalibration with The Roman High-Latitude Imaging Survey]{Weak gravitational lensing shear estimates with \textsc{metacalibration} for the \emph{Roman} High-Latitude Imaging Survey}
+\title[Metacalibration for the Roman High-Latitude Imaging Survey]{Weak gravitational lensing shear estimates with \textsc{metacalibration} for the \emph{Roman} High-Latitude Imaging Survey}
 
@@
 Rachel Mandelbaum,$^{3}$
-Christopher Hirata$^{4,5,6}$
-\\
+Christopher Hirata,$^{4,5,6}$
+ et al.\\
 % List of institutions
@@
 We find that compared with the non-calibrated results from previous work, \textsc{metacalibration} as used in current experiments can significantly reduce the shear calibration bias to the percent level.
-With the single-epoch images, across all three filters we are able to achieve a multiplicative bias \textcolor{red}{$m=0.70\%$ within 1.8 $\sigma$}, while for coadd cutouts, \textcolor{red}{$m=-2.16\%$}.
+With the single-epoch images, across all three filters we are able to achieve a multiplicative bias $m=-1.34\%$ within 2 $\sigma$, while for coadd cutouts, $m=-2.33\%$ within about 4 $\sigma$.
 In both single-epoch and coadd cases, we find that shape calibration becomes worse with decreasing image sampling factor.
 Overall, within the current simulation volume, there is evidence that \textsc{metacalibration} as currently implemented will not calibrate shapes with zero shear bias in the \emph{Roman} HLIS and further work on the shear calibration methodology is necessary.
-In the future, we will need to substantially increase the simulation volume to reach the precision necessary for the HLIS.
-\textcolor{red}{insert approx.
-factor of sim size needed}
+In the future, we will need to substantially increase the simulation volume by 400 (about the same size as the survey area of 2000 $deg^{2}$) to reach the precision necessary for the HLIS.
 \end{abstract}
@@
 It is, therefore, necessary to build a robust strategy to reconstruct well-sampled images to estimate the PSF to allow unbiased shape measurement.
-Recently, Kannawadi et al.
-(2021) addressed this potential issue of the limitations of \textsc{metacalibration} on undersampled images in \emph{Euclid} image simulations.
-They found that for the \emph{Euclid} mission the shear estimate is biased by about 1$\%$ (\citealt{2021MNRAS.502.4048K}).
+Recently, \cite{2021MNRAS.502.4048K} (hereafter K21) addressed this potential issue of the limitations of \textsc{metacalibration} on undersampled images in \emph{Euclid} image simulations.
+They found that for the \emph{Euclid} mission the shear estimate is biased by about 1$\%$.
 It is mentioned that their result could be extended to the \emph{Roman} mission due to similarities in the instruments and for \emph{Roman} they predicted the multiplicative bias was more than 1\%.
@@
 \begin{figure}
-	\includegraphics[width=\columnwidth]{figure1.pdf}
-	\vspace*{-3mm}
+	\includegraphics[width=\columnwidth]{psf_rotation.pdf}
+% 	\vspace*{-3mm}
     \caption{The rotation of the Roman PSF produced from the \texttt{galsim.roman} module.
@@
 \begin{figure*}
-	\includegraphics[width=\textwidth]{figure2.pdf}
-	\vspace*{-10mm}
+	\includegraphics[width=\textwidth]{lowsnr_highsnr_galaxies.pdf}
+	%\vspace*{-10mm}
     \caption{The top row shows the first entry of the single epoch images and its coadded image, and the corresponding single-epoch and coadded oversampled PSF images for an object with low signal-to-noise ratio (S/N=9.69 in a single-epoch image).
@@
 Out of several interpolation methods we tried, \texttt{lanczos3} produced the best coadd of the PSF.
-    \item Recreates a coadd noise image from the weight of the original weight map. \textcolor{red}{don't follow this -> line 76-78 in psc code.}
+    \item Creates a coadded noise image from the weight of the original images. 
 \end{enumerate}
@@
 
-Before we measure and calibrate shapes with \texttt{ngmix}, we downsample the high-resolution PSF to the original pixel size \textcolor{red}{you mean new coadd pixel size?}.
+Before we measure and calibrate shapes with \texttt{ngmix}, we downsample the high-resolution PSF to the original pixel size.
 Figure \ref{fig:coadd_oversample_res} shows the coadded oversampled PSF and the then-downsampled PSF, and their differences.
@@
 \begin{figure}
-	\includegraphics[width=\columnwidth]{figure3.pdf}
-    \vspace*{-5mm}
+	\includegraphics[width=\columnwidth]{psf_differences.pdf}
+    % \vspace*{-5mm}
     \caption{The left and middle panels illustrate the coadded \emph{Roman} PSF at its original pixel scale and the coadded PSF with a pixel scale that is generated with a pixel scale that is smaller by a factor of 4 and then down-sampled to this original pixel scale.
@@
 \begin{figure*}
-	\includegraphics[width=\textwidth]{figure4_og.pdf}
-    \vspace*{-20mm}
+	\includegraphics[width=\textwidth]{coadd_galaxy_example_log.pdf}
+    %\vspace*{-20mm}
     \caption{The left 3 panels show an example of the coadded galaxy images for each filter.
-The S/N for each filter is S/N=2292, 1558, 1336, respectively.
+The S/N for each filter is S/N=90, 68, 108, respectively.
 The 4th and 5th panels show the multiband coadd images of the same object; each with linear scale and RGB scale.
-The S/N of the coadd image is S/N=1755 \textbf{red}{check?}.
-Finally, the right-most panel shows the coadded oversampled PSF in linear scale.}
+The S/N of the coadd image is S/N=110.
+Finally, the right-most panel shows the coadded oversampled PSF in a log scale.}
     \label{fig:single_to_coadd_rgb}
@@
 We verify that our input gravitational shear is unbiased in \textsc{metacalibration} framework and the uncertainty in the recovered shape is small enough by constructing a simpler framework of the fiducial image simulations which renders Gaussian profile galaxies and PSFs on the \emph{Roman} pixel scale cutout image without any detector effects or other complications in the fiducial simulations.
-Figure \ref{fig:metacal_shear_linear} shows the performance as a function of input shear leading to the choice of $\delta\gamma=\pm 0.01$.
+Figure \ref{fig:metacal_shear_linear} shows the performance as a function of input shear leading to the choice of input shear $\gamma=\pm 0.02$.
 
@@
 	\includegraphics[width=\columnwidth]{metacal_bias_shear.png}
-    \vspace*{-5mm}
+    %\vspace*{-5mm}
     \caption{At first order, the \textsc{metacalibration} method only works for small shears.
@@
     \langle\vb*{R_{ij}}\rangle = 
-    \frac{\langle e^{+}_{i} - e^{-}_{i} \rangle}{\Delta\gamma_{j}}, 
+    \frac{\langle e^{+}_{i} - e^{-}_{i} \rangle}{\delta\gamma_{j}}, 
 \end{equation}
@@
 Then, this shear response is used to compute the multiplicative ($\vb*{M}$) and additive ($\vb*{C}$) bias using the linear shear bias model (\ref{eqn:linear}).
-
-\textcolor{red}{
-\begin{equation}
-    \small
-    \vb*{M_{ij}} = 
-    \frac{\langle e^{+}_{i}/R_{ii} \rangle - \langle e^{-}_{i}/R_{ii} \rangle}{\abs{\Delta g_{j}}} - \delta_{ij} 
-    = \frac{\langle e^{obs,+}_{i}\rangle - \langle e^{obs,-}_{i}\rangle}{\abs{\Delta g_{j}}} - \delta_{ij}, 
-\end{equation}
-where the numerator calculates the \textsc{metacalibration} calibrated observed shear by dividing $i$-th component of the ellipticity of the unsheared \textsc{metacalibration} catalog by shear response.
-\begin{equation}
-    \small
-    \vb*{C_{ij}} = \frac{\langle e^{obs,+}_{i} - (\delta_{ij}+M_{ij})e^{true,+}_{i})\rangle + \langle e^{obs,-}_{i} - (\delta_{ij}+M_{ij})e^{true,-}_{i}) \rangle}{2}
-\end{equation}
- (could remove this)}
-
 The covariances are computed using the bootstrap estimate of standard error.
@@
 \subsection{Statistics of the Shape Catalog}
-From the COSMOS catalog, based on the \emph{Roman} Weak Lensing mission requirements, objects are pre-selected and simulated.
+From the CANDELS catalog, based on the \emph{Roman} Weak Lensing mission requirements, objects are pre-selected and simulated.
 In total, we simulate 907,170 galaxies on 18 SCAs across 198 pointings for F184, 227 pointings for H158, and 238 pointings for J129 bandpass.
@@
 \begin{figure}
-    \hspace*{-1.5cm}
-	\includegraphics[scale=0.3]{true_properties.pdf}
+	\includegraphics[width=\columnwidth]{true_properties.pdf}
 	\centering
@@
 \begin{figure*}
-    \hspace*{-3.0cm}
+    %\hspace*{-3.1cm}
     \centering
-	\includegraphics[scale=0.34]{ngmix_snr_T.pdf}
+	\includegraphics[width=\textwidth]{ngmix_snr_T.pdf}
     \caption{The histograms of measured galaxy and PSF properties in \texttt{ngmix} for single-band coadd and multiband coadd measurements.
@@
 These are usually symmetric, except in the case of the coadd measurements, where $c_1>c_2$.
-The comprehensive results can be found in Table \ref{tab:bias_summary}.
+The comprehensive results can be found in Table \ref{tab:bias_summary} and the single-band coadd result compared to the previously measured values in Fig.
+\ref{fig:final_result}.
 
@@
 This relationship between sampling factor and shear bias was previously explored in \citealt{2021MNRAS.502.4048K} using \emph{Euclid} simulation with different shape measurement algorithms, where they found that the estimated multiplicative bias has a relatively large dependence on the sampling factor.
-Their result can be extrapolated to our single-band coadd results in Figure \ref{fig:final_result}.
-The multiplicative bias of single-band single-epoch measurements for each filter is, \textcolor{red}{1.04$\pm$0.47 per cent for J129, -1.30$\pm$0.46 per cent for H158 and -0.40$\pm$0.53 per cent for F184}.
-When the coadd images for each filter are used, the bias is \textcolor{red}{-0.47$\pm$0.49 per cent for J129, -0.07$\pm$0.45 per cent for H158 and -0.06$\pm$0.61 per cent for F184}.
-We can conclude that in the current \emph{Roman} simulation the multiplicative bias has a similar dependence on the sampling factor as shown in \citealt{2021MNRAS.502.4048K}, but with a smaller amplitude.
+Their result can be extrapolated to our single-band single-epoch results.
+The multiplicative bias of single-band single-epoch measurements is roughly 1\% in each filter.
+When the coadded images for each filter are used, the bias is at the similar level or worse within the uncertainties.
+We can conclude that in the current \emph{Roman} simulation the multiplicative bias has a similar dependence on the sampling factor as shown in K21, but with a smaller amplitude.
 We do not see any clear improvements in the recovered shear when we coadd the single-epoch images, despite having a smaller pixel scale (better sampling) in the images.
-This is most likely due to an issue with how we're currently treating the PSF or correlated noise in the coadding process, given the large observed $c_1$ when coadding discussed below.
+This is most likely due to an issue with how we are currently treating the PSF or correlated noise in the coadding process, given the large observed $c_1$ when coadding discussed below.
 
-The additive bias of the single-band single-epochs measurements for each filter is, \textcolor{red}{(3.22$\pm$0.92)$10^{-4}$ for J129, (2.63$\pm$0.88)$10^{-4}$ for H158 and (3.25$\pm$1.11)$10^{-4}$ for F184}.
-When the measurements are based on coadds, the bias is, \textcolor{red}{(3.39$\pm$0.90)$10^{-4}$ for J129, (8.08$\pm$0.87)$10^{-4}$ for H158 and (9.36$\pm$1.10)$10^{-4}$ for F184}.
+The additive bias of the single-band single-epochs measurements for each filter is smaller about an order of magnitude than that of the coadd measurements.
 The estimated additive bias is the same order as that found in the Y3 analysis in DES, which uses a similar shear calibration pipeline.
@@
 
-\textcolor{red}{You can reference the table of m,c values and just summarize in the text, instead of listing them for all cases again.}
-
 Finally, we discuss the results with multiband measurements.
@@
 One multiband measurement used all of the single epoch images from all the filters and jointly fit the shape of the galaxy.
-The multiplicative and additive bias is, respectively, \textcolor{red}{$m=(-1.34\pm0.67)$ per cent and $c=(2.58\pm1.26)10^{-4}$}.
+The multiplicative and additive bias is, respectively, $m=(-1.34\pm0.67)$ per cent and $c=(2.58\pm1.26)10^{-4}$.
 This result generally agrees with the single-band single-epochs measurements, and is consistent with zero bias at the approx.
 2$\sigma$ level.
-We can't conclude more than that this result may be acceptable without significantly larger simulation volume \textcolor{red}{how large?}.
+We can't conclude more than that this result may be acceptable without significantly larger simulation volume of about 2000 $deg^{2}$.
 The other measurement is performed as a joint-fit across the coadd images for each filter.
-The multiplicative and additive bias is, respectively, \textcolor{red}{$m=(-2.16\pm0.60)$ per cent and $c=(9.24\pm1.22)10^{-4}$}.
+The multiplicative and additive bias is, respectively, $m=(-2.33\pm0.64)$ per cent and $c=(9.47\pm1.16)10^{-4}$.
 Figure \ref{fig:meanshear} shows the relationship between the mean shear and several input and measured properties of galaxies and PSF for all the measurement cases.
-We find that the mean shear has a linear trend as a function of input galaxy size.
-(\textcolor{red}{Any explanation?})
+We find that the mean shear has a linear trend as a function of input galaxy size, though the effect is one order of magnitude smaller than the mean signal.
 
@@
 		\hline
-		\textcolor{red}{single-epochs (J129)} & 1.01 & 1.30$\pm$0.70 & 0.30$\pm$0.63 & 4.65$\pm$1.45 & 1.33$\pm$1.40\\
+		single-epochs (J129) & 1.01 & 1.17$\pm$0.68 & 0.44$\pm$0.75 & 4.46$\pm$1.32 & 0.64$\pm$1.31\\
 		single-epochs (H158) & 1.23 & -1.07$\pm$0.62 & -1.61$\pm$0.66 & 2.83$\pm$1.35 & 2.33$\pm$1.22\\
@@
 		\hline
-		\textcolor{red}{single-band coadd (J129)} & 1.26 & -1.59$\pm$0.64 & -2.31$\pm$0.70 & 11.61$\pm$1.20 & -0.09$\pm$1.34\\
+		single-band coadd (J129) & 1.26 & -1.84$\pm$0.71 & -1.90$\pm$0.65 & 11.99$\pm$1.39 & 0.59$\pm$1.41\\
 		single-band coadd (H158) & 1.54 & -1.91$\pm$0.67 & -2.11$\pm$0.67 & 13.99$\pm$1.34 & 5.40$\pm$1.35\\
@@
 \begin{figure*}
-	\includegraphics[scale=0.5]{final_result.pdf}
+	\includegraphics[width=\textwidth]{final_result.pdf}
     \caption{The multiplicative ($m$) and additive ($c$) bias of the single-band coadd measurements. From left data point to the right, they represent each data for J129, H158, F184 bandpasses. }
@@
 	\includegraphics[scale=0.34]{H158_meanshear_measured_properties_perbin_e1_v2.pdf}
-    \caption{This shows the mean shear residual ($\Delta e_{1}$; $\langle e_{1,measured} \rangle - \langle e_{1,expected} \rangle$) as a function of various properties of galaxies for H158 single-band single-epochs, coadds, and multiband measurements.
+    \caption{(Working on fixing the figure bounds)This shows the mean shear residual ($\Delta e_{1}$; $\langle e_{1,measured} \rangle - \langle e_{1,expected} \rangle$) as a function of various properties of galaxies for H158 single-band single-epochs, coadds, and multiband measurements.
 In this plot, the shear response is computed in each bin.
@@
 
-\section{Discussion}
+\section{Future simulation needs and plan}
 \label{sec:discussion}
 
-We have so far found how \textsc{metacalibration} handles the relatively undersampled \emph{Roman} images without accounting for the effect of blending.
-However, it has been found that the galaxy blending at different redshifts could introduce a significant shear-dependent detection bias when calibrated with \textsc{metacalibration} (e.g., \citealt{2020ApJ...902..138S}).
-In the future study, we will investigate the impact of blending in the image simulations to verify if \textsc{metacalibration} combined with the new version of \texttt{ngmix} can be applied as the shear calibration algorithm in the real survey.
+We have investigated how \textsc{metacalibration} handles the relatively undersampled \emph{Roman} images without accounting for the effect of blending.
+However, it has been found that galaxy blending at different redshifts could introduce a significant shear-dependent detection bias when calibrated with \textsc{metacalibration} (e.g., \citealt{2020ApJ...902..138S}, \citealt{2020arXiv201208567M}).
+In future studies, we will investigate the impact of blending in Roman image simulations and implement an extended pipeline to correct shear-dependent blending/detection biases (e.g.,  \textsc{metadetection}) to explore more realistic shear calibration for the real survey.
 
-Our team continues to increase the realism of the image simulations in the future.
-In the next generation of the simulations, we would like to add the following updates or upgrade these parts of the simulation.
+We have also found our postage-stamp coadd pipeline may be contributing to bias in the shear measurement, even while mitigating the effect of undersampling in the images.
+This may be related to either how the undersampled PSF is treated or correlated noise effects from the simulated detector physics in the simulation.
+Running \textsc{metacalirbation} on simpler simulations without complex PSF shapes or detector effects showed no indication of residual bias at the level we see in the coadd shear calibration estimate.
+Correcting these algorithmic issues is beyond the scope of the current work, and will require a new set of improved simulations and coadd/measurement pipelines.
+It may also require modifications to the \textsc{metacalibration} or \textsc{metadetection} algorithms, which were constructed primarily for ground-based data, so the current calibration results serve as an important benchmark for the performance of current Stage III methods on \emph{Roman} data.
+
+Our team continues to increase the realism of the image simulations for future weak lensing calibration analyses.
+In the next generation of these simulations, we expect to include the following updates or upgrade these parts of the simulation.
 \begin{itemize}
     \setlength\itemsep{1em}
-    \item \textbf{Simulation Volume}: Expand the simulated area by at least 8 times. (Troxel et al. in prep.)
+    \item \textbf{Simulation Volume}: Expand the simulated area to 20 $deg^{2}$. (Troxel et al. in prep.)
 
-    \item \textbf{Near-Infrared Detector Effects}: Incorporate the detector effects measured in the real flight candidate detectors and produce two catalogs with and without them to determine the impact on the final cosmology result.
+    \item \textbf{Near-Infrared Detector Effects}: Incorporate more realistic detector effects as measured in tests on the flight-candidate detectors and produce two versions of the simulation with and without them to determine the impact on the final cosmology result.
 
-    \item \textbf{Image Coadditions}: Implement a new coadding methodology which coadds the whole scene instead of individual stamp cutouts (e.g., \texttt{AstroDrizzle}\footnote{\url{https://github.com/spacetelescope/drizzlepac}}: A Python implementation of MultiDrizzle which was used for \emph{Hubble} Space Telescope (\citealt{2003hstc.conf..325B})).
-With \texttt{AstroDrizzle} which employs the linear reconstruction of the individual images, we are able to further mitigate the effect of undersampled \emph{Roman} images.
-If we set the final coadd pixel scale with \texttt{AstroDrizzle} to be 70\% smaller than the original \emph{Roman} pixel scale, F184 will be fully sampled (Q > 2) and J129 will be sampled at the similar level with F184 without coadding.
+    \item \textbf{Image Coaddition}: We will implement a new coaddition strategy that coadds the whole scene instead of individual stamp cutouts using  \texttt{AstroDrizzle}\footnote{\url{https://github.com/spacetelescope/drizzlepac}}: A Python implementation of MultiDrizzle which was used for \emph{Hubble} Space Telescope (\citealt{2003hstc.conf..325B}).
+With \texttt{AstroDrizzle}, we are able to further mitigate the effect of undersampling in the \emph{Roman} images by going to smaller coadd pixel scales.
+We expect this to further reduce the measured shear bias by up to 1\% based on its trend with sampling factor.
 
-    \item \textbf{Source Detection}: Implement a source detection methodology with \texttt{Photutils}\footnote{\url{https://photutils.readthedocs.io/en/stable/}} on the coadds.
+    \item \textbf{Source Detection}: Implement a source detection and deblending methodology to allow more realistic tests of shear recovery.
 
-    \item \textbf{Selection Cuts}: Implement quality assurance cuts (e.g., S/N) on the shape catalog to avoid the noise on the shape fit and compute the measurement biases accounting for the selection effects (\citealt{2017ApJ...841...24S}).
+    \item \textbf{Selection Cuts}: Simulate objects to below the detection threshold of the survey and incorporate standard quality assurance cuts (e.g., S/N) on the shape catalog (\citealt{2017ApJ...841...24S}).
 \end{itemize}
-\textcolor{red}{Ongoing work to make a reference survey. }
 
 \section{Conclusions}
+We explored the performance of the \textsc{metacalibration} shape measurement calibration algorithm and presented the first shear calibration result on a realistic simulated \emph{Roman} HLIS.
+Accurately characterizing how much shear estimates are biased using realistic simulated survey images is a requirement to successfully complete the weak lensing program of the \emph{Roman} HLIS.
+In the current simulation framework, by coadding the single-epoch cutout images and using an oversampled PSF model, we found that shear estimates with an are still biased at the percent level using implementation of \textsc{metacalibration} that is similar to that used by ground-baesd Stage III surveys.
+To further constrain the shear calibration bias in the simulations and validate that the \emph{Roman} mission will be able to achieve the weak lensing calibration required for the survey, we need both more simulation volume -- about 400 times the area of the current simulation -- as well as significant improvements to the coadd and measurement pipelines currently used in this work.
+
+We find that our results are similar to what was previously found for \textsc{metacalibration} bias on undersampled images in the study by K21 using image simulations built for \emph{Euclid}, but at a lower level, due to differences in how we perform the shape fitting.
+Thus, our study further confirms the need for better treatment of the undersampled images for weak lensing.
+In future versions of the \emph{Romaan} simulations that are currently being developed, we will both be able to increase the simulation volume significantly and produce coadd images with a smaller pixel scale for shape measurement.
+With these and other changes to improve the realism of the simulations and measurement pipelines used with them, we will be able to better explore the possible origins of the current percent level residual shear bias and study mitigation strategies in order to reach the \emph{Roman} weak lensing mission requirement.
 \label{sec:conclusion}
-We explored the performance of \textsc{metacalibration} shape measurement calibration algorithm with \textsc{psc} coadding scheme to reduce the shear calibration bias in the image simulation framework of the \emph{Roman} Space Telescope.
-Accurately characterizing how much shear bias exists in this framework is required to successfully complete the weak lensing program of the High-Latitude Survey of the \emph{Roman}.
-By coadding the single-epoch images and oversampling the PSF for a better shape fit, we find that shear estimates with \textsc{metacalibration} are slightly biased within 1 $\sigma$.
-We conclude that to further constrain the shear calibration bias in the simulation and determine if the \emph{Roman} mission will be able to achieve the bias required for the survey without further developing new techniques that the current Stage-III imaging surveys do not use, we need more simulation volume well beyond the 2.5 deg$^{2}$ area of the simulated sky.
 
@@
 
-We thank Matthew Becker, Erin Sheldon, and Arun Kannawadi for many useful discussions. This work was supported by xx funding agencies.
+We thank Matthew Becker and Erin Sheldon for the useful discussions on the use of \texttt{ngmix}, and Arun Kannawadi for the consultation on his \emph{Euclid} shape measurement work.
+This work was supported by xx funding agencies.
 

### 2021-11-22 scratch.tex
v2

--- 2021-11-03 roman_metacal.tex
@@
-% mnras_template.tex 
-%
-% LaTeX template for creating an MNRAS paper
-%
-% v3.0 released 14 May 2015
-% (version numbers match those of mnras.cls)
-%
-% Copyright (C) Royal Astronomical Society 2015
-% Authors:
-% Keith T. Smith (Royal Astronomical Society)
-
-% Change log
-%
-% v3.0 May 2015
-%    Renamed to match the new package name
-%    Version number matches mnras.cls
-%    A few minor tweaks to wording
-% v1.0 September 2013
-%    Beta testing only - never publicly released
-%    First version: a simple (ish) template for creating an MNRAS paper
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% Basic setup. Most papers should leave these options alone.
-\documentclass[fleqn,usenatbib]{mnras}
-
-% MNRAS is set in Times font. If you don't have this installed (most LaTeX
-% installations will be fine) or prefer the old Computer Modern fonts, comment
-% out the following line
-\usepackage{newtxtext,newtxmath}
-% Depending on your LaTeX fonts installation, you might get better results with one of these:
-%\usepackage{mathptmx}
-%\usepackage{txfonts}
-
-% Use vector fonts, so it zooms properly in on-screen viewing software
-% Don't change these lines unless you know what you are doing
-\usepackage[T1]{fontenc}
-
-% Allow "Thomas van Noord" and "Simon de Laguarde" and alike to be sorted by "N" and "L" etc. in the bibliography.
-% Write the name in the bibliography as "\VAN{Noord}{Van}{van} Noord, Thomas"
-\DeclareRobustCommand{\VAN}[3]{#2}
-\let\VANthebibliography\thebibliography
-\def\thebibliography{\DeclareRobustCommand{\VAN}[3]{##3}\VANthebibliography}
-
-%%%%% AUTHORS - PLACE YOUR OWN PACKAGES HERE %%%%%
-\usepackage{indentfirst}
-\usepackage{physics}
-\usepackage{lineno}
-\linenumbers
-\usepackage{ulem}
-% Only include extra packages if you really need them. Common packages are:
-\usepackage{graphicx}	% Including figure files
-\usepackage{amsmath}	% Advanced maths commands
-\usepackage{amssymb}	% Extra maths symbols
-\usepackage{xcolor}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%% AUTHORS - PLACE YOUR OWN COMMANDS HERE %%%%%
-
-% Please keep new commands to a minimum, and use \newcommand not \def to avoid
-% overwriting existing commands. Example:
-%\newcommand{\pcm}{\,cm$^{-2}$}	% per cm-squared
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%% TITLE PAGE %%%%%%%%%%%%%%%%%%%
-
-% Title of the paper, and the short title which is used in the headers.
-% Keep the title short and informative.
-\normalem
-\title[Metacalibration with Roman High-Latitude Imaging Survey]{Weak gravitational lensing shear estimates with \textsc{metacalibration} for the High-Latitude Imaging Survey Program of the \emph{Roman} Space Telescope}
-
-% The list of authors, and the short list which is used in the headers.
-% If you need two or more lines of authors, add an extra line using \newauthor
-\author[M. Yamamoto et al.]{
-Masaya Yamamoto,$^{1}$\thanks{E-mail: masaya.yamamoto@duke.edu}
-Michael A. Troxel,$^{1}$
-Mike Jarvis,$^{2}$
-Rachel Mandelbaum,$^{3}$
-Christopher Hirata$^{4,5,6}$
-\\
-% List of institutions
-$^{1}$Department of Physics, Duke University, Durham, NC, 27710\\
-$^{2}$Department of Physics and Astronomy, University of Pennsylvania, Philadelphia, PA 19104, USA\\
-$^{3}$McWilliams Center for Cosmology, Department of Physics, Carnegie Mellon University, Pittsburgh, Pennsylvania 15213, USA\\
-$^{4}$Center for Cosmology and Astro-Particle Physics, The Ohio State University, 191 West Woodruff Avenue, Columbus, OH 43210, USA\\
-$^{5}$Department of Physics, The Ohio State University, 191 West Woodruff Avenue, Columbus, OH 43210, USA\\
-$^{6}$Department of Astronomy, The Ohio State University, 140 West 18th Avenue, Columbus, OH 43210, USA\\
-}
-
-% These dates will be filled out by the publisher
-\date{Accepted XXX. Received YYY; in original form ZZZ}
-
-% Enter the current year, for the copyright statements etc.
-\pubyear{2015}
-
-% Don't change these lines
-\begin{document}
-\label{firstpage}
-\pagerange{\pageref{firstpage}--\pageref{lastpage}}
-\maketitle
-
-% Abstract of the paper
-\begin{abstract}
-We investigate the performance of the \textsc{metacalibration} in the framework of the \emph{Nancy Grace Roman} Space Telescope (\emph{Roman}) image simulations.
-Compared with the non-calibrated results from the previous work, \textsc{metacalibration} can significantly reduce the shear calibration bias.
-Exploring shear bias is a robust way to test the requirements of the instrument and the overall weak lensing survey strategy.
-The weak lensing program of \emph{Roman} mission requires the galaxy shapes to be calibrated within about 0.03\%.
-To reach this goal, we can test our calibration scheme with these simulations and can isolate the sources where these residual shear biases arise.
-We incorporate \textcolor{red}{several new updates that are more realistic} and necessary to calibrate shear with a better precision relative to the previous version of the simulations.
-Without the coadditions of the single epoch images, across all three filters we are able to achieve the multiplicative bias of 0.70 per cent within 1.8 $\sigma$.
-Meanwhile, average additive bias is not consistent with zero due to the strong correlation with the input PSF for one of the spin-2 component directions.
-This additive bias is worse for the coadded images, while \textcolor{red}{the average multiplicative bias for multiband coadds was xxx}.
-We find no evidence that shape calibration becomes worse with decreasing image sampling factor based on the Nyquist sampling theorem.
-Overall, within the current simulation volume, we find that \textsc{metacalibration} can calibrate shapes with zero shear bias on relatively undersampled images that \emph{Roman} will produce.
-In the future, we will need to substantially increase the simulation volume by 8 to reach the accuracy necessary for the program.
-\end{abstract}
-
-% Select between one and six entries from the list of approved keywords.
-% Don't make up new ones.
-\begin{keywords}
-gravitational lensing: weak -- cosmology: observations -- techniques: image processing
-\end{keywords}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%% BODY OF PAPER %%%%%%%%%%%%%%%%%%
-
-\section{Introduction}
-
-Since the formulation of the physical cosmological model, more observational evidence has shown that the contents of the universe are mostly in the dark sector (\citealt{2020A&A...633A..69H, 2018PhRvD..98d3528T, 2019PhRvL.122q1301A, 2019PASJ...71...43H, 2021A&A...645A.104A}).
-Within the sector, dark energy accounts for the accelerating expansion of the universe (e.g., \citealt{1998AJ....116.1009R, 1999AIPC..478..129P}) and the combination of dark energy and dark matter which only interacts with non-relativistic matter are responsible for the growth of the large-scale structure (\citealt{2015RPPh...78h6901K, 2017grle.book.....D}).
-The growth can be studied by carefully reconstructing the paths of the light leaving distant galaxies and going through the region where masses concentrate in the universe; this physical phenomenon is called gravitational lensing.
-“Weak” gravitational lensing causes a slight distortion to intrinsic galaxy shapes when observed from the Earth.
-By detecting millions of these gravitationally lensed galaxies and computing their distortion levels, we can explore the matter density and the amplitude of matter fluctuation in the universe (e.g., \citealt{2001PhR...340..291B}).
-Measuring these quantities eventually help us learn the history of the development of the large-scale structure in the universe.
-For that reason, weak lensing is and will continue to be one of the powerful probes in the current and next-decade imaging surveys to constrain cosmological parameters with high precision.
-\par
-
-Due to the subtlety in the lensing effect and its systematics dominant nature in the “weak” regime, observational efforts have been challenging.
-Over the past decade, large international collaborations such as the Dark Energy Survey\footnote{\url{http://www.darkenergysurvey.org/}} (DES: \citealt{2005astro.ph.10346T}), the Hyper Supreme-Cam\footnote{\url{http://hsc.mtk.nao.ac.jp/ssp/}} (HSC: \citealt{2018PASJ...70S...4A}), and the Kilo-Degree Survey\footnote{\url{http://kids.strw.leidenuniv.nl/}} (KiDS) have been successful at constraining the cosmological parameters, and the precision in calibrating the shapes of distant galaxies has reached a few percent (\citealt{2020arXiv201103408G, 2020arXiv201208567M, 2021A&A...645A.105G}).
-As we cover more areas in the sky and develop better tools (observatories and algorithms), we find more galaxies and we have already reached to the point where statistical and systematic uncertainties are comparable.
-Thus, the next-decade legacy surveys, the Stage IV surveys (\citealt{2006astro.ph..9591A}) such as Euclid\footnote{\url{ http://sci.esa.int/euclid}} (Euclid Study Scientist \& the Science Advisory Team 2010), the Vera C.
-Rubin Observatory Legacy Survey of Space and Time\footnote{\url{ http://www.lsst.org}} (LSST: \citealt{2009arXiv0912.0201L, 2019ApJ...873..111I}), and \emph{Nancy Grace Roman} Space Telescope\footnote{\url{https://roman.gsfc.nasa.gov}} (\emph{Roman}: \citealt{2015arXiv150303757S}) require even better control of systematics.
-In order to manage the systematic uncertainties, we must develop realistic image simulations, apply the pre-existing shape measurement on the simulated images, and determine any potential systematic effects and build the strategy of mitigating them.
-
-Based on our current knowledge, systematic biases for weak lensing science, both observational and astrophysical, could occur throughout imaging surveys (e.g., \citealt{2018ARA&A..56..393M}).
-Particularly, observational systematics can be found in,
-\begin{itemize}
-    \item observing strategy
-    \item instrumentation effects such as Brighter-Fatter Effect
-    \item post-processing pipeline such as image coaddition and object detection
-\end{itemize}
-
-In this study, we focus on shear calibration bias, which describes the relationship between gravitational lensing shear and measured galaxy shapes.
-In the limit of weak lensing ($\lvert\gamma\rvert\ll1$), the ensemble average of ellipticities $\langle e \rangle$ of galaxy shapes is directly related to the shear field $\gamma$, and the estimated shear can be written as a linear model with multiplicative ($m_{i}$) and additive bias ($c_{i}$) as described in the equation below.
-(\citealt{2006MNRAS.368.1323H, 2006MNRAS.366..101H, 2007MNRAS.376...13M})
-\begin{equation}
-    \gamma^{obs}_{i} = (1+m_{i})\gamma^{true}_{i} + c_{i}, 
-    \label{eqn:linear}
-\end{equation}
-where i=(1,2) and $\gamma^{obs}_{i}$ is the two-component observed shear after calibrations and $\gamma^{true}_{i}$ is the true shear.
-The bias arises for various reasons.
-For space-based surveys, the bias can be mainly introduced in places such as PSF modelling, blending, and the undersampling of the image (e.g., \citealt{2018ARA&A..56..393M}).
-Additionally, complex detector effects such as brighter-fatter effect are the potential sources of bias (\citealt{2013MNRAS.429..661M}), where it is shown that for \emph{Roman} the effect of persistence will not be an issue (\citealt{2021arXiv210610273L}).
-Qualitatively, if the recovered shear is biased by 1$\%$ (m=0.01), $S_{8} = \sigma_{8} \sqrt{\Omega_{m}/0.3}$ would be biased about 1.5$\%$ in the final cosmology result.
-Thus, quantifying these biases before the real survey is extremely important.
-\par
-
-Several shear calibration and bias mitigation efforts have been proposed by STEP (\citealt{2006MNRAS.368.1323H, 2007MNRAS.376...13M}) and GREAT (\citealt{2010MNRAS.405.2044B, 2013ApJS..205...12K, 2015MNRAS.450.2963M}) challenges, to meet the requirements for the current imaging surveys.
-In particular, one of the state-of-the-art self-calibration methods, \textsc{metacalibration} (\citealt{2017arXiv170202600H, 2017ApJ...841...24S}) has been shown to be able to reduce the significant of shear bias.
-It has also confirmed that the shear can be calibrated with \textsc{metacalibration} at a-few-percent level in DES (\citealt{2018MNRAS.481.1149Z, 2020arXiv201103408G}), without accounting for galaxy blending.
-Tackling the issue of blending is on the way of DES Y6 analysis with the shear-dependent detection and calibration technique (\textsc{metadetect}; \citealt{2020ApJ...902..138S}).
-While the major advantage of \textsc{metacalibration} is that it can be directly applied upon real galaxy images, which does not depend on galaxy morphology in simulations, the limitations for future surveys are not well-known.
-One possible limitation might lie in the effect of the undersampled images, because future space-based surveys like \emph{Euclid} and \emph{Roman} have such a small pixel scale that galaxy images will not be Nyquist sampled at a native resolution (\citealt{2013PASP..125.1496S}) based on the Nyquist-Shannon Sampling Theorem.
-We define the sampling factor of each filter in \emph{Roman} to be,
-\begin{equation}
-    Q = \frac{\lambda_{min}N_{f}}{p}, 
-    \label{eqn:sampling}
-\end{equation}
-where $\lambda_{min}$ is the shortest wavelength of the incident light in the filter, $N_{f}$ is the focal ratio of the telescope ($N_{f}=7.8$ for \emph{Roman}) and $p$ is the pixel spacing of the sensor ($p=10\mu m$ for \emph{Roman}).
-The image with the sampling factor, $Q < 2$, is not Nyquist sampled and reffered to as the undersampled image.
-It is problematic to measure galaxy shapes solely from the undersampled images, because the \emph{Roman} PSF that will be used to recover the shapes is also undersampled and has a complex structure, not simply Gaussian.
-\textcolor{red}{It is, therefore, necessary to build a robust strategy that can reconstruct better sampled PSF to allow unbiased shape measurement.
-}
-
-Recently, Kannawadi et al.
-(2021) addressed this potential issue of the limitations of \textsc{metacalibration} on undersampled images on \emph{Euclid} image simulations.
-They found that for \emph{Euclid} mission the shear estimate is biased about 1$\%$ (\citealt{2021MNRAS.502.4048K}).
-It is mentioned that their result could be extended to the \emph{Roman} mission due to their similarities in the instruments and for \emph{Roman} they predicted the multiplicative bias was more than 1\% for H158 and F184 filters.
-Regardless of this extended result, we should validate if \textsc{metacalibration} is unbiased with the image simulations specifically made for the \emph{Roman} mission.
-Our work is based on the image simulation suite of the \emph{Roman} Space Telescope developed by \citet{2021MNRAS.501.2044T}, where we render star and galaxy images from \texttt{GalSim}\footnote{\url{ https://github.com/GalSim-developers/GalSim}} (\citealt{2015A&C....10..121R}).
-With a few simulation updates and an implementation of \textsc{metacalibration}, we can start to explore if the shear calibration goal of the High-Latitude Survey program for \emph{Roman} ($m=~3.2\times10^{-4}$) (\citealt{2019BAAS...51c.341D}) can be achieved.
-\par
-
-This paper is organized as follows.
-We briefly discuss the simulation suite details we used and the updates we implemented for this project in Sec.~\ref{sec:sims}.
-Then, in Sec.~\ref{sec:methods}, we show how coadditions of single exposure postage stamps are produced and how shape measurements are completed using \textsc{metacalibration}.
-We present the galaxy catalog properties and calibration results for single-band and multiband measurements in Sec.~\ref{sec:results}.
-Finally, in Sec.~\ref{sec:discussion}, we discuss how we will be able to constrain the shear bias better in terms of further updates in the image simulations and what we can conclude from this study.
-
-\section{Simulations}
-\label{sec:sims}
-In this section, we briefly summarize the full simulation details from building a truth catalog to measuring galaxy shapes. Then we describe the simulation updates that are implemented for this work.
-\subsection{Simulation Summary}
-\label{subsec:imsim}
-The base of our image simulations of the \emph{Roman} Space Telescope is the \emph{Roman} simulation suite\footnote{\url{ https://github.com/matroxel/roman_imsim}} developed by \citet{2021MNRAS.501.2044T}, which renders realistic galaxy and star images on 18 Sensor-Chip Assemblies (SCAs) of a 2.5$\times$2.5 deg$^{2}$ patch of the sky provided the observing strategy for the 5-year reference mission and Cycle7 specifications\footnote{\url{https://roman.gsfc.nasa.gov/science/Roman_Reference_Information.html}}.
-We begin by creating a truth catalog using the simulated galaxy distribution from the Buzzard simulation (\citealt{2019arXiv190102401D}), photometric galaxy catalog sampled from the CANDELS survey (e.g., \citealt{2019ApJ...877..117H}), and Milky Way simulation (Galaxia; \citealt{2011ApJ...730....3S}) for star positions and magnitudes.
-Then, the following properties are applied to each galaxy.
-\begin{itemize}
-    \item positions (RA, Dec)
-    \item photometries for each \emph{Roman} filter (F184/H158/J129/Y106)
-    \item intrinsic galaxy shapes and random orientations
-    \item flux ratios of de Vaucouleurs bulge, exponential disk, and star-forming knots
-    \item artificial gravitational lensing shears
-\end{itemize} 
-Within the identical realizations of the simulation, we produce four truth catalogs using four sets of gravitational shears ($e_{1}$, $e_{2}$)=\{(+0.02, 0.00), (-0.02, 0.00), (0.00, +0.02), (0.00, -0.02)\}.
-This approach helps us to reduce shape and measurement noise when taking the difference in recovered shapes to compute multiplicative bias (\citealt{2019A&A...621A...2P}).
-
-The next step of the process is to create postage stamps and SCA images using \texttt{GalSim}.
-In this stage, Point-Spread Function (PSF) is convolved with the stamps.
-Here, the \emph{Roman} PSF is rendered using the \texttt{galsim.roman} module under \texttt{GalSim}, which has implemented \emph{Roman}-specific instrument properties such as the PSF and World Coordinate System (WCS).
-The module is able to estimate an object position on the sky in RA, Dec using the \emph{Roman} WCS and produce the \emph{Roman} PSF which, for example, correctly describes the diffraction spikes pattern made by the struts and camera in the pupil plane.
-
-After we generate the object stamps across all the SCAs and pointings, we create Multi-Epoch Data Structure (MEDS) files in which each unique object dictionary contains information of all the exposures.
-These MEDS files are generated according to the Hierarchical Equal Area isoLatitude Pixelisation (HEALPix) of $n_{side}=512$.
-These MEDS files contain all objects that are located in the area of the sky partitioned according to a HEALPix of $n_{side}$=512.
-Once the objects are sorted in MEDS files, we pass these multiple exposures with the corresponding PSF to \textsc{ngmix}\footnote{\url{ https://github.com/esheldon/ngmix}} to fit the galaxy shapes with the Gaussian mixture fitting method (\citealt{2014MNRAS.444L..25S}).
-This shape measurement process produces shape catalogs from which the shear calibration bias can be calculated with \textsc{metacalibration}.
-
-\begin{figure}
-	\includegraphics[width=\columnwidth]{figure1.pdf}
-	\vspace*{-3mm}
-    \caption{The rotation of the Roman PSF produced from the \texttt{galsim.roman} module.
-Position angle (PA) which determines the rotation of the telescope is $0^{\circ}$ and $30^{\circ}$.
-The rotation of the PSF is particularly important when an object has multiple exposures and needs to be coadded.
-If each galaxy image is rotated but each PSF is not, the coadded PSF would have a particular pattern and its shape would not be averaged down.
-By correctly rotating the PSF that is convolved with galaxy images, the effect of the PSF on the recoverd galaxy shape will be less.}
-    \label{fig:psfrot}
-\end{figure}
-
-\begin{figure*}
-	\includegraphics[width=\textwidth]{figure2.pdf}
-	\vspace*{-10mm}
-    \caption{The top row shows the first entry of the single epoch images and its coadded image, single and coadded oversampled PSF for an object with low signal-to-noise ratio (S/N=9.69).
-The bottom row shows the same for an object with high signal-to-noise ratio (S/N=1552.97).}
-    \label{fig:singlecoadd}
-\end{figure*}
-
-\subsection{Simulation Updates}
-In order to accomplish science goals, and build and test the pipelines of weak lensing program in \emph{Roman}, we must keep updating the simulations to be more realistic.
-We have implemented and made updates to the following parts of the simulation framework to be able to measure unbiased shapes with \textsc{metacalibration}.
-\begin{itemize}
-    \setlength\itemsep{1em}
-    \item \textbf{Saturation Cuts}:
-    We have implemented the pixel saturation of 100,000 electrons.
-This value is an approximate pixel saturation but in the next generation of the simulations we will use the true saturation from the flight candidate detectors.
-
-    \item \textbf{Rotation of the \emph{Roman} PSF on the sky}:
-    In the study by Troxel et al.
-(2021), the rotations of the \emph{Roman} PSF with respect to the telescope rotation were not engaged properly by \texttt{galsim.roman} module.
-Since a non-rotating PSF could trigger a preferred direction in the shapes when being deconvolved, we believe that this contributed to the non-zero multiplicative bias result.
-There has been an update in \texttt{galsim.roman} module to correctly rotate the PSF given the WCS on the SCA.
-Figure \ref{fig:psfrot} shows a toy PSF of the same pointing but with a different rotation angle of the telescope.
-
-    \item \textbf{Single-band and Multiband Coadds}: 
-    We have added and modified the postage stamp coadds (\texttt{psc}) algorithm\footnote{\url{https://github.com/esheldon/psc}} to create coadditions of single-epoch postage stamps.
-Coadds are usually performed to enhance the signal-to-noise ratio (S/N) of an object and mitigate the measurement noise.
-If we take advantage of fitting an object in the coadd instead of fitting multiple images of each object in each filter, we can save a factor of 6 in computing time, which is the average number of exposures from the reference survey.
-Additionally, coadding is one way to reduce the effect of the undersampling of the images since the coadd is naturally better sampled.
-For these reasons, we must utilize a coadding scheme for the \emph{Roman} galaxies.
-The detailed overview of the coadd process in \texttt{psc} is in Sec.
-\ref{subsec:psc}.
-
-    \item \textbf{\textsc{metacalibration} in \textsc{ngmix}}: We implemented \textsc{metacalibration}\footnote{\url{https://github.com/esheldon/ngmix/wiki/Metacalibration}} bootstrapper method, which is a wrapper class to run measurements in the \textsc{ngmix} package and is used extensively to produce weak lensing shape catalog in DES Y3 analysis.
-\textsc{metacalibration} process takes place after making coadded images.
-\textsc{ngmix} is able to fit multiple exposures in case for measuring shapes on single-epoch images.
-With this calibration method, we hope to significantly reduce some of the shear calibration bias Troxel et al.
-(2021) measured.
-The detailed overview of \textsc{metacalibration} can be found in Sec.\ref{subsec:mcal}.
-    %\item (Any other changes?)
-\end{itemize}
-
-%\subsection{Simple Simulations}
-%\label{subsec:simplesim}
-%The purpose of the simple simulations is to verify that there are no systematic biases at the basic levels of the simulation (e.g., no complex detector effects).
-The simple simulation is based on the real observational pointing strategy, and we use the real Sensor-Array Chips (SCAs) scheme, the band filters and the pixel scale as basic Roman specifications.
-
-\section{Post-catalog Processes}
-\label{sec:methods}
-Our goal is to show that the recovered shapes with \textsc{metacalibration} are non-biased.
-In order to do so, we need to build a measurement pipeline within the current simulation framework that contributes to the final measurement.
-In this section, we present in detail how coadds are produced with \texttt{psc} from the undersampled single-epoch images, how \textsc{metacalibration} calibrates shapes, and how we measure the shear calibration bias from the \textsc{metacalibration} catalog.
-
-\subsection{Postage Stamp Coadds}
-\label{subsec:psc}
-Coaddition is the process that reconstructs a Nyquist-sampled image out of multiple exposures of an object.
-While this process can benefit in increasing the S/N value of an object and reducing the impact of pixel noise, several challenges need to be addressed for images taken with telescopes that can rotate.
-When the rotation is introduced, this coadding process becomes more complex to interpolate the image to stack pixel grid.
-While coaddition could introduce systematic bias due to the complexity of the original PSF and its interpolation scheme, the bias with the undersampled images can be overcome \textcolor{red}{by the combinations of the effective coadding process and the careful treatment of the input PSF}.
-We describe our coaddition pipeline that is based on \texttt{psc}.
-
-We reconstruct the Nyquist-sampled image from multiple exposures in MEDS files.
-For the coaddition of the PSF, we choose to coadd the image with the oversampled PSF.
-We oversample the original PSF by a factor of 4 to simulate the better sampled PSF that \emph{Roman} will eventually produce when it constructs the PSF from the full focal plane.
-It will be highly resolved than native pixel scale.
-For each exposure of the object we render the \emph{Roman} PSF with a stamp size of 32 pixels at the galaxy centroid, not the image centroid.
-We modified the original code to improve performance of the \textsc{metacalibration} process later, and these modifications are listed below with the general coadding process in \texttt{psc}.
-
-The algorithm: 
-\begin{enumerate}
-    \setlength\itemsep{1em}
-    \item Finds the wcs of the first exposure of the object.
-    \item Translates the original wcs to a flat wcs, because it produces stable results with \textsc{ngmix}.
-    \item Creates the coadd stamp with 0.8 $\times$ original pixel scale.
-We scale the original pixel scale of the final coadd stamp to minimize the effect of undersampling.
-We noticed that too much oversampling can introduce the artifacts into the structure of the PSF.
-    \item Creates the interpolated image with \texttt{GalSim} with the center offset for each image with \texttt{lanczos3} resampling method.
-Out of several interpolation methods we tried, \texttt{lanczos3} produced the best coadd of the PSF.
-    \item Recreates the coadded noise image from the weight of the original weight map.
-\end{enumerate}
-
-Figure \ref{fig:singlecoadd} shows an example of the simulated single-epoch and coadded images and PSFs for objects with low and high S/N.
-Note that the shape and struts pattern in the original PSF can be washed out by coadding the rotationally dithered PSFs.
-
-Before we calibrate and measure shapes with \textsc{ngmix}, we downsample the high-resolution PSF to the original pixel size.
-Figure \ref{fig:coadd_oversample_res} shows the coadded oversampled PSF and the then-downsampled PSF, and their differences.
-We downsampled the oversampled PSF (128 x 128 pixels) by summing 4 square-pixels and creating the original size PSF (32 x 32 pixels), in order to ensure that the shape fit with \textsc{ngmix} can be processed.
-Since a better sampled PSF generally enables the shape of the PSF to be more isotropic, we can state that the original PSF can lead to the biased shape measurement from Figure \ref{fig:coadd_oversample_res}.
-
-\begin{figure}
-	\includegraphics[width=\columnwidth]{figure3.pdf}
-    \vspace*{-5mm}
-    \caption{The left and middle panel of the figure illustrates the coadded \emph{Roman} PSF at its native pixel scale and the coadded PSF with a pixel scale that is oversampled by a factor of 4 and then down-sampled.
-These are visualized in a log scale.
-The right panel shows the difference image between the two linear-scaled PSFs.
-}
-    \label{fig:coadd_oversample_res}
-\end{figure}
-
-Finally, Figure \ref{fig:single_to_coadd_rgb} shows the coadd products in different bandpasses for a relatively high S/N object.
-It is worth noting that the multiband PSF is the oversampled version for a visualization purpose.
-
-\begin{figure*}
-	\includegraphics[width=\textwidth]{figure4_og.pdf}
-    \vspace*{-20mm}
-    \caption{The left 3 panels show an example of the coadded galaxy images for each filter.
-The S/N for each filter is S/N=2292, 1558, 1336.
-The 4th and 5th panels show the multiband coadd images of the same object; each with xxx scale and RGB scale.
-The S/N of the image is S/N=1755.
-Finally, the right-most panel shows the coadded oversampled PSF with the original scale.}
-    \label{fig:single_to_coadd_rgb}
-\end{figure*}
-
-\par
-
-\subsection{Shape Measurement with \textsc{metacalibration}}
-\label{subsec:mcal}
-Once we construct the coadds from the galaxy catalogs to recover the shear signal, we feed them into the \textsc{metacalibration} process.
-The bootstrapper method in \textsc{ngmix} wraps the \textsc{metacalibration} and the shape fit steps.
-The priors passed to the fit are listed below.
-
-\begin{table}
-    \centering
-    \begin{tabular}{|p{3cm}||p{3cm}|p{3cm}|p{3cm}|}
-    \hline
-    Prior & Value \\
-    \hline
-    Pixel centroid offset & 0 < $p_{x,y}$ < 0.11\\
-    Shear & $|g|=1.0$, $\sigma_{|g|} = 0.3$\\
-    Half-light radius & $10^{-5}$ < T < $10^{4}$\\
-    Flux fraction of the bulge component & $\langle f\rangle = 0.5$, $\sigma_{f} = 0.1$\\
-    Total flux & $0$ < F < $10^{6}$\\
-    \hline
-    \end{tabular}
-    \caption{List of prior values used for the Gaussian mixture fit.}
-    \label{tab:priors}
-\end{table}
-
-Once we have the \textsc{metacalibration} catalog, we can calculate shear calibration bias from the measured object ellipticities, $\vb*{e}$ = ($e_{1}$, $e_{2}$).
-The observed ellipticities can be approximated using a Taylor expansion around the two-component shear, $\vb*{\gamma}=0$.
-Higher terms here can be dropped assuming the gravitational shear is small.
-It is also known that \textsc{metacalibration} works under the same assumption, otherwise the recovered shear would be biased.
-It is challenging to find a good input shear that results in higher S/N of an object and unbiased shape measurement.
-We verify that our input gravitational shear is unbiased in \textsc{metacalibration} framework and the uncertainty in the recovered shape is small enough by constructing the same but simpler framework of the fiducial image simulations which renders Gaussian profile galaxy and PSF on the \emph{Roman} pixel scale cutout image without any detector effects.
-Figure \ref{fig:metacal_shear_linear} demonstrates that even with the simple enough simulations \textsc{metacalibration} becomes biased after $g=0.05$ since the assumption is starting to break down.
-\begin{equation}
-    \vb*{e} = \vb*{e}\rvert_{\vb*{\gamma}=0} + \frac{\partial \vb*{e}}{\partial \vb*{\gamma}}\bigg\rvert_{\vb*{\gamma}=0}\vb*{\gamma} + \ldots
-\end{equation}
-From this expression, the shear response matrix can be defined as, 
-\begin{equation}
-    \vb*{R} \equiv \frac{\partial \vb*{e}}{\partial \vb*{\gamma}}\bigg\rvert_{\vb*{\gamma}=0} = 
-    \begin{pmatrix}
-        \partial e_{1}/\partial \gamma_{1} & \partial e_{2}/\partial \gamma_{1} \\ 
-        \partial e_{1}/\partial \gamma_{2} & \partial e_{2}/\partial \gamma_{2}
-    \end{pmatrix}. 
-\end{equation}
-For each redshift bin, the ensemble mean of measured ellipticities $\langle\vb*{e}\rangle$ is computed.
-Since we expect galaxies in the redshift bin to be randomly oriented such that $\langle\vb*{e}\rangle\rvert_{\vb*{\gamma}=0}=0$, we have a relationship between the measured ellipticities and the input shear in the simulations,
-\begin{equation}
-    \langle\vb*{e}\rangle \approx \langle \vb*{R}\vb*{\gamma} \rangle. 
-\end{equation} 
-In actual observations, the observable is the galaxy shapes $\langle\vb*{e}\rangle$ and we can take advantage of image simulations and calculate the shear response of the particular calibration technique we employ, and finally compute the gravitational lensing shear signal $\langle\vb*{\gamma}\rangle$.
-
-\begin{figure}
-	\includegraphics[width=\columnwidth]{metacal_bias_shear.png}
-    \vspace*{-5mm}
-    \caption{It shows the quadratic relationship between the input gravitational shear for the simple simulations and the multiplicative bias estimated from the recovered shape in the \textsc{metacalibration} catalogs.
-}
-    \label{fig:metacal_shear_linear}
-\end{figure}
-
-\textsc{metacalibration} creates one unsheared and four artificially-sheared images of each galaxy stamp.
-Each is deconvolved with the original PSF, unsheard or sheared with the gravitational shear of $\gamma=0.01$ in four directions ($+g1$, $-g1$, $+g2$, $-g2$) and re-convolved with a new slightly larger isotropic, Gaussian PSF.
-In our simulation framework, we know the exact input shear and five measured galaxy shapes for each galaxy produced by \textsc{metacalibration} and fitted with the Gaussian mixture method in \textsc{ngmix}.
-We can calculate the ensemble mean of the shear response from the five versions of \textsc{metacalibration} catalog with the equation below.
-
-\begin{equation}
-    \langle\vb*{R_{ij}}\rangle = 
-    \frac{\langle e^{+}_{i} - e^{-}_{i} \rangle}{\Delta\gamma_{j}}, 
-\end{equation}
-where $e^{+}_{i}$ and $e^{-}_{i}$ is the $i$-th component of the galaxy ellipticity where positive ($+$) or negative ($-$) shear is applied in $i$-th direction.
-
-Then, this shear response is used to compute the multiplicative ($\vb*{M}$) and additive ($\vb*{C}$) bias using the linear shear bias model (\ref{eqn:linear}).
-
+\textcolor{red}{
 \begin{equation}
@@
 \end{equation}
-
-The covariances are computed using the bootstrap estimate of standard error.
-From the observed ellipticity catalogs, we randomly choose $n$ samples with replacement which is the length of the data set, and compute the distributions of multiplicative ($f^{M}_{i}$) and additive ($f^{C}_{i}$) bias for $i=1,2,3,...,N$ in the same way as above.
-The distributions are then used to compute the error estimate,
-
-\begin{equation}
-    \sigma_{N,f} = \sqrt{\frac{1}{N-1} \sum_{i=1}^{N}(f_{i}-\bar{f_{i}})^{2}}, 
-\end{equation}
-where we use sample $N$=200.
-
-\textcolor{red}{\textsc{ngmix} utilizes xx method to compute the size of the galaxy, while we compute the adaptive moments of objects to measure the shape and size of the input PSF (\citealt{2003MNRAS.343..459H})}.
-
-\section{Results}
-\label{sec:results}
-In this section, we present the properties of the simulated data products and the shape measurement results from various simulation variants.
-We divide our shape measurements into two categories; single-band and multiband.
-For single-band measurements, in each filter, we measure the shapes from the original single exposures by joint-fitting them.
-We set our base case to be this single-band joint-fit measurement.
-As the more developed case, we measure shapes with the single-band coadd in each filter by single-fitting it.
-For one multiband measurement, we match the objects between each filter and measure the shapes with the joint-fit of single exposures across all the filters.
-The other multiband measurement joint-fit the three coadds from each filter to recover the shapes.
-
-\subsection{Statistics of the Shape Catalog}
-From the COSMOS catalog, based on the \emph{Roman} Weak Lensing mission requirements, objects are pre-selected and simulated.
-In total, we simulate 907,170 galaxies on 18 SCAs across 198 pointings for F184, 227 pointings for H158, and 238 pointings for J129 bandpass.
-We do not make any selection cuts on the simulated catalogs based on measured properties.
-Even so, due to the misestimation of the PSF or low S/N, the Gaussian mixture in \textsc{ngmix} fails to fit about 5\% of all simulated objects, and so the total number of the recovered objects for single-band measurements is, 861,960 for F184, 863,358 for H158, and 859,645 for J129.
-For the multiband (H158+J129+F184) coadd measurements, we measure objects that are found by all of the filters and the total number of the recovered objects is 851,821.
-Figure \ref{fig:true_properties} and \ref{fig:measured_properties} show the true properties from the truth catalog and measured properties from the \textsc{metacalibration} shape catalogs.
-
-\begin{figure}
-    \hspace*{-1.5cm}
-	\includegraphics[scale=0.3]{true_properties.pdf}
-	\centering
-    \caption{The left panel shows input galaxies magnitudes for all the 3 filter we have used to measure shapes.
-The mean magnitude for H158, F184, J129 are respectively 23.098, 22.976, and 23.273.
-The right panel shows the half-light radius in units of arcsec for H158 for input and measured objects.
-The mean half-light radii for input and measured galaxies are 0.294 and 0.221 arcsec for H158.
-For these histograms, we are showing the objects with the successful fit in \textsc{ngmix}.}
-    \label{fig:true_properties}
-\end{figure}
-
-\begin{figure*}
-    \hspace*{-3.0cm}
-    \centering
-	\includegraphics[scale=0.34]{ngmix_snr_T.pdf}
-    \caption{add multiband to each window and F184 coadd for PSF properties.}
-    \label{fig:measured_properties}
-\end{figure*}
-
-\subsection{Shape Calibration Bias}
-\label{subsec:shapes}
-We compute the estimated values of multiplicative and additive bias from the recovered shear with \textsc{metacalibration}.
-The results from the complete set of different runs are in Table \ref{tab:bias_summary} and the summary plot can be found in Figure \ref{fig:final_result}.
-
-For the single-band measurements, we can use the sampling factor defined in Equation \ref{eqn:sampling} to visualize the relationship between the sampling factor and the shear bias.
-The sampling factor is an indication of how undersampled the image in the filter is and it is respectively $Q_{J129}=1.01, Q_{H158}=1.23, Q_{F184}=1.44$.
-This was previously explored in \citealt{2021MNRAS.502.4048K}, where they found that the estimates shear bias has a large dependence on the sampling factor.
-We note that we have run \textsc{metacalibration} with \texttt{fitgauss} and \texttt{gauss} parameters for the new PSF model, and we found that it is preferrable to use \texttt{gauss} for our case.
-Hence, from here we present the result that is calibrated with \texttt{gauss} PSF model for \textsc{metacalibration}.
-The multiplicative bias of single-band single-epochs measurements for each filter is, 1.04$\pm$0.47 per cent for J129, -1.30$\pm$0.46 per cent for H158 and -0.40$\pm$0.53 per cent for F184.
-When the coadds of each filter are used, the bias becomes, -0.47$\pm$0.49 per cent for J129, -0.07$\pm$0.45 per cent for H158 and -0.06$\pm$0.61 per cent for F184.
-Coadd results are consistent with zero multiplicative bias within 1 sigma and the signals increase by xx per cent.
-Generally, coadding produces better sampled images as in Figure \ref{fig:single_to_coadd_rgb} and less multiplicative bias than single epochs measurements.
-We can conclude that in the \emph{Roman} simulation we have seen that the multiplicative bias has no strong dependence on the sampling factor.
-
-Meanwhile the measured additive bias is the same level as the Y3 analysis in DES.
-The additive bias of the single-band single-epochs measurements for each filter is, (3.22$\pm$0.92)$10^{-4}$ for J129, (2.63$\pm$0.88)$10^{-4}$ for H158 and (3.25$\pm$1.11)$10^{-4}$ for F184.
-When the coadds of each filter are used, the bias becomes, (3.39$\pm$0.90)$10^{-4}$ for J129, (8.08$\pm$0.87)$10^{-4}$ for H158 and (9.36$\pm$1.10)$10^{-4}$ for F184.
-From the Table \ref{tab:result}, it is worth noting that the coadd process clearly introduces non-trivial additive biases in one direction, but not the other.
-We believe this is due to the effect of an imperfect PSF model.
-We see this in the Figure xx where the recovered shear has a strong linear dependence on the PSF ellipticity measured by an adaptive moments method.
-The impact of the PSF leakage can be estimated by computing $\rho$-statistics (\citealt{2008A&A...484...67P, 2010MNRAS.404..350R, 2016MNRAS.460.2245J}).
-However, we do not explore the $\rho$-statistics for our PSF model since it is an approximation to accurately represent the features of the instrument, not computed from the real pupil plane images, and the coadding scheme for the 5-year mission has not been finalized yet.
-
-Next, we pressent the results with multiband measurements.
-We performed multiband measurements with 3 filters used in the previous measurements.
-One multiband measurement used all of the single epoch images from all the filters and joint-fit the shape of the galaxy.
-The multiplicative and additive bias is, respectively, $m=(-0.70\pm0.39)$ per cent and $c=(2.96\pm0.85)10^{-4}$.
-The other measurement performed the joint-fit on the three coadded image for each filter.
-The multiplicative and additive bias is, respectively, $m=(-0.59\pm0.46)$ per cent and $c=(7.78\pm0.94)10^{-4}$.
-The multiplicative bias is reduced but the additive bias increased due to the imperfect PSF modeling in one of the spin-2 axes.
-
-\begin{table*}
-	\centering
-	\label{tab:bias_summary}
-	\begin{tabular}[scale=1.4]{ c|c|c|c|c } 
-		\hline
-		simulation variants & $m_{1}\times10^{-2}$ & $m_{2}\times10^{-2}$ & $c_{1}\times10^{-4}$ & $c_{2}\times10^{-4}$\\
-		\hline
-		\textcolor{red}{single-epochs (J129)} & 1.30$\pm$0.70 & 0.30$\pm$0.63 & 4.65$\pm$1.45 & 1.33$\pm$1.40\\
-		single-epochs (F184) & -0.86$\pm$0.72 & -0.69$\pm$0.83 & 2.62$\pm$1.56 & 0.23$\pm$1.53\\
-		single-epochs (H158) & -1.07$\pm$0.62 & -1.61$\pm$0.66 & 2.83$\pm$1.35 & 2.33$\pm$1.22\\
-		\hline
-		\textcolor{red}{single-band coadd with oversampling (H158; w/ noise fix)} & -1.51$\pm$0.68 & -1.41$\pm$0.66 & 14.79$\pm$1.32 & 4.45$\pm$1.42\\
-		\textcolor{red}{single-band coadd with oversampling (J129 w/ noise fix)} & -1.59$\pm$0.64 & -2.31$\pm$0.70 & 11.61$\pm$1.20 & -0.09$\pm$1.34\\
-		\textcolor{red}{single-band coadd with oversampling (F184 w/ noise fix)} & 0.47$\pm$0.80 & -0.59$\pm$0.81 & 12.40$\pm$1.67 & 6.32$\pm$1.82\\
-		\hline
-		\textcolor{red}{multiband single-epochs (gauss) (H158+J129+F184)} & -0.66$\pm$0.58 & -0.74$\pm$0.59 & 4.32$\pm$1.17 & 1.60$\pm$1.16 \\
-		\textcolor{red}{multiband coadd (w/ noise fix)} & -2.16$\pm$0.60 & -2.16$\pm$0.60 & 14.03$\pm$1.13 & 4.44$\pm$1.31\\
-
-		\hline
-	\end{tabular}
-	\caption{Shear calibration bias for different simulation runs.}
-	\label{tab:result}
-\end{table*}
-
-\begin{figure*}
-	\includegraphics[scale=0.5]{final_result.pdf}
-    \caption{The multiplicative ($m$) and additive ($c$) bias of several simulation runs.
-The left panel shows $m$ and $c$ against the sampling factor for each filter.
-The right panel shows the same for multiband fit result.
-The number in the parenthesis gives how many filters are used.
-(3) means J129, H158 and F184 are used, whereas (2) means only J129 and H158 are used.
-Include the definition of sampling factor.
-}
-    \label{fig:final_result}
-\end{figure*}
-
-\begin{figure*}
-    \hspace*{-3.5cm}
-    \centering
-	\includegraphics[scale=0.34]{H158_meanshear_measured_properties_perbin.pdf}
-    \caption{H158 coadd, add multiband, do delta e.}
-    \label{fig:meanshear}
-\end{figure*}
-
-\section{Discussion}
-\label{sec:discussion}
-
-So far we have seen how \textsc{metacalibration} handles the relatively undersampled \emph{Roman} images without the effect of blending.
-However, it has been found that the galaxy blending at different redshifts could introduce a significant shear-dependent detection bias when calibrated with \textsc{metacalibration} (\citealt{2020ApJ...902..138S}).
-In the future study, we should investigate the impact of blending in the image simulations to verify if \textsc{metacalibration} combined with the new version of \textsc{ngmix} can be the shear calibration algorithm in the real survey.
-
-In the next generation of the simulations, we would like to add the following updates or upgrade these parts of the simulation. 
-\begin{itemize}
-    \setlength\itemsep{1em}
-    \item \textbf{Simulation Volume}: Expand the simulated area by at least 8 times. (Troxel et al. in prep.)
-
-    \item \textbf{Near-Infrared Detectors}: Incorporate the detector effects measured in the real flight candidate detectors and produce two catalogs with and without them to determine the impact on the final cosmology result.
-
-    \item \textbf{Image Coadditions}: Implement a new coadding methodology which coadds the whole scene instead of individual stamp cutouts (e.g., \textsc{astrodrizzle}\footnote{\url{https://github.com/spacetelescope/drizzlepac}}).
-With \textsc{astrodrizzle} which employs the linear reconstruction of the individual images, we are able to further mitigate the effect of undersampled \emph{Roman} images.
-If we set the final coadd pixel scale with \textsc{astrodrizzle} to be 70\% smaller than the original \emph{Roman} pixel scale, F184 will be fully sampled (Q > 2) and J129 will be sampled at the similar level with F184 without coadding.
-
-    \item \textbf{Source Detection}: Implement a source detection methodology with \texttt{Photutils}\footnote{\url{https://photutils.readthedocs.io/en/stable/}} on the coadds.
-
-    \item \textbf{Selection Cuts}: Implement quality assurance cuts (e.g., S/N) on the shape catalog to avoid the noise on the shape fit and compute the measurement biases accounting for the selection effects (\citealt{2017ApJ...841...24S}).
-\end{itemize}
-\textcolor{red}{With these potential changes, we will produce a reference image and shape catalog that can be widely used by other communities.}
-
-\section{Conclusions}
-\label{sec:conclusion}
-We explored the performance of \textsc{metacalibration} methodology with \textsc{psc} coadding scheme to reduce the shear calibration bias in the image simulation framework of the \emph{Roman} Space Telescope.
-Accurately characterizing how much shear bias exists in this framework is required to successfully complete the weak lensing program of the High-Latitude Survey of the \emph{Roman}.
-\par
-
-By coadding the single-epoch images and oversampling the PSF for a better shape fit, we find that shear estimates with \textsc{metacalibration} are slightly biased within 1 sigma but within the mission requirement.
-We conclude that to further constrain the shear calibration bias in the simulation and determine if the \emph{Roman} mission will be able to use the current Stage-III imaging survey schemes, we need more simulation volume well beyond the 2.5 deg$^{2}$ area of the simulated sky.
-
-\section{Acknowledgements}
-
-We thank Matthew Becker, Erin Sheldon, and Arun Kannawadi for many useful discussions. This work was supported by xx funding agencies.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% \section*{Data Availability}
-
-% The inclusion of a Data Availability Statement is a requirement for articles published in MNRAS.
-Data Availability Statements provide a standardised format for readers to understand the availability of data underlying the research results described in the article.
-The statement may refer to original data generated in the course of the study or to third-party data analysed in the article.
-The statement should describe and provide means of access, where possible, by linking to the data or providing the required accession numbers for the relevant databases or DOIs.
-
-%%%%%%%%%%%%%%%%%%%% REFERENCES %%%%%%%%%%%%%%%%%%
-
-% The best way to enter references is to use BibTeX:
-
-\bibliographystyle{mnras}
-\bibliography{example} % if your bibtex file is called example.bib
-
-%%%%%%%%%%%%%%%%% APPENDICES %%%%%%%%%%%%%%%%%%%%%
-
-\appendix
-
-\section{Simple Simulations}
-\label{app:coadd_F}
-% If you want to present additional material which would interrupt the flow of the main paper,
-% it can be placed in an Appendix which appears after the list of references.
-
-% fitgauss or gauss appendix
-% \begin{table*}
-% 	\centering
-% 	\label{tab:bias_table}
-% 	\begin{tabular}[width=0.9*\textwidth]{ c|c|c|c|c|c } 
-% 		\hline
-% 		Bands & simulation variants & $m_{1}\times10^{-2}$ & $m_{2}\times10^{-2}$ & $c_{1}\times10^{-4}$ & $c_{2}\times10^{-4}$\\
-% 		\hline
-% 		\multirow{single-band} & single-epochs (J129) & 1.80$\pm$0.67 & 0.28$\pm$0.69 & 6.48$\pm$1.31 & -0.04$\pm$1.51\\
-% 		& single-epochs (H158) & -1.09$\pm$0.63 & -1.50$\pm$0.68 & 3.90$\pm$1.21 & 1.37$\pm$1.28\\
-% 		& single-epochs (F184) & -0.62$\pm$0.81 & -0.17$\pm$0.79 & 3.92$\pm$1.52 & 2.58$\pm$1.57\\
-% 		& single-band coadd with oversampling (J129) & -0.49$\pm$0.65 & -0.45$\pm$0.62 & 10.50$\pm$1.33 & -3.72$\pm$1.42\\
-% 		& single-band coadd with oversampling (H158) & -0.03$\pm$0.59 & -0.11$\pm$0.67 & 14.10$\pm$1.24 & 2.05$\pm$1.42\\
-% 		& single-band coadd with oversampling (F184) & 0.47$\pm$0.80 & -0.59$\pm$0.81 & 12.40$\pm$1.67 & 6.32$\pm$1.82\\
-
-% 		\multirow{multiband} & multiband single-epochs (fitgauss) (H158+J129+F184) & 1.78$\pm$0.62 & 0.07$\pm$0.63 & 8.80$\pm$1.22 & 1.57$\pm$1.27 \\
-% 		& multiband single-epochs (gauss) (H158+J129+F184) & -0.66$\pm$0.58 & -0.74$\pm$0.59 & 4.32$\pm$1.17 & 1.60$\pm$1.16 \\
-% 		& multiband coadd with oversampling (fitgauss; H158+J129) & -1.02$\pm$0.63 & 0.02$\pm$0.70 & 18.51$\pm$1.36 & 0.70$\pm$1.33\\
-% 		& multiband coadd with oversampling (gauss; H158+J129) & -0.39$\pm$0.59 & -0.32$\pm$0.68 & 13.72$\pm$1.24 & 1.85$\pm$1.29\\
-% 		& (v2) multiband coadd with oversampling (fitgauss; H158+J129) & -0.73$\pm$0.45 & -0.08$\pm$0.48 & 15.80$\pm$0.88 & 0.53$\pm$0.96\\
-% 		& (v2) multiband coadd with oversampling (gauss; H158+J129) & -0.36$\pm$0.45 & -0.35$\pm$0.43 & 11.45$\pm$0.93 & 1.83$\pm$0.98\\
-
-% 		\hline
-% 	\end{tabular}
-% 	\caption{Shear calibration bias for different simulation runs.}
-% 	\label{tab:result}
-% \end{table*}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-% Don't change these lines
-\bsp	% typesetting comment
-\label{lastpage}
-\end{document}
-
-% End of mnras_template.tex

### 2021-12-13 roman_metacal_v2.tex
v2.1 with simple simulations section added

@@
 As we observe more area of the sky and develop better tools (observatories and algorithms), we detect more galaxies, and have already reached the point where statistical and systematic uncertainties are comparable.
-Thus, near-future Stage IV surveys (\citealt{2006astro.ph..9591A}) such as Euclid\footnote{\url{ http://sci.esa.int/euclid}} (Euclid Study Scientist \& the Science Advisory Team 2010), the Vera C.
+Thus, near-future Stage IV surveys (\citealt{2006astro.ph..9591A}) such as Euclid\footnote{\url{ http://sci.esa.int/euclid}} (\citealt{2011arXiv1110.3193L}), the Vera C.
 Rubin Observatory Legacy Survey of Space and Time\footnote{\url{ http://www.lsst.org}} (\emph{Rubin}: \citealt{2009arXiv0912.0201L, 2019ApJ...873..111I}), and \emph{Nancy Grace Roman} Space Telescope\footnote{\url{https://roman.gsfc.nasa.gov}} (\emph{Roman}: \citealt{2015arXiv150303757S}) require even better control of systematics.
@@
 It has been confirmed that shear can be calibrated with \textsc{metacalibration} at the few-percent level in DES (\citealt{2018MNRAS.481.1149Z, 2020arXiv201103408G}), without accounting for galaxy blending and detection.
-Tackling the issue of blending/detection is one key step forward for the DES Y6 analysis and preparatory Rubin LSST work with the shear-dependent detection and calibration technique (\textsc{metadetect}; \citealt{2020ApJ...902..138S}).
+Tackling the issue of blending/detection is one key step forward for the DES Y6 analysis and preparatory Rubin LSST work with the shear-dependent detection and calibration technique (\textsc{metadetection}; \citealt{2020ApJ...902..138S}).
 While the major advantage of \textsc{metacalibration} is that it can be directly applied to real galaxy images without needing to rely on an ensemble calibration from image simulations, limitations for future surveys are not well-known.
 
-One possible limitation might lie in the effect of undersampled images in space-based misssions like \emph{Euclid} and \emph{Roman}, which have such a small pixel scale that images will not be Nyquist sampled in the near-infrared at the detector pixel scale (\citealt{2013PASP..125.1496S}) based on the Nyquist-Shannon Sampling Theorem.
+One possible limitation might lie in the effect of undersampled images in space-based misssions like \emph{Euclid} and \emph{Roman}, which have such a small pixel scale that images will not be Nyquist sampled in the near-infrared (NIR) at the detector pixel scale (\citealt{2013PASP..125.1496S}) based on the Nyquist-Shannon Sampling Theorem.
 We define the sampling factor of each filter in \emph{Roman} to be,
@@
 
-%\subsection{Simple Simulations}
-%\label{subsec:simplesim}
-%The purpose of the simple simulations is to verify that there are no systematic biases at the basic levels of the simulation (e.g., no complex detector effects).
-The simple simulation is based on the real observational pointing strategy, and we use the real Sensor-Array Chips (SCAs) scheme, the band filters and the pixel scale as basic Roman specifications.
+\subsection{Validations with Simple Simulations}
+\label{subsec:simplesim}
+The purpose of the simple simulations is to verify that there are no systematic biases at the fundamental levels of the simulation (e.g., no complex detector effects).
+These simple simulations play roles in ruling out the sources of systematic biases that may potentially be a problem in the use of \textsc{metacalibration} with space-based images.
+
+The parameter choices are listed in Table.
+\ref{tab:params}.
+With these parameters set, we simulated images with varying galaxy model profile, PSF model profile, the artificial shear, and background noise level, without any complications in the images and pipelines such as detector effects and coaddition.
+We first verify that our input gravitational shear is unbiased in \textsc{metacalibration} framework and the uncertainty in the recovered shape is small enough for the \emph{Roman} requirement (Fig.
+\ref{fig:metacal_shear_linear}).
+We then test the pipeline by doubling the background noise.
+Due to the \emph{Roman} being in NIR range, the expected background noise level in the images is higher compared to optical imaging surveys like DES.
+With this test, we can confirm that the treatment of correlated noise induced in \textsc{metacalibration} process for low S/N objects does not trigger any bias at the level we should be concerned (\citealt{2017ApJ...841...24S}).
+Another test with \emph{Roman} PSF instead of Gaussian PSF does guarantee that the PSF features particular to \emph{Roman} do not bias the shape recovery even though it is undersampled.
+Upon validating there does not exist any bias at the fundamental level, we began constructing coadd and more complex measurement pipeline.
+\begin{table}
+    \centering
+    \begin{tabular}[width=\columnwidth]{|p{3cm}||p{3cm}|p{3cm}|p{3cm}|}
+    \hline
+    Parameter & Value \\
+    \hline
+    Pixel scale & 0.11 arcsec/pixel\\
+    Dither, SCA & 22535, 1 \\ 
+    Bandpass & H158 \\
+    Half-light radius & 1.0 arcsec\\
+    Magnitude & randomly chosen from \emph{CANDELS} \\ 
+    Stamp size & 32 pixels each side\\
+    \hline
+    \end{tabular}
+    \caption{List of the parameter choices for the simple simulations.}
+    \label{tab:params}
+\end{table}
+
+\begin{table*}
+	\centering
+	\label{tab:simple_sim}
+	\begin{tabular}[width=\textwidth]{ c|c|c|c|c|c|c|c|c|c } 
+		\hline
+		simulation variants & galaxy profile & PSF profile & shear & background noise level & $m_{1}\times10^{-2}$ & $m_{2}\times10^{-2}$ & $c_{1}\times10^{-4}$ & $c_{2}\times10^{-4}$\\
+		\hline
+		Basic-0.02 & Gaussian & Gaussian & 0.02 & roman.getSkyLevel & 0.01$\pm$0.10 & -0.02$\pm$0.10 & -0.02$\pm$0.14 & 1.06$\pm$0.14\\
+		Basic-0.05 & Gaussian & Gaussian & 0.05 & roman.getSkyLevel & 0.23$\pm$0.07 & 0.22$\pm$0.07 & 0.05$\pm$0.33 & 1.08$\pm$0.33\\
+		Basic-0.1 & Gaussian & Gaussian & 0.1 & roman.getSkyLevel & 0.99$\pm$0.03 & 0.99$\pm$0.03 & 0.13$\pm$0.33 & 0.88$\pm$0.33\\
+		\hline
+		Doublesky-0.02 & Gaussian & Gaussian & 0.02 & 2 $\times$ roman.getSkyLevel & -0.12$\pm$0.18 & 0.01$\pm$0.18 & 0.06$\pm$0.36 & 1.04$\pm$0.36\\
+		\hline
+		RomanPSF-0.02 (non-rotated) & Gaussian & Roman & 0.02 & roman.getSkyLevel & 0.13$\pm$0.10 & 0.18$\pm$0.10 & -0.02$\pm$0.19 & 5.33$\pm$0.19\\
+		\hline
+	\end{tabular}
+	\caption{This table compares the shear calibration bias, both multiplicative and additive bias for different simulation runs.}
+	\label{tab:result}
+\end{table*}
+
+\begin{figure}
+	\includegraphics[width=\columnwidth]{metacal_bias_shear.png}
+    %\vspace*{-5mm}
+    \caption{At first order, the \textsc{metacalibration} method only works for small shears.
+The next order effect is seen as a quadratic dependence of the multiplicative shear bias on on the applied shear.
+A larger input shear increases the signal-to-noise of bias estimates, but to keep this effect small compared to requirements, we limit input shears to $\pm 0.01$.}
+    \label{fig:metacal_shear_linear}
+\end{figure}
 
@@
 It is a balance to choose an input shear that results in higher S/N of an object and unbiased shape measurement.
-We verify that our input gravitational shear is unbiased in \textsc{metacalibration} framework and the uncertainty in the recovered shape is small enough by constructing a simpler framework of the fiducial image simulations which renders Gaussian profile galaxies and PSFs on the \emph{Roman} pixel scale cutout image without any detector effects or other complications in the fiducial simulations.
 Figure \ref{fig:metacal_shear_linear} shows the performance as a function of input shear leading to the choice of input shear $\gamma=\pm 0.02$.
@@
 \end{equation}
-
-\begin{figure}
-	\includegraphics[width=\columnwidth]{metacal_bias_shear.png}
-    %\vspace*{-5mm}
-    \caption{At first order, the \textsc{metacalibration} method only works for small shears.
-The next order effect is seen as a quadratic dependence of the multiplicative shear bias on on the applied shear.
-A larger input shear increases the signal-to-noise of bias estimates, but to keep this effect small compared to requirements, we limit input shears to $\pm 0.01$.}
-    \label{fig:metacal_shear_linear}
-\end{figure}
 
@@
 This is most likely due to an issue with how we are currently treating the PSF or correlated noise in the coadding process, given the large observed $c_1$ when coadding discussed below.
+\textcolor{red}{Although we have verified that the handling of correlated noise in \textsc{metacalibration} proess for single-epoch images is unbiased, it is possible that the \texttt{psc} process induces more correlated noise that is not corrected further.
+}
 
@@
 	\label{tab:bias_summary}
-	\begin{tabular}[scale=1.4]{ c|c|c|c|c|c } 
+	\begin{tabular}[width=\textwidth]{ c|c|c|c|c|c } 
 		\hline
@@
 		single-band coadd (J129) & 1.26 & -1.84$\pm$0.71 & -1.90$\pm$0.65 & 11.99$\pm$1.39 & 0.59$\pm$1.41\\
-		single-band coadd (H158) & 1.54 & -1.91$\pm$0.67 & -2.11$\pm$0.67 & 13.99$\pm$1.34 & 5.40$\pm$1.35\\
+		single-band coadd (H158) & 1.54 & -1.75$\pm$0.67 & -1.68$\pm$0.64 & 14.39$\pm$1.32 & 4.29$\pm$1.35\\
 		single-band coadd (F184) & 1.79 & -0.28$\pm$0.83 & -0.27$\pm$0.78 & 12.15$\pm$1.56 & 5.66$\pm$1.56\\
@@
 \begin{figure*}
-    \hspace*{-3.5cm}
+    %\hspace*{-3.5cm}
     \centering
-	\includegraphics[scale=0.34]{H158_meanshear_measured_properties_perbin_e1_v2.pdf}
+	\includegraphics[width=\textwidth]{H158_meanshear_measured_properties_perbin_e1_v2.pdf}
     \caption{(Working on fixing the figure bounds)This shows the mean shear residual ($\Delta e_{1}$; $\langle e_{1,measured} \rangle - \langle e_{1,expected} \rangle$) as a function of various properties of galaxies for H158 single-band single-epochs, coadds, and multiband measurements.

### 2021-12-13 scratch.tex
v2.1 with simple simulations section added

--- 2021-11-09 roman_metacal.tex
@@
+\textcolor{red}{
+\begin{equation}
+    \small
+    \vb*{M_{ij}} = 
+    \frac{\langle e^{+}_{i}/R_{ii} \rangle - \langle e^{-}_{i}/R_{ii} \rangle}{\abs{\Delta g_{j}}} - \delta_{ij} 
+    = \frac{\langle e^{obs,+}_{i}\rangle - \langle e^{obs,-}_{i}\rangle}{\abs{\Delta g_{j}}} - \delta_{ij}, 
+\end{equation}
+where the numerator calculates the \textsc{metacalibration} calibrated observed shear by dividing $i$-th component of the ellipticity of the unsheared \textsc{metacalibration} catalog by shear response.
+\begin{equation}
+    \small
+    \vb*{C_{ij}} = \frac{\langle e^{obs,+}_{i} - (\delta_{ij}+M_{ij})e^{true,+}_{i})\rangle + \langle e^{obs,-}_{i} - (\delta_{ij}+M_{ij})e^{true,-}_{i}) \rangle}{2}
+\end{equation}
+
 % mnras_template.tex 
@@
 Thus, the next-decade legacy surveys, the Stage IV surveys (\citealt{2006astro.ph..9591A}) such as Euclid\footnote{\url{ http://sci.esa.int/euclid}} (Euclid Study Scientist \& the Science Advisory Team 2010), the Vera C.
-Rubin Observatory Legacy Survey of Space and Time\footnote{\url{ http://www.lsst.org}} (LSST: \citealt{2009arXiv0912.0201L, 2019ApJ...873..111I}), and \emph{Nancy Grace Roman} Space Telescope\footnote{\url{https://roman.gsfc.nasa.gov}} (\emph{Roman}: \citealt{2015arXiv150303757S}) require even better control of systematics.
+Rubin Observatory Legacy Survey of Space and Time\footnote{\url{ http://www.lsst.org}} (\emph{Rubin}: \citealt{2009arXiv0912.0201L, 2019ApJ...873..111I}), and \emph{Nancy Grace Roman} Space Telescope\footnote{\url{https://roman.gsfc.nasa.gov}} (\emph{Roman}: \citealt{2015arXiv150303757S}) require even better control of systematics.
 In order to manage the systematic uncertainties, we must develop realistic image simulations, apply the pre-existing shape measurement on the simulated images, and determine any potential systematic effects and build the strategy of mitigating them.
@@
 The image with the sampling factor, $Q < 2$, is not Nyquist sampled and reffered to as the undersampled image.
-It is problematic to measure galaxy shapes solely from the undersampled images, because the \emph{Roman} PSF that will be used to recover the shapes is also undersampled and has a complex structure, not simply Gaussian.
-\textcolor{red}{It is, therefore, necessary to build a robust strategy that can reconstruct better sampled PSF to allow unbiased shape measurement.
+The PSF needs to be interpolated and estimated from well-sampled images to deconvolve and measure shapes from, because the \emph{Roman} PSF has a complex structure that cannot be captured in undersampled images.
+\textcolor{red}{It is, therefore, necessary to build a robust strategy that reconstruct well-sampled images to estimate the PSF to allow unbiased shape measurement.
 }
@@
 Our work is based on the image simulation suite of the \emph{Roman} Space Telescope developed by \citet{2021MNRAS.501.2044T}, where we render star and galaxy images from \texttt{GalSim}\footnote{\url{ https://github.com/GalSim-developers/GalSim}} (\citealt{2015A&C....10..121R}).
-With a few simulation updates and an implementation of \textsc{metacalibration}, we can start to explore if the shear calibration goal of the High-Latitude Survey program for \emph{Roman} ($m=~3.2\times10^{-4}$) (\citealt{2019BAAS...51c.341D}) can be achieved.
+With a few simulation updates and an implementation of \textsc{metacalibration}, we can start to explore if the shear calibration goal of the High-Latitude Survey program for \emph{Roman} ($m=~3.2\times10^{-4}$) (\citealt{2018arXiv180403628D}) can be achieved.
 \par
@@
 		\textcolor{red}{single-band coadd (J129)} & -1.59$\pm$0.64 & -2.31$\pm$0.70 & 11.61$\pm$1.20 & -0.09$\pm$1.34\\
-		\textcolor{red}{single-band coadd (H158)} & -1.51$\pm$0.68 & -1.41$\pm$0.66 & 14.79$\pm$1.32 & 4.45$\pm$1.42\\
-		\textcolor{red}{single-band coadd (F184)} & 0.47$\pm$0.80 & -0.59$\pm$0.81 & 12.40$\pm$1.67 & 6.32$\pm$1.82\\
+		single-band coadd (H158) & -1.91$\pm$0.67 & -2.11$\pm$0.67 & 13.99$\pm$1.34 & 5.40$\pm$1.35\\
+		single-band coadd (F184) & -0.28$\pm$0.83 & -0.27$\pm$0.78 & 12.15$\pm$1.56 & 5.66$\pm$1.56\\
 		\hline
 		multiband single-epochs & -1.07$\pm$0.66 & -1.61$\pm$0.67 & 2.83$\pm$1.30 & 2.33$\pm$1.22 \\
-		\textcolor{red}{multiband coadd} & -2.16$\pm$0.60 & -2.16$\pm$0.60 & 14.03$\pm$1.13 & 4.44$\pm$1.31\\
+		multiband coadd & -2.32$\pm$0.64 & -2.34$\pm$0.63 & 14.45$\pm$1.10 & 4.49$\pm$1.22\\
 
@@
 
-    \item \textbf{Image Coadditions}: Implement a new coadding methodology which coadds the whole scene instead of individual stamp cutouts (e.g., \textsc{astrodrizzle}\footnote{\url{https://github.com/spacetelescope/drizzlepac}}).
-With \textsc{astrodrizzle} which employs the linear reconstruction of the individual images, we are able to further mitigate the effect of undersampled \emph{Roman} images.
-If we set the final coadd pixel scale with \textsc{astrodrizzle} to be 70\% smaller than the original \emph{Roman} pixel scale, F184 will be fully sampled (Q > 2) and J129 will be sampled at the similar level with F184 without coadding.
+    \item \textbf{Image Coadditions}: Implement a new coadding methodology which coadds the whole scene instead of individual stamp cutouts (e.g., \texttt{AstroDrizzle}\footnote{\url{https://github.com/spacetelescope/drizzlepac}}.
+It is the Python implementation of \texttt{MultiDrizzle} that was utilized to coadd images for \emph{Hubble} Space Telescope).
+With \texttt{AstroDrizzle} which employs the linear reconstruction of the individual images, we are able to further mitigate the effect of undersampled \emph{Roman} images.
+If we set the final coadd pixel scale with \texttt{AstroDrizzle} to be 70\% smaller than the original \emph{Roman} pixel scale, F184 will be fully sampled (Q > 2) and J129 will be sampled at the similar level with F184 without coadding.
 

### 2022-02-08 paper_v3.tex
v3; accomodating comments

--- 2021-12-13 roman_metacal_v2.tex
@@
 The weak lensing program of the \emph{Roman} mission requires the galaxy shapes to be calibrated within about 0.03\%.
-To reach this goal, we can test our calibration process with these simulations and ultimately isolate the sources where these residual shear biases arise.
+To reach this goal, we can test our calibration process with various simulations and ultimately isolate the sources where these residual shear biases arise.
 In this work, we incorporate several new realistic processing-pipeline updates necessary to calibrate shear with a better precision relative to the previous version of the simulations and show first results for the reference HLIS using \textsc{metacalibration}.
-We find that compared with the non-calibrated results from previous work, \textsc{metacalibration} as used in current experiments can significantly reduce the shear calibration bias to the percent level.
-With the single-epoch images, across all three filters we are able to achieve a multiplicative bias $m=-1.34\%$ within 2 $\sigma$, while for coadd cutouts, $m=-2.33\%$ within about 4 $\sigma$.
-In both single-epoch and coadd cases, we find that shape calibration becomes worse with decreasing image sampling factor.
-Overall, within the current simulation volume, there is evidence that \textsc{metacalibration} as currently implemented will not calibrate shapes with zero shear bias in the \emph{Roman} HLIS and further work on the shear calibration methodology is necessary.
-In the future, we will need to substantially increase the simulation volume by 400 (about the same size as the survey area of 2000 $deg^{2}$) to reach the precision necessary for the HLIS.
+We find that in the simplified simulations where objects are drawn with the Gaussian light profile, \textsc{metacalibration} can calibrate shapes within the requirement, $m=(-0.01\pm 0.10)$\%.
+However, \textsc{metacalibration} as used in the most-realistic version of the simulations can only reduce the shear calibration bias to the percent level.
+With the single-epoch images, across all three filters we estimate the multiplicative bias $m=(-1.34\pm 0.67)$\%.
+This is we believe caused by the undersampled \emph{Roman} images.
+\textcolor{red}{In an attempt to reduce the effect of undersampling, we esimate the bias on the coadd cutouts and find that $m=(-2.33\pm 0.64)$\%.} Overall, within the current simulation volume, there is evidence that \textsc{metacalibration} as currently implemented will not calibrate shapes with zero shear bias in the \emph{Roman} HLIS and further work on the shear calibration methodology is necessary.
+In the future, we will need to substantially increase the simulation volume by 400 (about the same size as the survey area of 2000 deg$^{2}$) to reach the precision necessary for the HLIS.
 \end{abstract}
@@
 For that reason, weak lensing is one of the most powerful probes in current and near-future imaging surveys to constrain cosmological parameters with high precision.
-\par
 
@@
 
-In this study, we focus on the shear calibration bias, which describes the relationship between gravitational lensing shear $\gamma$ and measured galaxy shapes.
-In the limit of weak lensing ($\lvert\gamma\rvert\ll1$) and random intrinsic galaxy shapes, the ensemble average of ellipticities $\langle e \rangle$ of galaxy shapes is directly related to the shear field $\gamma$, and the estimated shear can be written as a linear model with multiplicative ($m_{i}$) and additive bias ($c_{i}$) as described in the equation below (\citealt{2006MNRAS.368.1323H, 2006MNRAS.366..101H, 2007MNRAS.376...13M})
-\begin{equation}
-    \gamma^{obs}_{i} = (1+m_{i})\gamma^{true}_{i} + c_{i}, 
-    \label{eqn:linear}
-\end{equation}
-where i=(1,2) and $\gamma^{obs}_{i}$ is the two-component observed shear after calibrations and $\gamma^{true}_{i}$ is the true shear.
-The bias can be introduced in places such as PSF modeling, blending, and the undersampling of the image (e.g., \citealt{2018ARA&A..56..393M}).
-Additionally, complex detector effects such as the brighter-fatter effect are potential sources of bias (\citealt{2013MNRAS.429..661M}), while it has been shown that for \emph{Roman} the effect of persistence will not be an issue (\citealt{2021arXiv210610273L}).
-Qualitatively, if the recovered shear is biased by 1$\%$ (m=0.01), $S_{8} = \sigma_{8} \sqrt{\Omega_{m}/0.3}$ could be biased about 1.5$\%$ in the final cosmology result.
-Thus, quantifying and correcting these biases before the real survey begins is extremely important.
-\par
-
-Several shear calibration and bias mitigation efforts have been proposed by STEP (\citealt{2006MNRAS.368.1323H, 2007MNRAS.376...13M}) and GREAT (\citealt{2010MNRAS.405.2044B, 2013ApJS..205...12K, 2015MNRAS.450.2963M}) challenges, to meet the requirements for the current imaging surveys.
+Conventionally, these observational systematic biases are realized through a number of simulations and validations, and these propagate into the final galaxy shapes we measure.
+We quantify this impact as shear calibration bias.
+There have been several shear calibration and bias mitigation efforts that were proposed by STEP (\citealt{2006MNRAS.368.1323H, 2007MNRAS.376...13M}) and GREAT (\citealt{2010MNRAS.405.2044B, 2013ApJS..205...12K, 2015MNRAS.450.2963M}) challenges, to meet the requirements for the current imaging surveys.
 In particular, one of the state-of-the-art self-calibration methods, \textsc{metacalibration} (\citealt{2017arXiv170202600H, 2017ApJ...841...24S}) has been shown to be able to substantially reduce the significance of shear bias.
@@
 
-One possible limitation might lie in the effect of undersampled images in space-based misssions like \emph{Euclid} and \emph{Roman}, which have such a small pixel scale that images will not be Nyquist sampled in the near-infrared (NIR) at the detector pixel scale (\citealt{2013PASP..125.1496S}) based on the Nyquist-Shannon Sampling Theorem.
-We define the sampling factor of each filter in \emph{Roman} to be,
-\begin{equation}
-    Q = \frac{\lambda_{min}N_{f}}{p}, 
-    \label{eqn:sampling}
-\end{equation}
-where $\lambda_{min}$ is the shortest wavelength of the incident light in the filter, $N_{f}$ is the focal ratio of the telescope ($N_{f}=7.8$ for \emph{Roman}) and $p$ is the pixel spacing of the sensor ($p=10\mu m$ for \emph{Roman}).
-An image with sampling factor $Q < 2$ is not Nyquist sampled (i.e., undersampled).
+One possible limitation might lie in the effect of undersampled images in space-based surveys like \emph{Euclid} and \emph{Roman}, which will operate at its diffraction-limit.
 The PSF needs to be interpolated and estimated from well-sampled images to deconvolve and measure shapes with, because the \emph{Roman} PSF has a complex structure that cannot be captured in the original undersampled images.
@@
 Recently, \cite{2021MNRAS.502.4048K} (hereafter K21) addressed this potential issue of the limitations of \textsc{metacalibration} on undersampled images in \emph{Euclid} image simulations.
-They found that for the \emph{Euclid} mission the shear estimate is biased by about 1$\%$.
+They found that for the \emph{Euclid} mission the shear estimate with \textsc{metacalibration} is biased by about 1$\%$.
 It is mentioned that their result could be extended to the \emph{Roman} mission due to similarities in the instruments and for \emph{Roman} they predicted the multiplicative bias was more than 1\%.
@@
 This paper is organized as follows.
-We briefly discuss the simulation suite details we used and the updates we implemented for this project in Sec.~\ref{sec:sims}.
-Then, in Sec.~\ref{sec:methods}, we show how coadditions of single exposure postage stamps are produced and how shape measurements are completed using \textsc{metacalibration}.
+We first introduce the formalism of shear bias and image sampling relevant to the space-based surveys in Sec.~\ref{sec:background}.
+We then briefly discuss the simulation suite details we used and the updates we implemented for this project in Sec.~\ref{sec:sims}.
+In Sec.~\ref{sec:methods}, we show how coadditions of single exposure postage stamps are produced and how shape measurements are completed using \textsc{metacalibration}.
 We present the galaxy catalog properties and calibration results for single-band and multiband measurements in Sec.~\ref{sec:results}.
 Finally, in Sec.~\ref{sec:discussion}, we discuss how we will be able to constrain the shear bias better in terms of further updates in the image simulations and what we can conclude from this study.
+
+\section{Background}
+\label{sec:background}
+In this section, we provide a brief introduction of image sampling defined through the Nyquist-Shannon Sampling Theorem, an overview of shear calibration bias within the context of weak lensing, and \textsc{metacalibration} formalism.
+
+\subsection{Image Sampling}
+Based on the Nyquist-Shannon Sampling Theorem which states that in order to reconstruct the unbiased continuous band-limited function without a loss of information, the sufficient sample rate is twice the bandlimiting frequency per second.
+In the context of image sampling, the criterion that the sample pixel spacing needs to satisfy is $p < \frac{1}{2u_{max}}$ ($u_{max}$ is the max.
+spatial bandlimiting frequency).
+Since the spatial bandlimiting frequency in an astronomical image is defined as,
+\begin{equation}
+    u_{max} = \frac{1}{\lambda_{min}N_{f}}
+\end{equation}
+the sampling factor of the \emph{Roman} images is defined as, 
+\begin{equation}
+    Q = \frac{\lambda_{min}N_{f}}{p}, 
+    \label{eqn:sampling}
+\end{equation}
+where $\lambda_{min}$ is the shortest wavelength of the incident light in each filter, $N_{f}$ is the focal ratio of the telescope ($N_{f}=7.8$ for \emph{Roman}) and $p$ is the pixel spacing of the sensor ($p=10\mu m$ for \emph{Roman}) (\citealt{2013PASP..125.1496S}).
+An image with sampling factor $Q=2$ is called a Nyquist-sampled image and an image with with sampling factor $Q<2$ is called an undersampled image.
+\textcolor{red}{An undersampled image...
+why is this an issue with weak lensing.
+What is the process of reconstructing better-sampled images.}
+
+\subsection{Shear Calibration Bias}
+In the observation of cosmic shear, we can quantify the bias associated with the shear recovery processes such as PSF estimation and shape measurement in image simulations.
+We call this shear calibration bias and we compute the deviations of the measured gravitational lensing shear $\gamma$ from the input shear.
+In the limit of weak lensing ($\lvert\gamma\rvert\ll1$) and random intrinsic galaxy shapes, the ensemble average of ellipticities $\langle e \rangle$ of galaxy shapes is directly related to the reduced shear field $g$, and the estimated shear can be written as a linear model with multiplicative ($m_{i}$) and additive bias ($c_{i}$) as described in the equation below (\citealt{2006MNRAS.368.1323H, 2006MNRAS.366..101H, 2007MNRAS.376...13M})
+\begin{equation}
+    g^{obs}_{i} = (1+m_{i})g^{true}_{i} + c_{i}, 
+    \label{eqn:linear}
+\end{equation}
+where i=(1,2) and $g^{obs}_{i}$ is the two-component observed reduced shear after calibrations and $g^{true}_{i}$ is the true shear.
+The bias can be introduced in places such as PSF modeling, blending, and the undersampling of the image (e.g., \citealt{2018ARA&A..56..393M}).
+Additionally, complex detector effects such as the brighter-fatter effect are potential sources of bias (\citealt{2013MNRAS.429..661M}), while it has been shown that for \emph{Roman} the effect of persistence will not be an issue (\citealt{2021arXiv210610273L}).
+Qualitatively, if the recovered shear is biased by 1$\%$ ($m=0.01$), $S_{8} = \sigma_{8} \sqrt{\Omega_{m}/0.3}$ could be biased about 1.5$\%$ in the final cosmology result.
+Thus, quantifying and correcting these biases before the real survey begins is extremely important.
+
+\subsection{\textsc{metacalibration} Formalism}
+Here, we describe the general features of how \textsc{metacalibration} calibrates the biased measurement of galaxy ellipticities on the image stamps.
+\textsc{metacalibration} creates one unsheared and four artificially-sheared galaxy stamps.
+Each is deconvolved with the input PSF, left unsheared or sheared with an additional gravitational shear of $\delta\gamma=\pm 0.01$ in the two basis directions ($+g1$, $-g1$, $+g2$, $-g2$) and re-convolved with a new slightly larger isotropic, Gaussian PSF.
+\textsc{metacalibration} works under the assumption that the input shear is small, otherwise the recovered shear would be biased without accounting for higher order terms.
+It is a balance to choose an input shear that results in higher S/N of an object and unbiased shape measurement.
+Figure \ref{fig:metacal_shear_linear} shows the performance as a function of input shear leading to the choice of input shear $\gamma=\pm 0.02$.
+
+After processing the images in \textsc{metacalibration} and measuring the shapes in \texttt{ngmix}, we have 5 shape catalogs in each \textsc{metacalibration} shear direction.
+We can then compute the shear response from these catalogs and calculate the calibrated ensemble galaxy ellipticities.
+The shear response can be understood as the change in objects' ellipticities with respect to the change in gravitational shear.
+Mathematically, the observed ellipticities, $\vb*{e}$ = ($e_{1}$, $e_{2}$), can be approximated using a Taylor expansion around the two-component shear, $\vb*{\gamma}=0$.
+Higher terms here can be dropped assuming the gravitational shear is small (reduced shear).
+\begin{equation}
+    \vb*{e} = \vb*{e}\rvert_{\vb*{\gamma}=0} + \frac{\partial \vb*{e}}{\partial \vb*{\gamma}}\bigg\rvert_{\vb*{\gamma}=0}\vb*{\gamma} + \ldots
+\end{equation}
+From this expression, the shear response matrix can be defined as, 
+\begin{equation}
+    \vb*{R} \equiv \frac{\partial \vb*{e}}{\partial \vb*{\gamma}}\bigg\rvert_{\vb*{\gamma}=0} = 
+    \begin{pmatrix}
+        \partial e_{1}/\partial \gamma_{1} & \partial e_{2}/\partial \gamma_{1} \\ 
+        \partial e_{1}/\partial \gamma_{2} & \partial e_{2}/\partial \gamma_{2}
+    \end{pmatrix}. 
+\end{equation}
+The ensemble mean of measured ellipticities $\langle\vb*{e}\rangle$ can then computed.
+Since we expect galaxies to be randomly oriented such that $\langle\vb*{e}\rangle\rvert_{\vb*{\gamma}=0}=0$, we have a relationship between the measured ellipticities and the input shear in the simulations,
+\begin{equation}
+    \langle\vb*{e}\rangle \approx \langle \vb*{R}\vb*{\gamma} \rangle. 
+\end{equation}
+
+In practice, we compute the mean shear response from the five versions of \textsc{metacalibration} catalog using the finite difference method.
+
+\begin{equation}
+    \langle\vb*{R_{ij}}\rangle = 
+    \frac{\langle e^{+}_{i} - e^{-}_{i} \rangle}{\delta\gamma_{j}}, 
+\end{equation}
+where $e^{+}_{i}$ and $e^{-}_{i}$ is the $i$-th component of the galaxy ellipticity where positive ($+$) or negative ($-$) shear is applied in $i$-th direction.
+
+The mean shear response is then used to get the \textsc{metacalibration}-calibrated shapes from the unsheared catalog.
+For individual objects, using Eq.
+\ref{eqn:linear}.
+we compare the input shear and the calibrated shapes to calculate multiplicative ($\vb*{M}$) and additive bias ($\vb*{C}$).
 
@@
 % 	\vspace*{-3mm}
-    \caption{The rotation of the Roman PSF produced from the \texttt{galsim.roman} module.
-The position angle (PA) which determines the rotation of the focal plane is $0^{\circ}$ and $30^{\circ}$.
+    \caption{The rotation of the Roman PSF produced by the \texttt{galsim.roman} module.
+The position angle (PA) which determines the rotation of the focal plane is $0^{\circ}$ and $30^{\circ}$ clockwise.
+These are drawn for SCA=1 and H158 bandpass at a native pixel scale.
 The rotation of the PSF is particularly important when an object has multiple exposures.
@@
 	%\vspace*{-10mm}
-    \caption{The top row shows the first entry of the single epoch images and its coadded image, and the corresponding single-epoch and coadded oversampled PSF images for an object with low signal-to-noise ratio (S/N=9.69 in a single-epoch image).
-The bottom row shows the same for an object with high signal-to-noise ratio (S/N=1552.97 in a single-epoch image).
-The PSFs are shown in a log-scale.}
+    \caption{The top row shows the first observation of the single epoch images and its coadded image, and the corresponding single-epoch and coadded oversampled PSF images for a galaxy with low signal-to-noise ratio (S/N=9.69 in a single-epoch image).
+The bottom row shows the same for a galaxy with high signal-to-noise ratio (S/N=1552.97 in a single-epoch image).
+The PSFs are shown in a log-scale.
+The single epoch PSFs are almost identical, since there is no visually different feature for modeling them in different dithers and SCAs.
+There are two features to note here.
+One is how coadding helps for low S/N objects, and the other feature is the coadded PSFs look more isotropic than the single-epoch PSF due to different numbers of exposures.}
     \label{fig:singlecoadd}
@@
 \ref{subsec:psc}.
+\textcolor{red}{mention figure 2!}
 
@@
 
-The parameter choices are listed in Table.
+The fixed parameters for the simulations are listed in Table.
 \ref{tab:params}.
-With these parameters set, we simulated images with varying galaxy model profile, PSF model profile, the artificial shear, and background noise level, without any complications in the images and pipelines such as detector effects and coaddition.
-We first verify that our input gravitational shear is unbiased in \textsc{metacalibration} framework and the uncertainty in the recovered shape is small enough for the \emph{Roman} requirement (Fig.
-\ref{fig:metacal_shear_linear}).
-We then test the pipeline by doubling the background noise.
-Due to the \emph{Roman} being in NIR range, the expected background noise level in the images is higher compared to optical imaging surveys like DES.
-With this test, we can confirm that the treatment of correlated noise induced in \textsc{metacalibration} process for low S/N objects does not trigger any bias at the level we should be concerned (\citealt{2017ApJ...841...24S}).
-Another test with \emph{Roman} PSF instead of Gaussian PSF does guarantee that the PSF features particular to \emph{Roman} do not bias the shape recovery even though it is undersampled.
+With these parameters, we simulated images with varying galaxy model profile, PSF model profile, the artificial shear, and background noise level, without any complications in the images and pipelines such as detector effects and coaddition.
+We set the basic light profiles for galaxies and PSF to be Gaussian, and first attempted to verify that our input gravitational shear ($\abs{g}$=0.02) is unbiased in \textsc{metacalibration} framework and the required multiplicative bias for the \emph{Roman} is satisfied.
+Figure \ref{fig:metacal_shear_linear} shows that our choice of applied shear is within the requirement; therefore, it will not be the contributor to the bias in the full simulations.
+As in the Table \ref{tab:simple_sim}, the multiplicative bias is within the requirement.
+We believe that this test is unbiased because \texttt{ngmix} can build a faithful forward-model of undersampled Gaussian galaxy, even though the PSF image is undersampled.
+
+Next, we tested the shape measurement pipeline by doubling the background noise.
+This test should validate that \textsc{metacalibration} process can tolerate the Poisson noise in the objects since it is not corrected in the process unlike the background noise (\citealt{2017ApJ...841...24S}).
+From the second variant in the Table \ref{tab:simple_sim}, while this might be a problem to satisfy the mission requirement, we can confirm that the treatment of correlated noise for low S/N objects does not trigger any bias at the level we are concerned.
+
+As in the final row in Table \ref{tab:simple_sim} we finally validated that the use of the \emph{Roman} PSF instead of Gaussian PSF does not bias the shape recovery even though it is undersampled and the PSF has particular features of the telescope.
 Upon validating there does not exist any bias at the fundamental level, we began constructing coadd and more complex measurement pipeline.
@@
     %\vspace*{-5mm}
-    \caption{At first order, the \textsc{metacalibration} method only works for small shears.
-The next order effect is seen as a quadratic dependence of the multiplicative shear bias on on the applied shear.
-A larger input shear increases the signal-to-noise of bias estimates, but to keep this effect small compared to requirements, we limit input shears to $\pm 0.01$.}
+    \caption{We show the recovered multiplicative bias on the shear as a function of applied shear for the choice of the applied shear in our simulations.
+At first order, the \textsc{metacalibration} algorithm only works for small input shears.
+The next order effect is seen as a quadratic dependence of the multiplicative shear bias on on the applied shear (\citealt{2017ApJ...841...24S}).
+A larger input shear increases the signal-to-noise of bias estimates, but to keep the non-linear effect small compared to requirements, we limit input shears to $\pm 0.02$.
+}
     \label{fig:metacal_shear_linear}
@@
 \label{sec:methods}
-Our goal is to test whether the recovered shapes with \textsc{metacalibration} are non-biased for \emph{Roman}.
+Our goal is to test whether the recovered shapes with \textsc{metacalibration} are non-biased for \emph{Roman} and to understand the factors that might contribute to the non-negligible bias.
 In order to do so, we need to build measurement pipelines within the current simulation framework that produces a final calibrated shear measurement.
@@
 
+Among imaging surveys, coadding a small region of the sky is common, for example \textsc{swarp} (Bertin et al.
+2002) or \textsc{drizzle} (\citealt{2002PASP..114..144F}), because the Nyquist-sampled coadded images can be fully utilized to detect objects and model the PSF.
+However, we decided to coadd the postage-stamp cutouts since we know the true centers of the simulated galaxies and we have the true simulated PSF.
+It is also beneficial to use this method because we need coadds which can directly be injected into the shape measurement due to the number of cutouts.
+We specifically use \texttt{psc} (postage stamp coadds) as our coadding process.
+
 We reconstruct a better-sampled coadd image from multiple exposures in MEDS files.
-For the coaddition of the PSF, we choose to coadd the image with an oversampled PSF `model'.
-We oversample the original PSF by a factor of 4 to simulate the better sampled PSF model that will eventually be possible to construct during the \emph{Roman} mission.
-For each exposure of the object we render the \emph{Roman} PSF with a stamp size of 32 pixels at the galaxy centroid.
-We modified the original \texttt{psc} code to improve performance for this \emph{Roman} study, and these modifications are listed below with the general coadding process in \texttt{psc}.
+\textcolor{red}{For the coaddition of the PSF, we choose to coadd the image with an oversampled PSF `model'.
+We oversample the original PSF by a factor of 4 to simulate the better sampled PSF model that will eventually be possible to construct during the \emph{Roman} mission.} For each exposure of the object we render the \emph{Roman} PSF with a stamp size of 32 pixels at the galaxy centroid.
+We modified the original \texttt{psc} code to improve performance for this \emph{Roman} study, and these modifications are explained below with the general coadding process in \texttt{psc}.
 
@@
     \item Creates the coadd stamp with 0.8 $\times$ original pixel scale.
-We scale the original pixel scale of the final coadd stamp to mitigate the effect of undersampling.
+We scale the original pixel scale of the final coadd stamp to increase the image sampling.
 This final pixel scale was chosen to prevent the presence of visual artifacts in the structure of the coadd PSF image.
@@
 
-Before we measure and calibrate shapes with \texttt{ngmix}, we downsample the high-resolution PSF to the original pixel size.
+\textcolor{red}{Before we measure and calibrate shapes with \texttt{ngmix}, we downsample the high-resolution PSF to the original pixel size.
 Figure \ref{fig:coadd_oversample_res} shows the coadded oversampled PSF and the then-downsampled PSF, and their differences.
@@
 Figure \ref{fig:single_to_coadd_rgb} shows the coadd products in different bandpasses for a relatively high S/N object.
-The multiband PSF image is the oversampled version for better visualization.
+The multiband PSF image is the oversampled version for better visualization.}
 
-\begin{figure}
-	\includegraphics[width=\columnwidth]{psf_differences.pdf}
-    % \vspace*{-5mm}
-    \caption{The left and middle panels illustrate the coadded \emph{Roman} PSF at its original pixel scale and the coadded PSF with a pixel scale that is generated with a pixel scale that is smaller by a factor of 4 and then down-sampled to this original pixel scale.
+% \begin{figure}
+% 	\includegraphics[width=\columnwidth]{psf_differences_v2.pdf}
+%     % \vspace*{-5mm}
+%     \caption{The left and middle panels illustrate the coadded \emph{Roman} PSF at its original pixel scale and the coadded PSF with a pixel scale that is generated with a pixel scale that is smaller by a factor of 4 and then down-sampled to this original pixel scale.
 These are visualized in a log scale.
@@
 }
-    \label{fig:coadd_oversample_res}
-\end{figure}
+%     \label{fig:coadd_oversample_res}
+% \end{figure}
 
@@
 The S/N of the coadd image is S/N=110.
-Finally, the right-most panel shows the coadded oversampled PSF in a log scale.}
+Finally, \textcolor{red}{the right-most panel shows the coadded oversampled PSF in a log scale.}}
     \label{fig:single_to_coadd_rgb}
@@
 \label{subsec:mcal}
-Once we construct the individual galaxy stamp coadds from the MEDS files, we recover the calibrated shear signal using the \textsc{metacalibration} process.
+Once we construct the individual galaxy stamp coadds from the MEDS files, we recover the calibrated shear signal using the \textsc{metacalibration} process (\citealt{2017arXiv170202600H, 2017ApJ...841...24S}).
 The bootstrapper method used in \texttt{ngmix} wraps the \textsc{metacalibration} and the shape fit processes.
 The priors needed for the fit are listed in Table \ref{tab:priors}.
-We note that we have run \textsc{metacalibration} with \texttt{fitgauss} and \texttt{gauss} parameters for the new PSF model, and we found that the \texttt{gauss} method performs better for our case.
+We note that we have run \textsc{metacalibration} with the \texttt{fitgauss} and \texttt{gauss} PSF model to reconvolve the sheared galaxy images, and the measurement with \texttt{fitgauss} model was numerically unstable resulting in the inconsistency between $m_{1}$ and $m_{2}$.
+We, therefore, use the \texttt{gauss} model for the rest of the simulations.
 
@@
 
-\textsc{metacalibration} creates one unsheared and four artificially-sheared galaxy stamps.
-Each is deconvolved with the input PSF, left unsheared or sheared with an additional gravitational shear of $\delta\gamma=\pm 0.01$ in the two basis directions ($+g1$, $-g1$, $+g2$, $-g2$) and re-convolved with a new slightly larger isotropic, Gaussian PSF.
-\textsc{metacalibration} works under the assumption that the input shear is small, otherwise the recovered shear would be biased without accounting for higher order terms.
-It is a balance to choose an input shear that results in higher S/N of an object and unbiased shape measurement.
-Figure \ref{fig:metacal_shear_linear} shows the performance as a function of input shear leading to the choice of input shear $\gamma=\pm 0.02$.
-
-After processing the images in \textsc{metacalibration} and measuring the shapes in \texttt{ngmix}, we have 5 shape catalogs in each \textsc{metacalibration} shear direction.
-We can then compute the shear response from these catalogs and calculate the calibrated ensemble galaxy ellipticities.
-The shear response can be understood as the change in objects' ellipticities with respect to the change in gravitational shear.
-Mathematically, the observed ellipticities, $\vb*{e}$ = ($e_{1}$, $e_{2}$), can be approximated using a Taylor expansion around the two-component shear, $\vb*{\gamma}=0$.
-Higher terms here can be dropped assuming the gravitational shear is small.
-\begin{equation}
-    \vb*{e} = \vb*{e}\rvert_{\vb*{\gamma}=0} + \frac{\partial \vb*{e}}{\partial \vb*{\gamma}}\bigg\rvert_{\vb*{\gamma}=0}\vb*{\gamma} + \ldots
-\end{equation}
-From this expression, the shear response matrix can be defined as, 
-\begin{equation}
-    \vb*{R} \equiv \frac{\partial \vb*{e}}{\partial \vb*{\gamma}}\bigg\rvert_{\vb*{\gamma}=0} = 
-    \begin{pmatrix}
-        \partial e_{1}/\partial \gamma_{1} & \partial e_{2}/\partial \gamma_{1} \\ 
-        \partial e_{1}/\partial \gamma_{2} & \partial e_{2}/\partial \gamma_{2}
-    \end{pmatrix}. 
-\end{equation}
-The ensemble mean of measured ellipticities $\langle\vb*{e}\rangle$ can then computed.
-Since we expect galaxies to be randomly oriented such that $\langle\vb*{e}\rangle\rvert_{\vb*{\gamma}=0}=0$, we have a relationship between the measured ellipticities and the input shear in the simulations,
-\begin{equation}
-    \langle\vb*{e}\rangle \approx \langle \vb*{R}\vb*{\gamma} \rangle. 
-\end{equation}
-
-In practice, we compute the shear response from the five versions of \textsc{metacalibration} catalog using the finite difference method.
-
-\begin{equation}
-    \langle\vb*{R_{ij}}\rangle = 
-    \frac{\langle e^{+}_{i} - e^{-}_{i} \rangle}{\delta\gamma_{j}}, 
-\end{equation}
-where $e^{+}_{i}$ and $e^{-}_{i}$ is the $i$-th component of the galaxy ellipticity where positive ($+$) or negative ($-$) shear is applied in $i$-th direction.
-
-Then, this shear response is used to compute the multiplicative ($\vb*{M}$) and additive ($\vb*{C}$) bias using the linear shear bias model (\ref{eqn:linear}).
 The covariances are computed using the bootstrap estimate of standard error.
@@
 We divide our shape measurement into two categories; single-band and multiband.
-For single-band measurements, in each filter, we measure the shapes from the original single exposures by jointly fitting them.
+For single-band measurements, in each filter, we measured the shapes from the original single exposures by jointly fitting them.
 We set our base case to be this single-band joint-fit measurement.
-As the more developed case, we measure shapes with the single-band coadd in each filter.
-For the single-epoch multiband measurement, we match the objects between each filter and measure the shapes with the joint-fit of single exposures across all the filters.
-The coadd multiband measurement is jointly fit across the three coadds from each filter to recover the shapes.
+As the more developed case, we measured shapes with the single-band coadd in each filter.
+For the single-epoch multiband measurement, we matched the objects between each filter and measured the shapes with the joint-fit of single exposures across all the filters.
+The coadd multiband measurement was jointly fit across the three coadds from each filter to recover the shapes.
 
 \subsection{Statistics of the Shape Catalog}
-From the CANDELS catalog, based on the \emph{Roman} Weak Lensing mission requirements, objects are pre-selected and simulated.
-In total, we simulate 907,170 galaxies on 18 SCAs across 198 pointings for F184, 227 pointings for H158, and 238 pointings for J129 bandpass.
-We do not make any selection cuts on the simulated catalogs based on measured properties, since all input objects should pass requirements for weak lensing selection (e.g., S/N>18).
-Even so, due to the misestimation of the PSF or low S/N, the Gaussian mixture in \texttt{ngmix} fails to fit about 5\% of all simulated objects, and so the total number of the recovered objects for single-band measurements is, 861,960 for F184, 863,358 for H158, and 859,645 for J129.
-For the multiband (H158+J129+F184) coadd measurements, we use objects that are measured successfully in all of the filters and the total number of the recovered objects is 851,821.
-Figures \ref{fig:true_properties} and \ref{fig:measured_properties} show the true properties from the truth catalog and measured properties from the \textsc{metacalibration} shape catalogs.
+From the CANDELS catalog, based on the \emph{Roman} Weak Lensing mission requirements, objects were pre-selected and simulated.
+In total, the galaxy photometry catalog contains 907,170 galaxies and from this catalog we simulated galaxies on 18 SCAs across 198 pointings for F184, 227 pointings for H158, and 238 pointings for J129 bandpass.
+We did not make any selection cuts on the simulated catalogs based on measured properties, since all input objects should pass requirements for weak lensing selection.
+In our samples, no de-blending was necessary since the shape measurement was performed on object stamps without neighboring objects.
+Blending issues related to the object detection is mentioned later in Sec.
+\ref{sec:discussion}.
+
+In the end, we were able to recover about 95\% of all the simulated objects in each filter, excluding objects that are at the SCA edges or the Gaussian mixture in \texttt{ngmix} failed to fit.
+The total number of the recovered objects for single-band measurements was, 861,407 for F184, 863,146 for H158, and 859,193 for J129.
+For the multiband (H158+J129+F184) coadd measurements, we used objects that are measured successfully in all of the filters and the total number of the recovered objects is 851,821.
+Figures \ref{fig:true_properties}, \ref{fig:ngmix_measured_properties} and \ref{fig:hsm_measured_properties} show the true properties from the truth catalog and measured properties from the \textsc{metacalibration} shape catalogs.
 
@@
 	\centering
-    \caption{The left panel shows the simulated magnitudes of galaxies for all the 3 filter we have used to measure shapes.
+    \caption{The left panel shows the measured magnitudes of galaxies for all the 3 filter we have used to measure shapes.
 The mean magnitude for H158, F184, and J129 are respectively 23.098, 22.976, and 23.273.
@@
 The mean half-light radii for input and measured galaxies are 0.294 and 0.221 arcsec for H158.
-For these histograms, we are showing the objects with a successful fit in \texttt{ngmix}.}
+\textcolor{red}{we'll see the result from the new coadd run.
+ngmix output is arcsec2}}
     \label{fig:true_properties}
@@
     \centering
-	\includegraphics[width=\textwidth]{ngmix_snr_T.pdf}
-    \caption{The histograms of measured galaxy and PSF properties in \texttt{ngmix} for single-band coadd and multiband coadd measurements.
-It includes S/N, galaxy size $T{gal}$, and the shape and size of the PSF.
+	\includegraphics[width=\textwidth]{true_ngmix_measured_properties.pdf}
+    \caption{The histograms of measured galaxy properties in \texttt{ngmix} for single-band coadd and multiband coadd measurements.
+It includes magnitude, S/N, galaxy size $T{gal}$.
 The S/N is significantly improved in the multiband fit.}
-    \label{fig:measured_properties}
+    \label{fig:ngmix_measured_properties}
+\end{figure*}
+
+\begin{figure*}
+    %\hspace*{-3.1cm}
+    \centering
+	\includegraphics[width=\textwidth]{hsm_PSF_properties.pdf}
+    \caption{The histograms of measured PSF properties in adaptive moments method for single-band coadd and multiband coadd measurements.
+The shape and size of the PSF are shown.
+\textcolor{red}{We may not to present this plot, as it is hard to explain the trends.}}
+    \label{fig:hsm_measured_properties}
 \end{figure*}
@@
 The multiplicative and additive bias values listed in the text are the average of $m_{1}$ and $m_{2}$, and $c_{1}$ and $c_{2}$.
-These are usually symmetric, except in the case of the coadd measurements, where $c_1>c_2$.
-The comprehensive results can be found in Table \ref{tab:bias_summary} and the single-band coadd result compared to the previously measured values in Fig.
+\textcolor{red}{These are usually symmetric, except in the case of the coadd measurements, where $c_1>c_2$.} The comprehensive results can be found in Table \ref{tab:bias_summary} and the single-band coadd result compared to the previously measured values in Fig.
 \ref{fig:final_result}.
+These multiple simulation variants were run to achieve three milestones.
+One is to characterize how much the shear bias exists if we were to use the original, undersampled images, by recovering shears from the single exposures in each bandpass.
+Second step is to verify if coadding/better-sampling by 0.8 pixels can mitigate the effect of undersampling.
+Lastly, as the final assessment we investigate if combining the three bandpasses would result in constraining the recovered shapes.
 
@@
 Their result can be extrapolated to our single-band single-epoch results.
-The multiplicative bias of single-band single-epoch measurements is roughly 1\% in each filter.
+The multiplicative bias of single-band single-epoch measurements is consistent with zero within 2$\sigma$ in each filter ($\sigma$=0.72\%), except for $m_{2}=(-1.61\pm0.66)\%$ in H158.
+This level of bias is consistent with the finding from K21, which explored the effect of undersampled images in \emph{Euclid} image simulations.
+
 When the coadded images for each filter are used, the bias is at the similar level or worse within the uncertainties.
-We can conclude that in the current \emph{Roman} simulation the multiplicative bias has a similar dependence on the sampling factor as shown in K21, but with a smaller amplitude.
-We do not see any clear improvements in the recovered shear when we coadd the single-epoch images, despite having a smaller pixel scale (better sampling) in the images.
+\textcolor{red}{We can conclude that in the current \emph{Roman} simulation the multiplicative bias has a similar dependence on the sampling factor as shown in K21, but with a smaller amplitude.} We do not see any clear improvements in the recovered shear when we coadd the single-epoch images, despite having a smaller pixel scale (better sampling) in the images.
 This is most likely due to an issue with how we are currently treating the PSF or correlated noise in the coadding process, given the large observed $c_1$ when coadding discussed below.
@@
 		\hline
-		single-epochs (J129) & 1.01 & 1.17$\pm$0.68 & 0.44$\pm$0.75 & 4.46$\pm$1.32 & 0.64$\pm$1.31\\
-		single-epochs (H158) & 1.23 & -1.07$\pm$0.62 & -1.61$\pm$0.66 & 2.83$\pm$1.35 & 2.33$\pm$1.22\\
-		single-epochs (F184) & 1.44 & -0.86$\pm$0.72 & -0.69$\pm$0.83 & 2.62$\pm$1.56 & 0.23$\pm$1.53\\
+		single-epochs (J129) & 0.88 & 1.17$\pm$0.68 & 0.44$\pm$0.75 & 4.46$\pm$1.32 & 0.64$\pm$1.31\\
+		single-epochs (H158) & 1.08 & -1.07$\pm$0.62 & -1.61$\pm$0.66 & 2.83$\pm$1.35 & 2.33$\pm$1.22\\
+		single-epochs (F184) & 1.31 & -0.86$\pm$0.72 & -0.69$\pm$0.83 & 2.62$\pm$1.56 & 0.23$\pm$1.53\\
 		\hline
-		single-band coadd (J129) & 1.26 & -1.84$\pm$0.71 & -1.90$\pm$0.65 & 11.99$\pm$1.39 & 0.59$\pm$1.41\\
-		single-band coadd (H158) & 1.54 & -1.75$\pm$0.67 & -1.68$\pm$0.64 & 14.39$\pm$1.32 & 4.29$\pm$1.35\\
-		single-band coadd (F184) & 1.79 & -0.28$\pm$0.83 & -0.27$\pm$0.78 & 12.15$\pm$1.56 & 5.66$\pm$1.56\\
+		single-band coadd (J129) & 1.10 & -1.84$\pm$0.71 & -1.90$\pm$0.65 & 11.99$\pm$1.39 & 0.59$\pm$1.41\\
+		\textcolor{red}{single-band coadd (H158) with oversampled PSF & 1.35 & -1.75$\pm$0.67 & -1.68$\pm$0.64 & 14.39$\pm$1.32 & 4.29$\pm$1.35}\\
+		single-band coadd (H158) & 1.35 & -0.69$\pm$0.63 & -0.83$\pm$0.61 & 2.16$\pm$1.31 & 0.77$\pm$1.19\\
+		single-band coadd (F184) & 1.64 & -0.28$\pm$0.83 & -0.27$\pm$0.78 & 12.15$\pm$1.56 & 5.66$\pm$1.56\\
 		\hline
@@
 \begin{figure*}
-	\includegraphics[width=\textwidth]{final_result.pdf}
-    \caption{The multiplicative ($m$) and additive ($c$) bias of the single-band coadd measurements. From left data point to the right, they represent each data for J129, H158, F184 bandpasses. }
+	\includegraphics[width=\textwidth]{final_result_v2.pdf}
+    \caption{The multiplicative ($m$) and additive ($c$) bias of the single-band coadd measurements.
+From left data point to the right, they represent each data for J129, H158, F184 bandpasses.
+T21 refers the non-calibrated result from the first-generation of the simulations by \cite{2021MNRAS.501.2044T}.
+}
     \label{fig:final_result}
@@
     \setlength\itemsep{1em}
-    \item \textbf{Simulation Volume}: Expand the simulated area to 20 $deg^{2}$. (Troxel et al. in prep.)
+    \item \textbf{Simulation Volume}: Expand the simulated area to 20 $deg^{2}$. (Troxel et al. in prep.), in order to obtain smaller error bars on the resulting shear calibration biases.
 
@@
     \item \textbf{Image Coaddition}: We will implement a new coaddition strategy that coadds the whole scene instead of individual stamp cutouts using  \texttt{AstroDrizzle}\footnote{\url{https://github.com/spacetelescope/drizzlepac}}: A Python implementation of MultiDrizzle which was used for \emph{Hubble} Space Telescope (\citealt{2003hstc.conf..325B}).
-With \texttt{AstroDrizzle}, we are able to further mitigate the effect of undersampling in the \emph{Roman} images by going to smaller coadd pixel scales.
+With \texttt{AstroDrizzle}, we are able to further mitigate the effect of undersampling in the \emph{Roman} images with smaller coadd pixel scales.
 We expect this to further reduce the measured shear bias by up to 1\% based on its trend with sampling factor.

### 2022-02-23 paper_v3.tex
v3.2

@@
 %    Renamed to match the new package name
-%    Version number matches mnras.cls
+%    Version number matches mnras.clshttps://www.overleaf.com/project/605371a91cecb490b3d4a73e
 %    A few minor tweaks to wording
@@
 \documentclass[fleqn,usenatbib]{mnras}
-
 % MNRAS is set in Times font. If you don't have this installed (most LaTeX
@@
 \begin{abstract}
-We investigate the performance of the \textsc{metacalibration} shear calibration framework using image simulations for the \emph{Nancy Grace Roman} Space Telescope (\emph{Roman}) reference High-Latitude Imaging Survey (HLIS).
-These large-scale realistic image simulations are necessary to measure shear bias to confirm that the requirements of the instrument and the overall weak lensing survey strategy are met.
-The weak lensing program of the \emph{Roman} mission requires the galaxy shapes to be calibrated within about 0.03\%.
-To reach this goal, we can test our calibration process with various simulations and ultimately isolate the sources where these residual shear biases arise.
-In this work, we incorporate several new realistic processing-pipeline updates necessary to calibrate shear with a better precision relative to the previous version of the simulations and show first results for the reference HLIS using \textsc{metacalibration}.
-We find that in the simplified simulations where objects are drawn with the Gaussian light profile, \textsc{metacalibration} can calibrate shapes within the requirement, $m=(-0.01\pm 0.10)$\%.
-However, \textsc{metacalibration} as used in the most-realistic version of the simulations can only reduce the shear calibration bias to the percent level.
-With the single-epoch images, across all three filters we estimate the multiplicative bias $m=(-1.34\pm 0.67)$\%.
-This is we believe caused by the undersampled \emph{Roman} images.
-\textcolor{red}{In an attempt to reduce the effect of undersampling, we esimate the bias on the coadd cutouts and find that $m=(-2.33\pm 0.64)$\%.} Overall, within the current simulation volume, there is evidence that \textsc{metacalibration} as currently implemented will not calibrate shapes with zero shear bias in the \emph{Roman} HLIS and further work on the shear calibration methodology is necessary.
-In the future, we will need to substantially increase the simulation volume by 400 (about the same size as the survey area of 2000 deg$^{2}$) to reach the precision necessary for the HLIS.
+We investigate the performance of the \textsc{metacalibration} shear calibration framework using simulated imaging data for the \emph{Nancy Grace Roman} Space Telescope (\emph{Roman}) reference High-Latitude Imaging Survey (HLIS).
+%These large-scale realistic image simulations are necessary to measure shear bias to confirm that the requirements of the instrument and the overall weak lensing survey strategy are met. 
+The weak lensing program of the \emph{Roman} mission requires the mean galaxy ellipticity to be calibrated within about 0.03\%.
+To reach this goal, we can test our calibration process with various simulations and ultimately isolate the sources where these residual shear biases might arise in order to improve our methods.
+In this work, we build on the first set of Roman HLIS simulated imaging data in \cite{2021MNRAS.501.2044T} to incorporate several new realistic processing-pipeline updates necessary to more accurately process the imaging data and calibrate the shear.
+We show the first results of this calibration for six deg$^{2}$ of the simulated reference HLIS using \textsc{metacalibration} and compare these results to measurements on more simple, faster Roman-like image simulations.
+In both cases, we neglect the impact of blending of objects.
+We find that in the simplified simulations, \textsc{metacalibration} can calibrate shapes to within $m=(-0.01\pm 0.10)$\%.
+When applied to the current most-realistic version of the simulations, the precision is much lower, with a \textsc{metacalibration} estimate of $m=(-1.34\pm 0.67)$\% for joint multi-band single-epoch measurements and $m=(-1.13\pm 0.60)$\% for multi-band coadd measurements.
+These results are all consistent with zero within 1--2$\sigma$, indicating we are currently limited by our simulated survey volume.
+Further work on testing the shear calibration methodology is necessary at higher precision to reach the levels of the \textit{Roman} requirements, in particular in the presence of blending.
+%In the future, we will need to substantially increase the simulation volume by $\sim$400 (about the same size as the survey area of 2000 deg$^{2}$) to reach the precision necessary to test the HLIS requirements.
+Current results demonstrate, however, that the \textsc{metacalibration} method can work on undersampled space-based imaging data at well-below the requirements levels of current weak lensing surveys.
 \end{abstract}
@@
 
-Since the formulation of a physical cosmological model, more observational evidence has shown that the contents of the universe are mostly in the dark sector (\citealt{2020A&A...633A..69H, 2018PhRvD..98d3528T, 2019PhRvL.122q1301A, 2019PASJ...71...43H, 2021A&A...645A.104A}).
+Since the formulation of a physical cosmological model, observational evidence has shown that the contents of the universe are mostly in the dark sector (\citealt{2020A&A...641A...8P, 2020MNRAS.498.2492G, 2020MNRAS.499.5527T, 2021A&A...645A.104A, 2022PhRvD.105b3520A, 2022arXiv220204077B}).
 Within this sector, dark energy accounts for the accelerating expansion of the universe (e.g., \citealt{1998AJ....116.1009R, 1999AIPC..478..129P}) and the combination of dark energy and dark matter are responsible for the observed growth of large-scale structure (\citealt{2015RPPh...78h6901K, 2017grle.book.....D}).
 The growth can be studied by carefully reconstructing the paths of the light leaving distant galaxies and going through the regions where mass concentrates in the universe; this physical phenomenon is called gravitational lensing.
-“Weak” gravitational lensing causes a slight distortion to intrinsic galaxy shapes when observed from the Earth.
-By detecting millions of these gravitationally lensed galaxies and computing their ensemble distortion levels, we can explore the dark matter density and the amplitude of matter fluctuation in the universe (e.g., \citealt{2001PhR...340..291B}).
+“Weak” gravitational lensing causes a slight distortion to intrinsic galaxy shapes called shear.
+By detecting millions of these gravitationally lensed galaxies and computing their ensemble shear, we can explore the dark matter density and the amplitude of matter fluctuation in the universe (e.g., \citealt{2001PhR...340..291B}).
 Measuring these quantities eventually helps us learn about the history of the development of the large-scale structure in the universe.
@@
 Thus, near-future Stage IV surveys (\citealt{2006astro.ph..9591A}) such as Euclid\footnote{\url{ http://sci.esa.int/euclid}} (\citealt{2011arXiv1110.3193L}), the Vera C.
-Rubin Observatory Legacy Survey of Space and Time\footnote{\url{ http://www.lsst.org}} (\emph{Rubin}: \citealt{2009arXiv0912.0201L, 2019ApJ...873..111I}), and \emph{Nancy Grace Roman} Space Telescope\footnote{\url{https://roman.gsfc.nasa.gov}} (\emph{Roman}: \citealt{2015arXiv150303757S}) require even better control of systematics.
-In order to understand the systematic uncertainties we face, we must develop realistic image simulations, apply pre-existing shape measurement to the simulated images, and determine any potential residual systematic effects and build a strategy for modifying the calibration methodology to mitigate them.
+Rubin Observatory Legacy Survey of Space and Time\footnote{\url{ http://www.lsst.org}} (\emph{Rubin}: \citealt{2009arXiv0912.0201L, 2019ApJ...873..111I}), and the \emph{Nancy Grace Roman} Space Telescope\footnote{\url{https://roman.gsfc.nasa.gov}} (\emph{Roman}: \citealt{2015arXiv150303757S}) require even better control of systematics.
+In order to understand the systematic uncertainties we face, we must develop realistic image simulations, apply existing shape measurement methods to the simulated images, and determine any potential residual systematic effects and build a strategy for modifying the calibration methodology to mitigate them.
 
@@
 \end{itemize} 
-
-Conventionally, these observational systematic biases are realized through a number of simulations and validations, and these propagate into the final galaxy shapes we measure.
+Conventionally, these observational systematic biases are characterized through a number of simulations and validation tests, and these propagate into uncertainties on the final mean galaxy shear we measure.
 We quantify this impact as shear calibration bias.
-There have been several shear calibration and bias mitigation efforts that were proposed by STEP (\citealt{2006MNRAS.368.1323H, 2007MNRAS.376...13M}) and GREAT (\citealt{2010MNRAS.405.2044B, 2013ApJS..205...12K, 2015MNRAS.450.2963M}) challenges, to meet the requirements for the current imaging surveys.
+There have been several shear calibration and bias mitigation efforts that were proposed by the STEP (\citealt{2006MNRAS.368.1323H, 2007MNRAS.376...13M}) and GREAT (\citealt{2010MNRAS.405.2044B, 2013ApJS..205...12K, 2015MNRAS.450.2963M}) challenges, to meet the requirements for the current imaging surveys.
 In particular, one of the state-of-the-art self-calibration methods, \textsc{metacalibration} (\citealt{2017arXiv170202600H, 2017ApJ...841...24S}) has been shown to be able to substantially reduce the significance of shear bias.
 It has been confirmed that shear can be calibrated with \textsc{metacalibration} at the few-percent level in DES (\citealt{2018MNRAS.481.1149Z, 2020arXiv201103408G}), without accounting for galaxy blending and detection.
-Tackling the issue of blending/detection is one key step forward for the DES Y6 analysis and preparatory Rubin LSST work with the shear-dependent detection and calibration technique (\textsc{metadetection}; \citealt{2020ApJ...902..138S}).
-While the major advantage of \textsc{metacalibration} is that it can be directly applied to real galaxy images without needing to rely on an ensemble calibration from image simulations, limitations for future surveys are not well-known.
+Tackling the issue of blending/detection is one key step forward for the DES Y6 analysis and preparatory Rubin LSST work with the shear-dependent detection and calibration technique \textsc{metadetection} (\citealt{2020ApJ...902..138S}).
+While the major advantage of \textsc{metacalibration} or \textsc{metadetection} is that they can be directly applied to real galaxy images without needing to rely on an ensemble calibration from image simulations, limitations for future surveys are not well-known.
 
 One possible limitation might lie in the effect of undersampled images in space-based surveys like \emph{Euclid} and \emph{Roman}, which will operate at its diffraction-limit.
-The PSF needs to be interpolated and estimated from well-sampled images to deconvolve and measure shapes with, because the \emph{Roman} PSF has a complex structure that cannot be captured in the original undersampled images.
+The PSF needs to be interpolated and estimated from well-sampled images to accurately deconvolve and measure shapes with, because the \emph{Roman} PSF has a complex structure that cannot be captured in the original undersampled images.
 It is, therefore, necessary to build a robust strategy to reconstruct well-sampled images to estimate the PSF to allow unbiased shape measurement.
@@
 In Sec.~\ref{sec:methods}, we show how coadditions of single exposure postage stamps are produced and how shape measurements are completed using \textsc{metacalibration}.
-We present the galaxy catalog properties and calibration results for single-band and multiband measurements in Sec.~\ref{sec:results}.
+We present the galaxy catalog properties and calibration results for single-band and multi-band measurements in Sec.~\ref{sec:results}.
 Finally, in Sec.~\ref{sec:discussion}, we discuss how we will be able to constrain the shear bias better in terms of further updates in the image simulations and what we can conclude from this study.
@@
 \label{sec:background}
-In this section, we provide a brief introduction of image sampling defined through the Nyquist-Shannon Sampling Theorem, an overview of shear calibration bias within the context of weak lensing, and \textsc{metacalibration} formalism.
+In this section, we provide a brief introduction of image sampling defined through the Nyquist-Shannon Sampling Theorem, an overview of shear calibration bias within the context of weak lensing, and the \textsc{metacalibration} formalism.
 
 \subsection{Image Sampling}
-Based on the Nyquist-Shannon Sampling Theorem which states that in order to reconstruct the unbiased continuous band-limited function without a loss of information, the sufficient sample rate is twice the bandlimiting frequency per second.
+Based on the Nyquist-Shannon Sampling Theorem which states that in order to reconstruct an unbiased continuous band-limited function without a loss of information, the sufficient sample rate is twice the bandlimiting frequency per second.
 In the context of image sampling, the criterion that the sample pixel spacing needs to satisfy is $p < \frac{1}{2u_{max}}$ ($u_{max}$ is the max.
@@
 where $\lambda_{min}$ is the shortest wavelength of the incident light in each filter, $N_{f}$ is the focal ratio of the telescope ($N_{f}=7.8$ for \emph{Roman}) and $p$ is the pixel spacing of the sensor ($p=10\mu m$ for \emph{Roman}) (\citealt{2013PASP..125.1496S}).
-An image with sampling factor $Q=2$ is called a Nyquist-sampled image and an image with with sampling factor $Q<2$ is called an undersampled image.
-\textcolor{red}{An undersampled image...
-why is this an issue with weak lensing.
-What is the process of reconstructing better-sampled images.}
+An image with sampling factor $Q=2$ is considered Nyquist-sampled and an image with with sampling factor $Q<2$ is undersampled.
+
+% \textcolor{red}{Undersampled images qualitatively have less flux distribution information of objects than the Nyquist-sampled images.
+This particularly affects weak lensing experiments, because it involves measuring galaxy shapes.
+Shape measurement can bias the experiments when the galaxy images are deconvolved with undersampled PSF which does not capture the true flux spread among pixels.
+It is therefore preferred to conduct weak lensing experiments with at least Nyquist-sampled images.
+}
 
@@
 Thus, quantifying and correcting these biases before the real survey begins is extremely important.
+
+\begin{figure}
+	\includegraphics[width=\columnwidth]{metacal_bias_shear.pdf}
+    %\vspace*{-5mm}
+    \caption{We show the recovered multiplicative bias on the shear as a function of applied shear for the choice of the applied shear in our simulations.
+The presented multiplicative bias is the average of $m_{1}$ and $m_{2}$.
+At first order, the \textsc{metacalibration} algorithm only works for small input shears.
+The next order effect is seen as a quadratic dependence of the multiplicative shear bias on on the applied shear (\citealt{2017ApJ...841...24S}).
+A larger input shear increases the signal-to-noise of bias estimates, but to keep the non-linear effect small compared to requirements, we limit input shears to $\pm 0.02$.
+}
+    \label{fig:metacal_shear_linear}
+\end{figure}
 
@@
 \begin{equation}
-    \langle\vb*{e}\rangle \approx \langle \vb*{R}\vb*{\gamma} \rangle. 
+    \langle\vb*{e}\rangle \approx \langle \vb*{R}\rangle\langle\vb*{\gamma} \rangle. 
 \end{equation}
@@
 \ref{eqn:linear}.
-we compare the input shear and the calibrated shapes to calculate multiplicative ($\vb*{M}$) and additive bias ($\vb*{C}$).
+we compare the input shear and the calibrated shapes to calculate multiplicative ($\vb*{m}$) and additive bias ($\vb*{c}$).
 
@@
 \label{sec:sims}
-The base of our image simulations of the \emph{Roman} Space Telescope is the \emph{Roman} simulation suite\footnote{\url{ https://github.com/matroxel/roman_imsim}} developed by T21, which renders realistic galaxy and star images on 18 Sensor-Chip Assemblies (SCAs) of a 2.5$\times$2.5 deg$^{2}$ patch of the sky following the observing strategy for the 5-year reference mission and Cycle7 instrument specifications\footnote{\url{https://roman.gsfc.nasa.gov/science/Roman_Reference_Information.html}}.
-We begin by creating a truth catalog using the simulated galaxy distribution from the Buzzard simulation (\citealt{2019arXiv190102401D}), a photometric galaxy catalog sampled from the CANDELS survey (e.g., \citealt{2019ApJ...877..117H}), and a Milky Way simulation (Galaxia; \citealt{2011ApJ...730....3S}) for star positions and magnitudes.
+The base of our image simulations of the \emph{Roman} Space Telescope is the \emph{Roman} simulation suite\footnote{\url{ https://github.com/matroxel/roman_imsim}} developed by T21, which renders realistic galaxy and star images on 18 Sensor-Chip Assemblies (SCAs) of a 2.5$\times$2.5 deg$^{2}$ patch of the sky following the observing strategy for the 5-year reference mission and Cycle7 instrument specifications.\footnote{\url{https://roman.gsfc.nasa.gov/science/Roman_Reference_Information.html}} We begin by creating a truth catalog using the simulated galaxy distribution from the Buzzard simulation (\citealt{2019arXiv190102401D}), a photometric galaxy catalog sampled from the CANDELS survey (e.g., \citealt{2019ApJ...877..117H}), and a Milky Way simulation (Galaxia; \citealt{2011ApJ...730....3S}) for star positions and magnitudes.
 Then, the following properties are applied to each galaxy:
@@
 After we generate the object stamps across all the SCAs and pointings, we create Multi-Epoch Data Structure (MEDS) files in which each unique object dictionary contains information of all the exposures it appears in.
-These MEDS files are generated according to the Hierarchical Equal Area isoLatitude Pixelisation (HEALPix) of $n_{side}=512$.
+These MEDS files are partitioned according to the Hierarchical Equal Area isoLatitude Pixelisation (HEALPix) of $n_{side}=512$.
 They contain all objects that are located in that region of the sky partitioned according HEALPixel\footnote{\url{https://healpix.jpl.nasa.gov/}} (\citealt{2005ApJ...622..759G, Zonca2019}).
+
 Once the objects are sorted in MEDS files, we pass these multiple exposures with the corresponding PSFs to \texttt{ngmix}\footnote{\url{ https://github.com/esheldon/ngmix}} to fit the galaxy shapes with the Gaussian mixture fitting method (\citealt{2014MNRAS.444L..25S}).
@@
     \caption{The rotation of the Roman PSF produced by the \texttt{galsim.roman} module.
-The position angle (PA) which determines the rotation of the focal plane is $0^{\circ}$ and $30^{\circ}$ clockwise.
+The position angle (PA) which determines the rotation of the focal plane is $0^{\circ}$ (\textbf{left}) and $30^{\circ}$ (\textbf{right}) clockwise.
 These are drawn for SCA=1 and H158 bandpass at a native pixel scale.
@@
 \begin{figure*}
-	\includegraphics[width=\textwidth]{lowsnr_highsnr_galaxies.pdf}
+	\includegraphics[width=\textwidth]{lowsnr_highsnr_galaxies_v2.pdf}
 	%\vspace*{-10mm}
-    \caption{The top row shows the first observation of the single epoch images and its coadded image, and the corresponding single-epoch and coadded oversampled PSF images for a galaxy with low signal-to-noise ratio (S/N=9.69 in a single-epoch image).
-The bottom row shows the same for a galaxy with high signal-to-noise ratio (S/N=1552.97 in a single-epoch image).
+    \caption{\textbf{Top Row}: the first observation of the single-epoch images and its coadded image, and the corresponding single-epoch and coadded oversampled PSF images for a galaxy with low signal-to-noise ratio (S/N=20.16 in a single-epoch image).
+\textbf{Bottom Row}: the same as above for a galaxy with high signal-to-noise ratio (S/N=390.47 in a single-epoch image).
+H158 bandpass was used to represent images here.
 The PSFs are shown in a log-scale.
-The single epoch PSFs are almost identical, since there is no visually different feature for modeling them in different dithers and SCAs.
+The single-epoch PSFs are almost identical, since there is no visually different feature for modeling them in different dithers and SCAs.
 There are two features to note here.
@@
 \subsection{Updates to Simulation Capabilities}
-In order to accomplish the science goals, and build and test weak lensing calibration pipelines for in \emph{Roman}, we have continued to update the realism of our image simulations.
+In order to accomplish the science goals, and build and test weak lensing calibration pipelines for \emph{Roman}, we have continued to update the realism of our image simulations.
 We have implemented and made updates to the following parts of the simulation framework to be able to better test shear calibration using \textsc{metacalibration}.
@@
 
-    \item \textbf{Single-band and Multiband Coadds}: 
+    \item \textbf{Single-band and multi-band Coadds}: 
     We have used the postage stamp coadds (\texttt{psc}) algorithm\footnote{\url{https://github.com/esheldon/psc}} to create coadditions of single-epoch postage stamps of individual objects.
-Coadds are usually performed to enhance the signal-to-noise ratio (S/N) of an image and mitigate the impacts of measurement noise, while allowing for better sampling of the image if the overlapping images are dithered.
+Coadds are usually performed to enhance the signal-to-noise ratio (S/N) of an image and mitigate the impact of measurement noise, while allowing for better sampling of the image if the overlapping images are dithered.
 However, it is challenging to create a robust, continuous coadd PSF model over an entire image.
@@
 Additionally, coadding is one way to reduce the effect of the undersampling of the images since the coadd can be better sampled due to dithering.
-For these reasons, we explore utilizing a coadding scheme for the \emph{Roman} galaxies.
+For these reasons, we explore utilizing this coadding scheme for the \emph{Roman} galaxies.
+The examples of the low and high S/N galaxy and PSF images for single-epoch and coadd are shown in Figure \ref{fig:singlecoadd}.
 The detailed overview of the coadd process in \texttt{psc} is described in in Sec.
 \ref{subsec:psc}.
-\textcolor{red}{mention figure 2!}
 
@@
 
+\subsection{Simulation Runtime, Data Products, and Data Access}
+The simulations here match those produced in T21, but with different true shear values, and so information about processing and data volume prior to the processing additions described in this paper match that provided in App.
+D of T21.
+The runtime of the shape measurement in the simulations and data volume on disk of the shape catalogs (5 \textsc{metacalibration} catalogs for one of four shear sets) is summarized in Table \ref{tab:data} for each of the different simulation runs.
+The simulations are run on the Duke Compute Cluster,\footnote{\url{https://oit-rc.pages.oit.duke.edu/rcsupportdocs/dcc/}}, with solid-state disks for the simulation I/O.
+The time it takes to process one MEDS file is shown.
+The simulation is composed of a total of 480 MEDS files, for a total run time of about 2381 CPU hours for the multi-band coadd measurement.
+
+The new measurement catalogs produced in this work are available by request to the authors.
+\begin{table}
+    \centering
+    \begin{tabular}[width=\columnwidth]{l|c|c|c}
+    \hline
+    Measurement type &  CPU runtime (hours) & Catalog disk size  \\
+    \hline 
+    single-band single-epoch  & 3.7 & 3.9 GB \\
+    single-band coadd  & 2.9 & 3.8 GB \\
+    multi-band single-epoch  & 4.8 & 3.8 GB \\
+    multi-band coadd  & 5.0 & 3.8 GB \\
+    \hline
+    \end{tabular}
+    \caption{The runtime for a single CPU and disk size of the shape catalogs for different simulation runs.
+The runtime for multi-band measurements are slower due to having to copy, uncompress, and read from the three MEDS files (each 1GB compressed) for each bandpass.
+Runtime for coadd measurements also includes the postage-stamp coadding.}
+    \label{tab:data}
+\end{table}
+
 \subsection{Validations with Simple Simulations}
 \label{subsec:simplesim}
-The purpose of the simple simulations is to verify that there are no systematic biases at the fundamental levels of the simulation (e.g., no complex detector effects).
-These simple simulations play roles in ruling out the sources of systematic biases that may potentially be a problem in the use of \textsc{metacalibration} with space-based images.
+In addition to the main, realistic simulation of the \emph{Roman} reference HLIS survey, we also produce several sets of much faster, simple simulations  to verify that there are no obvious fundamental sources of systematic biases with using the \textsc{metacalibration} method on undersampled space-based images.
+These simple simulations thus play a role in ruling out the sources of systematic biases that may a priori  potentially be a problem in the use of \textsc{metacalibration} with space-based images.
 
-The fixed parameters for the simulations are listed in Table.
-\ref{tab:params}.
-With these parameters, we simulated images with varying galaxy model profile, PSF model profile, the artificial shear, and background noise level, without any complications in the images and pipelines such as detector effects and coaddition.
-We set the basic light profiles for galaxies and PSF to be Gaussian, and first attempted to verify that our input gravitational shear ($\abs{g}$=0.02) is unbiased in \textsc{metacalibration} framework and the required multiplicative bias for the \emph{Roman} is satisfied.
-Figure \ref{fig:metacal_shear_linear} shows that our choice of applied shear is within the requirement; therefore, it will not be the contributor to the bias in the full simulations.
-As in the Table \ref{tab:simple_sim}, the multiplicative bias is within the requirement.
-We believe that this test is unbiased because \texttt{ngmix} can build a faithful forward-model of undersampled Gaussian galaxy, even though the PSF image is undersampled.
+The fixed parameters for the simulations are listed in Table \ref{tab:params}.
+We fix the original pixel scale of the \emph{Roman}, bandpass, input galaxy size and stamp size.
+With these parameters, we simulated images with varying galaxy model profile, PSF model profile, artificial shear, and background noise level, without any complications in the images and pipelines such as detector effects and coaddition.
+We first chose simple light profiles for galaxies and PSF to be Gaussian, and verified that our input gravitational shear ($\abs{g}$=0.02) is unbiased in the \textsc{metacalibration} framework and achieves the required multiplicative bias for \emph{Roman}.
+Figure \ref{fig:metacal_shear_linear} shows that our choice of applied shear is below the shear requirement; therefore, it will not be the contributor to the bias in the other simulation variants or the full simulation.
+The values of inferred bias are shown in Table \ref{tab:simple_sim_result}.
+We believe that this test is unbiased because \texttt{ngmix} can build a faithful forward-model of an undersampled Gaussian galaxy, even though the PSF image is undersampled.
 
 Next, we tested the shape measurement pipeline by doubling the background noise.
-This test should validate that \textsc{metacalibration} process can tolerate the Poisson noise in the objects since it is not corrected in the process unlike the background noise (\citealt{2017ApJ...841...24S}).
-From the second variant in the Table \ref{tab:simple_sim}, while this might be a problem to satisfy the mission requirement, we can confirm that the treatment of correlated noise for low S/N objects does not trigger any bias at the level we are concerned.
+This test should validate that the \textsc{metacalibration} process can tolerate the induced correlation of Poisson noise in the object profiles during the \textsc{metacalibration} shearing process, since it is not currently symmetrized in the process as the background noise field is (\citealt{2017ApJ...841...24S}).
+We find that this result is also consistent with zero, so we can confirm that the treatment of correlated object Poisson noise does not trigger any bias at the level we can probe with the current simulations.
 
-As in the final row in Table \ref{tab:simple_sim} we finally validated that the use of the \emph{Roman} PSF instead of Gaussian PSF does not bias the shape recovery even though it is undersampled and the PSF has particular features of the telescope.
-Upon validating there does not exist any bias at the fundamental level, we began constructing coadd and more complex measurement pipeline.
+In the final row in Table \ref{tab:simple_sim_result}, we finally validate that the use of the complex \emph{Roman} PSF instead of a Gaussian PSF does not bias the shape recovery even though it is undersampled.
+Since none of these obvious potential issues using simple Gaussian galaxy profiles will cause bias at the level we can probe in the more complex simulation, we can more easily interpret results of the more complicated simulation and analysis pipelines described in the following sections.
+
 \begin{table}
@@
     Pixel scale & 0.11 arcsec/pixel\\
-    Dither, SCA & 22535, 1 \\ 
     Bandpass & H158 \\
     Half-light radius & 1.0 arcsec\\
-    Magnitude & randomly chosen from \emph{CANDELS} \\ 
     Stamp size & 32 pixels each side\\
@@
     \end{tabular}
-    \caption{List of the parameter choices for the simple simulations.}
+    \caption{List of the parameter choices for the simple simulations.
+For all the simple simulation runs, we used the Gaussian galaxy profile and the magnitude for each object is drawn randomly from the \emph{CANDELS} catalog.
+}
     \label{tab:params}
@@
 	\centering
-	\label{tab:simple_sim}
 	\begin{tabular}[width=\textwidth]{ c|c|c|c|c|c|c|c|c|c } 
@@
 		\hline
-		Basic-0.02 & Gaussian & Gaussian & 0.02 & roman.getSkyLevel & 0.01$\pm$0.10 & -0.02$\pm$0.10 & -0.02$\pm$0.14 & 1.06$\pm$0.14\\
-		Basic-0.05 & Gaussian & Gaussian & 0.05 & roman.getSkyLevel & 0.23$\pm$0.07 & 0.22$\pm$0.07 & 0.05$\pm$0.33 & 1.08$\pm$0.33\\
-		Basic-0.1 & Gaussian & Gaussian & 0.1 & roman.getSkyLevel & 0.99$\pm$0.03 & 0.99$\pm$0.03 & 0.13$\pm$0.33 & 0.88$\pm$0.33\\
+		Basic-0.02 & Gaussian & Gaussian & 0.02 & 5714.36 e-/arcsec$^2$ & 0.01$\pm$0.10 & -0.02$\pm$0.10 & -0.02$\pm$0.14 & 1.06$\pm$0.14\\
+		Basic-0.05 & Gaussian & Gaussian & 0.05 & 5714.36 e-/arcsec$^2$ & 0.23$\pm$0.07 & 0.22$\pm$0.07 & 0.05$\pm$0.33 & 1.08$\pm$0.33\\
+		Basic-0.1 & Gaussian & Gaussian & 0.1 & 5714.36 e-/arcsec$^2$ & 0.99$\pm$0.03 & 0.99$\pm$0.03 & 0.13$\pm$0.33 & 0.88$\pm$0.33\\
 		\hline
-		Doublesky-0.02 & Gaussian & Gaussian & 0.02 & 2 $\times$ roman.getSkyLevel & -0.12$\pm$0.18 & 0.01$\pm$0.18 & 0.06$\pm$0.36 & 1.04$\pm$0.36\\
+		Doublesky-0.02 & Gaussian & Gaussian & 0.02 & 11428.72 e-/arcsec$^2$ & -0.12$\pm$0.18 & 0.01$\pm$0.18 & 0.06$\pm$0.36 & 1.04$\pm$0.36\\
 		\hline
-		RomanPSF-0.02 (non-rotated) & Gaussian & Roman & 0.02 & roman.getSkyLevel & 0.13$\pm$0.10 & 0.18$\pm$0.10 & -0.02$\pm$0.19 & 5.33$\pm$0.19\\
+		RomanPSF-0.02 (non-rotated) & Gaussian & Roman & 0.02 & 5714.36 e-/arcsec$^2$ & 0.13$\pm$0.10 & 0.18$\pm$0.10 & -0.02$\pm$0.19 & 5.33$\pm$0.19\\
 		\hline
 	\end{tabular}
-	\caption{This table compares the shear calibration bias, both multiplicative and additive bias for different simulation runs.}
-	\label{tab:result}
+	\caption{This table compares the shear calibration bias, both multiplicative and additive bias for different simulation runs.
+In each simulation except the first row, 5 million objects were simulated.
+We simulated 15 million objects for the first row to obtain enough uncertainties.}
+	\label{tab:simple_sim_result}
 \end{table*}
-
-\begin{figure}
-	\includegraphics[width=\columnwidth]{metacal_bias_shear.png}
-    %\vspace*{-5mm}
-    \caption{We show the recovered multiplicative bias on the shear as a function of applied shear for the choice of the applied shear in our simulations.
-At first order, the \textsc{metacalibration} algorithm only works for small input shears.
-The next order effect is seen as a quadratic dependence of the multiplicative shear bias on on the applied shear (\citealt{2017ApJ...841...24S}).
-A larger input shear increases the signal-to-noise of bias estimates, but to keep the non-linear effect small compared to requirements, we limit input shears to $\pm 0.02$.
-}
-    \label{fig:metacal_shear_linear}
-\end{figure}
 
@@
 \label{sec:methods}
-Our goal is to test whether the recovered shapes with \textsc{metacalibration} are non-biased for \emph{Roman} and to understand the factors that might contribute to the non-negligible bias.
+Our goal is to test whether the recovered shear with \textsc{metacalibration} are non-biased for \emph{Roman} and to understand the factors that might contribute to the non-negligible bias.
 In order to do so, we need to build measurement pipelines within the current simulation framework that produces a final calibrated shear measurement.
@@
 Coaddition is the process of summing information from multiple overlapping images.
-If the single-epoch images are dithered, a Nyquist-sampled image can be constructed out of multiple exposures of an object.
+If the single-epoch images are dithered, a Nyquist-sampled image can be constructed out of multiple undersampled exposures of an object.
 While this process can also be beneficial in increasing the S/N value of an object and reducing the impact of pixel noise, several challenges need to be addressed for images taken with telescopes that can rotate.
 When rotation is introduced, this coadding process becomes more complex to interpolate the image to stack a pixel grid.
-While coaddition can introduce new challenges and potential biases due to the complexity of coadding the original PSF and its interpolation scheme, the bias due to the undersampling of the original images can be mitigated by appropriately coadding dithered images.
+While coaddition can introduce new challenges and potential biases due to the complexity of coadding the original PSF and its interpolation scheme, potential bias due to the undersampling of the original images can be mitigated by appropriately coadding dithered images.
 
 Among imaging surveys, coadding a small region of the sky is common, for example \textsc{swarp} (Bertin et al.
-2002) or \textsc{drizzle} (\citealt{2002PASP..114..144F}), because the Nyquist-sampled coadded images can be fully utilized to detect objects and model the PSF.
-However, we decided to coadd the postage-stamp cutouts since we know the true centers of the simulated galaxies and we have the true simulated PSF.
-It is also beneficial to use this method because we need coadds which can directly be injected into the shape measurement due to the number of cutouts.
+2002) or \textsc{drizzle} (\citealt{2002PASP..114..144F}).
+However, we decided to coadd the postage-stamp cutouts simplify the treatment of the coadd PSF.
+It is also beneficial to use this method because we need coadds which can be directly injected into the shape measurement pipeline in memory rather than written as images to disk due to the number of cutouts we have to process.
 We specifically use \texttt{psc} (postage stamp coadds) as our coadding process.
@@
 We reconstruct a better-sampled coadd image from multiple exposures in MEDS files.
-\textcolor{red}{For the coaddition of the PSF, we choose to coadd the image with an oversampled PSF `model'.
-We oversample the original PSF by a factor of 4 to simulate the better sampled PSF model that will eventually be possible to construct during the \emph{Roman} mission.} For each exposure of the object we render the \emph{Roman} PSF with a stamp size of 32 pixels at the galaxy centroid.
+For each exposure of the object we render the \emph{Roman} PSF with a stamp size of 32 pixels at the galaxy centroid.
 We modified the original \texttt{psc} code to improve performance for this \emph{Roman} study, and these modifications are explained below with the general coadding process in \texttt{psc}.
@@
 This final pixel scale was chosen to prevent the presence of visual artifacts in the structure of the coadd PSF image.
-    \item Creates an interpolated image with \texttt{GalSim} with the object centroid appropriately offset for each image using a \texttt{lanczos3} interpolantion method and sums them.
-Out of several interpolation methods we tried, \texttt{lanczos3} produced the best coadd of the PSF.
+    \item Creates an interpolated image with \texttt{GalSim}  using a \texttt{lanczos3} interpolant and sums them. 
     \item Creates a coadded noise image from the weight of the original images. 
@@
 Figure \ref{fig:singlecoadd} shows an example of the simulated single-epoch and coadded images and PSFs for objects with low and high S/N.
-Note that the shape and struts pattern in the original PSF can be washed out by coadding the rotationally dithered PSFs.
+Note that the shape and struts pattern in the original PSF can be isotropized by coadding the rotationally dithered PSFs.
 
-\textcolor{red}{Before we measure and calibrate shapes with \texttt{ngmix}, we downsample the high-resolution PSF to the original pixel size.
-Figure \ref{fig:coadd_oversample_res} shows the coadded oversampled PSF and the then-downsampled PSF, and their differences.
-Having a matching pixel scale in the galaxy and PSF image is a requirement for the current \texttt{ngmix} pipeline.
-Future versions of these measurements should include the ability to provide a better-sampled PSF image for deconvolution in the measurement.
 Figure \ref{fig:single_to_coadd_rgb} shows the coadd products in different bandpasses for a relatively high S/N object.
-The multiband PSF image is the oversampled version for better visualization.}
 
@@
 \begin{figure*}
-	\includegraphics[width=\textwidth]{coadd_galaxy_example_log.pdf}
+	\includegraphics[width=\textwidth]{coadd_galaxy_example_log_v2.pdf}
     %\vspace*{-20mm}
@@
 The S/N for each filter is S/N=90, 68, 108, respectively.
-The 4th and 5th panels show the multiband coadd images of the same object; each with linear scale and RGB scale.
+The 4th and 5th panels show the multi-band coadd images of the same object; each with linear scale and RGB scale.
 The S/N of the coadd image is S/N=110.
-Finally, \textcolor{red}{the right-most panel shows the coadded oversampled PSF in a log scale.}}
+Finally, the right-most panel shows the coadded multi-band PSF in a log scale.}
     \label{fig:single_to_coadd_rgb}
 \end{figure*}
-
-\par
 
@@
 The bootstrapper method used in \texttt{ngmix} wraps the \textsc{metacalibration} and the shape fit processes.
-The priors needed for the fit are listed in Table \ref{tab:priors}.
-We note that we have run \textsc{metacalibration} with the \texttt{fitgauss} and \texttt{gauss} PSF model to reconvolve the sheared galaxy images, and the measurement with \texttt{fitgauss} model was numerically unstable resulting in the inconsistency between $m_{1}$ and $m_{2}$.
+The priors used for the fit are listed in Table \ref{tab:priors}.
+
+The deconvolution process in  \textsc{metacalibration} was performed using the coadded PSF that is still undersampled.
+Since having a matching pixel scale in the galaxy and PSF image is a requirement for the version of the \texttt{ngmix} pipeline we implemented, we were not able to oversample the simulated \emph{Roman} PSF to utilize a more accurate PSF model.
+Future versions of these measurements should include the ability to provide a better-sampled PSF image for the deconvolution in the measurement.
+We also note that for the reconvolution process in \textsc{metacalibration} we have attempted the measurement with the \texttt{fitgauss} and \texttt{gauss} PSF model to reconvolve the sheared galaxy images, and the measurement with \texttt{fitgauss} model was numerically unstable resulting in the inconsistency between $m_{1}$ and $m_{2}$.
 We, therefore, use the \texttt{gauss} model for the rest of the simulations.
@@
     Pixel centroid offset & 0 < $p_{x,y}$ < 0.11\\
-    Shear & $|g|=1.0$, $\sigma_{|g|} = 0.3$\\
+    Shear & $\sigma_{|g|} = 0.3$\\
     Half-light radius & $10^{-5}$ < T < $10^{4}$\\
@@
 The covariances are computed using the bootstrap estimate of standard error.
-From the observed ellipticity catalogs, we randomly choose $n$ samples with replacement which is the length of the data set, and compute the distributions of multiplicative ($f^{M}_{i}$) and additive ($f^{C}_{i}$) bias for $i=1,2,3,...,N$ in the same way as above.
+From the observed ellipticity catalogs, we randomly choose $n$ samples with replacement which is the length of the data set, and compute the distributions of multiplicative ($f^{m}_{i}$) and additive ($f^{c}_{i}$) bias for $i=1,2,3,...,N$ in the same way as above.
 The distributions are then used to compute the error estimate,
@@
 \end{equation}
-where we use sample $N$=200.  \textcolor{red}{is it the same if you do jackknife?}
+where we use sample $N$=200.
 
@@
 In this section, we present the properties of the simulated data products and the shape measurement results from various simulation variants.
-We divide our shape measurement into two categories; single-band and multiband.
+We divide our shape measurement into two categories; single-band and multi-band.
 For single-band measurements, in each filter, we measured the shapes from the original single exposures by jointly fitting them.
-We set our base case to be this single-band joint-fit measurement.
-As the more developed case, we measured shapes with the single-band coadd in each filter.
-For the single-epoch multiband measurement, we matched the objects between each filter and measured the shapes with the joint-fit of single exposures across all the filters.
-The coadd multiband measurement was jointly fit across the three coadds from each filter to recover the shapes.
+We also measured shapes with the single-band coadd in each filter.
+For the single-epoch multi-band measurement, we matched the objects between each filter and measured the shapes with the joint-fit of single exposures across all the filters.
+The coadd multi-band measurement was jointly fit across the three coadds from each filter to recover the shapes.
 
 \subsection{Statistics of the Shape Catalog}
-From the CANDELS catalog, based on the \emph{Roman} Weak Lensing mission requirements, objects were pre-selected and simulated.
+Galaxies that are simulated are pre-selected to meet the \emph{Roman} Weak Lensing selection used for the mission requirements.
 In total, the galaxy photometry catalog contains 907,170 galaxies and from this catalog we simulated galaxies on 18 SCAs across 198 pointings for F184, 227 pointings for H158, and 238 pointings for J129 bandpass.
-We did not make any selection cuts on the simulated catalogs based on measured properties, since all input objects should pass requirements for weak lensing selection.
+We did not make any selection cuts on the simulated catalogs based on measured properties, since all input objects are selected to pass requirements for weak lensing selection.
 In our samples, no de-blending was necessary since the shape measurement was performed on object stamps without neighboring objects.
@@
 
-In the end, we were able to recover about 95\% of all the simulated objects in each filter, excluding objects that are at the SCA edges or the Gaussian mixture in \texttt{ngmix} failed to fit.
+In the end, we were able to recover about 95\% of all the simulated objects in each filter, excluding objects that are at the SCA edges, are too large (require a stamp size of greater than 256 pixels), or for which the Gaussian mixture in \texttt{ngmix} fit failed to converge.
 The total number of the recovered objects for single-band measurements was, 861,407 for F184, 863,146 for H158, and 859,193 for J129.
-For the multiband (H158+J129+F184) coadd measurements, we used objects that are measured successfully in all of the filters and the total number of the recovered objects is 851,821.
-Figures \ref{fig:true_properties}, \ref{fig:ngmix_measured_properties} and \ref{fig:hsm_measured_properties} show the true properties from the truth catalog and measured properties from the \textsc{metacalibration} shape catalogs.
+For the multi-band (H158+J129+F184) coadd measurements, we used objects that are measured successfully in all of the filters and the total number of the recovered objects is 851,821.
+Figures \ref{fig:ngmix_measured_properties} shows the true magnitude and size and the measured signal-to-noise and size of galaxies in the \textsc{metacalibration} shape catalogs.
+There is a significant boost in signal-to-noise in the multi-band catalog vs the single-band catalogs.
+While the measured size ($T$) does not agree well with the input size derived from the half-light radius, this is a known issue due to fitting a Gaussian model to a galaxy with size defined as part of a much more complex profile.
 
-\begin{figure}
-	\includegraphics[width=\columnwidth]{true_properties.pdf}
-	\centering
-    \caption{The left panel shows the measured magnitudes of galaxies for all the 3 filter we have used to measure shapes.
+% \begin{figure}
+% 	\includegraphics[width=\columnwidth]{true_properties.pdf}
+% 	\centering
+%     \caption{The left panel shows the measured magnitudes of galaxies for all the 3 filter we have used to measure shapes.
 The mean magnitude for H158, F184, and J129 are respectively 23.098, 22.976, and 23.273.
@@
 ngmix output is arcsec2}}
-    \label{fig:true_properties}
-\end{figure}
+%     \label{fig:true_properties}
+% \end{figure}
 
@@
 	\includegraphics[width=\textwidth]{true_ngmix_measured_properties.pdf}
-    \caption{The histograms of measured galaxy properties in \texttt{ngmix} for single-band coadd and multiband coadd measurements.
-It includes magnitude, S/N, galaxy size $T{gal}$.
-The S/N is significantly improved in the multiband fit.}
+    \caption{This shows the histograms of input and measured galaxy properties in \texttt{ngmix} for single-band coadd and multi-band coadd measurements.
+\textbf{Left}: the input magnitudes of galaxies for all the 3 filters we have used to measure shapes.
+The mean magnitude for J129 H158, F184 are respectively 23.273, 23.098, 22.976.
+\textbf{Middle}: the signal-to-noise ratio of the single-band and multi-band coadds.
+The mean S/N for JHF and multi-band are respectively 117.45, 161.64, 116.57, 205.39.
+\textbf{Right}: the input galaxy size for H158 where we approximated from the half-light radius, and the measured galaxy size for the single-band and the multi-band coadd in units of arcsec$^2$.
+The mean size for input and measured galaxies are 0.149 and 0.087 arcsec$^2$ for H158.
+It is important to note that there exists the discrepancy between the input and measured size.
+The measured size is the size of the best fit Gaussian (maximum likelihood in this case) and it is not expected to match with the true size based on the half-light radius of the nominal profiles.}
     \label{fig:ngmix_measured_properties}
@@
 
-\begin{figure*}
-    %\hspace*{-3.1cm}
-    \centering
-	\includegraphics[width=\textwidth]{hsm_PSF_properties.pdf}
-    \caption{The histograms of measured PSF properties in adaptive moments method for single-band coadd and multiband coadd measurements.
+% \begin{figure*}
+%     %\hspace*{-3.1cm}
+%     \centering
+% 	\includegraphics[width=\textwidth]{hsm_PSF_properties.pdf}
+%     \caption{The histograms of measured PSF properties in adaptive moments method for single-band coadd and multi-band coadd measurements.
 The shape and size of the PSF are shown.
 \textcolor{red}{We may not to present this plot, as it is hard to explain the trends.}}
-    \label{fig:hsm_measured_properties}
-\end{figure*}
+%     \label{fig:hsm_measured_properties}
+% \end{figure*}
 
@@
 The multiplicative and additive bias values listed in the text are the average of $m_{1}$ and $m_{2}$, and $c_{1}$ and $c_{2}$.
-\textcolor{red}{These are usually symmetric, except in the case of the coadd measurements, where $c_1>c_2$.} The comprehensive results can be found in Table \ref{tab:bias_summary} and the single-band coadd result compared to the previously measured values in Fig.
-\ref{fig:final_result}.
+The comprehensive results can be found in Table \ref{tab:bias_summary} and Fig.
+\ref{fig:final_result} shows the single-band coadd result compared to the previously non-calibrated bias estimates in T21.
 These multiple simulation variants were run to achieve three milestones.
 One is to characterize how much the shear bias exists if we were to use the original, undersampled images, by recovering shears from the single exposures in each bandpass.
-Second step is to verify if coadding/better-sampling by 0.8 pixels can mitigate the effect of undersampling.
-Lastly, as the final assessment we investigate if combining the three bandpasses would result in constraining the recovered shapes.
+Second is to verify if coadding can mitigate the effect of undersampling.
+Lastly, as the final assessment we investigate how combining the three bandpasses can result in better constraining the recovered shear.
 
 For the single-band measurements, we can use the sampling factor defined in Equation \ref{eqn:sampling} per bandpass to show the relationship between the shear bias and image sampling.
-The sampling factor is an indication of how undersampled the image in some bandpass is.
+The sampling factor is an indication of how undersampled the image is in each bandpass.
 The sampling factor for each single-band measurement can be found in Table \ref{tab:bias_summary}.
@@
 Their result can be extrapolated to our single-band single-epoch results.
-The multiplicative bias of single-band single-epoch measurements is consistent with zero within 2$\sigma$ in each filter ($\sigma$=0.72\%), except for $m_{2}=(-1.61\pm0.66)\%$ in H158.
-This level of bias is consistent with the finding from K21, which explored the effect of undersampled images in \emph{Euclid} image simulations.
+The multiplicative bias of single-band single-epoch measurements is consistent with zero within 2$\sigma$ in each filter, with mean uncertainty $\sigma_m$=0.72\%, except for $m_{2}=(-1.61\pm0.66)\%$ in H158, which is slightly larger.
+This level of bias is consistent with the finding from K21.
 
-When the coadded images for each filter are used, the bias is at the similar level or worse within the uncertainties.
-\textcolor{red}{We can conclude that in the current \emph{Roman} simulation the multiplicative bias has a similar dependence on the sampling factor as shown in K21, but with a smaller amplitude.} We do not see any clear improvements in the recovered shear when we coadd the single-epoch images, despite having a smaller pixel scale (better sampling) in the images.
-This is most likely due to an issue with how we are currently treating the PSF or correlated noise in the coadding process, given the large observed $c_1$ when coadding discussed below.
-\textcolor{red}{Although we have verified that the handling of correlated noise in \textsc{metacalibration} proess for single-epoch images is unbiased, it is possible that the \texttt{psc} process induces more correlated noise that is not corrected further.
-}
+When the coadded images for each filter are used, the recovered multiplicative shear bias is about half the single-epoch cases due to the increased S/N and better image sampling, and is consistent with zero at the $\sim$1$\sigma$ level.
+The additive bias remains at a similar level within uncertainties.
+The estimated additive bias is the same order as that found in the Y3 analysis in DES, which uses a similar shear calibration pipeline.
 
-The additive bias of the single-band single-epochs measurements for each filter is smaller about an order of magnitude than that of the coadd measurements.
-The estimated additive bias is the same order as that found in the Y3 analysis in DES, which uses a similar shear calibration pipeline.
-In Table \ref{tab:result}, it is worth noting that the coadd process clearly introduces non-trivial additive biases in one direction of the shear, but not the other.
-This is due to the effect of an imperfect coadd PSF model.
-We find this correlation in the Figure \ref{fig:meanshear} where the recovered shear on the coadd images has a strong linear dependence on the PSF ellipticity measured by an adaptive moments method (\citealt{2003MNRAS.343..459H}).
-The impact of the PSF shape and size leakage in the estimated galaxy shapes at the correlation function level can be estimated by computing $\rho$-statistics (\citealt{2008A&A...484...67P, 2010MNRAS.404..350R, 2016MNRAS.460.2245J}).
-However, we do not explore the $\rho$-statistics for our PSF model since there is no realistic shear field in this version of the simulations.
-We can explore these effects further in the next generation of simulations that are being worked on in parallel, which are commented on in Sec.
-\ref{sec:discussion}.
-We are also developing a more sophisticated coadd treatment that will be applied to future simulation versions and may alleviate these issues.
+Finally, we discuss the results with multi-band measurements.
+We performed multi-band measurements with the three filters used in the previous measurements.
+One multi-band measurement used all of the single epoch images from all the filters and jointly fit the shape of the galaxy.
+The multiplicative and additive bias is, respectively, $m=(-1.34\pm0.67)$\% and $c=(2.58\pm1.26)10^{-4}$.
+This result generally agrees with the single-band single-epochs measurements, and is consistent with zero bias at the $\sim$2$\sigma$ level.
+The other measurement is performed as a joint-fit across the coadd images for each filter.
+The multiplicative and additive bias is, respectively, $m=(-1.13\pm0.60)\%$ and $c=(2.38\pm1.24)10^{-4}$.
+These results are again consistent with zero at the 2$\sigma$ level, so we can't conclude more than that this result may be acceptable, without significantly larger simulation volume.
+To reach the requirements level for the \emph{Roman} HLIS, we will likely need approx.
+2000 deg$^{2}$ of simulated imaging for this complex simulation mode.
 
-Finally, we discuss the results with multiband measurements.
-We performed multiband measurements with the three filters used in the previous measurements.
-One multiband measurement used all of the single epoch images from all the filters and jointly fit the shape of the galaxy.
-The multiplicative and additive bias is, respectively, $m=(-1.34\pm0.67)$ per cent and $c=(2.58\pm1.26)10^{-4}$.
-This result generally agrees with the single-band single-epochs measurements, and is consistent with zero bias at the approx.
-2$\sigma$ level.
-We can't conclude more than that this result may be acceptable without significantly larger simulation volume of about 2000 $deg^{2}$.
-The other measurement is performed as a joint-fit across the coadd images for each filter.
-The multiplicative and additive bias is, respectively, $m=(-2.33\pm0.64)$ per cent and $c=(9.47\pm1.16)10^{-4}$.
-Figure \ref{fig:meanshear} shows the relationship between the mean shear and several input and measured properties of galaxies and PSF for all the measurement cases.
-We find that the mean shear has a linear trend as a function of input galaxy size, though the effect is one order of magnitude smaller than the mean signal.
+To further explore the shape catalogs, we performed a set of basic null tests and show representative results for $e_1$ for the the H158 single-epoch and coadd catalogs, and multi-band coadd catalog.
+The null tests should show that the mean shear residual ($\langle \Delta e_{1} \rangle$) should be zero (flat) in the absence of any systematic biases.
+Figure \ref{fig:meanshear} shows the relationship between the mean shear and several input and measured properties of galaxies for all the measurement cases.
+We find no significant trends in mean shear vs.
+signal-to-noise or vs PSF properties, which are not included in the figure.
+The mean shear does show a non-linear trend correlating with measured galaxy size.
+To investigate this, we show in Fig.
+\ref{fig:sizecorrelation} how the true and measured shape and size are related.
+Since there is no trend in either true or measured shape and size vs.
+measured or true values, respectively, the trend in the observed shape vs observed size must be a more subtle effect correlating the measured size and shape.
+Since there is no trend vs.
+true properties, we will check if this signal persists in future simulation and pipeline updates.
 
@@
 	\centering
-	\label{tab:bias_summary}
 	\begin{tabular}[width=\textwidth]{ c|c|c|c|c|c } 
@@
 		\hline
-		single-band coadd (J129) & 1.10 & -1.84$\pm$0.71 & -1.90$\pm$0.65 & 11.99$\pm$1.39 & 0.59$\pm$1.41\\
-		\textcolor{red}{single-band coadd (H158) with oversampled PSF & 1.35 & -1.75$\pm$0.67 & -1.68$\pm$0.64 & 14.39$\pm$1.32 & 4.29$\pm$1.35}\\
+		single-band coadd (J129) & 1.10 & -0.59$\pm$0.68 & -0.94$\pm$0.64 & 4.91$\pm$1.46 & 1.78$\pm$1.17\\
 		single-band coadd (H158) & 1.35 & -0.69$\pm$0.63 & -0.83$\pm$0.61 & 2.16$\pm$1.31 & 0.77$\pm$1.19\\
-		single-band coadd (F184) & 1.64 & -0.28$\pm$0.83 & -0.27$\pm$0.78 & 12.15$\pm$1.56 & 5.66$\pm$1.56\\
+		single-band coadd (F184) & 1.64 & 0.37$\pm$0.83 & 0.10$\pm$0.75 & 2.22$\pm$1.46 & 0.08$\pm$1.58\\
 		\hline
-		multiband single-epochs & N/A & -1.07$\pm$0.66 & -1.61$\pm$0.67 & 2.83$\pm$1.30 & 2.33$\pm$1.22 \\
-		multiband coadd & N/A & -2.32$\pm$0.64 & -2.34$\pm$0.63 & 14.45$\pm$1.10 & 4.49$\pm$1.22\\
+		multi-band single-epochs & N/A & -1.07$\pm$0.66 & -1.61$\pm$0.67 & 2.83$\pm$1.30 & 2.33$\pm$1.22 \\
+		multi-band coadd & N/A & -1.02$\pm$0.62 & -1.24$\pm$0.57 & 2.37$\pm$1.26 & 2.38$\pm$1.22\\
 
@@
 	\caption{This table compares the shear calibration bias, both multiplicative and additive bias for different simulation runs.}
-	\label{tab:result}
+	\label{tab:bias_summary}
 \end{table*}
@@
 \begin{figure*}
-	\includegraphics[width=\textwidth]{final_result_v2.pdf}
-    \caption{The multiplicative ($m$) and additive ($c$) bias of the single-band coadd measurements.
-From left data point to the right, they represent each data for J129, H158, F184 bandpasses.
-T21 refers the non-calibrated result from the first-generation of the simulations by \cite{2021MNRAS.501.2044T}.
-}
+	\includegraphics[width=\textwidth]{final_result_v4.pdf}
+    \caption{The multiplicative ($m \times 10^2$) (\textbf{left}) and additive ($c \times 10^4$) (\textbf{right}) bias of the single-band single-epoch and coadd measurements.
+From the left and to the right data points, they represent J129 single-epoch, H158 single-epoch, J129 coadd, F184 single-epoch, H158 coadd and F184 coadd measurements.
+The non-calibrated results from the first-generation of the simulations by \cite{2021MNRAS.501.2044T} were $m_1=(-7.56\pm0.19)\times10^{-2}$, $m=(-9.49\pm0.19)\times10^{-2}$ and $c_1=(1.20\pm0.17)\times10^{-3}$, $c_2=(-1.57\pm0.16)\times10^{-3}$.
+We can conclude that our calibration bias is an order of magnitude smaller than the previous versions of the simulations, and comparable or smaller than the bias-level seen in the Stage-III surveys.}
     \label{fig:final_result}
@@
     \centering
-	\includegraphics[width=\textwidth]{H158_meanshear_measured_properties_perbin_e1_v2.pdf}
-    \caption{(Working on fixing the figure bounds)This shows the mean shear residual ($\Delta e_{1}$; $\langle e_{1,measured} \rangle - \langle e_{1,expected} \rangle$) as a function of various properties of galaxies for H158 single-band single-epochs, coadds, and multiband measurements.
-In this plot, the shear response is computed in each bin.
-The properties include the S/N, measured galaxy size $T_{gal,measured}$, input galaxy size $T_{gal,input}$, the shape and size of the input PSF.}
+	\includegraphics[width=\textwidth]{H158_meanshear_measured_properties_perbin_e1_v4.pdf}
+    \caption{This shows the mean shear residual ($\Delta e_{1}$; $\langle e_{1,measured} \rangle - \langle e_{1,expected} \rangle$) as a function of various properties of galaxies for H158 single-band single-epochs, coadds, and multi-band measurements.
+We are only showing the $e_1$ residual because $e_{2}$ showed similar behaviors in each test.
+\textbf{Left}: the measured S/N shows a null signal.
+\textbf{Middle}: the true galaxy size shows a null signal.
+\textbf{Right}: the measured galaxy size shows a non-null signal, where this is mainly caused by the correlation between the true shapes of galaxies and the measured size in \textsc{ngmix}.
+This is explained in more detail in Fig.
+\ref{fig:sizecorrelation}.
+In this plot, the shear response is computed in each bin to account for the selection bias.}
     \label{fig:meanshear}
 \end{figure*}
+
+\begin{figure}
+    %\hspace*{-3.5cm}
+    \centering
+	\includegraphics[width=\columnwidth]{H158_true_obs_e1_size.pdf}
+    \caption{This shows the correlations between true and measured shape and size of galaxies.
+\textbf{Left}: the true galaxy shape ($e_1$) in the bins of measured galaxy size (arcsec$^2$).
+\textbf{Right}: the measured galaxy shape ($e_1$) in the bins of input galaxy size (arcsec).}
+    \label{fig:sizecorrelation}
+\end{figure}
 
@@
 
-We have investigated how \textsc{metacalibration} handles the relatively undersampled \emph{Roman} images without accounting for the effect of blending.
+We have investigated how \textsc{metacalibration} handles the complex \emph{Roman} PSF and undersampled images without accounting for the effect of blending.
 However, it has been found that galaxy blending at different redshifts could introduce a significant shear-dependent detection bias when calibrated with \textsc{metacalibration} (e.g., \citealt{2020ApJ...902..138S}, \citealt{2020arXiv201208567M}).
 In future studies, we will investigate the impact of blending in Roman image simulations and implement an extended pipeline to correct shear-dependent blending/detection biases (e.g.,  \textsc{metadetection}) to explore more realistic shear calibration for the real survey.
-
-We have also found our postage-stamp coadd pipeline may be contributing to bias in the shear measurement, even while mitigating the effect of undersampling in the images.
-This may be related to either how the undersampled PSF is treated or correlated noise effects from the simulated detector physics in the simulation.
-Running \textsc{metacalirbation} on simpler simulations without complex PSF shapes or detector effects showed no indication of residual bias at the level we see in the coadd shear calibration estimate.
-Correcting these algorithmic issues is beyond the scope of the current work, and will require a new set of improved simulations and coadd/measurement pipelines.
-It may also require modifications to the \textsc{metacalibration} or \textsc{metadetection} algorithms, which were constructed primarily for ground-based data, so the current calibration results serve as an important benchmark for the performance of current Stage III methods on \emph{Roman} data.
 
@@
     \setlength\itemsep{1em}
-    \item \textbf{Simulation Volume}: Expand the simulated area to 20 $deg^{2}$. (Troxel et al. in prep.), in order to obtain smaller error bars on the resulting shear calibration biases.
+    \item \textbf{Simulation Volume}: Expand the simulated area by a factor of four to 20 deg$^{2}$, in order to obtain smaller error bars on the resulting shear calibration biases.
 
@@
 With \texttt{AstroDrizzle}, we are able to further mitigate the effect of undersampling in the \emph{Roman} images with smaller coadd pixel scales.
-We expect this to further reduce the measured shear bias by up to 1\% based on its trend with sampling factor.
+We expect this to further reduce the measured shear bias based on its trend with sampling factor.
 
@@
 
-    \item \textbf{Selection Cuts}: Simulate objects to below the detection threshold of the survey and incorporate standard quality assurance cuts (e.g., S/N) on the shape catalog (\citealt{2017ApJ...841...24S}).
+    \item \textbf{Selection Cuts}: Simulate objects to below the detection threshold of the survey and incorporate standard quality assurance cuts (e.g., S/N) on the shape catalog. 
 \end{itemize}
 
-\section{Conclusions}
-We explored the performance of the \textsc{metacalibration} shape measurement calibration algorithm and presented the first shear calibration result on a realistic simulated \emph{Roman} HLIS.
+\section{Conclusions}\label{sec:conclusion}
+
+In this paper, we explored the performance of the \textsc{metacalibration} shape measurement calibration algorithm and presented the first shear calibration result on a realistic simulated version of the reference \emph{Roman} HLIS.
 Accurately characterizing how much shear estimates are biased using realistic simulated survey images is a requirement to successfully complete the weak lensing program of the \emph{Roman} HLIS.
-In the current simulation framework, by coadding the single-epoch cutout images and using an oversampled PSF model, we found that shear estimates with an are still biased at the percent level using implementation of \textsc{metacalibration} that is similar to that used by ground-baesd Stage III surveys.
-To further constrain the shear calibration bias in the simulations and validate that the \emph{Roman} mission will be able to achieve the weak lensing calibration required for the survey, we need both more simulation volume -- about 400 times the area of the current simulation -- as well as significant improvements to the coadd and measurement pipelines currently used in this work.
+This early work allows us to develop such simulation resources and to benchmark current weak lensing methods to explore where effort is still needed in development for the \emph{Roman} mission.
 
-We find that our results are similar to what was previously found for \textsc{metacalibration} bias on undersampled images in the study by K21 using image simulations built for \emph{Euclid}, but at a lower level, due to differences in how we perform the shape fitting.
-Thus, our study further confirms the need for better treatment of the undersampled images for weak lensing.
-In future versions of the \emph{Romaan} simulations that are currently being developed, we will both be able to increase the simulation volume significantly and produce coadd images with a smaller pixel scale for shape measurement.
-With these and other changes to improve the realism of the simulations and measurement pipelines used with them, we will be able to better explore the possible origins of the current percent level residual shear bias and study mitigation strategies in order to reach the \emph{Roman} weak lensing mission requirement.
-\label{sec:conclusion}
+In a larger suite of simple simulations, where the galaxy and PSF profiles are Gaussian, we find that the shear calibration bias using \textsc{metacalibration} is consistent with zero at the $0.1$\% level, even though the images are undersampled.
+This finding persists even when using an accurate, complex \emph{Roman} PSF model.
+When exploring the performance of \textsc{metacalibration} in the current simulation framework where realistic complexities are incorporated, the runtime cost is significantly increased, and we can only constrain the shear calibration bias at the $0.6$\% level.
+In these simulations we include coadding the single-epoch cutout images and fitting the shapes from multiple bandpasses, and we find that shear estimates with \textsc{metacalibration} are unbiased at the $\sim 2\sigma$ level, which is similar to current-survey constraints.
+At the original image sampling level, the trend in bias vs sampling factor $Q$ are similar to what was previously found for \textsc{metacalibration} bias on undersampled images in the study by K21 using image simulations built for \emph{Euclid}, but at lower levels of bias.
+By coadding the cutout images and increasing the image sampling factor, we find that the residual bias is reduced by about a factor of two, but this is similar to the uncertainty.
+However, this is a promising result for using coadd-level shape measurement for \emph{Roman}, and we plan to further investigate the use of \textsc{metacalibration} with image coadds that can reconstruct Nyquist-sampled images in all bandpasses in future work.
+
+These results are currently limited by the available simulation volume in the realistic simulated survey.
+To further constrain the shear calibration bias and validate that the \emph{Roman} mission will be able to achieve the weak lensing calibration required for the survey, we have outlined in Sec.
+\ref{sec:discussion} a variety of simulation improvements being planned in future versions of the \emph{Roman} simulations that are currently being developed, including an exploration of the impact of blending and object detection on the calibration.
+We will also need to simulate much larger volumes of data, which is a significant challenge in terms of computing resources and storage space.
+The next version of the realistic simulation will cover about a factor of four more of the sky.
+These first results with \textsc{metacalibration} in realistic simulated \emph{Roman} HLIS imaging demonstrate that the \textsc{metacalibration} shear calibration approach is a feasible strategy for the \emph{Roman} mission and undersampled imaging more generally.
+However, significant additional work to study shear calibration in the presence of blending and at significantly larger survey volumes is essential for reaching the precise requirements for the \emph{Roman} weak lensing mission.
 
@@
 
-We thank Matthew Becker and Erin Sheldon for the useful discussions on the use of \texttt{ngmix}, and Arun Kannawadi for the consultation on his \emph{Euclid} shape measurement work.
-This work was supported by xx funding agencies.
+We thank Matthew Becker and Erin Sheldon for the useful discussions on the use of \texttt{ngmix}, and Arun Kannawadi for discussions about related \emph{Euclid} shape measurement work.
+This work was supported by NASA Grant 15-WFIRST15-0008 as part of the Roman Cosmology with the High-Latitude Survey Science Investigation Team (https: //www.roman-hls-cosmology.space/).
+This work used resources from the Duke Compute Cluster.
 
@@
 
-% 		\multirow{multiband} & multiband single-epochs (fitgauss) (H158+J129+F184) & 1.78$\pm$0.62 & 0.07$\pm$0.63 & 8.80$\pm$1.22 & 1.57$\pm$1.27 \\
-% 		& multiband single-epochs (gauss) (H158+J129+F184) & -0.66$\pm$0.58 & -0.74$\pm$0.59 & 4.32$\pm$1.17 & 1.60$\pm$1.16 \\
-% 		& multiband coadd with oversampling (fitgauss; H158+J129) & -1.02$\pm$0.63 & 0.02$\pm$0.70 & 18.51$\pm$1.36 & 0.70$\pm$1.33\\
-% 		& multiband coadd with oversampling (gauss; H158+J129) & -0.39$\pm$0.59 & -0.32$\pm$0.68 & 13.72$\pm$1.24 & 1.85$\pm$1.29\\
-% 		& (v2) multiband coadd with oversampling (fitgauss; H158+J129) & -0.73$\pm$0.45 & -0.08$\pm$0.48 & 15.80$\pm$0.88 & 0.53$\pm$0.96\\
-% 		& (v2) multiband coadd with oversampling (gauss; H158+J129) & -0.36$\pm$0.45 & -0.35$\pm$0.43 & 11.45$\pm$0.93 & 1.83$\pm$0.98\\
+% 		\multirow{multi-band} & multi-band single-epochs (fitgauss) (H158+J129+F184) & 1.78$\pm$0.62 & 0.07$\pm$0.63 & 8.80$\pm$1.22 & 1.57$\pm$1.27 \\
+% 		& multi-band single-epochs (gauss) (H158+J129+F184) & -0.66$\pm$0.58 & -0.74$\pm$0.59 & 4.32$\pm$1.17 & 1.60$\pm$1.16 \\
+% 		& multi-band coadd with oversampling (fitgauss; H158+J129) & -1.02$\pm$0.63 & 0.02$\pm$0.70 & 18.51$\pm$1.36 & 0.70$\pm$1.33\\
+% 		& multi-band coadd with oversampling (gauss; H158+J129) & -0.39$\pm$0.59 & -0.32$\pm$0.68 & 13.72$\pm$1.24 & 1.85$\pm$1.29\\
+% 		& (v2) multi-band coadd with oversampling (fitgauss; H158+J129) & -0.73$\pm$0.45 & -0.08$\pm$0.48 & 15.80$\pm$0.88 & 0.53$\pm$0.96\\
+% 		& (v2) multi-band coadd with oversampling (gauss; H158+J129) & -0.36$\pm$0.45 & -0.35$\pm$0.43 & 11.45$\pm$0.93 & 1.83$\pm$0.98\\
 

### 2022-02-24 paper_v3.tex
v3.3_SIT sent

@@
 Masaya Yamamoto,$^{1}$\thanks{E-mail: masaya.yamamoto@duke.edu}
-Michael A. Troxel,$^{1}$
+M. A. Troxel,$^{1}$
 Mike Jarvis,$^{2}$
@@
 D of T21.
-The runtime of the shape measurement in the simulations and data volume on disk of the shape catalogs (5 \textsc{metacalibration} catalogs for one of four shear sets) is summarized in Table \ref{tab:data} for each of the different simulation runs.
+The runtime of the shape measurement per MEDS region in the simulations and data volume on disk of the full shape catalogs (5 \textsc{metacalibration} catalogs for one of four shear sets) is summarized in Table \ref{tab:data} for each of the different simulation runs.
 The simulations are run on the Duke Compute Cluster,\footnote{\url{https://oit-rc.pages.oit.duke.edu/rcsupportdocs/dcc/}}, with solid-state disks for the simulation I/O.
@@
 The comprehensive results can be found in Table \ref{tab:bias_summary} and Fig.
-\ref{fig:final_result} shows the single-band coadd result compared to the previously non-calibrated bias estimates in T21.
+\ref{fig:final_result} shows the single-band single exposures and coadd results compared.
 These multiple simulation variants were run to achieve three milestones.
@@
 One multi-band measurement used all of the single epoch images from all the filters and jointly fit the shape of the galaxy.
-The multiplicative and additive bias is, respectively, $m=(-1.34\pm0.67)$\% and $c=(2.58\pm1.26)10^{-4}$.
+The multiplicative and additive bias is, respectively, $m=(-1.34\pm0.67)$\% and $c=(2.58\pm1.26)\times10^{-4}$.
 This result generally agrees with the single-band single-epochs measurements, and is consistent with zero bias at the $\sim$2$\sigma$ level.
 The other measurement is performed as a joint-fit across the coadd images for each filter.
-The multiplicative and additive bias is, respectively, $m=(-1.13\pm0.60)\%$ and $c=(2.38\pm1.24)10^{-4}$.
+The multiplicative and additive bias is, respectively, $m=(-1.13\pm0.60)\%$ and $c=(2.38\pm1.24)\times10^{-4}$.
 These results are again consistent with zero at the 2$\sigma$ level, so we can't conclude more than that this result may be acceptable, without significantly larger simulation volume.
@@
 We find no significant trends in mean shear vs.
-signal-to-noise or vs PSF properties, which are not included in the figure.
-The mean shear does show a non-linear trend correlating with measured galaxy size.
+galaxy properties or vs PSF properties, which are not included in the figure.
+% The mean shear does show a non-linear trend correlating with measured galaxy size.
 To investigate this, we show in Fig.
@@
 From the left and to the right data points, they represent J129 single-epoch, H158 single-epoch, J129 coadd, F184 single-epoch, H158 coadd and F184 coadd measurements.
-The non-calibrated results from the first-generation of the simulations by \cite{2021MNRAS.501.2044T} were $m_1=(-7.56\pm0.19)\times10^{-2}$, $m=(-9.49\pm0.19)\times10^{-2}$ and $c_1=(1.20\pm0.17)\times10^{-3}$, $c_2=(-1.57\pm0.16)\times10^{-3}$.
+The non-calibrated results from the first-generation of the simulations by \cite{2021MNRAS.501.2044T} were $m_1=(-7.56\pm0.19)\%$, $m=(-9.49\pm0.19)\%$ and $c_1=(1.20\pm0.17)\times10^{-3}$, $c_2=(-1.57\pm0.16)\times10^{-3}$.
 We can conclude that our calibration bias is an order of magnitude smaller than the previous versions of the simulations, and comparable or smaller than the bias-level seen in the Stage-III surveys.}
@@
     \centering
-	\includegraphics[width=\textwidth]{H158_meanshear_measured_properties_perbin_e1_v4.pdf}
+	\includegraphics[width=\textwidth]{H158_meanshear_measured_properties_perbin_e1_v6.pdf}
     \caption{This shows the mean shear residual ($\Delta e_{1}$; $\langle e_{1,measured} \rangle - \langle e_{1,expected} \rangle$) as a function of various properties of galaxies for H158 single-band single-epochs, coadds, and multi-band measurements.
@@
 \textbf{Middle}: the true galaxy size shows a null signal.
-\textbf{Right}: the measured galaxy size shows a non-null signal, where this is mainly caused by the correlation between the true shapes of galaxies and the measured size in \textsc{ngmix}.
-This is explained in more detail in Fig.
-\ref{fig:sizecorrelation}.
-In this plot, the shear response is computed in each bin to account for the selection bias.}
+\textbf{Right}: the measured galaxy size shows a null signal.
+The mean shear is computed with the shear response and selection response in each bin to account for the selection bias.}
     \label{fig:meanshear}
@@
 
-\begin{figure}
-    %\hspace*{-3.5cm}
-    \centering
-	\includegraphics[width=\columnwidth]{H158_true_obs_e1_size.pdf}
-    \caption{This shows the correlations between true and measured shape and size of galaxies.
+% \begin{figure}
+%     %\hspace*{-3.5cm}
+%     \centering
+% 	\includegraphics[width=\columnwidth]{H158_true_obs_e1_size.pdf}
+%     \caption{This shows the correlations between true and measured shape and size of galaxies.
 \textbf{Left}: the true galaxy shape ($e_1$) in the bins of measured galaxy size (arcsec$^2$).
 \textbf{Right}: the measured galaxy shape ($e_1$) in the bins of input galaxy size (arcsec).}
-    \label{fig:sizecorrelation}
-\end{figure}
+%     \label{fig:sizecorrelation}
+% \end{figure}
 
@@
 However, it has been found that galaxy blending at different redshifts could introduce a significant shear-dependent detection bias when calibrated with \textsc{metacalibration} (e.g., \citealt{2020ApJ...902..138S}, \citealt{2020arXiv201208567M}).
-In future studies, we will investigate the impact of blending in Roman image simulations and implement an extended pipeline to correct shear-dependent blending/detection biases (e.g.,  \textsc{metadetection}) to explore more realistic shear calibration for the real survey.
+In future studies, we will investigate the impact of blending in \emph{Roman} image simulations and implement an extended pipeline to correct shear-dependent blending/detection biases (e.g.,  \textsc{metadetection}) to explore more realistic shear calibration for the real survey.
 

### 2022-03-11 old/roman_metacal_v2.tex
rachel's comments v4.1

--- 2021-12-13 roman_metacal_v2.tex
@@
 In this work, we incorporate several new realistic processing-pipeline updates necessary to calibrate shear with a better precision relative to the previous version of the simulations and show first results for the reference HLIS using \textsc{metacalibration}.
-We find that compared with the non-calibrated results from previous work, \textsc{metacalibration} as used in current experiments can significantly reduce the shear calibration bias to the percent level.
-With the single-epoch images, across all three filters we are able to achieve a multiplicative bias $m=-1.34\%$ within 2 $\sigma$, while for coadd cutouts, $m=-2.33\%$ within about 4 $\sigma$.
+We find that \textsc{metacalibration} as used in current experiments can significantly reduce the shear calibration bias to the percent level.
+With the single-epoch images, across all three filters we are able to achieve a multiplicative bias $m=(-1.34\pm 0.67)$\%, while for coadd cutouts, $m=(-2.33\pm 0.64)$\%.
 In both single-epoch and coadd cases, we find that shape calibration becomes worse with decreasing image sampling factor.
 Overall, within the current simulation volume, there is evidence that \textsc{metacalibration} as currently implemented will not calibrate shapes with zero shear bias in the \emph{Roman} HLIS and further work on the shear calibration methodology is necessary.
-In the future, we will need to substantially increase the simulation volume by 400 (about the same size as the survey area of 2000 $deg^{2}$) to reach the precision necessary for the HLIS.
+In the future, we will need to substantially increase the simulation volume by 400 (about the same size as the survey area of 2000 deg$^{2}$) to reach the precision necessary for the HLIS.
 \end{abstract}
@@
 Thus, near-future Stage IV surveys (\citealt{2006astro.ph..9591A}) such as Euclid\footnote{\url{ http://sci.esa.int/euclid}} (\citealt{2011arXiv1110.3193L}), the Vera C.
-Rubin Observatory Legacy Survey of Space and Time\footnote{\url{ http://www.lsst.org}} (\emph{Rubin}: \citealt{2009arXiv0912.0201L, 2019ApJ...873..111I}), and \emph{Nancy Grace Roman} Space Telescope\footnote{\url{https://roman.gsfc.nasa.gov}} (\emph{Roman}: \citealt{2015arXiv150303757S}) require even better control of systematics.
+Rubin Observatory Legacy Survey of Space and Time\footnote{\url{ http://www.lsst.org}} (\emph{Rubin}: \citealt{2009arXiv0912.0201L, 2019ApJ...873..111I}), and the \emph{Nancy Grace Roman} Space Telescope\footnote{\url{https://roman.gsfc.nasa.gov}} (\emph{Roman}: \citealt{2015arXiv150303757S}) require even better control of systematics.
 In order to understand the systematic uncertainties we face, we must develop realistic image simulations, apply pre-existing shape measurement to the simulated images, and determine any potential residual systematic effects and build a strategy for modifying the calibration methodology to mitigate them.
@@
 
+Conventionally, these observational systematic biases are realized through a number of simulations and validations, and these propagate into the final galaxy shapes we measure.
+We quantify this impact as shear calibration bias.
+There have been several shear calibration and bias mitigation efforts that were proposed by STEP (\citealt{2006MNRAS.368.1323H, 2007MNRAS.376...13M}) and GREAT (\citealt{2010MNRAS.405.2044B, 2013ApJS..205...12K, 2015MNRAS.450.2963M}) challenges, to meet the requirements for the current imaging surveys.
+In particular, one of the state-of-the-art self-calibration methods, \textsc{metacalibration} (\citealt{2017arXiv170202600H, 2017ApJ...841...24S}) has been shown to be able to substantially reduce the significance of shear bias.
+It has been confirmed that shear can be calibrated with \textsc{metacalibration} at the few-percent level in DES (\citealt{2018MNRAS.481.1149Z, 2020arXiv201103408G}), without accounting for galaxy blending and detection.
+Tackling the issue of blending/detection is one key step forward for the DES Y6 analysis and preparatory Rubin LSST work with the shear-dependent detection and calibration technique (\textsc{metadetection}; \citealt{2020ApJ...902..138S}).
+While the major advantage of \textsc{metacalibration} is that it can be directly applied to real galaxy images without needing to rely on an ensemble calibration from image simulations, limitations for future surveys are not well-known.
+
+One possible limitation might lie in the effect of undersampled images in space-based surveys like \emph{Euclid} and \emph{Roman}, which will operate at its diffraction-limit (\citealt{2013PASP..125.1496S}).
+The PSF needs to be interpolated and estimated from well-sampled images to deconvolve and measure shapes, because the \emph{Roman} PSF has a complex structure that cannot be captured in the original undersampled images.
+It is, therefore, necessary to build a robust strategy to reconstruct well-sampled images to estimate the PSF to allow unbiased shape measurement.
+Recently, \cite{2021MNRAS.502.4048K} (hereafter K21) addressed this potential issue of the limitations of \textsc{metacalibration} on undersampled images in \emph{Euclid} image simulations.
+They found that for the \emph{Euclid} mission the shear estimate with \textsc{metacalibration} is biased by about 1$\%$.
+It is mentioned that their result could be extended to the \emph{Roman} mission due to similarities in the instruments and for \emph{Roman} they predicted the multiplicative bias was more than 1\%.
+They show that these effects can be mitigated using additional weighting kernels in the measurement.
+
+In this work, we explore how \textsc{metacalibration} performs using coadd images at higher resolution, taking advantage of the dithering of images in the reference HLIS.
+We use an updated suite of image simulations specifically made for the \emph{Roman} reference HLIS mission.
+Our work is based on the image simulation suite for the \emph{Roman} Space Telescope developed by \cite{2021MNRAS.501.2044T} (hereafter T21), where we render star and galaxy images using \texttt{GalSim}\footnote{\url{ https://github.com/GalSim-developers/GalSim}} (\citealt{2015A&C....10..121R}).
+We describe several important updates to the simulation capabilities and realism following T21.
+We also implement for the first time \textsc{metacalibration} using the simulated imaging, so that we can start to explore if the shear calibration goals of the HLIS for \emph{Roman} ($m=~3.2\times10^{-4}$) (\citealt{2018arXiv180403628D}) can be achieved with current \textsc{metacalibration} pipelines,\footnote{We limit the study to \textsc{metacalibration} for now, since we can extract unblended cutouts of objects in our simulations.} or will require substantial additional development.
+\par
+
+This paper is organized as follows.
+We first introduce the formalism of shear bias and image sampling relevant to the space-based surveys in Sec.~\ref{sec:background}.
+We then briefly discuss the simulation suite details we used and the updates we implemented for this project in Sec.~\ref{sec:sims}.
+In Sec.~\ref{sec:methods}, we show how coadditions of single exposure postage stamps are produced and how shape measurements are completed using \textsc{metacalibration}.
+We present the galaxy catalog properties and calibration results for single-band and multiband measurements in Sec.~\ref{sec:results}.
+Finally, in Sec.~\ref{sec:discussion}, we discuss how we will be able to constrain the shear bias better in terms of further updates in the image simulations and what we can conclude from this study.
+
+\section{Background}
+\label{sec:background}
+In this section, we provide an overview of shear calibration bias within the weak lensing formalism and the brief introduction of image sampling defined through the Nyquist-Shannon Sampling Theorem.
+
+\subsection{Shear Calibration Bias}
+weak lensing quantities. shear, reduced shear, ellipticity, shear bias.
 In this study, we focus on the shear calibration bias, which describes the relationship between gravitational lensing shear $\gamma$ and measured galaxy shapes.
@@
 
-Several shear calibration and bias mitigation efforts have been proposed by STEP (\citealt{2006MNRAS.368.1323H, 2007MNRAS.376...13M}) and GREAT (\citealt{2010MNRAS.405.2044B, 2013ApJS..205...12K, 2015MNRAS.450.2963M}) challenges, to meet the requirements for the current imaging surveys.
-In particular, one of the state-of-the-art self-calibration methods, \textsc{metacalibration} (\citealt{2017arXiv170202600H, 2017ApJ...841...24S}) has been shown to be able to substantially reduce the significance of shear bias.
-It has been confirmed that shear can be calibrated with \textsc{metacalibration} at the few-percent level in DES (\citealt{2018MNRAS.481.1149Z, 2020arXiv201103408G}), without accounting for galaxy blending and detection.
-Tackling the issue of blending/detection is one key step forward for the DES Y6 analysis and preparatory Rubin LSST work with the shear-dependent detection and calibration technique (\textsc{metadetection}; \citealt{2020ApJ...902..138S}).
-While the major advantage of \textsc{metacalibration} is that it can be directly applied to real galaxy images without needing to rely on an ensemble calibration from image simulations, limitations for future surveys are not well-known.
-
-One possible limitation might lie in the effect of undersampled images in space-based misssions like \emph{Euclid} and \emph{Roman}, which have such a small pixel scale that images will not be Nyquist sampled in the near-infrared (NIR) at the detector pixel scale (\citealt{2013PASP..125.1496S}) based on the Nyquist-Shannon Sampling Theorem.
-We define the sampling factor of each filter in \emph{Roman} to be,
+\subsection{Image Sampling}
+Based on the Nyquist-Shannon Sampling Theorem, 
+we define the sampling factor of each filter in \emph{Roman} to be, 
 \begin{equation}
@@
 An image with sampling factor $Q < 2$ is not Nyquist sampled (i.e., undersampled).
-The PSF needs to be interpolated and estimated from well-sampled images to deconvolve and measure shapes with, because the \emph{Roman} PSF has a complex structure that cannot be captured in the original undersampled images.
-It is, therefore, necessary to build a robust strategy to reconstruct well-sampled images to estimate the PSF to allow unbiased shape measurement.
-Recently, \cite{2021MNRAS.502.4048K} (hereafter K21) addressed this potential issue of the limitations of \textsc{metacalibration} on undersampled images in \emph{Euclid} image simulations.
-They found that for the \emph{Euclid} mission the shear estimate is biased by about 1$\%$.
-It is mentioned that their result could be extended to the \emph{Roman} mission due to similarities in the instruments and for \emph{Roman} they predicted the multiplicative bias was more than 1\%.
-They show that these effects can be mitigated using additional weighting kernels in the measurement.
-
-In this work, we explore how \textsc{metacalibration} performs using coadd images at higher resolution, taking advantage of the dithering of images in the reference HLIS.
-We use an updated suite of image simulations specifically made for the \emph{Roman} reference HLIS mission.
-Our work is based on the image simulation suite for the \emph{Roman} Space Telescope developed by \cite{2021MNRAS.501.2044T} (hereafter T21), where we render star and galaxy images using \texttt{GalSim}\footnote{\url{ https://github.com/GalSim-developers/GalSim}} (\citealt{2015A&C....10..121R}).
-We describe several important updates to the simulation capabilities and realism following T21.
-We also implement for the first time \textsc{metacalibration} using the simulated imaging, so that we can start to explore if the shear calibration goals of the HLIS for \emph{Roman} ($m=~3.2\times10^{-4}$) (\citealt{2018arXiv180403628D}) can be achieved with current \textsc{metacalibration} pipelines,\footnote{We limit the study to \textsc{metacalibration} for now, since we can extract unblended cutouts of objects in our simulations.} or will require substantial additional development.
-\par
-
-This paper is organized as follows.
-We briefly discuss the simulation suite details we used and the updates we implemented for this project in Sec.~\ref{sec:sims}.
-Then, in Sec.~\ref{sec:methods}, we show how coadditions of single exposure postage stamps are produced and how shape measurements are completed using \textsc{metacalibration}.
-We present the galaxy catalog properties and calibration results for single-band and multiband measurements in Sec.~\ref{sec:results}.
-Finally, in Sec.~\ref{sec:discussion}, we discuss how we will be able to constrain the shear bias better in terms of further updates in the image simulations and what we can conclude from this study.
 
@@
 \label{sec:sims}
-The base of our image simulations of the \emph{Roman} Space Telescope is the \emph{Roman} simulation suite\footnote{\url{ https://github.com/matroxel/roman_imsim}} developed by T21, which renders realistic galaxy and star images on 18 Sensor-Chip Assemblies (SCAs) of a 2.5$\times$2.5 deg$^{2}$ patch of the sky following the observing strategy for the 5-year reference mission and Cycle7 instrument specifications\footnote{\url{https://roman.gsfc.nasa.gov/science/Roman_Reference_Information.html}}.
+The base of our image simulations for the \emph{Roman} Space Telescope is the \emph{Roman} simulation suite\footnote{\url{ https://github.com/matroxel/roman_imsim}} developed by T21, which renders realistic galaxy and star images on 18 Sensor-Chip Assemblies (SCAs) of a 2.5$\times$2.5 deg$^{2}$ patch of the sky following the observing strategy for the 5-year reference mission and Cycle7 instrument specifications\footnote{\url{https://roman.gsfc.nasa.gov/science/Roman_Reference_Information.html}}.
 We begin by creating a truth catalog using the simulated galaxy distribution from the Buzzard simulation (\citealt{2019arXiv190102401D}), a photometric galaxy catalog sampled from the CANDELS survey (e.g., \citealt{2019ApJ...877..117H}), and a Milky Way simulation (Galaxia; \citealt{2011ApJ...730....3S}) for star positions and magnitudes.
@@
 	%\vspace*{-10mm}
-    \caption{The top row shows the first entry of the single epoch images and its coadded image, and the corresponding single-epoch and coadded oversampled PSF images for an object with low signal-to-noise ratio (S/N=9.69 in a single-epoch image).
-The bottom row shows the same for an object with high signal-to-noise ratio (S/N=1552.97 in a single-epoch image).
-The PSFs are shown in a log-scale.}
+    \caption{The top row shows the first observation of the single epoch images and its coadded image, and the corresponding single-epoch and coadded oversampled PSF images for a galaxy with low signal-to-noise ratio (S/N=9.69 in a single-epoch image).
+The bottom row shows the same for a galaxy with high signal-to-noise ratio (S/N=1552.97 in a single-epoch image).
+The PSFs are shown in a log-scale.
+The single epoch PSFs are almost identical, since there is no visually different feature for modeling them in different dithers and SCAs.
+Coadded PSFs look slightly different due to different numbers of single exposures.
+}
     \label{fig:singlecoadd}
@@
 For these reasons, we explore utilizing a coadding scheme for the \emph{Roman} galaxies.
-The detailed overview of the coadd process in \texttt{psc} is described in in Sec.
+The detailed overview of the coadd process in \texttt{psc} is described in Sec.
 \ref{subsec:psc}.
@@
 With this calibration method, we hope to significantly reduce some of the shear calibration bias T21 measured in order to make comparisons of effects contributing to the bias more realistic and meaningful as we explore future \emph{Roman} pipeline development.
-The detailed overview of \textsc{metacalibration} can be found in Sec.\ref{subsec:mcal}.
+The detailed overview of \textsc{metacalibration} can be found in Sec.~\ref{subsec:mcal}.
     %\item (Any other changes?)
@@
 The purpose of the simple simulations is to verify that there are no systematic biases at the fundamental levels of the simulation (e.g., no complex detector effects).
-These simple simulations play roles in ruling out the sources of systematic biases that may potentially be a problem in the use of \textsc{metacalibration} with space-based images.
+These simple simulations play a role in ruling out the sources of systematic biases that may potentially be a problem in the use of \textsc{metacalibration} with space-based images.
 
-The parameter choices are listed in Table.
+The fixed parameters for the simulations are listed in Table.
 \ref{tab:params}.
-With these parameters set, we simulated images with varying galaxy model profile, PSF model profile, the artificial shear, and background noise level, without any complications in the images and pipelines such as detector effects and coaddition.
+With these parameters, we simulated images with varying galaxy model profile, PSF model profile, the artificial shear, and background noise level, without any complications in the images and pipelines such as detector effects and coaddition.
+We set the basic light profiles for galaxies and PSF to be Gaussian.
 We first verify that our input gravitational shear is unbiased in \textsc{metacalibration} framework and the uncertainty in the recovered shape is small enough for the \emph{Roman} requirement (Fig.
@@
 We then test the pipeline by doubling the background noise.
-Due to the \emph{Roman} being in NIR range, the expected background noise level in the images is higher compared to optical imaging surveys like DES.
-With this test, we can confirm that the treatment of correlated noise induced in \textsc{metacalibration} process for low S/N objects does not trigger any bias at the level we should be concerned (\citealt{2017ApJ...841...24S}).
+Due to \emph{Roman} being in NIR range, the expected background noise level in the images is higher compared to optical imaging surveys like DES.
+With this test, we can confirm that the treatment of correlated noise induced in the  \textsc{metacalibration} process for low S/N objects does not trigger any bias at the level we should be concerned (\citealt{2017ApJ...841...24S}).
 Another test with \emph{Roman} PSF instead of Gaussian PSF does guarantee that the PSF features particular to \emph{Roman} do not bias the shape recovery even though it is undersampled.
@@
     %\vspace*{-5mm}
-    \caption{At first order, the \textsc{metacalibration} method only works for small shears.
-The next order effect is seen as a quadratic dependence of the multiplicative shear bias on on the applied shear.
-A larger input shear increases the signal-to-noise of bias estimates, but to keep this effect small compared to requirements, we limit input shears to $\pm 0.01$.}
+    \caption{We show the recovered multiplicative bias on the shear as a function of applied shear for the choice of the applied shear in our simulations.
+At first order, the \textsc{metacalibration} method only works for small shears.
+The next order effect is seen as a quadratic dependence of the multiplicative shear bias on the applied shear.
+A larger input shear increases the signal-to-noise of bias estimates, but to keep the non-linear effect small compared to requirements, we limit input shears to $\pm 0.01$.}
     \label{fig:metacal_shear_linear}
@@
 \label{sec:methods}
-Our goal is to test whether the recovered shapes with \textsc{metacalibration} are non-biased for \emph{Roman}.
-In order to do so, we need to build measurement pipelines within the current simulation framework that produces a final calibrated shear measurement.
-In this section, we present in detail how coadd images are produced with \texttt{psc} from the undersampled single-epoch images and how \textsc{metacalibration} is implemented to calibrates the measured shear using the \textsc{metacalibration} catalog.
+Our goal is to test whether the recovered shapes with \textsc{metacalibration} are non-biased for \emph{Roman} and to understand the factors that might contribute to any non-negligible bias.
+In order to do so, we need to build a measurement pipeline within the current simulation framework that produces a final calibrated shear measurement.
+In this section, we present in detail how coadd images are produced with \texttt{psc} from the undersampled single-epoch images and how \textsc{metacalibration} is implemented to calibrate the measured shear using the \textsc{metacalibration} catalog.
 
@@
 While coaddition can introduce new challenges and potential biases due to the complexity of coadding the original PSF and its interpolation scheme, the bias due to the undersampling of the original images can be mitigated by appropriately coadding dithered images.
+(choice of psc?
+-> to avoid thinking about rotations of the whole image, coadding cutouts is much easier.
+)
 
@@
 This final pixel scale was chosen to prevent the presence of visual artifacts in the structure of the coadd PSF image.
-    \item Creates an interpolated image with \texttt{GalSim} with the object centroid appropriately offset for each image using a \texttt{lanczos3} interpolantion method and sums them.
+    \item Creates an interpolated image with \texttt{GalSim} with the object centroid appropriately offset for each image using a \texttt{lanczos3} interpolation method and sums them.
 Out of several interpolation methods we tried, \texttt{lanczos3} produced the best coadd of the PSF.
@@
 \begin{figure}
-	\includegraphics[width=\columnwidth]{psf_differences.pdf}
+	\includegraphics[width=\columnwidth]{psf_differences_v2.pdf}
     % \vspace*{-5mm}
-    \caption{The left and middle panels illustrate the coadded \emph{Roman} PSF at its original pixel scale and the coadded PSF with a pixel scale that is generated with a pixel scale that is smaller by a factor of 4 and then down-sampled to this original pixel scale.
-These are visualized in a log scale.
+    \caption{The left and middle panels illustrate the coadded \emph{Roman} PSF at its original pixel scale and the coadded PSF with a pixel scale that is generated with a pixel scale that is smaller by a factor of 4 and then downsampled to this original pixel scale.
+These are visualized on a log scale.
 The right panel shows the difference image between the two PSF images.
@@
 The S/N of the coadd image is S/N=110.
-Finally, the right-most panel shows the coadded oversampled PSF in a log scale.}
+Finally, the right-most panel shows the coadded oversampled PSF on a log scale.}
     \label{fig:single_to_coadd_rgb}
@@
 \label{subsec:mcal}
-Once we construct the individual galaxy stamp coadds from the MEDS files, we recover the calibrated shear signal using the \textsc{metacalibration} process.
+Once we construct the individual galaxy stamp coadds from the MEDS files, we recover the calibrated shear signal using the \textsc{metacalibration} process (\citealt{2017arXiv170202600H, 2017ApJ...841...24S}).
 The bootstrapper method used in \texttt{ngmix} wraps the \textsc{metacalibration} and the shape fit processes.
@@
 
-In practice, we compute the shear response from the five versions of \textsc{metacalibration} catalog using the finite difference method.
+In practice, we compute the mean shear response from the five versions of \textsc{metacalibration} catalog using the finite difference method.
 
@@
 From the CANDELS catalog, based on the \emph{Roman} Weak Lensing mission requirements, objects are pre-selected and simulated.
-In total, we simulate 907,170 galaxies on 18 SCAs across 198 pointings for F184, 227 pointings for H158, and 238 pointings for J129 bandpass.
+In total, the galaxy photometry catalog contains 907,170 galaxies and from this catalog we simulated galaxies on 18 SCAs across 198 pointings for F184, 227 pointings for H158, and 238 pointings for J129 bandpass.
 We do not make any selection cuts on the simulated catalogs based on measured properties, since all input objects should pass requirements for weak lensing selection (e.g., S/N>18).
-Even so, due to the misestimation of the PSF or low S/N, the Gaussian mixture in \texttt{ngmix} fails to fit about 5\% of all simulated objects, and so the total number of the recovered objects for single-band measurements is, 861,960 for F184, 863,358 for H158, and 859,645 for J129.
+Even so, due to the misestimation of the PSF or low S/N, the Gaussian mixture in \texttt{ngmix} fails to fit about 5\% of all simulated objects, and so the total number of the recovered objects for single-band measurements is, 861,407 for F184, 863,146 for H158, and 859,193 for J129.
 For the multiband (H158+J129+F184) coadd measurements, we use objects that are measured successfully in all of the filters and the total number of the recovered objects is 851,821.
@@
 	\centering
-    \caption{The left panel shows the simulated magnitudes of galaxies for all the 3 filter we have used to measure shapes.
+    \caption{The left panel shows the measured magnitudes of galaxies for  the 3 filters we have used to measure shapes.
 The mean magnitude for H158, F184, and J129 are respectively 23.098, 22.976, and 23.273.
 The right panel shows the half-light radius in units of arcsec for H158 for input and measured objects.
-The mean half-light radii for input and measured galaxies are 0.294 and 0.221 arcsec for H158.
-For these histograms, we are showing the objects with a successful fit in \texttt{ngmix}.}
+The mean half-light radii for input and measured galaxies are 0.294 and 0.221 arcsec for H158.}
     \label{fig:true_properties}
@@
 The multiplicative bias of single-band single-epoch measurements is roughly 1\% in each filter.
-When the coadded images for each filter are used, the bias is at the similar level or worse within the uncertainties.
+When the coadded images for each filter are used, the bias is at a similar level or worse within the uncertainties.
 We can conclude that in the current \emph{Roman} simulation the multiplicative bias has a similar dependence on the sampling factor as shown in K21, but with a smaller amplitude.
@@
 This is due to the effect of an imperfect coadd PSF model.
-We find this correlation in the Figure \ref{fig:meanshear} where the recovered shear on the coadd images has a strong linear dependence on the PSF ellipticity measured by an adaptive moments method (\citealt{2003MNRAS.343..459H}).
+We find this correlation in Figure \ref{fig:meanshear} where the recovered shear on the coadd images has a strong linear dependence on the PSF ellipticity measured by an adaptive moments method (\citealt{2003MNRAS.343..459H}).
 The impact of the PSF shape and size leakage in the estimated galaxy shapes at the correlation function level can be estimated by computing $\rho$-statistics (\citealt{2008A&A...484...67P, 2010MNRAS.404..350R, 2016MNRAS.460.2245J}).
@@
 		\hline
-		single-epochs (J129) & 1.01 & 1.17$\pm$0.68 & 0.44$\pm$0.75 & 4.46$\pm$1.32 & 0.64$\pm$1.31\\
-		single-epochs (H158) & 1.23 & -1.07$\pm$0.62 & -1.61$\pm$0.66 & 2.83$\pm$1.35 & 2.33$\pm$1.22\\
-		single-epochs (F184) & 1.44 & -0.86$\pm$0.72 & -0.69$\pm$0.83 & 2.62$\pm$1.56 & 0.23$\pm$1.53\\
+		single-epochs (J129) & 0.88 & 1.17$\pm$0.68 & 0.44$\pm$0.75 & 4.46$\pm$1.32 & 0.64$\pm$1.31\\
+		single-epochs (H158) & 1.08 & -1.07$\pm$0.62 & -1.61$\pm$0.66 & 2.83$\pm$1.35 & 2.33$\pm$1.22\\
+		single-epochs (F184) & 1.31 & -0.86$\pm$0.72 & -0.69$\pm$0.83 & 2.62$\pm$1.56 & 0.23$\pm$1.53\\
 		\hline
-		single-band coadd (J129) & 1.26 & -1.84$\pm$0.71 & -1.90$\pm$0.65 & 11.99$\pm$1.39 & 0.59$\pm$1.41\\
-		single-band coadd (H158) & 1.54 & -1.75$\pm$0.67 & -1.68$\pm$0.64 & 14.39$\pm$1.32 & 4.29$\pm$1.35\\
-		single-band coadd (F184) & 1.79 & -0.28$\pm$0.83 & -0.27$\pm$0.78 & 12.15$\pm$1.56 & 5.66$\pm$1.56\\
+		single-band coadd (J129) & 1.10 & -1.84$\pm$0.71 & -1.90$\pm$0.65 & 11.99$\pm$1.39 & 0.59$\pm$1.41\\
+		single-band coadd (H158) & 1.35 & -1.75$\pm$0.67 & -1.68$\pm$0.64 & 14.39$\pm$1.32 & 4.29$\pm$1.35\\
+		single-band coadd (F184) & 1.64 & -0.28$\pm$0.83 & -0.27$\pm$0.78 & 12.15$\pm$1.56 & 5.66$\pm$1.56\\
 		\hline
@@
 In the current simulation framework, by coadding the single-epoch cutout images and using an oversampled PSF model, we found that shear estimates with an are still biased at the percent level using implementation of \textsc{metacalibration} that is similar to that used by ground-baesd Stage III surveys.
-To further constrain the shear calibration bias in the simulations and validate that the \emph{Roman} mission will be able to achieve the weak lensing calibration required for the survey, we need both more simulation volume -- about 400 times the area of the current simulation -- as well as significant improvements to the coadd and measurement pipelines currently used in this work.
+To further constrain the shear calibration bias in the simulations and validate that the \emph{Roman} mission will be able to achieve the weak lensing calibration required for the survey, we need both more simulation volume --- about 400 times the area of the current simulation --- as well as significant improvements to the coadd and measurement pipelines currently used in this work.
 
@@
 Thus, our study further confirms the need for better treatment of the undersampled images for weak lensing.
-In future versions of the \emph{Romaan} simulations that are currently being developed, we will both be able to increase the simulation volume significantly and produce coadd images with a smaller pixel scale for shape measurement.
+In future versions of the \emph{Roman} simulations that are currently being developed, we will both be able to increase the simulation volume significantly and produce coadd images with a smaller pixel scale for shape measurement.
 With these and other changes to improve the realism of the simulations and measurement pipelines used with them, we will be able to better explore the possible origins of the current percent level residual shear bias and study mitigation strategies in order to reach the \emph{Roman} weak lensing mission requirement.

### 2022-03-11 paper_v3.tex
rachel's comments v4.1

@@
 \normalem
-\title[Metacalibration for the Roman High-Latitude Imaging Survey]{Weak gravitational lensing shear estimates with \textsc{metacalibration} for the \emph{Roman} High-Latitude Imaging Survey}
+\title[Metacalibration for the Roman High-Latitude Imaging Survey]{Weak gravitational lensing shear \textcolor{red}{estimation} with \textsc{metacalibration} for the \emph{Roman} High-Latitude Imaging Survey}
 
@@
 Christopher Hirata,$^{4,5,6}$
- et al.\\
+\newauthor{
+Ami Choi,$^{7}$
+Tianqing Zhang,$^{3}$}\\
 % List of institutions
@@
 $^{6}$Department of Astronomy, The Ohio State University, 140 West 18th Avenue, Columbus, OH 43210, USA\\
+$^{7}$Department of Physics, California Institute of Technology, 1200 E. California Blvd., Pasadena, California 91125, USA\\
 }
@@
 %These large-scale realistic image simulations are necessary to measure shear bias to confirm that the requirements of the instrument and the overall weak lensing survey strategy are met. 
-The weak lensing program of the \emph{Roman} mission requires the mean galaxy ellipticity to be calibrated within about 0.03\%.
-To reach this goal, we can test our calibration process with various simulations and ultimately isolate the sources where these residual shear biases might arise in order to improve our methods.
-In this work, we build on the first set of Roman HLIS simulated imaging data in \cite{2021MNRAS.501.2044T} to incorporate several new realistic processing-pipeline updates necessary to more accurately process the imaging data and calibrate the shear.
-We show the first results of this calibration for six deg$^{2}$ of the simulated reference HLIS using \textsc{metacalibration} and compare these results to measurements on more simple, faster Roman-like image simulations.
+The weak lensing program of the \emph{Roman} mission requires the mean weak lensing shear estimate to be calibrated within about 0.03\%.
+To reach this goal, we can test our calibration process with various simulations and ultimately isolate the sources of residual shear biases in order to improve our methods.
+In this work, we build on the Roman HLIS image simulation pipeline in \cite{2021MNRAS.501.2044T} to incorporate several new realistic processing-pipeline updates necessary to more accurately process the imaging data and calibrate the shear.
+We show the first results of this calibration for six \textrm{deg}$^{2}$ of the simulated reference HLIS using \textsc{metacalibration} and compare these results to measurements on more simple, faster Roman-like image simulations.
 In both cases, we neglect the impact of blending of objects.
@@
 %In the future, we will need to substantially increase the simulation volume by $\sim$400 (about the same size as the survey area of 2000 deg$^{2}$) to reach the precision necessary to test the HLIS requirements.
-Current results demonstrate, however, that the \textsc{metacalibration} method can work on undersampled space-based imaging data at well-below the requirements levels of current weak lensing surveys.
+Current results demonstrate, however, that the \textsc{metacalibration} method can work on undersampled space-based imaging data at the levels comparable to the requirements levels of current weak lensing surveys.
 \end{abstract}
@@
 
-Since the formulation of a physical cosmological model, observational evidence has shown that the contents of the universe are mostly in the dark sector (\citealt{2020A&A...641A...8P, 2020MNRAS.498.2492G, 2020MNRAS.499.5527T, 2021A&A...645A.104A, 2022PhRvD.105b3520A, 2022arXiv220204077B}).
+Since the formulation of the standard cosmological model, most observational evidence has been consistent with the flat $\Lambda$-CDM model in which the contents of the universe are mostly in the dark sector (\citealt{2020A&A...641A...8P, 2020MNRAS.498.2492G, 2020MNRAS.499.5527T, 2021A&A...645A.104A, 2022PhRvD.105b3520A, 2022arXiv220204077B}).
 Within this sector, dark energy accounts for the accelerating expansion of the universe (e.g., \citealt{1998AJ....116.1009R, 1999AIPC..478..129P}) and the combination of dark energy and dark matter are responsible for the observed growth of large-scale structure (\citealt{2015RPPh...78h6901K, 2017grle.book.....D}).
-The growth can be studied by carefully reconstructing the paths of the light leaving distant galaxies and going through the regions where mass concentrates in the universe; this physical phenomenon is called gravitational lensing.
-“Weak” gravitational lensing causes a slight distortion to intrinsic galaxy shapes called shear.
+\textcolor{red}{The growth can be studied by measuring quantities that are sensitive to the way light rays are deflected by intervening mass in the Universe, a physical phenomenon called gravitational lensing.} “Weak” gravitational lensing causes a slight distortion to intrinsic galaxy shapes called shear.
 By detecting millions of these gravitationally lensed galaxies and computing their ensemble shear, we can explore the dark matter density and the amplitude of matter fluctuation in the universe (e.g., \citealt{2001PhR...340..291B}).
@@
 
-Due to the subtlety in the lensing effect and its systematics-dominant nature in the weak regime, observational efforts have been challenging.
-Over the past decade, large international collaborations such as the Dark Energy Survey\footnote{\url{http://www.darkenergysurvey.org/}} (DES: \citealt{2005astro.ph.10346T}), the Hyper Supreme-Cam\footnote{\url{http://hsc.mtk.nao.ac.jp/ssp/}} (HSC: \citealt{2018PASJ...70S...4A}), and the Kilo-Degree Survey\footnote{\url{http://kids.strw.leidenuniv.nl/}} (KiDS: \citealt{2013ExA....35...25D}) have been successful at constraining the cosmological parameters, and the precision in calibrating the shapes of distant galaxies has reached a few percent (\citealt{2020arXiv201103408G, 2020arXiv201208567M, 2021A&A...645A.105G}).
-As we observe more area of the sky and develop better tools (observatories and algorithms), we detect more galaxies, and have already reached the point where statistical and systematic uncertainties are comparable.
+Due to the subtlety in the lensing effect and its systematics-dominant nature in the weak regime (\citealt{2018ARA&A..56..393M}), observational efforts have been challenging.
+Over the past decade, large international collaborations such as the Dark Energy Survey\footnote{\url{http://www.darkenergysurvey.org/}} (DES: \citealt{2005astro.ph.10346T}), the Hyper Suprime-Cam Subaru Strategic Program\footnote{\url{http://hsc.mtk.nao.ac.jp/ssp/}} (HSC: \citealt{2018PASJ...70S...4A}), and the Kilo-Degree Survey\footnote{\url{http://kids.strw.leidenuniv.nl/}} (KiDS: \citealt{2013ExA....35...25D}) have been successful at constraining the cosmological parameters, and the precision in calibrating the estimates of shear from the shapes of distant galaxies has reached a few percent (\citealt{2018MNRAS.481.3170M, 2020arXiv201103408G, 2020arXiv201208567M, 2021A&A...645A.105G}).
+As we observe more area on the sky and develop better tools (observatories and algorithms), we detect more galaxies, and have already reached the point where statistical and systematic uncertainties are comparable.
 Thus, near-future Stage IV surveys (\citealt{2006astro.ph..9591A}) such as Euclid\footnote{\url{ http://sci.esa.int/euclid}} (\citealt{2011arXiv1110.3193L}), the Vera C.
-Rubin Observatory Legacy Survey of Space and Time\footnote{\url{ http://www.lsst.org}} (\emph{Rubin}: \citealt{2009arXiv0912.0201L, 2019ApJ...873..111I}), and the \emph{Nancy Grace Roman} Space Telescope\footnote{\url{https://roman.gsfc.nasa.gov}} (\emph{Roman}: \citealt{2015arXiv150303757S}) require even better control of systematics.
+Rubin Observatory Legacy Survey of Space and Time\footnote{\url{ http://www.lsst.org}} (\emph{LSST}: \citealt{2009arXiv0912.0201L, 2019ApJ...873..111I}), and the \emph{Nancy Grace Roman} Space Telescope\footnote{\url{https://roman.gsfc.nasa.gov}} (\emph{Roman}: \citealt{2015arXiv150303757S}) require even better control of systematics.
 In order to understand the systematic uncertainties we face, we must develop realistic image simulations, apply existing shape measurement methods to the simulated images, and determine any potential residual systematic effects and build a strategy for modifying the calibration methodology to mitigate them.
@@
 Based on our current knowledge, systematic biases for weak lensing science, both observational and astrophysical, can occur at all stages of the imaging survey (e.g., \citealt{2018ARA&A..56..393M}).
-Particularly, observational systematics can be due to:
+In particular, observational systematics can be due to:
 \begin{itemize}
     \item inhomogeneous observing strategy,
-    \item instrumentation effects,
+    \item \textcolor{red}{atmospheric and} instrumentation effects,
     \item post-processing pipelines such as image coaddition and object detection.
@@
 We quantify this impact as shear calibration bias.
-There have been several shear calibration and bias mitigation efforts that were proposed by the STEP (\citealt{2006MNRAS.368.1323H, 2007MNRAS.376...13M}) and GREAT (\citealt{2010MNRAS.405.2044B, 2013ApJS..205...12K, 2015MNRAS.450.2963M}) challenges, to meet the requirements for the current imaging surveys.
+Several shear calibration and bias mitigation efforts have been inspired by the outcomes of the Shear TEsting Programme (STEP; \citealt{2006MNRAS.368.1323H, 2007MNRAS.376...13M}), the GRavitational lEnsing Accuracy Testing challenges (GREAT; \citealt{2010MNRAS.405.2044B, 2013ApJS..205...12K, 2015MNRAS.450.2963M}) \textcolor{red}{and other image simulations work (e.g., \citealt{2017MNRAS.468.3295H})}, to meet the requirements for the current imaging surveys.
 In particular, one of the state-of-the-art self-calibration methods, \textsc{metacalibration} (\citealt{2017arXiv170202600H, 2017ApJ...841...24S}) has been shown to be able to substantially reduce the significance of shear bias.
 It has been confirmed that shear can be calibrated with \textsc{metacalibration} at the few-percent level in DES (\citealt{2018MNRAS.481.1149Z, 2020arXiv201103408G}), without accounting for galaxy blending and detection.
-Tackling the issue of blending/detection is one key step forward for the DES Y6 analysis and preparatory Rubin LSST work with the shear-dependent detection and calibration technique \textsc{metadetection} (\citealt{2020ApJ...902..138S}).
+Tackling the issue of blending/detection is one key step forward for the DES Y6 analysis and preparatory Rubin LSST work with the shear-dependent detection and calibration technique \textsc{metadetection}\footnote{\textcolor{red}{\textsc{metadetection} reduces a significant amount of shear-dependent detection bias by shearing a small region of the sky and applying detection.} } (\citealt{2020ApJ...902..138S}).
 While the major advantage of \textsc{metacalibration} or \textsc{metadetection} is that they can be directly applied to real galaxy images without needing to rely on an ensemble calibration from image simulations, limitations for future surveys are not well-known.
 
-One possible limitation might lie in the effect of undersampled images in space-based surveys like \emph{Euclid} and \emph{Roman}, which will operate at its diffraction-limit.
-The PSF needs to be interpolated and estimated from well-sampled images to accurately deconvolve and measure shapes with, because the \emph{Roman} PSF has a complex structure that cannot be captured in the original undersampled images.
+One possible limitation might lie in the effect of undersampled images in space-based surveys like \emph{Euclid} and \emph{Roman}, which will operate at \textcolor{red}{their respective diffraction limits}.
+The \textcolor{red}{Point Spread Function (PSF)} needs to be interpolated and estimated from well-sampled images to accurately deconvolve and measure shapes with, because the \emph{Roman} PSF has a complex structure that cannot be captured in the original undersampled images.
 It is, therefore, necessary to build a robust strategy to reconstruct well-sampled images to estimate the PSF to allow unbiased shape measurement.
@@
 
-In this work, we explore how \textsc{metacalibration} performs using coadd images at higher resolution, taking advantage of the dithering of images in the reference HLIS.
+In this work, we explore how \textsc{metacalibration} performs using coadd images at higher resolution than the native resolution of the instrument, taking advantage of the dithering of images in the reference HLIS.
 We use an updated suite of image simulations specifically made for the \emph{Roman} reference HLIS mission.
@@
 We describe several important updates to the simulation capabilities and realism following T21.
-We also implement for the first time \textsc{metacalibration} using the simulated imaging, so that we can start to explore if the shear calibration goals of the HLIS for \emph{Roman} ($m=~3.2\times10^{-4}$) (\citealt{2018arXiv180403628D}) can be achieved with current \textsc{metacalibration} pipelines,\footnote{We limit the study to \textsc{metacalibration} for now, since we can extract unblended cutouts of objects in our simulations.} or will require substantial additional development.
+We also implement for the first time \textsc{metacalibration} using the simulated imaging within the T21 simulation suite, so that we can start to explore if the shear calibration goals of the HLIS for \emph{Roman} ($m=~3.2\times10^{-4}$) (\citealt{2018arXiv180403628D}) can be achieved with current \textsc{metacalibration} implementations,\footnote{We limit the study to \textsc{metacalibration} for now, since we can extract unblended cutouts of objects in our simulations.} or will require substantial additional development.
 \par
@@
 \label{sec:background}
-In this section, we provide a brief introduction of image sampling defined through the Nyquist-Shannon Sampling Theorem, an overview of shear calibration bias within the context of weak lensing, and the \textsc{metacalibration} formalism.
+In this section, we provide a brief introduction to image sampling defined through the Nyquist-Shannon Sampling Theorem, an overview of shear calibration bias within the context of weak lensing, and the \textsc{metacalibration} formalism.
 
 \subsection{Image Sampling}
-Based on the Nyquist-Shannon Sampling Theorem which states that in order to reconstruct an unbiased continuous band-limited function without a loss of information, the sufficient sample rate is twice the bandlimiting frequency per second.
-In the context of image sampling, the criterion that the sample pixel spacing needs to satisfy is $p < \frac{1}{2u_{max}}$ ($u_{max}$ is the max.
-spatial bandlimiting frequency).
-Since the spatial bandlimiting frequency in an astronomical image is defined as,
+Based on the Nyquist-Shannon Sampling Theorem, which states that in order to reconstruct an unbiased continuous band-limited function without a loss of information, the sufficient sample rate is twice the bandlimiting frequency per second.
+In the context of image sampling, the criterion that the sample pixel spacing needs to satisfy is $p < \frac{1}{2u_{\text{max}}}$ ($u_{\text{max}}$ is the maximum spatial bandlimiting frequency).
+\textcolor{red}{The angular resolution of the diffraction-limited system is $\theta = \lambda/D$ (D: the diameter of an effective aperture) and .} Since the spatial bandlimiting frequency in an astronomical image is defined as
 \begin{equation}
-    u_{max} = \frac{1}{\lambda_{min}N_{f}}
+    u_{max} = \frac{1}{\lambda_{\text{min}}N_{f}}
 \end{equation}
-the sampling factor of the \emph{Roman} images is defined as, 
+the sampling factor for \textcolor{red}{a space telescope} is defined as 
 \begin{equation}
-    Q = \frac{\lambda_{min}N_{f}}{p}, 
+    Q = \frac{\lambda_{\text{min}}N_{f}}{p}, 
     \label{eqn:sampling}
 \end{equation}
-where $\lambda_{min}$ is the shortest wavelength of the incident light in each filter, $N_{f}$ is the focal ratio of the telescope ($N_{f}=7.8$ for \emph{Roman}) and $p$ is the pixel spacing of the sensor ($p=10\mu m$ for \emph{Roman}) (\citealt{2013PASP..125.1496S}).
-An image with sampling factor $Q=2$ is considered Nyquist-sampled and an image with with sampling factor $Q<2$ is undersampled.
+where $\lambda_{\text{min}}$ is the shortest wavelength of the incident light in each filter, $N_{f}$ is the focal ratio of the telescope ($N_{f}=7.8$ for \emph{Roman}) and $p$ is the pixel spacing of the sensor ($p=10\,\mu m$ for \emph{Roman}) (\citealt{2013PASP..125.1496S}).
+An image with sampling factor $Q=2$ is considered Nyquist-sampled and an image with sampling factor $Q<2$ is undersampled.
+\textcolor{red}{The image samplings for \emph{Roman} are $Q$=0.88, 1.08, 1.31 for J129, H158, and F184 bandpasses respectively.
+}
 
@@
 \subsection{Shear Calibration Bias}
-In the observation of cosmic shear, we can quantify the bias associated with the shear recovery processes such as PSF estimation and shape measurement in image simulations.
+In the observation of weak lensing, we can quantify the bias associated with the shear recovery processes such as PSF estimation and shape measurement in image simulations.
 We call this shear calibration bias and we compute the deviations of the measured gravitational lensing shear $\gamma$ from the input shear.
-In the limit of weak lensing ($\lvert\gamma\rvert\ll1$) and random intrinsic galaxy shapes, the ensemble average of ellipticities $\langle e \rangle$ of galaxy shapes is directly related to the reduced shear field $g$, and the estimated shear can be written as a linear model with multiplicative ($m_{i}$) and additive bias ($c_{i}$) as described in the equation below (\citealt{2006MNRAS.368.1323H, 2006MNRAS.366..101H, 2007MNRAS.376...13M})
+\textcolor{red}{Here we define the reduced shear $g \equiv \gamma/(1-\kappa)$, and it is safe to approximate $\gamma \approx g$ in the context of cosmic shear.} In the limit of weak lensing ($\lvert\gamma\rvert\ll1$, $\lvert\kappa\rvert\ll1$) and random intrinsic galaxy shapes, the ensemble average of ellipticities $\langle e \rangle$ of galaxy shapes is directly related to the reduced shear field $g$, and the estimated shear can be written as a linear model with multiplicative ($m_{i}$) and additive bias ($c_{i}$) as described in the equation below (\citealt{2006MNRAS.368.1323H, 2006MNRAS.366..101H, 2007MNRAS.376...13M})
 \begin{equation}
-    g^{obs}_{i} = (1+m_{i})g^{true}_{i} + c_{i}, 
+    g^{\textrm{obs}}_{i} = (1+m_{i})g^{\textrm{true}}_{i} + c_{i}, 
     \label{eqn:linear}
 \end{equation}
-where i=(1,2) and $g^{obs}_{i}$ is the two-component observed reduced shear after calibrations and $g^{true}_{i}$ is the true shear.
+where $i$=(1,2) \textcolor{red}{due to the rotational symmetry of an ellipse} and $g^{\textrm{obs}}_{i}$ is the two-component observed reduced shear after calibrations and $g^{\textrm{true}}_{i}$ is the true shear.
 The bias can be introduced in places such as PSF modeling, blending, and the undersampling of the image (e.g., \citealt{2018ARA&A..56..393M}).
-Additionally, complex detector effects such as the brighter-fatter effect are potential sources of bias (\citealt{2013MNRAS.429..661M}), while it has been shown that for \emph{Roman} the effect of persistence will not be an issue (\citealt{2021arXiv210610273L}).
-Qualitatively, if the recovered shear is biased by 1$\%$ ($m=0.01$), $S_{8} = \sigma_{8} \sqrt{\Omega_{m}/0.3}$ could be biased about 1.5$\%$ in the final cosmology result.
+Additionally, complex detector effects such as the brighter-fatter effect are potential sources of bias (\citealt{2020PASP..132a4502C}), while it has been shown that for \emph{Roman} the effect of persistence will not be an issue (\citealt{2021arXiv210610273L}).
+Qualitatively, if the recovered shear is biased by 1$\%$ ($m=0.01$), \textcolor{red}{from the cosmic shear power spectrum $S_{8} = \sigma_{8} \sqrt{\Omega_{m}/0.3}$ could be estimated to be biased} about 1.5$\%$ in the final cosmology result.
 Thus, quantifying and correcting these biases before the real survey begins is extremely important.
@@
 \begin{figure}
-	\includegraphics[width=\columnwidth]{metacal_bias_shear.pdf}
+	\includegraphics[width=\columnwidth]{metacal_bias_shear_pplt.pdf}
     %\vspace*{-5mm}
-    \caption{We show the recovered multiplicative bias on the shear as a function of applied shear for the choice of the applied shear in our simulations.
-The presented multiplicative bias is the average of $m_{1}$ and $m_{2}$.
+    \caption{We show the recovered multiplicative bias on the shear as a function of applied shear for the choice of the applied shear in our \textcolor{red}{simplified} simulations.
+The presented multiplicative bias is the average of $m_{1}$ and $m_{2}$, and the grey shaded region represents the mission requirement.
 At first order, the \textsc{metacalibration} algorithm only works for small input shears.
@@
 \subsection{\textsc{metacalibration} Formalism}
-Here, we describe the general features of how \textsc{metacalibration} calibrates the biased measurement of galaxy ellipticities on the image stamps.
-\textsc{metacalibration} creates one unsheared and four artificially-sheared galaxy stamps.
-Each is deconvolved with the input PSF, left unsheared or sheared with an additional gravitational shear of $\delta\gamma=\pm 0.01$ in the two basis directions ($+g1$, $-g1$, $+g2$, $-g2$) and re-convolved with a new slightly larger isotropic, Gaussian PSF.
-\textsc{metacalibration} works under the assumption that the input shear is small, otherwise the recovered shear would be biased without accounting for higher order terms.
-It is a balance to choose an input shear that results in higher S/N of an object and unbiased shape measurement.
-Figure \ref{fig:metacal_shear_linear} shows the performance as a function of input shear leading to the choice of input shear $\gamma=\pm 0.02$.
+Here, we briefly summarize how \textsc{metacalibration} (\citealt{2017arXiv170202600H, 2017ApJ...841...24S}) calibrates the biased measurement of galaxy ellipticities on the image stamps.
+\textcolor{red}{Each stamp is defined to be an image cutout with one galaxy.} \textsc{metacalibration} creates one unsheared and four artificially-sheared galaxy stamps.
+Each is deconvolved with the input PSF, left unsheared or sheared with an additional gravitational shear of $\delta g=\pm 0.01$ in the two basis directions ($g_1$, $g_2$) and re-convolved with a new slightly larger isotropic, Gaussian PSF.
+\textcolor{red}{We have adopted to use the Gaussian PSF since it resembles the process in the current surveys and it requires complex operations to use a non-Gaussian PSF for the space-based survey.
+This choice could imply that we potentially isotropize the shapes of galaxies.} \textsc{metacalibration} works under the assumption that the input shear is small, otherwise the recovered shear would be biased without accounting for higher order terms.
+It is a balance to choose an input shear that results in higher S/N of the estimated shear bias  and unbiased shear measurement.
+Figure \ref{fig:metacal_shear_linear} shows the performance as a function of input shear leading to the choice of input shear $g=\pm 0.02$.
 
-After processing the images in \textsc{metacalibration} and measuring the shapes in \texttt{ngmix}, we have 5 shape catalogs in each \textsc{metacalibration} shear direction.
-We can then compute the shear response from these catalogs and calculate the calibrated ensemble galaxy ellipticities.
+After processing the images with \textsc{metacalibration} and measuring the shapes with \texttt{ngmix}, we have 5 shape catalogs for the five values of shear applied by \textsc{metacalibration}.
+We can then compute the shear response from these catalogs and calculate the calibrated ensemble galaxy shears.
 The shear response can be understood as the change in objects' ellipticities with respect to the change in gravitational shear.
-Mathematically, the observed ellipticities, $\vb*{e}$ = ($e_{1}$, $e_{2}$), can be approximated using a Taylor expansion around the two-component shear, $\vb*{\gamma}=0$.
-Higher terms here can be dropped assuming the gravitational shear is small (reduced shear).
+Mathematically, the observed ellipticities, $\vb*{e}$ = ($e_{1}$, $e_{2}$), can be approximated using a Taylor expansion around the two-component shear, $\vb*{g}=0$.
+Higher terms here can be dropped assuming the gravitational shear is small:
 \begin{equation}
-    \vb*{e} = \vb*{e}\rvert_{\vb*{\gamma}=0} + \frac{\partial \vb*{e}}{\partial \vb*{\gamma}}\bigg\rvert_{\vb*{\gamma}=0}\vb*{\gamma} + \ldots
+    \vb*{e} = \vb*{e}\rvert_{\vb*{g}=0} + \frac{\partial \vb*{e}}{\partial \vb*{g}}\bigg\rvert_{\vb*{g}=0}\vb*{g} + \ldots
 \end{equation}
-From this expression, the shear response matrix can be defined as, 
+From this expression, the shear response matrix can be defined as 
 \begin{equation}
-    \vb*{R} \equiv \frac{\partial \vb*{e}}{\partial \vb*{\gamma}}\bigg\rvert_{\vb*{\gamma}=0} = 
+    \vb*{R} \equiv \frac{\partial \vb*{e}}{\partial \vb*{g}}\bigg\rvert_{\vb*{g}=0} = 
     \begin{pmatrix}
-        \partial e_{1}/\partial \gamma_{1} & \partial e_{2}/\partial \gamma_{1} \\ 
-        \partial e_{1}/\partial \gamma_{2} & \partial e_{2}/\partial \gamma_{2}
+        \partial e_{1}/\partial g_{1} & \partial e_{2}/\partial g_{1} \\ 
+        \partial e_{1}/\partial g_{2} & \partial e_{2}/\partial g_{2}
     \end{pmatrix}. 
@@
 The ensemble mean of measured ellipticities $\langle\vb*{e}\rangle$ can then computed.
-Since we expect galaxies to be randomly oriented such that $\langle\vb*{e}\rangle\rvert_{\vb*{\gamma}=0}=0$, we have a relationship between the measured ellipticities and the input shear in the simulations,
+Since we expect galaxies to be randomly oriented such that $\langle\vb*{e}\rangle\rvert_{\vb*{g}=0}=0$, we have a relationship between the measured ellipticities and the input shear in the simulations,
 \begin{equation}
-    \langle\vb*{e}\rangle \approx \langle \vb*{R}\rangle\langle\vb*{\gamma} \rangle. 
+    \langle\vb*{e}\rangle \approx \langle \vb*{R}\rangle\langle\vb*{g} \rangle. 
 \end{equation}
 
-In practice, we compute the mean shear response from the five versions of \textsc{metacalibration} catalog using the finite difference method.
-
+In practice, we compute the mean shear response from the four versions of \textsc{metacalibration} catalog using the finite difference method. 
 \begin{equation}
     \langle\vb*{R_{ij}}\rangle = 
-    \frac{\langle e^{+}_{i} - e^{-}_{i} \rangle}{\delta\gamma_{j}}, 
+    \frac{\langle e^{+}_{i} - e^{-}_{i} \rangle}{2\delta g_{j}}, 
 \end{equation}
@@
 
-The mean shear response is then used to get the \textsc{metacalibration}-calibrated shapes from the unsheared catalog.
-For individual objects, using Eq.
-\ref{eqn:linear}.
-we compare the input shear and the calibrated shapes to calculate multiplicative ($\vb*{m}$) and additive bias ($\vb*{c}$).
+The mean shear response is then used to get the \textsc{metacalibration}-calibrated shears from the unsheared catalog.
+For individual objects, using Eqn.~\eqref{eqn:linear}, we compare the input shear and the calibrated shapes to calculate multiplicative ($\vb*{m}$) and additive bias ($\vb*{c}$).
 
@@
 \label{sec:sims}
-The base of our image simulations of the \emph{Roman} Space Telescope is the \emph{Roman} simulation suite\footnote{\url{ https://github.com/matroxel/roman_imsim}} developed by T21, which renders realistic galaxy and star images on 18 Sensor-Chip Assemblies (SCAs) of a 2.5$\times$2.5 deg$^{2}$ patch of the sky following the observing strategy for the 5-year reference mission and Cycle7 instrument specifications.\footnote{\url{https://roman.gsfc.nasa.gov/science/Roman_Reference_Information.html}} We begin by creating a truth catalog using the simulated galaxy distribution from the Buzzard simulation (\citealt{2019arXiv190102401D}), a photometric galaxy catalog sampled from the CANDELS survey (e.g., \citealt{2019ApJ...877..117H}), and a Milky Way simulation (Galaxia; \citealt{2011ApJ...730....3S}) for star positions and magnitudes.
-Then, the following properties are applied to each galaxy:
+The base of our image simulations of the \emph{Roman} Space Telescope is the \emph{Roman} simulation suite\footnote{\url{ https://github.com/matroxel/roman_imsim}} developed by T21, which renders realistic galaxy and star images on 18 Sensor-Chip Assemblies (SCAs) of a 2.5$\times$2.5 \textrm{deg}$^{2}$ patch of the sky following the observing strategy for the 5-year reference mission and Cycle 7 instrument specifications.\footnote{\url{https://roman.gsfc.nasa.gov/science/Roman_Reference_Information.html}} We begin by creating a truth catalog using the simulated galaxy distribution from the Buzzard simulation (\citealt{2019arXiv190102401D}), a photometric galaxy catalog sampled from the Cosmic Assembly Near-infrared Deep Extragalactic Legacy Survey (CANDELS; \citealt{2011ApJS..197...35G, 2011ApJS..197...36K, 2019ApJ...877..117H}), and a Milky Way simulation (Galaxia; \citealt{2011ApJ...730....3S}) for star positions and magnitudes.
+Then, the following properties are assigned to each galaxy:
 \begin{itemize}
@@
 The next step of the process is to create postage stamps and SCA images using \texttt{GalSim}.
-In this stage, the point-spread function (PSF) is convolved with the stamps.
-Here, the \emph{Roman} PSF is rendered using the \texttt{galsim.roman} module under \texttt{GalSim}, which has implemented \emph{Roman}-specific instrument properties such as the PSF and World Coordinate System (WCS) for a given telescope pointing, rotation angle, and SCA.
+In this stage, the point-spread function (PSF) is convolved with the intrinsic galaxy light profile.
+Here, the \emph{Roman} PSF is rendered using the \texttt{galsim.roman} module, which has implemented \emph{Roman}-specific instrument properties such as the PSF and World Coordinate System (WCS) for a given telescope pointing, rotation angle, and SCA.
+\textcolor{red}{Depending on the pointing, the simulated detector effects were added to the images in the following order: reciprocity failure, quantization, dark current, persistence, non-linearity, interpixel capacitance, read noise, and electron-to-ADU conversion (\citealt{2020JATIS...6d6001M}).}
 
-After we generate the object stamps across all the SCAs and pointings, we create Multi-Epoch Data Structure (MEDS) files in which each unique object dictionary contains information of all the exposures it appears in.
-These MEDS files are partitioned according to the Hierarchical Equal Area isoLatitude Pixelisation (HEALPix) of $n_{side}=512$.
-They contain all objects that are located in that region of the sky partitioned according HEALPixel\footnote{\url{https://healpix.jpl.nasa.gov/}} (\citealt{2005ApJ...622..759G, Zonca2019}).
+After we generate the object stamps across all the SCAs and pointings, we create Multi-Epoch Data Structure (MEDS\footnote{\url{https://github.com/esheldon/meds}}; e.g., \citealt{2016MNRAS.460.2245J}) files in which each unique object dictionary contains information of all the exposures in which it appears in.
+These MEDS files are partitioned in a given Hierarchical Equal Area isoLatitude Pixelisation (\textsc{HEALPix}) of $n_{\text{side}}=512$.
+They contain all objects that are located in that region of the sky partitioned according \textsc{HEALPixel}\footnote{\url{https://healpix.jpl.nasa.gov/}} (\citealt{2005ApJ...622..759G, Zonca2019}).
 
 Once the objects are sorted in MEDS files, we pass these multiple exposures with the corresponding PSFs to \texttt{ngmix}\footnote{\url{ https://github.com/esheldon/ngmix}} to fit the galaxy shapes with the Gaussian mixture fitting method (\citealt{2014MNRAS.444L..25S}).
-This shape measurement process produces shape catalogs from which the shear calibration bias can be calculated with \textsc{metacalibration}.
+This shape measurement process produces shape catalogs from which the shear response is calculated with \textsc{metacalibration}, and shear calibration bias can finally be computed.
 
@@
 \textbf{Bottom Row}: the same as above for a galaxy with high signal-to-noise ratio (S/N=390.47 in a single-epoch image).
-H158 bandpass was used to represent images here.
+The H158 bandpass was used to represent images here.
 The PSFs are shown in a log-scale.
@@
 There are two features to note here.
-One is how coadding helps for low S/N objects, and the other feature is the coadded PSFs look more isotropic than the single-epoch PSF due to different numbers of exposures.}
+One is how coaddition helps for low S/N objects, and the other feature is that the coadded PSFs look more isotropic than the single-epoch PSF due to different numbers of exposures.}
     \label{fig:singlecoadd}
@@
 \subsection{Updates to Simulation Capabilities}
+\label{subsec:updates}
 In order to accomplish the science goals, and build and test weak lensing calibration pipelines for \emph{Roman}, we have continued to update the realism of our image simulations.
@@
     In the study by T21, the rotations of the \emph{Roman} PSF with respect to the telescope rotation were not properly applied by the \texttt{galsim.roman} module.
-Since a non-rotating PSF produces an artificial preferred direction, which can translate to galaxy shapes through errors in the process of deconvolvution, properly accounting for the averaging of the PSF orientation across exposures due to the survey dithering strategy is essential for a realistic shear calibration estimate.
+Since a non-rotating PSF produces an artificial preferred direction, which can translate to galaxy shapes through errors in the process of deconvolution, properly accounting for the averaging of the PSF orientation across exposures due to the survey dithering strategy is essential for a realistic shear calibration estimate.
 There has been an update in the \texttt{galsim.roman} module to correctly rotate the PSF given the WCS of the SCA in a given telescope pointing.
@@
 This is mitigated if we instead construct small, local coadds (at the size of an object postage stamp cutout in this work), which is a method also utilized in \textsc{metadetection}.
-If we take advantage of fitting an object in the coadd instead of fitting multiple images of each object in each filter, we can save a factor of approx.
-six in computing time, which is the average number of exposures from the reference survey.
+If we take advantage of fitting an object in the coadd instead of fitting multiple images of each object in each filter, we can save a factor of approximately six in computing time, since there are on average six exposures at any point on the sky in the reference survey.
 Additionally, coadding is one way to reduce the effect of the undersampling of the images since the coadd can be better sampled due to dithering.
@@
 The examples of the low and high S/N galaxy and PSF images for single-epoch and coadd are shown in Figure \ref{fig:singlecoadd}.
-The detailed overview of the coadd process in \texttt{psc} is described in in Sec.
-\ref{subsec:psc}.
+The detailed overview of the coadd process in \texttt{psc} is described in in Sec.~\ref{subsec:psc}.
 
@@
 With this calibration method, we hope to significantly reduce some of the shear calibration bias T21 measured in order to make comparisons of effects contributing to the bias more realistic and meaningful as we explore future \emph{Roman} pipeline development.
-The detailed overview of \textsc{metacalibration} can be found in Sec.\ref{subsec:mcal}.
+The detailed overview of the \textsc{metacalibration} bootstrapper method can be found in Sec.\ref{sec:background}.
     %\item (Any other changes?)
@@
 \subsection{Simulation Runtime, Data Products, and Data Access}
-The simulations here match those produced in T21, but with different true shear values, and so information about processing and data volume prior to the processing additions described in this paper match that provided in App.
-D of T21.
+The simulations here match those produced in T21, but with different true shear values \textcolor{red}{and the updates mentioned in Sec.
+\ref{subsec:updates}}, and so information about processing and data volume prior to the processing additions described in this paper match that provided in App.~D of T21.
 The runtime of the shape measurement per MEDS region in the simulations and data volume on disk of the full shape catalogs (5 \textsc{metacalibration} catalogs for one of four shear sets) is summarized in Table \ref{tab:data} for each of the different simulation runs.
-The simulations are run on the Duke Compute Cluster,\footnote{\url{https://oit-rc.pages.oit.duke.edu/rcsupportdocs/dcc/}}, with solid-state disks for the simulation I/O.
-The time it takes to process one MEDS file is shown.
+The simulations are run on the Duke Compute Cluster\footnote{\url{https://oit-rc.pages.oit.duke.edu/rcsupportdocs/dcc/}}, with solid-state disks for the simulation I/O.
+The time it takes to process one MEDS file is shown in the table.
 The simulation is composed of a total of 480 MEDS files, for a total run time of about 2381 CPU hours for the multi-band coadd measurement.
@@
     Bandpass & H158 \\
-    Half-light radius & 1.0 arcsec\\
-    Stamp size & 32 pixels each side\\
+    Galaxy half-light radius & 1.0 arcsec\\
+    Stamp size & Multiples of 32 pixels each side\\
     \hline
@@
 For all the simple simulation runs, we used the Gaussian galaxy profile and the magnitude for each object is drawn randomly from the \emph{CANDELS} catalog.
-}
+For the stamp size, the multiplying factor was chosen so that 99.5\% of the flux is in the stamp.}
     \label{tab:params}
@@
 	\end{tabular}
-	\caption{This table compares the shear calibration bias, both multiplicative and additive bias for different simulation runs.
+	\caption{This table compares the shear calibration bias, both multiplicative and additive bias for different simple simulation runs.
 In each simulation except the first row, 5 million objects were simulated.
-We simulated 15 million objects for the first row to obtain enough uncertainties.}
+We simulated 15 million objects for the first and last row to obtain sufficiently small uncertainties.}
 	\label{tab:simple_sim_result}
@@
     \setlength\itemsep{1em}
-    \item Finds the wcs of the first exposure of the object.
-    \item Translates the original wcs to a flat wcs, because it produces more stable results with \texttt{ngmix}.
+    \item Finds the WCS of the first exposure of the object.
+    \item Translates the original WCS to a flat WCS, because it produces more stable results with \texttt{ngmix}.
     \item Creates the coadd stamp with 0.8 $\times$ original pixel scale.
@@
 The S/N of the coadd image is S/N=110.
-Finally, the right-most panel shows the coadded multi-band PSF in a log scale.}
+Finally, the right-most panel shows the coadded multi-band PSF in a log scale.
+\textcolor{red}{Some zero pixels were produced in the process of making the multi-band coadd PSF.
+}}
     \label{fig:single_to_coadd_rgb}
@@
 Future versions of these measurements should include the ability to provide a better-sampled PSF image for the deconvolution in the measurement.
-We also note that for the reconvolution process in \textsc{metacalibration} we have attempted the measurement with the \texttt{fitgauss} and \texttt{gauss} PSF model to reconvolve the sheared galaxy images, and the measurement with \texttt{fitgauss} model was numerically unstable resulting in the inconsistency between $m_{1}$ and $m_{2}$.
+We also note that for the reconvolution process in \textsc{metacalibration} we have attempted the measurement with the \texttt{fitgauss}\footnote{\textcolor{red}{A round Gaussian PSF model fitted with the original PSF.}} and \texttt{gauss} PSF model to reconvolve the sheared galaxy images, and the measurement with \texttt{fitgauss} model was numerically unstable resulting in the inconsistency between $m_{1}$ and $m_{2}$.
 We, therefore, use the \texttt{gauss} model for the rest of the simulations.
@@
     Shear & $\sigma_{|g|} = 0.3$\\
-    Half-light radius & $10^{-5}$ < T < $10^{4}$\\
+    Galaxy size & $10^{-5}$ < T (\textcolor{red}{arcsec$^2$}) < $10^{4}$\\
     Flux fraction of the bulge  & $\langle f\rangle = 0.5$, $\sigma_{f} = 0.1$\\
-    Total flux & $0$ < F < $10^{6}$\\
+    Total flux & $0$ < F(\textcolor{red}{image units}) < $10^{6}$\\
     \hline
@@
     \centering
-	\includegraphics[width=\textwidth]{true_ngmix_measured_properties.pdf}
+	\includegraphics[width=\textwidth]{true_ngmix_measured_properties_pplt.pdf}
     \caption{This shows the histograms of input and measured galaxy properties in \texttt{ngmix} for single-band coadd and multi-band coadd measurements.
@@
 
-For the single-band measurements, we can use the sampling factor defined in Equation \ref{eqn:sampling} per bandpass to show the relationship between the shear bias and image sampling.
+For the single-band measurements, we can use the sampling factor defined in Equation \eqref{eqn:sampling} per bandpass to show the relationship between the shear bias and image sampling.
 The sampling factor is an indication of how undersampled the image is in each bandpass.
@@
 The additive bias remains at a similar level within uncertainties.
-The estimated additive bias is the same order as that found in the Y3 analysis in DES, which uses a similar shear calibration pipeline.
+\textcolor{red}{\sout{The estimated additive bias is the same order as that found in the Y3 analysis in DES, which uses a similar shear calibration pipeline.}}
 
@@
 The multiplicative and additive bias is, respectively, $m=(-1.13\pm0.60)\%$ and $c=(2.38\pm1.24)\times10^{-4}$.
-These results are again consistent with zero at the 2$\sigma$ level, so we can't conclude more than that this result may be acceptable, without significantly larger simulation volume.
-To reach the requirements level for the \emph{Roman} HLIS, we will likely need approx.
-2000 deg$^{2}$ of simulated imaging for this complex simulation mode.
+These results are again consistent with zero at the 2$\sigma$ level, \textcolor{red}{but we will need significantly larger simulation volume of about 2000 \textrm{deg}$^2$ before we can draw firm conclusion about the performance of multiband measurements.} \textcolor{red}{\sout{we can't conclude more than that this result may be acceptable, without significantly larger simulation volume.}} To reach the requirements level for the \emph{Roman} HLIS, \textcolor{red}{, so we can do back-of-the-envelope calculation (6.25 \textrm{deg}$^2$ \times (0.60/0.032)$^2$)} and we will likely need approx.
+2000 \textrm{deg}$^{2}$ of simulated imaging for this complex simulation mode.
 
@@
 \begin{figure*}
-	\includegraphics[width=\textwidth]{final_result_v4.pdf}
+	\includegraphics[width=\textwidth]{final_result_v4_pplt.pdf}
     \caption{The multiplicative ($m \times 10^2$) (\textbf{left}) and additive ($c \times 10^4$) (\textbf{right}) bias of the single-band single-epoch and coadd measurements.
-From the left and to the right data points, they represent J129 single-epoch, H158 single-epoch, J129 coadd, F184 single-epoch, H158 coadd and F184 coadd measurements.
-The non-calibrated results from the first-generation of the simulations by \cite{2021MNRAS.501.2044T} were $m_1=(-7.56\pm0.19)\%$, $m=(-9.49\pm0.19)\%$ and $c_1=(1.20\pm0.17)\times10^{-3}$, $c_2=(-1.57\pm0.16)\times10^{-3}$.
+From the left to the right data points, they represent the data for each of the J129 single-epoch, H158 single-epoch, J129 coadd, F184 single-epoch, H158 coadd and F184 coadd measurements.\textcolor{red}{The sampling factor on $m_2$ and $c_2$ measurements is shifted by +0.01 for a visualization purpose.} The non-calibrated results from the first-generation of the simulations by \cite{2021MNRAS.501.2044T} were $m_1=(-7.56\pm0.19)\%$, $m=(-9.49\pm0.19)\%$ and $c_1=(1.20\pm0.17)\times10^{-3}$, $c_2=(-1.57\pm0.16)\times10^{-3}$.
 We can conclude that our calibration bias is an order of magnitude smaller than the previous versions of the simulations, and comparable or smaller than the bias-level seen in the Stage-III surveys.}
@@
     \centering
-	\includegraphics[width=\textwidth]{H158_meanshear_measured_properties_perbin_e1_v6.pdf}
+	\includegraphics[width=\textwidth]{H158_meanshear_measured_properties_perbin_e1_v6_pplt.pdf}
     \caption{This shows the mean shear residual ($\Delta e_{1}$; $\langle e_{1,measured} \rangle - \langle e_{1,expected} \rangle$) as a function of various properties of galaxies for H158 single-band single-epochs, coadds, and multi-band measurements.
@@
     \setlength\itemsep{1em}
-    \item \textbf{Simulation Volume}: Expand the simulated area by a factor of four to 20 deg$^{2}$, in order to obtain smaller error bars on the resulting shear calibration biases.
+    \item \textbf{Simulation Volume}: Expand the simulated area by a factor of four to 20 \textrm{deg}$^{2}$, in order to obtain smaller error bars on the resulting shear calibration biases.
+\textcolor{red}{Increasing the simulation volume has more benefits such as an ability to calibrate spatial dependence of shear.
+This will also allow us to measure two-point correlation function and propagate the biases into the cosmological analysis.
+}
 
-    \item \textbf{Near-Infrared Detector Effects}: Incorporate more realistic detector effects as measured in tests on the flight-candidate detectors and produce two versions of the simulation with and without them to determine the impact on the final cosmology result.
+    \item \textcolor{red}{\textbf{Pixel Masks? - see chris's comments.}}
+
+    \item \textbf{Near-Infrared Detector Effects}: Incorporate more realistic detector effects as measured in tests on the flight detectors (\citealt{2020JATIS...6d6001M}) and produce two versions of the simulation with and without them to determine the impact on the final cosmology result.
+\textcolor{red}{The soon-to-be incorporated detector effects that are not simulated in this paper include, relative quantum efficiency, quantum yield, charge diffusion, brighter-fatter effect, burn-in, count rate non-linearity, classical non-linearity, vertical trailing pixel effect, bad pixels, gain, and bias frame.}
 

### 2022-03-15 paper_v3.tex
v4.2 - submission

@@
 \normalem
-\title[Metacalibration for the Roman High-Latitude Imaging Survey]{Weak gravitational lensing shear \textcolor{red}{estimation} with \textsc{metacalibration} for the \emph{Roman} High-Latitude Imaging Survey}
+\title[Metacalibration for the Roman High-Latitude Imaging Survey]{Weak gravitational lensing shear estimation with \textsc{metacalibration} for the \emph{Roman} High-Latitude Imaging Survey}
 
@@
 \newauthor{
-Ami Choi,$^{7}$
+Heyang Long,$^{4,5}$ Ami Choi,$^{7}$
 Tianqing Zhang,$^{3}$}\\
@@
 These results are all consistent with zero within 1--2$\sigma$, indicating we are currently limited by our simulated survey volume.
-Further work on testing the shear calibration methodology is necessary at higher precision to reach the levels of the \textit{Roman} requirements, in particular in the presence of blending.
+Further work on testing the shear calibration methodology is necessary at higher precision to reach the level of the \textit{Roman} requirements, in particular in the presence of blending.
 %In the future, we will need to substantially increase the simulation volume by $\sim$400 (about the same size as the survey area of 2000 deg$^{2}$) to reach the precision necessary to test the HLIS requirements.
-Current results demonstrate, however, that the \textsc{metacalibration} method can work on undersampled space-based imaging data at the levels comparable to the requirements levels of current weak lensing surveys.
+Current results demonstrate, however, that the \textsc{metacalibration} method can work on undersampled space-based Roman imaging data at levels comparable to the requirements of current weak lensing surveys.
 \end{abstract}
@@
 Within this sector, dark energy accounts for the accelerating expansion of the universe (e.g., \citealt{1998AJ....116.1009R, 1999AIPC..478..129P}) and the combination of dark energy and dark matter are responsible for the observed growth of large-scale structure (\citealt{2015RPPh...78h6901K, 2017grle.book.....D}).
-\textcolor{red}{The growth can be studied by measuring quantities that are sensitive to the way light rays are deflected by intervening mass in the Universe, a physical phenomenon called gravitational lensing.} “Weak” gravitational lensing causes a slight distortion to intrinsic galaxy shapes called shear.
+The growth of structure can be studied by measuring quantities that are sensitive to the way light rays are deflected by intervening mass in the Universe, a physical phenomenon called gravitational lensing.
+“Weak” gravitational lensing causes a slight distortion to intrinsic galaxy shapes called shear.
 By detecting millions of these gravitationally lensed galaxies and computing their ensemble shear, we can explore the dark matter density and the amplitude of matter fluctuation in the universe (e.g., \citealt{2001PhR...340..291B}).
@@
     \item inhomogeneous observing strategy,
-    \item \textcolor{red}{atmospheric and} instrumentation effects,
+    \item atmospheric and instrumentation effects,
     \item post-processing pipelines such as image coaddition and object detection.
@@
 We quantify this impact as shear calibration bias.
-Several shear calibration and bias mitigation efforts have been inspired by the outcomes of the Shear TEsting Programme (STEP; \citealt{2006MNRAS.368.1323H, 2007MNRAS.376...13M}), the GRavitational lEnsing Accuracy Testing challenges (GREAT; \citealt{2010MNRAS.405.2044B, 2013ApJS..205...12K, 2015MNRAS.450.2963M}) \textcolor{red}{and other image simulations work (e.g., \citealt{2017MNRAS.468.3295H})}, to meet the requirements for the current imaging surveys.
+Several shear calibration and bias mitigation efforts have been inspired by the outcomes of the Shear TEsting Programme (STEP; \citealt{2006MNRAS.368.1323H, 2007MNRAS.376...13M}), the GRavitational lEnsing Accuracy Testing challenges (GREAT; \citealt{2010MNRAS.405.2044B, 2013ApJS..205...12K, 2015MNRAS.450.2963M}) and other image simulations work (e.g., \citealt{2017MNRAS.468.3295H}), to meet the requirements for the current imaging surveys.
 In particular, one of the state-of-the-art self-calibration methods, \textsc{metacalibration} (\citealt{2017arXiv170202600H, 2017ApJ...841...24S}) has been shown to be able to substantially reduce the significance of shear bias.
 It has been confirmed that shear can be calibrated with \textsc{metacalibration} at the few-percent level in DES (\citealt{2018MNRAS.481.1149Z, 2020arXiv201103408G}), without accounting for galaxy blending and detection.
-Tackling the issue of blending/detection is one key step forward for the DES Y6 analysis and preparatory Rubin LSST work with the shear-dependent detection and calibration technique \textsc{metadetection}\footnote{\textcolor{red}{\textsc{metadetection} reduces a significant amount of shear-dependent detection bias by shearing a small region of the sky and applying detection.} } (\citealt{2020ApJ...902..138S}).
+Tackling the issue of blending/detection is one key step forward for the DES Y6 analysis and preparatory Rubin LSST work with the shear-dependent detection and calibration technique \textsc{metadetection}\footnote{\textsc{metadetection} reduces a significant amount of shear-dependent detection bias by detecting objects after shearing a small region of the sky to measure the shear-dependent detection selection bias.
+} (\citealt{2020ApJ...902..138S}).
 While the major advantage of \textsc{metacalibration} or \textsc{metadetection} is that they can be directly applied to real galaxy images without needing to rely on an ensemble calibration from image simulations, limitations for future surveys are not well-known.
 
-One possible limitation might lie in the effect of undersampled images in space-based surveys like \emph{Euclid} and \emph{Roman}, which will operate at \textcolor{red}{their respective diffraction limits}.
-The \textcolor{red}{Point Spread Function (PSF)} needs to be interpolated and estimated from well-sampled images to accurately deconvolve and measure shapes with, because the \emph{Roman} PSF has a complex structure that cannot be captured in the original undersampled images.
+One possible limitation might lie in the effect of undersampled images in space-based surveys like \emph{Euclid} and \emph{Roman}, which will operate at their respective diffraction limits.
+The Point Spread Function (PSF) needs to be interpolated and estimated from well-sampled images to accurately deconvolve and measure shapes with, because the \emph{Roman} PSF has a complex structure that cannot be captured in the original undersampled images.
 It is, therefore, necessary to build a robust strategy to reconstruct well-sampled images to estimate the PSF to allow unbiased shape measurement.
@@
 In the context of image sampling, the criterion that the sample pixel spacing needs to satisfy is $p < \frac{1}{2u_{\text{max}}}$ ($u_{\text{max}}$ is the maximum spatial bandlimiting frequency).
-\textcolor{red}{The angular resolution of the diffraction-limited system is $\theta = \lambda/D$ (D: the diameter of an effective aperture) and .} Since the spatial bandlimiting frequency in an astronomical image is defined as
+Since the spatial bandlimiting frequency in an astronomical image is defined as
 \begin{equation}
@@
 \end{equation}
-the sampling factor for \textcolor{red}{a space telescope} is defined as 
+the sampling factor for a space telescope is defined as 
 \begin{equation}
@@
 An image with sampling factor $Q=2$ is considered Nyquist-sampled and an image with sampling factor $Q<2$ is undersampled.
-\textcolor{red}{The image samplings for \emph{Roman} are $Q$=0.88, 1.08, 1.31 for J129, H158, and F184 bandpasses respectively.
-}
+The image sampling for \emph{Roman} are $Q$=0.88, 1.08, 1.31 for the J129, H158, and F184 bandpasses respectively.
 
@@
 We call this shear calibration bias and we compute the deviations of the measured gravitational lensing shear $\gamma$ from the input shear.
-\textcolor{red}{Here we define the reduced shear $g \equiv \gamma/(1-\kappa)$, and it is safe to approximate $\gamma \approx g$ in the context of cosmic shear.} In the limit of weak lensing ($\lvert\gamma\rvert\ll1$, $\lvert\kappa\rvert\ll1$) and random intrinsic galaxy shapes, the ensemble average of ellipticities $\langle e \rangle$ of galaxy shapes is directly related to the reduced shear field $g$, and the estimated shear can be written as a linear model with multiplicative ($m_{i}$) and additive bias ($c_{i}$) as described in the equation below (\citealt{2006MNRAS.368.1323H, 2006MNRAS.366..101H, 2007MNRAS.376...13M})
+Here we define the reduced shear $g \equiv \gamma/(1-\kappa)$, and it is safe to approximate $\gamma \approx g$ in the context of cosmic shear.
+In the limit of weak lensing ($\lvert\gamma\rvert\ll1$, $\lvert\kappa\rvert\ll1$) and random intrinsic galaxy shapes, the ensemble average of ellipticities $\langle e \rangle$ of galaxy shapes is directly related to the reduced shear field $g$, and the estimated shear can be written as a linear model with multiplicative ($m_{i}$) and additive bias ($c_{i}$) as described in the equation below (\citealt{2006MNRAS.368.1323H, 2006MNRAS.366..101H, 2007MNRAS.376...13M})
 \begin{equation}
@@
 \end{equation}
-where $i$=(1,2) \textcolor{red}{due to the rotational symmetry of an ellipse} and $g^{\textrm{obs}}_{i}$ is the two-component observed reduced shear after calibrations and $g^{\textrm{true}}_{i}$ is the true shear.
+where $i$=(1,2) are the two components representing an elliptical distortion, which can be derived from the major and minor axes, and $g^{\textrm{obs}}_{i}$ is the two-component observed reduced shear after calibrations and $g^{\textrm{true}}_{i}$ is the true shear.
 The bias can be introduced in places such as PSF modeling, blending, and the undersampling of the image (e.g., \citealt{2018ARA&A..56..393M}).
 Additionally, complex detector effects such as the brighter-fatter effect are potential sources of bias (\citealt{2020PASP..132a4502C}), while it has been shown that for \emph{Roman} the effect of persistence will not be an issue (\citealt{2021arXiv210610273L}).
-Qualitatively, if the recovered shear is biased by 1$\%$ ($m=0.01$), \textcolor{red}{from the cosmic shear power spectrum $S_{8} = \sigma_{8} \sqrt{\Omega_{m}/0.3}$ could be estimated to be biased} about 1.5$\%$ in the final cosmology result.
+Qualitatively, if the recovered shear is biased by 1$\%$ ($m=0.01$), from the cosmic shear power spectrum $S_{8} = \sigma_{8} \sqrt{\Omega_{m}/0.3}$ could be estimated to be biased about 1.5$\%$ in the final cosmology result.
 Thus, quantifying and correcting these biases before the real survey begins is extremely important.
@@
     %\vspace*{-5mm}
-    \caption{We show the recovered multiplicative bias on the shear as a function of applied shear for the choice of the applied shear in our \textcolor{red}{simplified} simulations.
+    \caption{We show the recovered multiplicative bias on the shear as a function of the applied shear in our simplified simulations.
 The presented multiplicative bias is the average of $m_{1}$ and $m_{2}$, and the grey shaded region represents the mission requirement.
@@
 Here, we briefly summarize how \textsc{metacalibration} (\citealt{2017arXiv170202600H, 2017ApJ...841...24S}) calibrates the biased measurement of galaxy ellipticities on the image stamps.
-\textcolor{red}{Each stamp is defined to be an image cutout with one galaxy.} \textsc{metacalibration} creates one unsheared and four artificially-sheared galaxy stamps.
+Each stamp is defined to be an image cutout with one galaxy.
+\textsc{metacalibration} creates one unsheared and four artificially-sheared galaxy stamps.
 Each is deconvolved with the input PSF, left unsheared or sheared with an additional gravitational shear of $\delta g=\pm 0.01$ in the two basis directions ($g_1$, $g_2$) and re-convolved with a new slightly larger isotropic, Gaussian PSF.
-\textcolor{red}{We have adopted to use the Gaussian PSF since it resembles the process in the current surveys and it requires complex operations to use a non-Gaussian PSF for the space-based survey.
-This choice could imply that we potentially isotropize the shapes of galaxies.} \textsc{metacalibration} works under the assumption that the input shear is small, otherwise the recovered shear would be biased without accounting for higher order terms.
+We have chosen to use a Gaussian PSF since it simplifies the following (de)convolution operations and appears to be sufficient at our current testing precision.
+It will need to be verified that this continues to hold at limit of the Roman requirements.
+\textsc{metacalibration} works under the assumption that the input shear is small, otherwise the recovered shear would be biased without accounting for higher order terms.
 It is a balance to choose an input shear that results in higher S/N of the estimated shear bias  and unbiased shear measurement.
@@
 
-In practice, we compute the mean shear response from the four versions of \textsc{metacalibration} catalog using the finite difference method. 
+In practice, we compute the mean shear response from the four sheared versions of \textsc{metacalibration} catalog using the finite difference method. 
 \begin{equation}
@@
 Here, the \emph{Roman} PSF is rendered using the \texttt{galsim.roman} module, which has implemented \emph{Roman}-specific instrument properties such as the PSF and World Coordinate System (WCS) for a given telescope pointing, rotation angle, and SCA.
-\textcolor{red}{Depending on the pointing, the simulated detector effects were added to the images in the following order: reciprocity failure, quantization, dark current, persistence, non-linearity, interpixel capacitance, read noise, and electron-to-ADU conversion (\citealt{2020JATIS...6d6001M}).}
+The simulated detector effects were added to the images in the following order: reciprocity failure, quantization, dark current, persistence, non-linearity, interpixel capacitance, read noise, and electron-to-ADU conversion (\citealt{2020JATIS...6d6001M}).
 
@@
 	%\vspace*{-10mm}
-    \caption{\textbf{Top Row}: the first observation of the single-epoch images and its coadded image, and the corresponding single-epoch and coadded oversampled PSF images for a galaxy with low signal-to-noise ratio (S/N=20.16 in a single-epoch image).
-\textbf{Bottom Row}: the same as above for a galaxy with high signal-to-noise ratio (S/N=390.47 in a single-epoch image).
+    \caption{\textbf{Top Row}: the first observation of the single-epoch images and its coadded image, and the corresponding single-epoch and coadded oversampled PSF images for a galaxy with low signal-to-noise ratio (S/N=20 in a single-epoch image).
+\textbf{Bottom Row}: the same as above for a galaxy with high signal-to-noise ratio (S/N=390 in a single-epoch image).
 The H158 bandpass was used to represent images here.
@@
 For these reasons, we explore utilizing this coadding scheme for the \emph{Roman} galaxies.
+In future work, a coaddition algorithm could be used such as \textsc{imcom\footnote{\url{https://github.com/barnabytprowe/imcom}} (\citealt{2011ApJ...741...46R})} that explicitly addresses the undersampling in a way that \texttt{psc} does not.
 The examples of the low and high S/N galaxy and PSF images for single-epoch and coadd are shown in Figure \ref{fig:singlecoadd}.
@@
 \subsection{Simulation Runtime, Data Products, and Data Access}
-The simulations here match those produced in T21, but with different true shear values \textcolor{red}{and the updates mentioned in Sec.
-\ref{subsec:updates}}, and so information about processing and data volume prior to the processing additions described in this paper match that provided in App.~D of T21.
+The simulations here match those produced in T21, but with different true shear values and the updates mentioned in Sec.
+\ref{subsec:updates}, and so information about processing and data volume prior to the processing additions described in this paper match that provided in App.~D of T21.
 The runtime of the shape measurement per MEDS region in the simulations and data volume on disk of the full shape catalogs (5 \textsc{metacalibration} catalogs for one of four shear sets) is summarized in Table \ref{tab:data} for each of the different simulation runs.
@@
 
-The new measurement catalogs produced in this work are available by request to the authors.
 \begin{table}
@@
 \label{sec:methods}
-Our goal is to test whether the recovered shear with \textsc{metacalibration} are non-biased for \emph{Roman} and to understand the factors that might contribute to the non-negligible bias.
-In order to do so, we need to build measurement pipelines within the current simulation framework that produces a final calibrated shear measurement.
-In this section, we present in detail how coadd images are produced with \texttt{psc} from the undersampled single-epoch images and how \textsc{metacalibration} is implemented to calibrates the measured shear using the \textsc{metacalibration} catalog.
+Our goal is to test whether the recovered shear with \textsc{metacalibration} is non-biased for \emph{Roman} and to understand the factors that might contribute to any non-negligible bias.
+In order to do so, we need to build measurement pipelines within the current simulation framework that produce a final calibrated shear measurement.
+In this section, we present in detail how coadd images are produced with \texttt{psc} from the undersampled single-epoch images and how \textsc{metacalibration} is implemented to calibrate the measured shear.
 
@@
 It is also beneficial to use this method because we need coadds which can be directly injected into the shape measurement pipeline in memory rather than written as images to disk due to the number of cutouts we have to process.
-We specifically use \texttt{psc} (postage stamp coadds) as our coadding process.
+We specifically use the simple interpolation-based coadding method using \texttt{GalSim}, \texttt{psc} (postage stamp coadds), as our coadding process.
+While this method does not explicitly account for undersampling of the images and will produce aliasing at some level, we find that this is not an important factor at our current precision of tests in this work.
+Future work can explore more principled methods like \textsc{imcom} (\citealt{2011ApJ...741...46R}) that explicitly account for the undersampling of space-based imaging like our Roman image simulation.
 
@@
 For each exposure of the object we render the \emph{Roman} PSF with a stamp size of 32 pixels at the galaxy centroid.
+This choice of stamp size ends up losing about 2-4\% of the total flux of the PSF.
+However, we have no evidence that this impacts the shape measurement.
 We modified the original \texttt{psc} code to improve performance for this \emph{Roman} study, and these modifications are explained below with the general coadding process in \texttt{psc}.
@@
 Finally, the right-most panel shows the coadded multi-band PSF in a log scale.
-\textcolor{red}{Some zero pixels were produced in the process of making the multi-band coadd PSF.
-}}
+Some pixels with negative values were produced in the process of making the multi-band coadd PSF due to limitations in the fast interpolant functions used, but this has no impact on the results.
+}
     \label{fig:single_to_coadd_rgb}
@@
 Future versions of these measurements should include the ability to provide a better-sampled PSF image for the deconvolution in the measurement.
-We also note that for the reconvolution process in \textsc{metacalibration} we have attempted the measurement with the \texttt{fitgauss}\footnote{\textcolor{red}{A round Gaussian PSF model fitted with the original PSF.}} and \texttt{gauss} PSF model to reconvolve the sheared galaxy images, and the measurement with \texttt{fitgauss} model was numerically unstable resulting in the inconsistency between $m_{1}$ and $m_{2}$.
+We also note that for the reconvolution process in \textsc{metacalibration} we have attempted the measurement with the \texttt{fitgauss}\footnote{An isotropic Gaussian PSF model fitted to the original PSF.} and \texttt{gauss} PSF model to reconvolve the sheared galaxy images, and the measurement with \texttt{fitgauss} model was numerically unstable resulting in the inconsistency between $m_{1}$ and $m_{2}$.
 We, therefore, use the \texttt{gauss} model for the rest of the simulations.
@@
     \centering
-    \begin{tabular}{|p{3cm}||p{3cm}|p{3cm}|p{3cm}|}
+    \begin{tabular}{l l l}
     \hline
-    Prior & Value \\
+    Parameter & &  Prior \\
     \hline
-    Pixel centroid offset & 0 < $p_{x,y}$ < 0.11\\
-    Shear & $\sigma_{|g|} = 0.3$\\
-    Galaxy size & $10^{-5}$ < T (\textcolor{red}{arcsec$^2$}) < $10^{4}$\\
-    Flux fraction of the bulge  & $\langle f\rangle = 0.5$, $\sigma_{f} = 0.1$\\
-    Total flux & $0$ < F(\textcolor{red}{image units}) < $10^{6}$\\
+    Pixel centroid offset & Flat & 0 < $p_{x,y}$ < 0.11\\
+    Shear & Gaussian &$\langle g\rangle = 0.0$, $\sigma_{|g|} = 0.3$\\
+    Galaxy size & Flat &$10^{-5}$ < T (arcsec$^2$) < $10^{4}$\\
+    Flux fraction of the bulge  & Gaussian &$\langle f\rangle = 0.5$, $\sigma_{f} = 0.1$\\
+    Total flux & Flat &$0$ < F (ADU) < $10^{6}$\\
     \hline
     \end{tabular}
-    \caption{List of prior values used for the Gaussian mixture fit.}
+    \caption{List of prior values and distributions used for the Gaussian mixture fit.}
     \label{tab:priors}
@@
 The covariances are computed using the bootstrap estimate of standard error.
-From the observed ellipticity catalogs, we randomly choose $n$ samples with replacement which is the length of the data set, and compute the distributions of multiplicative ($f^{m}_{i}$) and additive ($f^{c}_{i}$) bias for $i=1,2,3,...,N$ in the same way as above.
+From the observed ellipticity catalogs, we randomly choose $n$ samples with replacement, where $n$ is the length of the data set, and compute the distributions of multiplicative ($f^{m}_{i}$) and additive ($f^{c}_{i}$) bias for $i=1,2,3,...,N$ ($N$ is the number of times the resampling is carried out) in the same way as above.
 The distributions are then used to compute the error estimate,
@@
 \subsection{Statistics of the Shape Catalog}
-Galaxies that are simulated are pre-selected to meet the \emph{Roman} Weak Lensing selection used for the mission requirements.
+Galaxies that are simulated are pre-selected to meet the \emph{Roman} Weak Lensing selection used for the mission requirements (\citealt{2018arXiv180403628D, 2021MNRAS.501.2044T}).
 In total, the galaxy photometry catalog contains 907,170 galaxies and from this catalog we simulated galaxies on 18 SCAs across 198 pointings for F184, 227 pointings for H158, and 238 pointings for J129 bandpass.
@@
 	\includegraphics[width=\textwidth]{true_ngmix_measured_properties_pplt.pdf}
-    \caption{This shows the histograms of input and measured galaxy properties in \texttt{ngmix} for single-band coadd and multi-band coadd measurements.
-\textbf{Left}: the input magnitudes of galaxies for all the 3 filters we have used to measure shapes.
-The mean magnitude for J129 H158, F184 are respectively 23.273, 23.098, 22.976.
+    \caption{The histograms of input and measured galaxy properties in \texttt{ngmix} for single-band coadd and multi-band coadd measurements.
+\textbf{Left}: the input magnitudes of galaxies for all three filters we have used to measure shapes.
+The mean magnitude for J129, H158, F184 are respectively 23.3, 23.1, 23.0.
 \textbf{Middle}: the signal-to-noise ratio of the single-band and multi-band coadds.
-The mean S/N for JHF and multi-band are respectively 117.45, 161.64, 116.57, 205.39.
-\textbf{Right}: the input galaxy size for H158 where we approximated from the half-light radius, and the measured galaxy size for the single-band and the multi-band coadd in units of arcsec$^2$.
-The mean size for input and measured galaxies are 0.149 and 0.087 arcsec$^2$ for H158.
-It is important to note that there exists the discrepancy between the input and measured size.
-The measured size is the size of the best fit Gaussian (maximum likelihood in this case) and it is not expected to match with the true size based on the half-light radius of the nominal profiles.}
+The median S/N for JHF and multi-band are respectively 29, 39, 27, and 50.
+\textbf{Right}: the input galaxy size for H158 approximated from the half-light radius, and the measured galaxy size for the single-band and the multi-band coadd in units of arcsec$^2$.
+The mean size for input and measured galaxies are 0.15 and 0.09 arcsec$^2$ for H158.
+The measured size is the size of the best fit Gaussian (maximum likelihood in this case) and it is not expected to match with the true size based on the half-light radius of the nominal (non-Gaussian) profiles.}
     \label{fig:ngmix_measured_properties}
@@
 The sampling factor for each single-band measurement can be found in Table \ref{tab:bias_summary}.
-This relationship between sampling factor and shear bias was previously explored in \citealt{2021MNRAS.502.4048K} using \emph{Euclid} simulation with different shape measurement algorithms, where they found that the estimated multiplicative bias has a relatively large dependence on the sampling factor.
+This relationship between sampling factor and shear bias was previously explored in K21 using \emph{Euclid} simulation with different shape measurement algorithms, where they found that the estimated multiplicative bias has a relatively large dependence on the sampling factor.
 Their result can be extrapolated to our single-band single-epoch results.
@@
 
-When the coadded images for each filter are used, the recovered multiplicative shear bias is about half the single-epoch cases due to the increased S/N and better image sampling, and is consistent with zero at the $\sim$1$\sigma$ level.
+When the coadded images for each filter are used, the recovered multiplicative shear bias is about half the single-epoch cases, and is consistent with zero at the $\sim$1$\sigma$ level.
 The additive bias remains at a similar level within uncertainties.
-\textcolor{red}{\sout{The estimated additive bias is the same order as that found in the Y3 analysis in DES, which uses a similar shear calibration pipeline.}}
 
@@
 The multiplicative and additive bias is, respectively, $m=(-1.13\pm0.60)\%$ and $c=(2.38\pm1.24)\times10^{-4}$.
-These results are again consistent with zero at the 2$\sigma$ level, \textcolor{red}{but we will need significantly larger simulation volume of about 2000 \textrm{deg}$^2$ before we can draw firm conclusion about the performance of multiband measurements.} \textcolor{red}{\sout{we can't conclude more than that this result may be acceptable, without significantly larger simulation volume.}} To reach the requirements level for the \emph{Roman} HLIS, \textcolor{red}{, so we can do back-of-the-envelope calculation (6.25 \textrm{deg}$^2$ \times (0.60/0.032)$^2$)} and we will likely need approx.
-2000 \textrm{deg}$^{2}$ of simulated imaging for this complex simulation mode.
+These results are again consistent with zero at the 2$\sigma$ level, but have a large uncertainty relative to the Roman mission requirements.
+Scaling simply by volume, assuming a Gaussian error distribution, we would need a significantly larger simulation volume of about 2000 \textrm{deg}$^2$ in this complex simulation mode to draw firm conclusion about the performance of multiband measurements.
+This is comparable to the area of the reference Roman survey.
 
 To further explore the shape catalogs, we performed a set of basic null tests and show representative results for $e_1$ for the the H158 single-epoch and coadd catalogs, and multi-band coadd catalog.
-The null tests should show that the mean shear residual ($\langle \Delta e_{1} \rangle$) should be zero (flat) in the absence of any systematic biases.
+The null tests should show that the mean shear residual ($\langle \Delta e_{1} \rangle$) should be zero (flat as a function of galaxy properties) in the absence of any systematic biases.
 Figure \ref{fig:meanshear} shows the relationship between the mean shear and several input and measured properties of galaxies for all the measurement cases.
@@
 		\hline
-		simulation variants & sampling factor ($Q$) & $m_{1}\times10^{-2}$ & $m_{2}\times10^{-2}$ & $c_{1}\times10^{-4}$ & $c_{2}\times10^{-4}$\\
+		simulation variants & sampling factor ($Q$) & $m_{1}\times10^{2}$ & $m_{2}\times10^{2}$ & $c_{1}\times10^{4}$ & $c_{2}\times10^{4}$\\
 		\hline
@@
 	\end{tabular}
-	\caption{This table compares the shear calibration bias, both multiplicative and additive bias for different simulation runs.}
+	\caption{A comparison of the shear calibration bias, both multiplicative and additive bias, for different simulation runs.}
 	\label{tab:bias_summary}
@@
     \caption{The multiplicative ($m \times 10^2$) (\textbf{left}) and additive ($c \times 10^4$) (\textbf{right}) bias of the single-band single-epoch and coadd measurements.
-From the left to the right data points, they represent the data for each of the J129 single-epoch, H158 single-epoch, J129 coadd, F184 single-epoch, H158 coadd and F184 coadd measurements.\textcolor{red}{The sampling factor on $m_2$ and $c_2$ measurements is shifted by +0.01 for a visualization purpose.} The non-calibrated results from the first-generation of the simulations by \cite{2021MNRAS.501.2044T} were $m_1=(-7.56\pm0.19)\%$, $m=(-9.49\pm0.19)\%$ and $c_1=(1.20\pm0.17)\times10^{-3}$, $c_2=(-1.57\pm0.16)\times10^{-3}$.
+From the left to the right data points, they represent the data for each of the J129 single-epoch, H158 single-epoch, J129 coadd, F184 single-epoch, H158 coadd and F184 coadd measurements.
+The data points for the $m_2$ and $c_2$ measurements are shifted by +0.01 for visual clarity.
+The non-calibrated results from the first-generation of the simulations by \cite{2021MNRAS.501.2044T} were $m_1=(-7.56\pm0.19)\%$, $m_2=(-9.49\pm0.19)\%$ and $c_1=(1.20\pm0.17)\times10^{-3}$, $c_2=(-1.57\pm0.16)\times10^{-3}$.
 We can conclude that our calibration bias is an order of magnitude smaller than the previous versions of the simulations, and comparable or smaller than the bias-level seen in the Stage-III surveys.}
@@
 	\includegraphics[width=\textwidth]{H158_meanshear_measured_properties_perbin_e1_v6_pplt.pdf}
-    \caption{This shows the mean shear residual ($\Delta e_{1}$; $\langle e_{1,measured} \rangle - \langle e_{1,expected} \rangle$) as a function of various properties of galaxies for H158 single-band single-epochs, coadds, and multi-band measurements.
+    \caption{The mean shear residual ($\langle \Delta e_{1} \rangle$; $\langle e_{1,\text{measured}} \rangle - \langle e_{1,\text{expected}} \rangle$) as a function of various properties of galaxies for H158 single-band single-epochs, coadds, and multi-band measurements.
 We are only showing the $e_1$ residual because $e_{2}$ showed similar behaviors in each test.
-\textbf{Left}: the measured S/N shows a null signal.
-\textbf{Middle}: the true galaxy size shows a null signal.
-\textbf{Right}: the measured galaxy size shows a null signal.
+We find results that are consistent with a null signal for signal-to-noise (left), true galaxy size (middle), and measured galaxy size (right).
 The mean shear is computed with the shear response and selection response in each bin to account for the selection bias.}
@@
     \item \textbf{Simulation Volume}: Expand the simulated area by a factor of four to 20 \textrm{deg}$^{2}$, in order to obtain smaller error bars on the resulting shear calibration biases.
-\textcolor{red}{Increasing the simulation volume has more benefits such as an ability to calibrate spatial dependence of shear.
-This will also allow us to measure two-point correlation function and propagate the biases into the cosmological analysis.
-}
+Increasing the simulation volume has additional benefits beyond a more precise bias estimate, such as the ability to calibrate spatial dependence of shear and to measure two-point correlation function and propagate the biases into a cosmological analysis.
 
-    \item \textcolor{red}{\textbf{Pixel Masks? - see chris's comments.}}
+    \item \textbf{Pixel Masks}: Future versions of the simulations will take into account complex pixel masking of detector non-idealities, such as hot or dead pixels.
+This masking will be propagated through the analysis to provide realistic masking challenges.
 
     \item \textbf{Near-Infrared Detector Effects}: Incorporate more realistic detector effects as measured in tests on the flight detectors (\citealt{2020JATIS...6d6001M}) and produce two versions of the simulation with and without them to determine the impact on the final cosmology result.
-\textcolor{red}{The soon-to-be incorporated detector effects that are not simulated in this paper include, relative quantum efficiency, quantum yield, charge diffusion, brighter-fatter effect, burn-in, count rate non-linearity, classical non-linearity, vertical trailing pixel effect, bad pixels, gain, and bias frame.}
+The detector effects that are not simulated in this paper but will be incorporated are relative quantum efficiency, quantum yield, charge diffusion, brighter-fatter effect, burn-in, count rate non-linearity, classical non-linearity, vertical trailing pixel effect, bad pixels, gain, and the bias frame.
 
-    \item \textbf{Image Coaddition}: We will implement a new coaddition strategy that coadds the whole scene instead of individual stamp cutouts using  \texttt{AstroDrizzle}\footnote{\url{https://github.com/spacetelescope/drizzlepac}}: A Python implementation of MultiDrizzle which was used for \emph{Hubble} Space Telescope (\citealt{2003hstc.conf..325B}).
+    \item \textbf{Image Coaddition}: As one of the scene coadd algorithms, we will implement a new coaddition strategy that coadds the whole scene instead of individual stamp cutouts using  \texttt{AstroDrizzle}\footnote{\url{https://github.com/spacetelescope/drizzlepac}}: A Python implementation of MultiDrizzle which was used for \emph{Hubble} Space Telescope (\citealt{2003hstc.conf..325B}).
 With \texttt{AstroDrizzle}, we are able to further mitigate the effect of undersampling in the \emph{Roman} images with smaller coadd pixel scales.
 We expect this to further reduce the measured shear bias based on its trend with sampling factor.
+As a more mathematically-principled method that directly accounts for the undersampling of the images, we can also evaluate the use of, e.g., the \textsc{imcom}) algorithm (\citealt{2011ApJ...741...46R}) in the future.
 
@@
 
-In this paper, we explored the performance of the \textsc{metacalibration} shape measurement calibration algorithm and presented the first shear calibration result on a realistic simulated version of the reference \emph{Roman} HLIS.
+In this paper, we explored the performance of the \textsc{metacalibration} shape measurement calibration algorithm and presented the first shear calibration result without the effect of blending on a realistic simulated version of the reference \emph{Roman} HLIS.
 Accurately characterizing how much shear estimates are biased using realistic simulated survey images is a requirement to successfully complete the weak lensing program of the \emph{Roman} HLIS.
@@
 We thank Matthew Becker and Erin Sheldon for the useful discussions on the use of \texttt{ngmix}, and Arun Kannawadi for discussions about related \emph{Euclid} shape measurement work.
-This work was supported by NASA Grant 15-WFIRST15-0008 as part of the Roman Cosmology with the High-Latitude Survey Science Investigation Team (https: //www.roman-hls-cosmology.space/).
+This work was supported by NASA Grant 15-WFIRST15-0008 as part of the Roman Cosmology with the High-Latitude Survey Science Investigation Team (\url{https: //www.roman-hls-cosmology.space/}).
 This work used resources from the Duke Compute Cluster.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% \section*{Data Availability}
+\section*{Data Availability}
 
-% The inclusion of a Data Availability Statement is a requirement for articles published in MNRAS.
-Data Availability Statements provide a standardised format for readers to understand the availability of data underlying the research results described in the article.
-The statement may refer to original data generated in the course of the study or to third-party data analysed in the article.
-The statement should describe and provide means of access, where possible, by linking to the data or providing the required accession numbers for the relevant databases or DOIs.
+The new measurement catalogs produced in this work are available on reasonable request to the authors.
 

### 2022-03-23 paper_v3.tex
mnras submitted v1

@@
-% mnras_template.tex 
-%
-% LaTeX template for creating an MNRAS paper
-%
-% v3.0 released 14 May 2015
-% (version numbers match those of mnras.cls)
-%
-% Copyright (C) Royal Astronomical Society 2015
-% Authors:
-% Keith T. Smith (Royal Astronomical Society)
-
-% Change log
-%
-% v3.0 May 2015
-%    Renamed to match the new package name
-%    Version number matches mnras.clshttps://www.overleaf.com/project/605371a91cecb490b3d4a73e
-%    A few minor tweaks to wording
-% v1.0 September 2013
-%    Beta testing only - never publicly released
-%    First version: a simple (ish) template for creating an MNRAS paper
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \documentclass[fleqn,usenatbib]{mnras}
-% MNRAS is set in Times font. If you don't have this installed (most LaTeX
-% installations will be fine) or prefer the old Computer Modern fonts, comment
-% out the following line
 \usepackage{newtxtext,newtxmath}
-% Depending on your LaTeX fonts installation, you might get better results with one of these:
-%\usepackage{mathptmx}
-%\usepackage{txfonts}
-
-% Use vector fonts, so it zooms properly in on-screen viewing software
-% Don't change these lines unless you know what you are doing
 \usepackage[T1]{fontenc}
 
-% Allow "Thomas van Noord" and "Simon de Laguarde" and alike to be sorted by "N" and "L" etc. in the bibliography.
-% Write the name in the bibliography as "\VAN{Noord}{Van}{van} Noord, Thomas"
 \DeclareRobustCommand{\VAN}[3]{#2}
@@
 \usepackage{physics}
-\usepackage{lineno}
-\linenumbers
+% \usepackage{lineno}
+% \linenumbers
 \usepackage{ulem}
@@
 \usepackage{amsmath}	% Advanced maths commands
-\usepackage{amssymb}	% Extra maths symbols
+% \usepackage{amssymb}	% Extra maths symbols
 \usepackage{xcolor}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%% AUTHORS - PLACE YOUR OWN COMMANDS HERE %%%%%
-
-% Please keep new commands to a minimum, and use \newcommand not \def to avoid
-% overwriting existing commands. Example:
-%\newcommand{\pcm}{\,cm$^{-2}$}	% per cm-squared
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
-% Title of the paper, and the short title which is used in the headers.
-% Keep the title short and informative.
 \normalem
-\title[Metacalibration for the Roman High-Latitude Imaging Survey]{Weak gravitational lensing shear estimation with \textsc{metacalibration} for the \emph{Roman} High-Latitude Imaging Survey}
+\title[Metacalibration for the Roman HLIS]{Weak gravitational lensing shear estimation with \textsc{metacalibration} for the \emph{Roman} High-Latitude Imaging Survey}
 
-% The list of authors, and the short list which is used in the headers.
-% If you need two or more lines of authors, add an extra line using \newauthor
 \author[M. Yamamoto et al.]{
@@
 Heyang Long,$^{4,5}$ Ami Choi,$^{7}$
-Tianqing Zhang,$^{3}$}\\
+and Tianqing Zhang$^{3}$}\\
 % List of institutions
-$^{1}$Department of Physics, Duke University, Durham, NC, 27710\\
+$^{1}$Department of Physics, Duke University, Durham, NC, 27708\\
 $^{2}$Department of Physics and Astronomy, University of Pennsylvania, Philadelphia, PA 19104, USA\\
@@
 \begin{abstract}
+\textcolor{red}{ADD Henk's papers}
 We investigate the performance of the \textsc{metacalibration} shear calibration framework using simulated imaging data for the \emph{Nancy Grace Roman} Space Telescope (\emph{Roman}) reference High-Latitude Imaging Survey (HLIS).
-%These large-scale realistic image simulations are necessary to measure shear bias to confirm that the requirements of the instrument and the overall weak lensing survey strategy are met. 
-The weak lensing program of the \emph{Roman} mission requires the mean weak lensing shear estimate to be calibrated within about 0.03\%.
+The weak lensing program of \emph{Roman} requires the mean weak lensing shear estimate to be calibrated within about 0.03\%.
 To reach this goal, we can test our calibration process with various simulations and ultimately isolate the sources of residual shear biases in order to improve our methods.
-In this work, we build on the Roman HLIS image simulation pipeline in \cite{2021MNRAS.501.2044T} to incorporate several new realistic processing-pipeline updates necessary to more accurately process the imaging data and calibrate the shear.
-We show the first results of this calibration for six \textrm{deg}$^{2}$ of the simulated reference HLIS using \textsc{metacalibration} and compare these results to measurements on more simple, faster Roman-like image simulations.
-In both cases, we neglect the impact of blending of objects.
-We find that in the simplified simulations, \textsc{metacalibration} can calibrate shapes to within $m=(-0.01\pm 0.10)$\%.
-When applied to the current most-realistic version of the simulations, the precision is much lower, with a \textsc{metacalibration} estimate of $m=(-1.34\pm 0.67)$\% for joint multi-band single-epoch measurements and $m=(-1.13\pm 0.60)$\% for multi-band coadd measurements.
+In this work, we build on the HLIS image simulation pipeline to incorporate several more realistic processing-pipeline updates.
+We show the first \textsc{metacalibration} results for six \textrm{deg}$^2$ of the simulated reference HLIS and compare them to measurements on simpler, faster \emph{Roman}-like image simulations.
+We neglect the impact of blending of objects.
+We find in the simplified simulations, \textsc{metacalibration} can calibrate shapes to within $m=(-0.01\pm 0.10)$\%.
+When applied to the current most-realistic version of the simulations, the precision is much lower, with estimates of $m=(-1.34\pm 0.67)$\% for joint multi-band single-epoch measurements and $m=(-1.13\pm 0.60)$\% for multi-band coadd measurements.
 These results are all consistent with zero within 1--2$\sigma$, indicating we are currently limited by our simulated survey volume.
-Further work on testing the shear calibration methodology is necessary at higher precision to reach the level of the \textit{Roman} requirements, in particular in the presence of blending.
-%In the future, we will need to substantially increase the simulation volume by $\sim$400 (about the same size as the survey area of 2000 deg$^{2}$) to reach the precision necessary to test the HLIS requirements.
-Current results demonstrate, however, that the \textsc{metacalibration} method can work on undersampled space-based Roman imaging data at levels comparable to the requirements of current weak lensing surveys.
+Further work on testing the shear calibration methodology is necessary at the precision of the \emph{Roman} requirements, in particular in the presence of blending.
+Current results demonstrate, however, that \textsc{metacalibration} can work on undersampled space-based \emph{Roman} imaging data at levels comparable to requirements of current weak lensing surveys.
 \end{abstract}
 
-% Select between one and six entries from the list of approved keywords.
-% Don't make up new ones.
 \begin{keywords}
@@
 
-% \textcolor{red}{Undersampled images qualitatively have less flux distribution information of objects than the Nyquist-sampled images.
-This particularly affects weak lensing experiments, because it involves measuring galaxy shapes.
-Shape measurement can bias the experiments when the galaxy images are deconvolved with undersampled PSF which does not capture the true flux spread among pixels.
-It is therefore preferred to conduct weak lensing experiments with at least Nyquist-sampled images.
-}
-
 \subsection{Shear Calibration Bias}
@@
 Qualitatively, if the recovered shear is biased by 1$\%$ ($m=0.01$), from the cosmic shear power spectrum $S_{8} = \sigma_{8} \sqrt{\Omega_{m}/0.3}$ could be estimated to be biased about 1.5$\%$ in the final cosmology result.
-Thus, quantifying and correcting these biases before the real survey begins is extremely important.
+Thus, quantifying and correcting these biases before the real survey begins are extremely important.
 
@@
 	\includegraphics[width=\columnwidth]{metacal_bias_shear_pplt.pdf}
-    %\vspace*{-5mm}
     \caption{We show the recovered multiplicative bias on the shear as a function of the applied shear in our simplified simulations.
@@
 We have chosen to use a Gaussian PSF since it simplifies the following (de)convolution operations and appears to be sufficient at our current testing precision.
-It will need to be verified that this continues to hold at limit of the Roman requirements.
+It will need to be verified that this continues to hold at the limit of the Roman requirements.
 \textsc{metacalibration} works under the assumption that the input shear is small, otherwise the recovered shear would be biased without accounting for higher order terms.
@@
 
-After processing the images with \textsc{metacalibration} and measuring the shapes with \texttt{ngmix}, we have 5 shape catalogs for the five values of shear applied by \textsc{metacalibration}.
+After processing the images with \textsc{metacalibration} and measuring the shapes, we have 5 shape catalogs for the five values of shear applied by \textsc{metacalibration}.
 We can then compute the shear response from these catalogs and calculate the calibrated ensemble galaxy shears.
@@
 
-In practice, we compute the mean shear response from the four sheared versions of \textsc{metacalibration} catalog using the finite difference method. 
+In practice, we compute the mean shear response from the four sheared versions of the \textsc{metacalibration} catalogs using the finite difference method. 
 \begin{equation}
@@
 \end{equation}
-where $e^{+}_{i}$ and $e^{-}_{i}$ is the $i$-th component of the galaxy ellipticity where positive ($+$) or negative ($-$) shear is applied in $i$-th direction.
+where $e^{+}_{i}$ and $e^{-}_{i}$ are the $i$-th component of the galaxy ellipticity where positive ($+$) or negative ($-$) shear is applied in $i$-th direction.
 
@@
 Here, the \emph{Roman} PSF is rendered using the \texttt{galsim.roman} module, which has implemented \emph{Roman}-specific instrument properties such as the PSF and World Coordinate System (WCS) for a given telescope pointing, rotation angle, and SCA.
-The simulated detector effects were added to the images in the following order: reciprocity failure, quantization, dark current, persistence, non-linearity, interpixel capacitance, read noise, and electron-to-ADU conversion (\citealt{2020JATIS...6d6001M}).
+The simulated detector effects were then added to the images in the following order: reciprocity failure, quantization, dark current, persistence, non-linearity, interpixel capacitance, read noise, and electron-to-ADU conversion (\citealt{2020JATIS...6d6001M}).
 
@@
 	\includegraphics[width=\columnwidth]{psf_rotation.pdf}
-% 	\vspace*{-3mm}
     \caption{The rotation of the Roman PSF produced by the \texttt{galsim.roman} module.
@@
 	\includegraphics[width=\textwidth]{lowsnr_highsnr_galaxies_v2.pdf}
-	%\vspace*{-10mm}
     \caption{\textbf{Top Row}: the first observation of the single-epoch images and its coadded image, and the corresponding single-epoch and coadded oversampled PSF images for a galaxy with low signal-to-noise ratio (S/N=20 in a single-epoch image).
@@
 The H158 bandpass was used to represent images here.
-The PSFs are shown in a log-scale.
 The single-epoch PSFs are almost identical, since there is no visually different feature for modeling them in different dithers and SCAs.
@@
     We have implemented a pixel saturation limit of 100,000 electrons.
-This value is an approximate pixel saturation level, but in the next generation of the simulations we will use a more accurate pixel saturation limit measured directly from the flight candidate detectors.
+This value is an approximate pixel saturation level, but in the next generation of the simulations we will use a more accurate pixel saturation limit measured directly from the flight detectors.
 
@@
 The detailed overview of the \textsc{metacalibration} bootstrapper method can be found in Sec.\ref{sec:background}.
-    %\item (Any other changes?)
 \end{itemize}
@@
     \caption{The runtime for a single CPU and disk size of the shape catalogs for different simulation runs.
-The runtime for multi-band measurements are slower due to having to copy, uncompress, and read from the three MEDS files (each 1GB compressed) for each bandpass.
+The runtime for multi-band measurements is slower due to having to copy, uncompress, and read from the three MEDS files (each 1GB compressed) for each bandpass.
 Runtime for coadd measurements also includes the postage-stamp coadding.}
@@
 \label{subsec:simplesim}
-In addition to the main, realistic simulation of the \emph{Roman} reference HLIS survey, we also produce several sets of much faster, simple simulations  to verify that there are no obvious fundamental sources of systematic biases with using the \textsc{metacalibration} method on undersampled space-based images.
+In addition to the main, realistic simulation of the \emph{Roman} reference HLIS survey, we also produce several sets of much faster, simple simulations  to verify that there are no obvious fundamental sources of systematic biases using the \textsc{metacalibration} method on undersampled space-based images.
 These simple simulations thus play a role in ruling out the sources of systematic biases that may a priori  potentially be a problem in the use of \textsc{metacalibration} with space-based images.
@@
 The fixed parameters for the simulations are listed in Table \ref{tab:params}.
-We fix the original pixel scale of the \emph{Roman}, bandpass, input galaxy size and stamp size.
+We fix the original pixel scale of the \emph{Roman}, bandpass and input galaxy size.
 With these parameters, we simulated images with varying galaxy model profile, PSF model profile, artificial shear, and background noise level, without any complications in the images and pipelines such as detector effects and coaddition.
@@
 This test should validate that the \textsc{metacalibration} process can tolerate the induced correlation of Poisson noise in the object profiles during the \textsc{metacalibration} shearing process, since it is not currently symmetrized in the process as the background noise field is (\citealt{2017ApJ...841...24S}).
-We find that this result is also consistent with zero, so we can confirm that the treatment of correlated object Poisson noise does not trigger any bias at the level we can probe with the current simulations.
+We find that this result is also consistent with zero, so we can confirm that the treatment of correlated Poisson noise does not trigger any bias at the level we can probe with the current simulations.
 
@@
 	\caption{This table compares the shear calibration bias, both multiplicative and additive bias for different simple simulation runs.
-In each simulation except the first row, 5 million objects were simulated.
+In each simulation except the first and last row, 5 million objects were simulated.
 We simulated 15 million objects for the first and last row to obtain sufficiently small uncertainties.}
@@
 2002) or \textsc{drizzle} (\citealt{2002PASP..114..144F}).
-However, we decided to coadd the postage-stamp cutouts simplify the treatment of the coadd PSF.
+However, we decided to coadd the postage-stamp cutouts to simplify the treatment of the coadd PSF.
 It is also beneficial to use this method because we need coadds which can be directly injected into the shape measurement pipeline in memory rather than written as images to disk due to the number of cutouts we have to process.
@@
 While this method does not explicitly account for undersampling of the images and will produce aliasing at some level, we find that this is not an important factor at our current precision of tests in this work.
-Future work can explore more principled methods like \textsc{imcom} (\citealt{2011ApJ...741...46R}) that explicitly account for the undersampling of space-based imaging like our Roman image simulation.
+Future work can explore more principled methods like \textsc{imcom} (\citealt{2011ApJ...741...46R}) that explicitly account for the undersampling of space-based imaging like our Roman image simulations.
 
@@
 
-% \begin{figure}
-% 	\includegraphics[width=\columnwidth]{psf_differences_v2.pdf}
-%     % \vspace*{-5mm}
-%     \caption{The left and middle panels illustrate the coadded \emph{Roman} PSF at its original pixel scale and the coadded PSF with a pixel scale that is generated with a pixel scale that is smaller by a factor of 4 and then down-sampled to this original pixel scale.
-These are visualized in a log scale.
-The right panel shows the difference image between the two PSF images.
-}
-%     \label{fig:coadd_oversample_res}
-% \end{figure}
-
 \begin{figure*}
 	\includegraphics[width=\textwidth]{coadd_galaxy_example_log_v2.pdf}
-    %\vspace*{-20mm}
     \caption{The left 3 panels show an example of the coadded galaxy images for each filter.
@@
 For the multi-band (H158+J129+F184) coadd measurements, we used objects that are measured successfully in all of the filters and the total number of the recovered objects is 851,821.
-Figures \ref{fig:ngmix_measured_properties} shows the true magnitude and size and the measured signal-to-noise and size of galaxies in the \textsc{metacalibration} shape catalogs.
+Figure \ref{fig:ngmix_measured_properties} shows the true magnitude and size, the measured signal-to-noise and size of galaxies in the \textsc{metacalibration} shape catalogs.
 There is a significant boost in signal-to-noise in the multi-band catalog vs the single-band catalogs.
@@
 
-% \begin{figure}
-% 	\includegraphics[width=\columnwidth]{true_properties.pdf}
-% 	\centering
-%     \caption{The left panel shows the measured magnitudes of galaxies for all the 3 filter we have used to measure shapes.
-The mean magnitude for H158, F184, and J129 are respectively 23.098, 22.976, and 23.273.
-The right panel shows the half-light radius in units of arcsec for H158 for input and measured objects.
-The mean half-light radii for input and measured galaxies are 0.294 and 0.221 arcsec for H158.
-\textcolor{red}{we'll see the result from the new coadd run.
-ngmix output is arcsec2}}
-%     \label{fig:true_properties}
-% \end{figure}
-
 \begin{figure*}
-    %\hspace*{-3.1cm}
     \centering
@@
 \end{figure*}
-
-% \begin{figure*}
-%     %\hspace*{-3.1cm}
-%     \centering
-% 	\includegraphics[width=\textwidth]{hsm_PSF_properties.pdf}
-%     \caption{The histograms of measured PSF properties in adaptive moments method for single-band coadd and multi-band coadd measurements.
-The shape and size of the PSF are shown.
-\textcolor{red}{We may not to present this plot, as it is hard to explain the trends.}}
-%     \label{fig:hsm_measured_properties}
-% \end{figure*}
 
@@
 
-To further explore the shape catalogs, we performed a set of basic null tests and show representative results for $e_1$ for the the H158 single-epoch and coadd catalogs, and multi-band coadd catalog.
-The null tests should show that the mean shear residual ($\langle \Delta e_{1} \rangle$) should be zero (flat as a function of galaxy properties) in the absence of any systematic biases.
+To further explore the shape catalogs, we performed a set of basic null tests and show representative results for $e_1$ for the H158 single-epoch and coadd catalogs, and multi-band coadd catalog.
+The null tests should show that the mean shear residual ($\langle \Delta e_{1} \rangle$) is zero (flat as a function of galaxy properties) in the absence of any systematic biases.
 Figure \ref{fig:meanshear} shows the relationship between the mean shear and several input and measured properties of galaxies for all the measurement cases.
@@
 galaxy properties or vs PSF properties, which are not included in the figure.
-% The mean shear does show a non-linear trend correlating with measured galaxy size.
-To investigate this, we show in Fig.
-\ref{fig:sizecorrelation} how the true and measured shape and size are related.
-Since there is no trend in either true or measured shape and size vs.
-measured or true values, respectively, the trend in the observed shape vs observed size must be a more subtle effect correlating the measured size and shape.
-Since there is no trend vs.
-true properties, we will check if this signal persists in future simulation and pipeline updates.
 
@@
 The data points for the $m_2$ and $c_2$ measurements are shifted by +0.01 for visual clarity.
-The non-calibrated results from the first-generation of the simulations by \cite{2021MNRAS.501.2044T} were $m_1=(-7.56\pm0.19)\%$, $m_2=(-9.49\pm0.19)\%$ and $c_1=(1.20\pm0.17)\times10^{-3}$, $c_2=(-1.57\pm0.16)\times10^{-3}$.
+The non-calibrated results from the first-generation of the simulations by T21 were $m_1=(-7.56\pm0.19)\%$, $m_2=(-9.49\pm0.19)\%$ and $c_1=(1.20\pm0.17)\times10^{-3}$, $c_2=(-1.57\pm0.16)\times10^{-3}$.
 We can conclude that our calibration bias is an order of magnitude smaller than the previous versions of the simulations, and comparable or smaller than the bias-level seen in the Stage-III surveys.}
@@
 \begin{figure*}
-    %\hspace*{-3.5cm}
     \centering
@@
 \end{figure*}
-
-% \begin{figure}
-%     %\hspace*{-3.5cm}
-%     \centering
-% 	\includegraphics[width=\columnwidth]{H158_true_obs_e1_size.pdf}
-%     \caption{This shows the correlations between true and measured shape and size of galaxies.
-\textbf{Left}: the true galaxy shape ($e_1$) in the bins of measured galaxy size (arcsec$^2$).
-\textbf{Right}: the measured galaxy shape ($e_1$) in the bins of input galaxy size (arcsec).}
-%     \label{fig:sizecorrelation}
-% \end{figure}
 
@@
 We expect this to further reduce the measured shear bias based on its trend with sampling factor.
-As a more mathematically-principled method that directly accounts for the undersampling of the images, we can also evaluate the use of, e.g., the \textsc{imcom}) algorithm (\citealt{2011ApJ...741...46R}) in the future.
+As a more mathematically-principled method that directly accounts for the undersampling of the images, we can also evaluate the use of the \textsc{imcom}) algorithm (\citealt{2011ApJ...741...46R}) in the future.
 
@@
 In these simulations we include coadding the single-epoch cutout images and fitting the shapes from multiple bandpasses, and we find that shear estimates with \textsc{metacalibration} are unbiased at the $\sim 2\sigma$ level, which is similar to current-survey constraints.
-At the original image sampling level, the trend in bias vs sampling factor $Q$ are similar to what was previously found for \textsc{metacalibration} bias on undersampled images in the study by K21 using image simulations built for \emph{Euclid}, but at lower levels of bias.
+At the original image sampling level, the trend in bias vs sampling factor $Q$ is similar to what was previously found for \textsc{metacalibration} bias on undersampled images in the study by K21 using image simulations built for \emph{Euclid}, but at lower levels of bias.
 By coadding the cutout images and increasing the image sampling factor, we find that the residual bias is reduced by about a factor of two, but this is similar to the uncertainty.
@@
 \bibliographystyle{mnras}
-\bibliography{example} % if your bibtex file is called example.bib
+\bibliography{paper_v3} % if your bibtex file is called example.bib
 
@@
 
-% \section{Simple Simulations}
-% \label{app:coadd_F}
-% If you want to present additional material which would interrupt the flow of the main paper,
-% it can be placed in an Appendix which appears after the list of references.
-
-% fitgauss or gauss appendix
-% \begin{table*}
-% 	\centering
-% 	\label{tab:bias_table}
-% 	\begin{tabular}[width=0.9*\textwidth]{ c|c|c|c|c|c } 
-% 		\hline
-% 		Bands & simulation variants & $m_{1}\times10^{-2}$ & $m_{2}\times10^{-2}$ & $c_{1}\times10^{-4}$ & $c_{2}\times10^{-4}$\\
-% 		\hline
-% 		\multirow{single-band} & single-epochs (J129) & 1.80$\pm$0.67 & 0.28$\pm$0.69 & 6.48$\pm$1.31 & -0.04$\pm$1.51\\
-% 		& single-epochs (H158) & -1.09$\pm$0.63 & -1.50$\pm$0.68 & 3.90$\pm$1.21 & 1.37$\pm$1.28\\
-% 		& single-epochs (F184) & -0.62$\pm$0.81 & -0.17$\pm$0.79 & 3.92$\pm$1.52 & 2.58$\pm$1.57\\
-% 		& single-band coadd with oversampling (J129) & -0.49$\pm$0.65 & -0.45$\pm$0.62 & 10.50$\pm$1.33 & -3.72$\pm$1.42\\
-% 		& single-band coadd with oversampling (H158) & -0.03$\pm$0.59 & -0.11$\pm$0.67 & 14.10$\pm$1.24 & 2.05$\pm$1.42\\
-% 		& single-band coadd with oversampling (F184) & 0.47$\pm$0.80 & -0.59$\pm$0.81 & 12.40$\pm$1.67 & 6.32$\pm$1.82\\
-
-% 		\multirow{multi-band} & multi-band single-epochs (fitgauss) (H158+J129+F184) & 1.78$\pm$0.62 & 0.07$\pm$0.63 & 8.80$\pm$1.22 & 1.57$\pm$1.27 \\
-% 		& multi-band single-epochs (gauss) (H158+J129+F184) & -0.66$\pm$0.58 & -0.74$\pm$0.59 & 4.32$\pm$1.17 & 1.60$\pm$1.16 \\
-% 		& multi-band coadd with oversampling (fitgauss; H158+J129) & -1.02$\pm$0.63 & 0.02$\pm$0.70 & 18.51$\pm$1.36 & 0.70$\pm$1.33\\
-% 		& multi-band coadd with oversampling (gauss; H158+J129) & -0.39$\pm$0.59 & -0.32$\pm$0.68 & 13.72$\pm$1.24 & 1.85$\pm$1.29\\
-% 		& (v2) multi-band coadd with oversampling (fitgauss; H158+J129) & -0.73$\pm$0.45 & -0.08$\pm$0.48 & 15.80$\pm$0.88 & 0.53$\pm$0.96\\
-% 		& (v2) multi-band coadd with oversampling (gauss; H158+J129) & -0.36$\pm$0.45 & -0.35$\pm$0.43 & 11.45$\pm$0.93 & 1.83$\pm$0.98\\
-
-% 		\hline
-% 	\end{tabular}
-% 	\caption{Shear calibration bias for different simulation runs.}
-% 	\label{tab:result}
-% \end{table*}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
 % Don't change these lines
@@
 \end{document}
-
-% End of mnras_template.tex
